\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cChupStudent{}}
 
You are \cChupStudent{\full} (\cChupStudent{\they}/\cChupStudent{\them}), and a 19 year old, first year student from the \pFarm{}. Most importantly, you are a zealous devotee of the \pGoaties{} — and this weekend is your big break. Just like the rest of your group, you conceal your true abilities. Your reputation is that of a slacker who skates by on \cChupStudent{\their} magical power — but you are cunning, dangerous\ldots and here to prove your worth to the \pGoaties{}.
 
You were born the second \cChupStudent{\offspring} of powerful nobles who control land along the \pTech{} border (luckily not coastal, so you don't have to deal with pirates — the \cWildCard{\formal}s get to deal with that). While this afforded you a privileged life, it didn't provide much in the way of future prospects — you were betrothed to the second child of a powerful \pTech{} family, \cHeir{\full}, at a young age for political gain. 

There were still people in your life who seemed to generally care for you, though. For example, your \cWildCardFriend{\parent}’s close friend from \cWildCardFriend{\their} days at \pSchool{}, \cWildCard{}, visited regularly and encouraged your mind and curiosity about the world. Growing up, \cWildCard{} was like a bonus \cWildCard{\auncle} to you. \cWildCard{\They} always seemed to be investigating something interesting and were more open with you than even your mother. Maybe it was because  \cWildCard{\they} said you reminded \cWildCard{\them} of \cWildCard{\their} sibling so much. You wished that you could be like \cWildCard{\them}, studying what you wanted, unburdened by what your parents decided was the right path.

The certainty that your life was not in your hands has always bothered you. Even being born with all of the magical power in the world into a politically powerful family, you were *still* doomed to be a pawn simply by virtue of being born second. The vast majority of people in this world were born with less than you in every way — and yet, your future *still* felt dim and lifeless. Yes, you worked hard. Your personal tutor, \cHistory{\full}, told you that you were one of the brightest students \cHistory{\they} had ever encountered. Learning at least gave you a feeling of purpose, as \cHistory{} and you spent hours delving into the history of the \pFarm{}, with you questioning and \cHistory{\them} providing answers that served their purpose of brainwashing you into believing that this was just how things had to happen. The feeling of helplessness combined with the guilt of having so much left you in a dark place mentally for many years.  
 
That was all up until that fateful day. One day when you were 14 years old, you were out on a leisurely survey of your family's lands with your servants when you heard distant screams and saw smoke rising from one of your peasant villages. You and your escorts hurried to the scene; when you arrived, you found the smoldering ruins of a barn, and a group of enraptured peasants surrounding a strange \cChupLeader{\person}. Apparently, the barn had caught fire, this stranger had raced in and rescued those trapped inside, and \cChupLeader{\theywere} now in the process of giving a sermon to the peasants. \cChupLeader{\They} spoke about true equality — an even platform for all who would stand on it. About the injustices of the feudal system, the tyranny of those with power, and about how only through re-imagining the world could it be made fair.
 
While you were as enraptured as your farmers, your escorts were not as thrilled. They wanted to arrest the man for sedition. But at a word from you, they let the \cChupLeader{\person} be. Second \cChupStudent{\offspring} you may be, but you still had (and have) considerable authority. You returned to your home with much to think about, after giving \cChupLeader{\them} a small amount of gold for saving your citizens.
 
That incident single-handedly changed you. No more were you willing to lament your fate — you now knew that there were people out there willing to fight to change it. You began sharpening your mind and your skills in preparation to be one of those people. It was good that at that point 
\cHistory{} had left your parent’s employ to go teach at the \pSchool{}. Your parents never really listened to what you had to say, but you know \cHistory{} would have, and would have tried to stop you.  

Two years later, after much clandestine searching, you managed to find them — and join them. They call themselves the \pGoaties{}, and they were everything you hoped. A year later your training was done, and you were a full fledged member, ready to do anything it took to bring the world closer to true equity. Between your true skills, your family's backing, the recommendation of \cHistory{} and the support of your new group, it was simple to qualify for your first mission — infiltrating the \pSchool{}.  
 
Your time at the \pSchool{} has been pretty successful. You have grown your knowledge and power, as well as met a few friends along the way, even though you have attempted to be careful to not let others know your true nature. That has been hard in terms of \cHistory{} especially, and you have noticed that \cHistory{\they} regularly seem\cHistory{\verbs} disappointed in you. You can coast through most of your classes, but \cHistory{\they} know\cHistory{\verbs} how smart you really are, and you worry that \cHistory{\they} may figure something out. You have actually had to start to try in \cHistory{\their} class so \cHistory{\they} leave\cHistory{\verbs} you alone. You also have become friends with two of the other \pGoaties{}, \cChupSecond{\full}, the economics teacher and \cChupInventor{\full} the political science and diplomacy teacher.They are the only teachers you can fully be yourself around, and your late night discussions about economic theory and the mistreatment of the lower classes politically and religiously by all countries. have only reinforced your belief in the righteousness of the cause. You hope that both  will let your leader know that you should be a cleric one day. Regardless, you find them both deeply impressive, and know with you all working together you will accomplish great things!

 It has been hard to make friends among the other nations besides the \pFarm{}, though you have tried, as honestly, you don’t care about nations.  Everyone is oppressed under the systems of society and magic. Other students don’t like  \cTechStar{}, who sit\cTechStar{\verbs} on the High Council of the \pTech{}. \cTechStar{} has a direct say in the policies of \cTechStar{\their} entire country, including those that hurt the \pFarm{}. And then there is \cWarlordDaughter{\full} from the \pShip{}. \cWarlordDaughter{} is the \pShippie{} Warlord, \cLoud{\full}'s, \cWarlordDaughter{\offspring}, and as such a lot of your fellow students blame \cWarlordDaughter{\them} for the war by association. You pretend along with the rest of the \pFarm{} students to distrust \cTechStar{} and  \cWarlordDaughter{}, but you wonder if all this distrust would let either of them  be more easily swayed to your cause as such distrust is so blatantly unfair. You will need to investigate this weekend.

This is not to say that you don’t have actual real friends at school. Chief among them is \cAmbition{\full}, your friend from the \pTech{} and a cunning mind to rival your own. \cAmbition{} once overheard you getting into a deeply theoretical discussion with \cChupSecond{} and did not hesitate to call your bluff. You tried to get out of it, but \cAmbition{\theywere} too smart.  \cAmbition{} is a bit like you, trying to find \cAmbition{\their} own way, though without the family pressure.  \cAmbition{} also introduced you to, \cPresident{full}, one of their fellow library assistants and the student council president from the \pShip{}. You have not been as open and honest with \cPresident{}, but \cPresident{\they} seem\cPresident{\verbs} to want to be your friend anyway.  

Through your connections, magical strength, and showing strategic flashes of your true abilities, you have managed to be recognized as a prized student and even a teacher favorite. 
Some of the other students are jealous, but that can't be helped. It probably does not hurt that your family has been supporting the \cPrince{\full} in \cPrince{\their} clear interest in the throne. If \cPrince{\they} want\cPrince{\verbs} to believe you also support \cPrince{\them}, so much the better. You do not want \cPrince{} to know what you are doing and \cPrince{\theyare} far too clever by half. You even have pretended to be a fan of \cPrince{} and introduced \cAmbition{} to \cPrince{\them} as a potential future protege. Of course, you never want that actually to come to pass.
 
Now that you're here and this crucial moment in time has come, you have a few important missions to accomplish. Your primary mission, given to you personally by the esteemed \cChupLeader{\full}, leader of the \pGoaties{} (and selfsame \cChupLeader{\person} who saved your farmers all those years ago), is to make sure that the Storm is sent to the \pSc{}. There are a few aspects to accomplishing this. First of all, the more student votes you can gain for sending the Storm to the school in the selection process, the better (see your Greensheets for details). This is made more challenging by your falsely dull persona, but you think you can get more Voting Stones from the teachers and advisors — the teachers all love you, after all, since you excel effortlessly in their classes. And you definitely have the magical power to back it up, plus the support of the other \pGoaties{} in attendance. In addition, you have other ways to manipulate the outcome of the voting (see your Abilities). In order to make the school a valid target for the Storm so that your hard earned votes don't just fizzle, other \pGoaties{} are working on installing a Relic attuned to the school in the Ritual to Control the Storm. All of this will be difficult and dangerous — but at the end of the day, if destroying the \pSchool{} makes the statement you're hoping for, you'll have done your job.
 
In order to ensure everyone else is too distracted to interfere with your group's efforts to send the Storm at the school, you have been tasked with a special mission by your friend \cChupSecond{}. \cChupLeader{} has let you know that if the Ley Lines are destroyed by the Storm striking the school, magic will be greatly weakened. You know this could hurt the world in general, as technology will stop working and crops will fail. But you also know that the world can’t continue existing as it is, and there is no greater force for inequality than magic. The \pGoaties{} have convinced you that things need a radical fresh start, and if this is what is needed, so be it. Much better to have everything equal than continue to live fat on magical exploitation.  

If others found out this is what would happen to magic if the Storm goes to the \pSchool{}, you know your ability to recruit will become much harder. Even one of your fellow \pGoaties{}, \cChupInventor{\full}, is being kept in the dark about this, as \cChupSecond{} has told you in no uncertain terms that \cChupInventor{\they} would not understand the sacrifice that must be made for the greater good. So \cChupSecond{} has asked you to find any books in the library that talk about the vulnerability of the Ley Lines or what might happen if the Storm were to strike the school and destroy them. Though \cChupSecond{\they} \cChupSecond{\have} been instrumental in helping you navigate the labyrinthine and often terrifying depths of the library, you have also been searching with the help of \cAmbition{} and \cPresident{}. You may have spent longer than needed with \cPresident{}. You have to admit, \cPresident{\theyare} incredibly cute. And charismatic, openhearted, smart. Okay, yes, you have a huge crush on \cPresident{\them}. Regardless, you found the book two months ago. Or at least, the pages. For such an important topic there is very little about it written down, at least that you could find. You have ripped out the important pages and, paranoid at having your room searched while you are off at class or something, have stashed them on your person.  

Unfortunatly, you were not alone when you ripped out those pages. Just as you had finished, you heard a noise and turned around to see someone with the \iScythe{}.  You are not fully sure, but you think it was a fellow student, \cScholarship{\full}. You ran as fast as you could out of that room, but you know \cScholarship{\they} saw you.  Of course, \cScholarship{} should not have been holding onto a relic! (How in \pEarth{} did \cScholarship{\they} even get it out of its display case? You want to keep \cScholarship{\them} quiet, and are hoping that mutually assured destruction is enough. You also want to find out why \cScholarship{\they} had that \iScythe{}.  Maybe you can use that information to the \pGoaties{} advantage? 
 
There is also the matter of recruitment. You'd dearly love to recruit your best friend \cAmbition{} into the \pGoaties{}. \cAmbition{} is constantly questioning, looking for a place to belong, and you think you have a good chance at convincing \cAmbition{\them} to join based on that alone — but if that isn't enough, you think you can sell \cAmbition{\them} on the angle that the \pGoaties{} are the underdog, since \cAmbition{} clawed \cAmbition{\their} way up from a middle class background. The time is ripe to make your move. You also think that \cPresident{}, who is from a rich background but has a deep sense of justice and care for basically everyone \cPresident{\they} meet may be a good recruit.  And that would also make you not have to, you know, lie to \cPresident{} about who you are if you ever started dating.

 Besides \cAmbition{}, you have a general charter to recruit anybody that you think would be a good fit for the group. \cAdopted{} and \cLibAssist{} might be good candidates too; they seem dissatisfied with their lot in life. Poor \cLibAssist{} especially seems to be receiving the same treatment as \cWarlordDaughter{} and \cTechStar{}, likely due to the fact that \cLibAssist{\their} family’s curse trebuchets failed and killed a lot of people on both sides. \cLibAssist{\They} may want a place to escape all of that. You also find yourself just liking \cLibAssist{\them} as a person. \cLibAssist{} clearly has schemes within schemes, and you can tell that \cLibAssist{\theyare} playing all sides of any situation.  In them, you see an equal in cunning and intelligence.  It bothers you that you need to pretend to be lazy around \cLibAssist{\them}.  If you two could work together, you could be unstoppable.  \cDisney{}, as a \cDisney{\cleric} of \cFarmGod{}, is surely beyond your reach.  
 
On a more personal and \emph{awkward} note, you have had an ongoing\ldots{} THING with another student named \cHeir{\full}. On your first day at the school, you found that \cHeir{}, your betrothed since you were children, was also attending. You had met several times when you were much younger, and had always cultivated a deep and mutual animosity for each other due to the unfairness of the situation. Unfortunately, that all came shattering down when you first laid eyes on \cHeir{\them} on orientation day. \cHeir{} had grown up HOT.  This made everything confusing.  You think you've managed to avoid giving away your new-found attraction until now — but that doesn't make it go away. Yet, for a few months, you were afraid to approach \cHeir{\them}, because you were pretty sure that \cHeir{\they} hated you.  

Being friends with \cAmbition{} and \cPresident{} does mean that you constantly are in \cHeir{}’s orbit.  \cHeir{} and you don’t talk.  In fact, you get the distinct impression that \cHeir{} still really really doesn’t like you, or at least the you that you are pretending to be. But the more you get to know \cHeir{\them}, the more you fall for \cHeir{\them}.  \cHeir{} is irreverent, passionate, caring. You even have heard them complaining to \cAmbition{} about the idea of being the heir apparent to the \cHeir{\formal} family. \cHeir{\Their} older \cHeirSibling{\sibling}, \cHeirSibling{}, was supposed to have that role, but \cHeirSibling{} was one of the students killed 6 years ago. So now the burden falls to \cHeir{}, who has no interest in the role, and wants to chart \cHeir{\their} own course. This rejection of an extremely privileged social position has only made you more attracted to \cHeir{\them}, and also left you seriously wondering if \cHeir{\they} might be ripe for recruitment to the \pGoaties{}.  Outside of all of this, even just being in \cHeir{}'s presence makes you feel more alive, especially when you caught \cHeir{\them} smiling at you. Maybe \cHeir{} doesn’t hate you anymore?  That’s not just wishful thinking on your part, right? What about \cPresident{}, who you also have a major crush on?  This is all very hard. 

You could never write to your family about these feelings.  The last thing you want to do is give them more ammunition in your life.  So you have been writing instead to your old friend \cWildCard{} about what to do with these very intense feelings.  You have not let \cWildCard{} know about your additional feelings for \cPresident{} of course.  \cWildCard{} has been advising you to just start talking more to \cHeir{}, to show interest and friendship, and once you know \cHeir{} enjoys your company, then approach the topic.  

You aren't sure how you'll choose between the two, and you really wish you didn't have to — especially in such a short timeframe. You know you have so many unjust privileges over commoners, but you do envy their freedom in matters of love. They get to marry whomever and however many people they wish, while you as a noble are expected to form a monogamous union with the scion of another powerful family. It makes you want all the more to overthrow the established order. If you could get both of them to join the \pGoaties{} then maybe you wouldn’t even have to make that choice and you will all be able to live together in the new, beautiful, fair world you are creating.
 
You were still sorting out your feelings when, this morning, you received some horrible news in the form of a letter delivered by an advisor named \cDiplomat{\full}. \cDiplomat{} is \cHeir{}’s \cDiplomat{\auncle}, a prominent diplomat, and often represents the family (i.e. does their dirty work). It seems your meddling parents have set your wedding to \cHeir{} to be THIS MONDAY. You weren't even remotely ready to make a choice yet — and you resent them for forcing you into this without your knowledge. You're conflicted about accepting under these circumstances — particularly with the \pGoaties{}’ plans for this weekend already in motion. If they had just stayed out of this, you might have proposed to \cHeir{} on your own!  Why must parents meddle?

You also found out that \cWildCard{} is going to be here this weekend, which is both wonderful and a little worrisome. \cWildCard{} knows you better from your childhood than almost anyone here (except, you know, your history teacher, \cHistory{}), and may be able to tell right away that something is up. But you really want to hang out with your honorary \cWildCard{\auncle}. You miss \cWildCard{\them}. \cWildCard{\They} used to visit several times a year to spend time with your \cWildCardFriend{\parent}. And \cWildCard{\they} wrote to you just recently to ask for your help (\emph{your} help!) with something from \cWildCard{\their} youth. Apparently \cWildCard{} was a twin, until that twin was killed as a teenager. \cWildCard{\They} have asked for your help trying to find out how that happened.Apparently \cWildCard{} has developed a ritual that can use \iMirror{} to look into the past?!? Unfortunately, you and \cWildCard{} will need to convince \cDiplomat{}, its current keeper,  to let you borrow it so you can use it to help \cWildCard{}. Maybe \cHeir{} can help with that part? You’d like to think that \cWildCard{} is more open minded than the Duke or your \cWildCardFriend{\parent}. Maybe \cWildCard{} could be a potential recruit for the \pGoaties{}?  

This weekend will be jam-packed.You have a few personal matters of love to resolve — and you have a lot of work to do for your found family, the \pGoaties{}. If you can manage to pull off this incredible feat, your Patron Deity will finally go mainstream — and you can finally step unburdened from the shadows.
 
\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Make sure that the Storm gets sent to the school by winning as many Voting Stones as you can, and convincing other students to vote to send the Storm there too — without letting them know the whole “magic diminishment” part.
   \item Keep the pages you ripped out from the book safe and make sure no one can tie that destruction back to you or learn what the pages say.
    \item Recruit \cAmbition{}, \cHeir{}, and any other good candidates you find to the \pGoaties{} — without getting caught by unsympathetic parties.
    \item Decide what you want to do with your romantic future — allow yourself to be wed to \cHeir{}, or pursue \cPresident{}. If only you could find a way to be with both\ldots{}
    \item Help \cWildCard{} learn what happened to \cWildCard{\their} twin.
\end{itemz}
   
\begin{itemz}[Notes]
    \item You have several ripped out pages from a library book about the Ley Line Nexus and its vulnerability to the Storm. You haven’t been able to bring yourself to destroy them yet.
\end{itemz}
 
\begin{contacts}
    \contact{\cAmbition{}} Your best friend — hopefully you can convince \cAmbition{\them} to join the \pGoaties{}.
    \contact{\cChupLeader{}} The leader of the \pGoaties{}, and your personal idol. You want to be like \cChupLeader{\them} when you grow up.
    \contact{\cChupSecond{}} The second in command of the \pGoaties{}, a friend who you can be your true self with. You are helping \cChupSecond{\them} hide the truth about the vulnerability of the Ley Lines Nexus to a direct strike from the Storm and what that would mean for magic.
    \contact{\cWildCard{}} An old family friend who always has encouraged your ambition and intelligence, who you deeply respect.
    \contact{\cHistory{}} Your former personal tutor, now a teacher of History at the \pSchool{} who has been worried about you and also pushing you to be who you used to be.
    \contact{\cDiplomat{}} An advisor for the \pTech{} and liaison between \cHeir{}'s family and your own.
    \contact{\cHeir{}} Your childhood Betrothed who you've always loathed\ldots{} but are now super crushing on.
    \contact{\cPresident{}} The student body president and your other crush\ldots{} You're pretty sure \cPresident{\they} like you back!
    \contact{\cLibAssist{}} \cLibAssist{}’s barely noble family was disgraced because of mistakes made by \cLibAssist{\their} older sibling during the war. \cLibAssist{\They} have been beaten down by the unjust system, so you think \cLibAssist{\they} might be a good recruit too.
\end{contacts}
\end{document}
 
 

