\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cPrince{}}

You are \cPrince{\intro}, and 38 years old. You've been teaching Curse Breaking at the \pSchool{} for the past 5 years but have much bigger plans. You are the youngest \cPrince{\offspring} of \cQueen{\intro}, ruler of the \pFarm{}. None of your siblings want the throne as badly as you, so you intend to take it — assuming, of course, you can remedy a\ldots{}small complication.

From a very young age, it was obvious you were your \cQueen{\parent}'s \cPrince{\offspring}. The royal court of \pFarm{} is a pit of vipers — something your \cQueen{\parent} encourages. The constant fighting is good for the nobility. It keeps them from thinking of uniting against \cQueen{\them}, and elevates the most devious and ruthless to the top of \cQueen{\their} counsel, which is crucial to protecting the \pFarm{} internationally. The other crucial benefit (which is sadly often overlooked) is that it occupies the sadistic tendencies of the nobility among each other, ensuring they aren’t being acted out on the commoners that they are tasked with protecting. 

You took to the whole thing like a duck to water, while your siblings floundered terribly. Still, you are the \emph{youngest} of quite a large family, and while your \cQueen{\parent} favors you, \cQueen{\they} cannot declare you the heir-apparent without good cause, as it is tradition to name the eldest as heir to the throne. They were named such before you were even born. While your \cQueen{\parent} worked on the details, you were sent off to teach at the \pSchool{} for a few years. This kept you safe from those clever enough to read the signs with a preference for one of your siblings.

At the school, you teach Curse Breaking. Curses aren't normally the purview of the nobility — noble magic (read: powerful magic, valuable magic, useful magic) is used to imbue the land with fertility so that the crops will grow. After all, without an infusion of magic every spring to both the land and the seeds, the \pFarm{} couldn't feed even one third of its population, let alone make exports to the \pTech{} and the \pShip{} (err, before the war anyway). But neither you nor your \cQueen{\parent} are fools. \emph{Protection} from curses is prudent for nobility, and royalty in particular. And it's not so hard to prepare them either. You've prepared your share of bespoke curses for powerful families when the issue at hand was too delicate for them to go to a commoner. In most cases, what you asked for in return was their support for your claim to the throne when your \cQueen{\parent} dies. Besides, you enjoy doing something that makes you stand out even more from your siblings in your \cQueen{\parent}’s eyes (and the rest of the nobility - whether they like it or not, the nobility \emph{needs} your skills). It makes you more valuable, and substantially harder for anyone to dispose of.

Most recently you created a bad luck curse that was a particularly clever bit of work — embedded nigh undetectably in a letter, it wouldn't trigger until opened by someone of the same flesh and blood as the one who commissioned the piece. It was somewhat to your surprise when that self-same curse showed up at the school — none other than \cInitiate{\intro} bore your curse. \cInitiate{\They} must be the grand\cInitiate{\offspring} so sorely sought by the Fairweather family who commissioned the curse. So far you've kept your mouth shut, as you don't want to upset the fairweather family or honestly, admit that you may be able to undo the curse. Removing it would have you lose support and admitting to having placed it would cause at least many students to not trust you. You do admit you feel a tiny bit bad - you often don't see the results of your curses this directly, and it hits strangely. You aren’t sure how you want to handle this yet. If your curse fails to fulfill its intended purpose, you'll lose the support of the Fairweathers.

Another crucial family is the \cAdopted{\formal} family. \cAdopted{\intros} family are staunch supporters of your \cQueen{\parent}, and they have some concerns that their adopted \cAdopted{\offspring} may be preparing to act out somehow. Doing what you can to put \cAdopted{\them} back on the straight and narrow could cement the \cAdopted{\formal}s' support for your bid for the throne. Although, depending on what exactly \cAdopted{} has in mind, it might remove the \cAdopted{\formal}s as major political players, or catapult \cAdopted{} to the head of the family. Neither alternative raises much concern for you, as long as it ultimately works to your benefit. And \cAdopted{} is \emph{good} at making curses, a skill you would like to help \cAdopted{\them} cultivate as long as it is to your advantage. If \cAdopted{} can view you as a mentor (which honestly you are trying to be) so much the better.

There is also \cMusic{\intro}, \cMusic{\auncle} to \cAdopted{}'s adoptive \cAdoptedParentOne{\parent} to consider. \cMusic{} is a fellow teacher and has spent long enough at the school that \cMusic{\their} loyalties to their home country and family may have atrophied significantly. You aren't sure where \cMusic{\they} stand on your bid for the throne. You need to carefully feel \cMusic{\them} out, and then either court \cMusic{\their} support, or neutralize \cMusic{\their} threat, as appropriate. This year \cMusic{} is running to become the immortal principal of the \pSc{}. \cMusic{\They} could be a powerful ally or a difficult enemy in the future. If you can solidify \cMusic{}’s support for you in secret, you can help \cMusic{\them} publicly with the bid for the Principalship. If  \cMusic{\they} win\cMusic{\verbs}, technically \cMusic{\theyare} not \emph{supposed} to take any side in any political issues, but no one will actually be able to stop \cMusic{\them} if \cMusic{\theydo}.

When the \cQueen{\Monarch}'s plan was ready for the next phase, your \cQueen{\parent} called you home, and gave you a task. One month ago, \cQueen{\they} entrusted you with one of the two royal signet rings. The other stays on your \cQueen{\parent}'s finger at all times. It was your task to bring it to Duke \cChupStudent{\formal}, father to \cChupStudent{\intro}, and use it to approve some piece of legislation he had drafted. A simple enough task, and one that you were more than capable of — unless, of course, the worst kind of bad luck were to strike. And strike it did. You were waylaid by \emph{pirates} on your way to your destination, and while you escaped with your life, almost all of your possessions were stolen — including the ornately carved wooden box in which the ring was kept. 

Pirates\ldots{} You thought you hated them before, but now they might have cost you the throne. \emph{Unacceptable}. The pirates who attacked you had an inside person embedded among your guard. When approached by the seemingly innocent caravan, they must have exchanged some code word or phrase. You remember them talking of bravery, and charting courses. You don't remember the exact words, but if you hear a phrase like, ``Those brave enough to chart the course claim the prize,'' you can be reasonably sure it has something to do with piracy.

For now you've managed to forestall your \cQueen{\parent} finding out, but that won't last much longer. \cQueen{\Theyhave} demanded the signed and stamped document as soon as possible — and you think you can only hold out until the end of the weekend at latest. You must recover the signet ring somehow, at all costs. You hope that the Black Market (of which you have heard only rumors) will have some leads. The information won't come cheaply, however, and you are prepared to trade in information and curses as necessary to get what you need.

Luckily, you are not without possible allies. \cAntiChup{\intro} has struck up a correspondence with you, and proven a welcome font of wisdom and outside perspective You have not yet secured a formal agreement of support for your bid for the throne, but this weekend proves a convenient opportunity to discuss the matter and see what \cAntiChup{} would ask for in return. To have an ally so well positioned in the \pTech{} would greatly bolster your position in the world. And what you know of \cAntiChup{} indicates that \cAntiChup{\their} morality dovetails well with yours. You think the two of you would make a potent political pair, as long as you focus on the ways that your actions will also help and protect the \pTech{}, not just the \pFarm{}.

Another sometime ally of yours is \cEvil{\intro}, head of the \pFarm{} diplomatic delegation and a ruthless political player. The two of you have worked together off and on for years, though you know full well that \cEvil{}'s ultimate loyalties are only to \cEvil{\themself}. The big thing to watch out for with \cEvil{} is \cEvil{\their} greed. You can’t promise \cEvil{\them} too much or you’ll have no political gifts left to distribute among your other allies and supporters.

Another person you may be able to make use of is \cAmbition{\intro}, an ambitious student from the \pTech{}who seems to be desperate for a place to belong. \cAmbition{} was introduced to you by \cAmbition{\their} friend \cChupStudent{\full}, second child of a powerful noble family whose favor you have been courting. While \cChupStudent{} is a lazy student who seems to coast on raw talent instead of hard work, you can see the advantages in humoring \cChupStudent{\their} friend in order to retain  the \cChupStudent{\formal} family favor. \cAmbition{} is also friends with \cHeir{\intro}, heir to the powerful Faledon family of the\pTech{}. \cAmbition{} is thus well positioned to whisper words in the right ears if you can keep \cAmbition{\them} under your influence. Perhaps \cAmbition{\they} could be persuaded to move to the \pFarm{}? You could probably arrange a marriage into a moderately important family for \cAmbition{\them}.

There are a lot of things you can accomplish this weekend that would help your bid for the throne as well. You can prevent \cHeadDiplomat{\intro} and \cHeadDiplomat{\their} underlings \cJuniorStatesman{\intro} and \cChupLeader{\intro} from gaining any traction on a ceasefire or a new treaty. While the war isn’t without sacrifice on the part of the \pFarm{}, neither is it without value. With every passing year, the \pTech{} becomes more dependent on the food produced by the \pFarm{}, and the strength of the \pShip{} erodes. The \pFarm{} endure, and will come out on top; of that you have no doubt. . If you somehow fail to prevent peace talks, you must not let the \pTech{} and the \pShip{} sign a treaty that excludes the \pFarm{}. At the absolute minimum, a new treaty would need to stipulate that the Storm not be sent to the \pFarm{} for at least this year since the country is completely unprepared for it. 

You could also bring back one or more sufficiently powerful magical artifacts. Relics are the obvious target, but those will be watched by many people and you are not a particularly accomplished thief. If the opportunity arose to smuggle out a fully charged Relic (i.e. one not used for the ritual), you'd probably take it. But with so many skilled magic users around this weekend, you are sure there are other things you could acquire. Any new magical innovation is fair game. If you've got the only working copy, so much the better. Come to think of it, \cCurse{\intro} is always working on \emph{something}\ldots{} If whatever \cCurse{\theyare} up to now isn't likely to explode in your face (never a guarantee with \cCurse{}), it might be ideal. While you have not worked much with \cCurse{}, you do know \cCurse{\them} to be very talented, for a commoner.You'll just have to make sure it's something that will be a permanent installation in the \pFarm{}, under your direction. Maybe if you can improve on it, make it better, you can finally show \cCurse{} that nobles are in fact better at everything. If \cCurse{} doesn't pan out, maybe you can find something promising among the \pTech{} students. They are always inventing things, and all you would have to do is entice them to leave the \pTech{} and move to the \pFarm{}.

Something you never expected to find at the school was romance. But when you arrived five years ago, there \cPirate{\intro} was. \cPirate{\Theyare} clever, funny, and reliable, and seeing as \cPirate{\they} hail\cPirate{\verbs} from the \pShip{}, \cPirate{\have} no complicated obligations among the \pFarm{} nobility. You started out as friends, but after the last ``Time of Deciding’’, the two of you began dating. You'd like very much to take \cPirate{} home with you at the end of all of this and get married. Surely being \cPirate{\spouse} to the heir apparent of an entire country will be an appealing offer. But you aren't entirely sure that \cPirate{} is ready to give up being a teacher at the school, so you'll have to talk about that. Since teachers are supposed to be neutral, it would be more than just awkward for the consort of the \cPrince{\heir} apparent of the \pFarm{} to be teaching here — it would be untenable. You hope \cPirate{\their} love for you outweighs \cPirate{\their} love of teaching.

This weekend, you also look forward to catching up with your friend \cHedonist{\intro}, a \cHedonist{\cleric} from the \pFarm{} with exquisite taste. \cHedonist{} is an intellectually stimulating person to talk to or play a game of chess with. (\cHedonist{\theyare} one of your few opponents you lose to with some regularity). Plied with appropriate amounts of alcohol, you can often also coax useful information from \cHedonist{\them}. You’ve noticed that \cHedonist{} never drinks to excess, but there is a sweet spot where \cHedonist{\they} let\cHedonist{\verbs} \cHedonist{\their} guard down. You honestly appreciate that \cHedonist{} knows \cHedonist{\their} limits. Not every noble does. And it is always useful to have allies in the Church.

Amidst all of your personal plans, as a teacher at the \pSc{}, you technically have duties you should see to. Helping \cBunker{\intro} with repairing the magical Bunkers is one. This task is at least useful to you — the royal family back home has a not dissimilar Bunker, and knowing the ins and outs would allow you to \emph{exploit} any design flaws, should it prove necessary in removing siblings between you and the throne.

It's been five years since you left your home in the royal court of \pFarm{}. Assuming you can reclaim the signet ring, you have a good shot at the throne. But you aren't one to leave things up to chance — you'd much rather stack the deck in your favor. By accomplishing everything you set out to, you can seize that advantage. And the icing on your coronation cake will of course be sharing it all with \cPirate{}.

\begin{itemz}[Major Goals]
    \item Find your signet ring. Make sure you leave game with it, as you cannot claim the \pFarm{} throne without it.
    \item Prevent the brokering of a treaty that ends the war. If that proves impossible, ensure that a stipulation that the Storm will not be sent to your nation at this Time of Deciding is included.
    \item Convince \cPirate{} to give up teaching and come home with you and marry you. \cPirate{\They} would have to forswear any and all other loyalties as well.
    \item Consolidate as much of a base of power as possible. Ways to do this include:
     \begin{itemize}
         \item Decide on the best ways to manipulate \cAdopted{}, \cAmbition{}, and \cChupStudent{}, to your advantage. Students are often easily swayed by promises of future power. Make sure \cAdopted{} is not up to anything inappropriate for a noble like shirking \cAdopted{\their} duties.
         \item Determine \cMusic{}’s current opinion of you, and see if you can secure further \cMusic{\formal} support.
         \item Secure agreements with \cAntiChup{} and \cEvil{} to support you.
         \item Convince \cInitiate{} to return to \cInitiate{\their} family in the \pFarm{}, at least for a visit.
         \item Continue to support your friend \cHedonist{}, as you never know when you’ll need an ally in the Church.
   \end{itemize} 
\end{itemz}

\begin{itemz}[Minor Goals]
   \item Learn as much as you can about how the Bunkers work from \cBunker{}, while helping with maintaining them.
    \item Acquire one or more magical artifacts or new inventions (ideally ones for which you have the only prototype). Finding out what \cCurse{} is working on, and if it is worth stealing, is a good start. Otherwise, you might try some of the \pTech{} students.
\end{itemz}

\begin{itemz}[Notes]
    \item You are the Curse Breaking teacher at the \pSchool{}.
    \item You only started teaching at the school five years ago, so you were not present for the mess six years ago in which the Storm was unexpectedly sent to the \pShip{} out of turn, and the 12 students who directed the Storm perished under mysterious circumstances shortly thereafter.
    \item You intend to leave the \pSchool{} after this year with \cPirate{} by your side, assuming you have accomplished what you need to claim the throne. If everything goes sideways, staying at the \pSc{} would protect you from political fallout, so you’d prefer not to get caught being too partisan and get fired.
    \item You think the pirate code phrase you heard was something like, ``Those brave enough chart the course claim the prize.'' Anyone using such language is to be viewed with deep suspicion of being a pirate.
\end{itemz}

\begin{contacts}
    \contact{\cPirate{}} Your romantic partner. Clever, witty, and politically neutral — ideal marriage material.
    \contact{\cAdopted{}} The adopted scion of a family whose support you hope to court. Also a skilled young Curse Maker. 
    \contact{\cMusic{}} A relative of \cAdopted{}'s adoptive family and a longtime teacher at the \pSchool{}. You wish to verify and possibly rekindle \cMusic{\their} loyalty to the \pFarm{}.
    \contact{\cAntiChup{}} A possible ally in your bid for the throne from the \pTech{}. You will need to figure out what you can offer \cAntiChup{\them} in exchange for official support.
    \contact{\cEvil{}} Head of the \pFarm{} advisors/diplomats at this ``Time of Deciding,’’ and a ruthless political player. A sometime correspondent and ally of yours, though you know full well that \cEvil{}'s ultimate loyalties are only to \cEvil{\themself}.
    \contact{\cHedonist{}} A friend of yours, a \cHedonist{\cleric} from the \pFarm{} with expensive tastes and a sharp mind. A good person to be around and play a game of chess with.
    \contact{\cInitiate{}} A \pShippie{} student and grandchild of the powerful Fairweather family. You cast a Bad Luck Curse on a letter that was delivered to \cInitiate{} at \cInitiate{\their} family's request in order to force \cInitiate{\them} to come home, in exchange for the family’s political support. You didn’t know \cInitiate{} was related to the Fairweather family, or that \cInitiate{\theywere} the intended target. But now what’s done is done, and the Fairweather family’s support is contingent on \cInitiate{} visiting their estate.
    \contact{\cCurse{}} One of the most skilled Curse Makers in all of \pEarth{} (though not as skilled as you!), who is always working on some side project.
    \contact{\cAmbition{}} An ambitious student with powerful friends, who seems to want to curry your favor. You can use this to your advantage. 
    \contact{\cChupStudent{}} A lazy student from a powerful noble family whose support you would like to retain. 
\end{contacts}
\end{document}
