\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cMusic{}}

You are \cMusic{\full} (\cMusic{\they}/\cMusic{\them}), and you are 50 years old. You are from the \pFarm{} and work as the Music teacher at the \pSchool{}. You are a devout follower of \cFarmGod{} and your spirituality is an important part of who you are. You are caring, approachable, and devoted to the wellbeing of all in your care. The balance of the world was broken 6 years ago, and you are in a position to help fix it now — so that's just what you intend to do.

Your early life was easy, since your family is old, landed nobility. You had the best education possible, including several focus programs. In one about the religions of \pEarth{}, you were assigned a pen-pal in \pTech{}. \cBeetle{\full} and you were a surprisingly good match, and you maintained your correspondence long after the program ended. You loved how thoughtful, open to new ideas, and genuine \cBeetle{\theywere} and you loved to hear about \cBeetle{\their} role caring for the Celestial Beetles at the temple. Talking with \cBeetle{\them} made you feel connected to the broader world.   

While you were afforded many privileges, not everything was always rosy with your family. You all have your share of black sheep and ruthless manipulators like any other noble family. One of the worst is your cousin \cEvilNemesis{\full}, who will stop at nothing to advance the family's position and destroy rivals. You are ashamed of such actions, but they permeate the culture of the royal court and there is little you can do to stop them. Instead, you try to make up for it by distancing yourself from \pFarm{} politics and doing as much good in the world as you can. 

With several elder siblings, you had always had the freedom to explore what called to you. You came to love music from a young age, and it was the first thing that drew you to the Church. You spent several years studying the spiritual and healing practice of music and preparing to enter the leadership of the Priesthood, encouraged by your family for the status boost it would have provided, only to realize that your true calling lay in teaching. Your family was initially disappointed — teaching being a noble profession, but nowhere near as prestigious as joining the Priesthood — but were ultimately appeased when you landed a position as the Music teacher at the \pSchool{} 18 years ago. To your personal delight, \cBeetle{} joined the faculty the same year, and your friendship has only deepened since. You truly are each other’s confidantes, though sometimes \cBeetle{}says you are a bit too nosy.  

You consider every student who passes through the school to be one of your children and care for them as deeply as if they were your own flesh and blood. Teaching music to students from all three nations has taken some getting used to, though. Not all music has healing magic, but all \pFarm{} healing magic is musical; therefore, all music is holy to those of your nation. You've come to understand that this isn't so in the other nations, so you try not to be too heavy handed about it, but it is still important to you to instill some reverence into your students. Sometimes you wonder about how tightly the priesthood restricts access to healing music in your homeland. Would it really be so bad for other \pFarmers{} who held the power in proper awe to be able to use it to take care of each other?

You made some close connections with fellow teachers over your years teaching at the \pSchool{}, chief among them \cFlowPriest{\full}, the mathematics teacher and Priest of \cFlow{}. The two of you shared many lively discussions about religion and how the Gods speak through the language of mathematics and music, two sides of the same coin. Compassionate, wise, and deeply curious about theology and magic, \cFlowPriest{} has become another close friend alongside \cBeetle{}. In fact, in those early years, over a decade ago, you had found yourself developing a bit of a crush, but you put it aside. You wanted to remain devoted to your students, and romance would be a distraction from your job. You still sometimes find yourself a bit jealous of what \cBeetle{} has with \cBeetle{\their} long-term partner \cJuniorStatesman{\full}, a diplomat of the \pShippies{}.  Though that relationship also reminds you how complicated the world is now.  

After 12 years at the \pSchool{}, you were feeling pretty comfortable in your life, but then everything seemed to go wrong at once. After the Ritual to Control the Storm six years ago was completed, the students were tired but jubilant. Someone proposed a toast — not an unusual occurrence — but somehow the idea was circulated that the students should toast in private. So they all adjourned from the Ritual Space to the Student Lounge, leaving the teachers and advisors on their own. After nearly an hour of waiting, \cDiplomat{\full}, \cPrincipal{\full}, and you decided to go check on the students. What you found was 11 dead bodies. A quick inspection indicated that it was probably the wine. But the twelfth student, your star pupil and personal favorite, \cKidScientist{\full}, was unaccounted for. The three of you stood in that room, the shock washing over you. Was \cKidScientist{} responsible? Or was it someone else's doing? The three of you spoke quietly, and ultimately agreed to keep the fact that \cKidScientist{} was not among the dead a secret. You simply could not believe that one of your children, let alone gentle \cKidScientist{}, could have been responsible for this. It was more likely that someone else had poisoned the students, \cKidScientist{} had managed to escape, and, not knowing who to trust, had fled for \cKidScientist{\their} life. Keeping it out of public knowledge that \cKidScientist{\they} escaped would avoid anyone continuing to hunt \cKidScientist{\them}. \cKidScientist{\They} would have a chance. And if \cKidScientist{\they} wanted to surface and return to the public eye, \cKidScientist{\they} could do so in \cKidScientist{\their} own time. 

The rest is history — in sending the Storm to the \pShip{}, the decades-old international treaty between the three nations was broken, the \pShip{} were betrayed, and a war started soon after. After you emerged from your grief over the lost students, you realized that it was time to take a more active role in the world around you. You and fellow veteran teachers \cEthics{\full} and \cFlowPriest{} worked together to offer comfort and guidance to the students in the wake of the Betrayal. 

Since the Ritual to Control the Storm went awry six years ago, you have taken a significant interest in ensuring that this crucial event goes smoothly and that the right students participate and vote wisely. To that end, you've volunteered to be on the committee preparing the ritual at the last Time of Deciding and this one. Under your watchful eye, matters have gone well, and you know \cPrincipal{\full} appreciates your efforts in ensuring the safety and success of the students. While nobody could reasonably solve all of this themselves, you know as a teacher that your best way to make a difference is to take on a greater role in guiding the students' morals and helping them to decide the solutions that would best preserve their futures. 

When \cPrincipal{} announced at the beginning of the year that \cPrincipal{\they} would be retiring, you knew that you were meant to take over the role and immediately applied. You are \emph{pretty sure} you want the principal position. There is a downside — as long as you serve in that role, you cannot leave the school grounds without terrible consequences to the school. Cheering you on in this endeavor is one of your favorite students, \cDisney{\full}, a bright and idealistic young \cDisney{\person} from the \pFarm{}. \cDisney{} is also the youngest Cleric of Luminary you have ever met, and the two of you have bonded over your shared faith and reverence for music. Alas, your old friend \cBeetle{} is one of your competitors for the principalship, along with a relatively new teacher, \cChupSecond{}. In order to help \cPrincipal{} decide who to select, \cPrincipal{\theyhave} asked each of you to oversee an important task that normally falls to the principal during the Time of Deciding. Your task is to oversee the arrangements for this year's Ceremony of Excellence. Part of that will mean selecting students, teachers, and advisors to participate in the various parts of the ceremony, and there are multiple people who are interested in each role. You know \cPrincipal{} is both counting on you and judging your performance in this task against \cBeetle{}'s performance overseeing the Ritual to Renew the Ley Lines and \cChupSecond{}’s performance overseeing the Ritual to Control the Storm. 

The horror of the Betrayal and death of the students six years ago also forced you to take stock of your personal life. Working so closely with \cFlowPriest{} over the past six years to train all of the new teachers has only deepened the affections you thought you had set aside. You have found yourself idly daydreaming often about what it would be like to be in a romantic relationship with \cFlowPriest{}. A part of you deeply wants to find out, but another part is concerned about forming such a strong attachment when your students, and hopefully the principalship, have first claim on your attention. 

Should you even consider entering into a romantic relationship when you may well end up the immortal principal of the school, guaranteed to long outlive any partner unless you retire in just a few years or decades (thus discarding much of the benefit to the \pSc{} of having an immortal principal)? You have been speaking to \cFlowPriest{} about what it means to be a the principal of the school a lot recently, secretly hoping that maybe if \cFlowPriest{\theyare} interested in you \cFlowPriest{\they} would show some distress. \cFlowPriest{\Theyhave} been more cautious about the prospects, counseling you to truly think about what it would mean for the balance of your life\ldots But then again, that could just be \cFlowPriest{\them} doing \cFlowPriest{\their} job as a friend and priest of \cFlow{}.

A newer friend of yours at the school is \cInterpol{\full}. A fellow teacher from the \pFarm{}, \cInterpol{} has been here for 4 years and you helped show \cInterpol{\them} the ropes when \cInterpol{\they} first arrived. \cInterpol{\They} teach\cInterpol{\verbes} magical combat, a subject you find somewhat antithetical to your own, but you don't let that come between you. \cInterpol{} shares your deep love of music, and you've had many a great conversation about musical theory. You plan on asking \cInterpol{\their} help organizing and preparing for the combat demonstration in the Ceremony of Excellence.

Someone who on the face of it should be an old friend by now, given how long you’ve worked together at the school, is \cEthics{}, but you don’t actually feel close to \cEthics{\them} at all. You try to see the good in everyone, but even though you and \cEthics{} seem like you should be best friends, you find yourself often at odds with how \cEthics{\they} approach\cEthics{\verbes} situations. Students may get advice and listening, but \cEthics{\theyare} always thinking about the logic of a situation, what is the most effective way to do the most good in the world. You think that \cEthics{} ignores the emotional (to say nothing of the cultural and religious) aspects of student care and can get students into situations that end up just leading to trouble or frustration. You have been tempted to tell \cEthics{\them} just what you think of \cEthics{\their} techniques, but it does feel a bit petty. So you mostly let the frustration simmer. You have clashed on occasion though, albeit quietly.

Speaking of simmering, you have also been paying special attention to \cAdopted{\full}, the adopted \cAdopted{\offspring} of your \cAdoptedParentOne{\nibling} (making \cAdopted{} your grand\cAdopted{\nibling}). You did not know \cAdopted{} well when \cAdopted{\they \were} young, since you were off teaching at the \pSc{} already. But \cAdopted{\they} seem\cAdopted{\verbs} to genuinely like you now. Since coming to the school, \cAdopted{\theyhave} been far closer with you than with any other family member. Which isn't necessarily saying much, since \cAdopted{} still chafes under the adoption arrangement and seems to resent the rest of the family. You think \cAdopted{} is being needlessly harsh, but you still sympathize with \cAdopted{\their} situation. You worry sometimes that \cAdopted{} might try something drastic, and you don't want anyone getting hurt, especially since \cAdopted{\they \have} seemed to grow even more sullen since \cAdopted{\they} started becoming good friends with \cLibAssist{\full}, a fellow \pFarm{} student who seems to always to be up to something. Maybe you can connect to them through \cAdopted{\their} skill and interest in music and through this gain more trust and help guide \cAdopted{\them} away from a bad path. If only you were \cAdopted{}’s legal guardian, which would let you help the most! Unfortunately, your \cAdoptedParentOne{\nibling} hasn't been willing to alter the terms of the adoption. If push came to shove, you could appeal to \cPrince{\full} to draft adoption papers — as long as they are sealed with the royal signet ring, they would be binding. You want to be there to support \cAdopted{} however you can. 

With less than three days remaining before the voting and the Ritual to Control the Storm, all of your hard work is coming together. Soon you'll see the fruits of your labor in the form of a promotion, increased hope for balance in the world, and a successful conclusion to the school year. Assuming, of course, that everything goes according to plan.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Ensure that the preparations for the Ritual to Control the Storm go off without a hitch.
    \item Encourage the students to show compassion in their voting on where to direct the Storm and undo the Betrayal of the \pShip{}.
    \item Win the promotion to Principal. Pursuant to that, put on a phenomenal Ceremony of Excellence (see greensheet for details). This will help with impressing \cPrincipal{}.
    \item Decide what to do about your romantic feelings for \cFlowPriest{}. You had almost given up on romance, and now you wonder if it isn’t too late and too complicated to start, especially if you become the immortal principal of the school.
    \item Decide which student to give your Voting Stone to. Your personal favorites are \cAdopted{} and \cDisney{}, and you believe both of them would use it wisely.
    \item Figure out why \cAdopted{} feels so resentful about being adopted, and make sure \cAdopted{\theydo}n't do anything drastic about it.
\end{itemz}

\begin{itemz}[Notes]
    \item Musical healing magic in \pFarm{} is strictly controlled by the Priesthood and licensed for use only to a select few outside of it. If only more of \cFarmGod{}'s people could rejoice in the gifts of their God in this way! You are one of the select few with such a license from the Church of \cFarmGod{}, since you teach music to students of all nations.
    \item You were here at the \pSchool{} six years ago. You are one of the three people who know the truth, that only 11 students were actually killed that day, and that the twelfth, \cKidScientist{\full}, remains at large. The other two people who know are \cDiplomat{\full} and \cPrincipal{\full}.
    \item \cKidScientist{\full} was your favorite student six years ago. \cKidScientist{\They} vanished when the other 11 students were murdered. You agreed to conceal the fact that \cKidScientist{}'s body was never found, and a small part of you still hopes that \cKidScientist{\theyare} still out there somewhere.
\end{itemz}

\begin{contacts}
    \contact{\cBeetle{}} Former pen-pal, dear friend, fellow teacher, and friendly rival for the principalship.
    \contact{\cChupSecond{}} Your other rival for the principalship. \cChupSecond{\Their} tenure at the school has been much shorter than yours, but what \cChupSecond{\they} lack in experience \cChupSecond{\they} make up for in competence and determination.
    \contact{\cAdopted{}} The adopted child of your \cAdoptedParentOne{\nibling}, whom you'd love to continue to get closer to. You know \cAdopted{\they} bear a lot of resentment at being cut off from \cAdopted{\their} birth family.
    \contact{\cDisney{}} One of your favorite students, and the youngest Cleric of Luminary you have ever met. You love \cDisney{\their} reverence for music, earnestness, and idealism.
    \contact{\cInterpol{}} A fellow teacher from \pFarm{}, \cInterpol{} has been here for four years and you helped show \cInterpol{\them} the ropes when \cInterpol{\they} first arrived. You consider \cInterpol{\them} a good friend.
    \contact{\cFlowPriest{}} A fellow teacher and Cleric of \cFlow{} you have grown very close with over the years. \cFlowPriest{\Theyare} compassionate, wise, and deeply curious, and you definitely feel the spark of romance.
    \contact{\cEthics{}} Another old colleague of yours, with whom you often have friction with over how to best teach and help the students.
    \contact{\cPrincipal{}} The current principal of the school, your friend, your boss, and the one keeping an eye on your performance to replace \cPrincipal{\them}.
    \contact{\cLibAssist{}} A student from Children of the Sun who is friends with \cAdopted{} and you feel may be a bad influence, encouraging \cAdopted{\their} resentment towards \cAdopted{\their} adoptive family.
\end{contacts}

\end{document}
