\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cCurse{}}

You are \cCurse{\intro}, greatest cursemaker in the \pFarm{} at a venerable 72 years old. Not everyone sees you that way — some insist on considering you a doddering old fool or a dangerous eccentric. And it is true — sometimes your stuff explodes when it wasn't supposed to. But far more often, you accomplish something previously thought impossible. You are the only commoner among the \pFarm{} delegation. As such, when you are obligated to engage in politics, you consider it your unofficial duty to speak for the commoners.

The problem with being a curse expert is that curses are generally dismissed as the purview of the common folk in the \pFarm{}, and most kids with any notable magical talent among the common folk are swept up by the nobility. You were never so lucky. So instead, you learned from the hedge magicians around you, and became quite adept at both curse making and breaking. Curses are making this war possible, yet still looked down on. Some things never change in the \pFarm{}.

In those early years, you still lived with your family on the western coast of the \pFarm{}. You were the eldest of six siblings, and your youngest sister Anemone (Nemy for short) was always your favorite — fiery, headstrong, and far too charming for her own good — she could get away with nearly anything. You were both sad and happy for her, but not surprised, when she ran off to marry a \pShippie{} and forsake a life of toiling in the fields. Fortunately, she continued to visit as often as she could, and you grew quite attached to her child \cChupLeader{}, who took after \cChupLeader{\their} mother. You were heartbroken when Nemy died of a sudden illness only a few years after giving birth to \cChupLeader{}, and you took it upon yourself to dote on her child even more whenever \cChupLeader{\they} came to visit. You watched \cChupLeader{\them} grow up, growing more like \cChupLeader{\their} mother every year, but with an undercurrent of deep anger at the injustices faced by the lower classes of the \pFarm{} and the \pShip{} alike. 

Shortly before the war began, \cChupLeader{\they} tried to recruit you to some sort of revolutionary group \cChupLeader{\they} had started. You gently but firmly rebuffed \cChupLeader{\them}, for it had been your experience that radical upheavals always seemed to harm the poor the most, and revolution could easily backfire. You believed that change must happen gradually from within the system, though you promised to keep \cChupLeader{\their} secret even if you disagreed with \cChupLeader{\their} methods. Now, as you grow more bitter with age, you wonder if \cChupLeader{} was right all those years ago. You kept in touch until the war began six years ago, tearing nations and families apart. You still love your \cChupLeader{\nibling} dearly, and greatly look forward to seeing \cChupLeader{\them} this weekend. You are undecided if you will ask where \cChupLeader{\their} politics now lie.

You quite enjoy the creation and casting of curses, and have made quite a few in your storied career. Some are quite mild — a fit of giggles whenever someone attempts to approach their crush, a touch of courage, or a dose of sexual vigor. Some are subtle — good luck under a waning gibbous moon, or red paint that makes customers want to spend more money. And some are sledgehammers — bad luck, locusts, and even memory loss that rivals that of the Gods. In your younger years, you made curses for whoever could pay, all over \pEarth{}, and never thought too hard about what they would be used for. It was just so nice not to be treated like dirt by the \pFarm{} nobility that you went, admittedly, a bit wild. You still do pro-bono work for commoners, whenever you can spare the time, though before the war, you started to tone down accepting jobs from just anyone  You gained principles, and your skills were in enough demand that you could even afford to have them.

But now there's a war on, and your country's war machine is fueled primarily with curses. Your services are in higher demand than ever. You even got to meet the \cQueen{\Monarch} a few years back. But even if you weren't already getting wiser as you got older, war has the kind of moral implications that would make anyone think twice. That point was driven home in the worst possible way when a \pShippie{} raiding party attacked your home village, killing one of your brothers and two of your niblings. Not even your curses were enough that day. That attack was led by none other than \cJuniorStatesman{\intro}, one of the leaders of the \pShippie{} delegation this weekend. What kind of a place has a warleader for a diplomat? How can you work on making peace when that is who the \pShip{} send? You are not the vengeful sort, but you certainly plan to give \cJuniorStatesman{\them} a piece of your mind, and if an opportunity presents itself to make \cJuniorStatesman{\their} life difficult, you won't pass it up. 

Every time you start to question the morality of the curses you are crafting for the trebuchets, you think of your family and the lives that can be saved by keeping the \pShippie{} ships at bay. But by that same token, you have nightmares about your beloved nibling \cChupLeader{} being killed or hurt by one of your curses; you could never live with yourself if that happened. Damn this war! The permanent end to the Storms promised by the \pTech{} had better come to fruition, or all this death will have been for nothing. Not like they asked you. If it was up to you, this treaty would never have been struck in the first place! But those in power never think about the repercussions of their actions, just the victories they can claim.  

But whether the research into the Storms pans out is still a big if. As with many folks on \pEarth{}, you have a variety of pen-pals. Among them is \cHedonist{\intro}, a \cHedonist{\cleric} of \cFarmGod{}. Your family, the \cCurse{\formal}s, actually live on \cHedonist{\formal} land. \cHedonist{} is among the more tolerable of the Nobility. You remember \cHedonist{} being a bit of a wild child, sometimes crashing the tavern the farmers gathered at and playing drinking games with you all. You were surprised when \cHedonist{\they} went to join the church suddenly, and even more surprised when you ran into \cHedonist{\them} again and began a correspondence.  \cHedonist{\They} seem\cHedonist{\verbs} changed, and the two of you have spent long hours discussing what little is known of the \pTech{} plan to end the Storms, debating whether or not it's actually possible, and what the cost might be if it is. The two of you have decided to work together this weekend to get to the truth once and for all. 

Your contact on the project, \cAssistantScientist{}, has told you that they might be very close to a solution, but has been cagey about the details. While you don’t doubt that \cAssistantScientist{} is doing the best \cAssistantScientist{\they} can, you wonder about \cAssistantScientist{\their} boss, \cHeadScientist{\intro}. \cHeadScientist{\They} dismissed your ideas in the past (more on that later), treating you as either a fool or blasphemous. \cHeadScientist{\they} also seem\cHeadScientist{\verbs} to be deeply in the pocket of the head diplomat for the Free People’s Federation, \cDiplomat{\full}, receiving \cHeadScientist{\their} position just after the events of six years ago. You don’t know if \cHeadScientist{\theyare{}} just unimaginative and traditionalist (which in your opinion would make \cHeadScientist{\them} bad at \cHeadScientist{\their} job) or if something else is up, but you worry \cHeadScientist{\they} may be telling \cAssistantScientist{} to lie about the findings. Once the scientists present their findings this weekend, you intend to ask a lot of people a lot of questions. If it turns out that the \pTech{} can't really end the Storms or that there is some huge catch to their plan, then well\ldots{}you've got some serious soul searching to do. 

Another pen-pal of yours is a teacher at the \pSc{} named \cChupSecond{\intro}. Even since before the war, \cChupSecond{} has occasionally abused the supposed neutrality of teachers at the \pSc{} to trade you some interesting artifact \cChupSecond{\they} \cChupSecond{\have} or another. The most recent was also one of the most interesting. About a month ago, \cChupSecond{} brought you an ornately carved wooden box with quite a powerful protection curse on it. You dismantled the curse and opened the box, only to have \cChupSecond{} snatch it away before you caught more than a glint of gold inside. What does \cChupSecond{} know about what was in that box? And what did \cChupSecond{\they} do with it afterwards?

Your favorite pen-pal, though, is \cFlowPriest{\intro}. \cFlowPriest{} is another Teacher at the \pSchool{} and quite a delight to discuss magical theory with. \cFlowPriest{} has a most creative and ambitious spark, something \cFlowPriest{\they} credit\cFlowPriest{\verbs} \cFlowPriest{\their} patron \cFlow{\God}, \cFlowFull{\full}, with. The two of you began collaborating several years ago on what you expect will be your greatest accomplishment, something that will blow everyone away (in a good way). You are working on a way to reach the Realm of the Gods, by creating a way to \emph{grow} a magical portal overnight. Once complete, people will be able to step through and talk to the Gods face to face. It's simply \emph{genius}! You started out doing the work because it was interesting and novel, but now you wonder...if you could talk to the Gods, could you maybe figure out a way to stop this whole war thing? Especially if the \pTech{} cannot stop the Storms.

A few years ago, you cautiously reached out to \cHeadScientist{\full}, the foremost scientist in the \pTech{}, for some advice on the technical aspects of your project; \cHeadScientist{\they} never responded, which makes you believe \cHeadScientist{\they} dismissed the idea as a foolish impossibility, but \cHeadScientist{\their} assistant, \cAssistantScientist{\full}, did, and \cAssistantScientist{\theyhave} been working with you on the project ever since. This morning, when the Advisors arrived, was your first real chance to sit down with \cFlowPriest{} and \cAssistantScientist{} and talk in person about the project. \cFlowPriest{\They} introduced you to \cAmbition{\full}, a student who has been assisting \cFlowPriest{\them} with the project. You know that any talk of traveling to the Divine Realm is considered blasphemy in the \pFarm{}, and to a lesser extent in the other nations, so you'd best keep this project just between the four of you for now.

Of course, beyond getting the opportunity to meet some of your friends and family and work on your secret project, you have other duties to consider as an Advisor. You are supposed to be at the negotiating table to discuss treaties and ceasefires and so forth — which is one of the most boring and odious uses of time you can imagine. Still, if you want to see an end to this terrible war, you suppose you'll have to hold your nose and put in an appearance. That is, if the head of your diplomatic delegation, \cEvil{\full}, will let you — \cEvil{\theyare} among the highest ranking nobility in the \pFarm{}, and as such \cEvil{\have} no desire to share power with anyone, least of all a commoner. 

Still, as long as you are here, you might as well see whether any of the students still have a taste for curses — or if they are all hoity-toity nobles who won't touch the damn things. You're not exactly looking for a prodigy, but if one happened to fall into your lap, you wouldn't object. As an Advisor, you have the carrot to offer of your Voting Stone, as well as an apprenticeship should any of them prove sufficiently promising. You figure your best bets are \cLibAssist{\full} and \cAdopted{\full}. \cLibAssist{}'s family is very low ranking nobility and probably won't look down on you too much. Besides, \cLibAssist{\their} family has recently had some pretty major screw ups in public around the war (a misfiring trebuchet run by \cLibAssist{\their} sibling killed many soldiers and that sibling ended up court-martialed). This honestly makes you feel for \cLibAssist{\them}, even as a noble, and you would rather help someone who needed it, not a rich student set for life. And \cAdopted{} has made no secret about being unhappy at having been adopted away from a commoner family. You have been particularly impressed with \cAdopted{}, who has taken a keen interest in curses already, and the two of you have been exchanging letters. You look forward to collaborating with \cAdopted{\them} more. Of course, you are just speaking about \pFarm{} students. While curse magic is a \pFarm{} speciality, you know that \pTech{} students may look a bit less down on you. You plan on talking to \cAssistantScientist{} to find out if any good candidates are among the \pTech{} students.

While you know that \cPrince{\intro} is the Curse Breaking teacher at the \pSc{}, \cPrince{} is, well, a \cPrince{\Heir}. You two have rarely worked together, and you know for certain \cPrince{} is nowhere near as good as you at what you both do, even though you are impressed \cPrince{\they} learned curse magic to begin with. Still, you hope this weekend to prove that while there may be two curse experts in attendance, a commoner can be more magically talented than even a Prince. You want to be on the lookout for the most interesting and challenging curses to remove (or build) this weekend. While you're happy to charge an arm and a leg to those who can afford it, you're also willing to show some flexibility for a good cause.

Speaking of good causes and inspiring students, one of the Advisors will be honored this weekend to give the speech at the Ceremony of Excellence where the students showcase what they have learned. When these students graduate, they will go on to be movers and shakers in their countries. The teachers shape their minds day in and day out, but as an Advisor, this is your one big chance. While you have no taste for politics and you know you can't turn the whole social order on its head with a single speech, you would still dearly love to be the first commoner from the \pFarm{} to give the speech, both to prove that it can be done and to tweak the nose of the nobility. \cMusic{\intro}, one of the teachers, is in charge of arranging the roster this year, and you intend to convince \cMusic{\them} to make you this year's speaker. Awkwardly, your primary competitor is your good friend \cHedonist{}, but what's a little healthy competition between friends?

If, by some miracle, you have time to spare from your other objectives this weekend, you are also hoping to help the famed \pShippie{} engineer, \cBunker{}, maintain the Bunkers. You would love to talk shop with one of the greatest magical minds from another nation and see how the Bunkers work.

This weekend has the potential to be the greatest of your illustrious career. Not only do you have a mystery to solve, but together with \cFlowPriest{} and others, you are going to open the first known portal to the Realm of the Gods! In the meantime, though, you've got a reputation to uphold as the greatest cursemaker in the entire \pFarm{} — no, in all of \pEarth{}. It'll be tough, but you're up for the challenge.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Assist with the myriad cursemaking and curse breaking requests you expect to receive this weekend. Uphold your reputation as the greatest cursemaker in \pEarth{}!
    \item Finish the \iBeansNB{} with \cFlowPriest{}, \cAssistantScientist{}, and \cAmbition{}, plant them in time for them to grow, and then visit the Realm of the Gods — just to say you've done it.
    \item Try to hammer out a new peace treaty with the other nations that stipulates the Storm will not get sent to the \pFarm{}. Your nation is ill prepared to receive it, and it is always the common people who suffer the most.
    \item Work with \cHedonist{} and \cAssistantScientist{} to verify the science the \pTech{} is touting to end the Storms once and for all.
    \item Reconnect with your \cChupLeader{\nibling} \cChupLeader{}, and try to keep \cChupLeader{\them} from getting in trouble for \cChupLeader{\their} revolutionary streak.
    \item You are not the vengeful sort, but you certainly plan to give \cJuniorStatesman{} a piece of your mind for leading the raid that killed some of your family, and if an opportunity presents itself to make \cJuniorStatesman{\their} life difficult, you won't pass it up.
    \item Land a role speaking at the Ceremony of Excellence.
    \item Help \cBunker{} manage the normal wear and tear on the bunkers. See if you can do anything to improve the protections already laid down.
\end{itemz}

\begin{itemz}[Notes]
    \item Many of your closest contacts are clerics. You find comfort in religious practices, and the culture and community built up around them.
    \item This is the first time you have ever been to the \pSchool{}.
\end{itemz}

\begin{contacts}
    \contact{\cFlowPriest{}} Your main collaborator on the \iBeansNB{} that will take you to the Realm of the Gods.
    \contact{\cAssistantScientist{}} Another collaborator on the \iBeansNB{}, and a research assistant on the \pTech{} project to end the Storms permanently.
    \contact{\cHeadScientist{}} The leader of the project to end the storms, who you believe to be short sighted or incompetent, and possibly lying about their research
    \contact{\cAmbition{}} A bright young student assisting you on the \iBeansNB{} project. 
    \contact{\cChupSecond{}} Your primary contact at the \pSc{} who trades you interesting artifacts. Not particularly friendly, but you've worked together long enough to build a rapport based on \cChupSecond{\them} always being efficient and honest during your dealings.
    \contact{\cHedonist{}} A \cHedonist{\cleric} of \cFarmGod{}. Your friend and collaborator for uncovering the truth behind the \pTech{}'s claim to be able to end the storms. Also your primary competition for the speaking role at the Ceremony of Excellence.
    \contact{\cEvil{}} The head of the \pFarm{} delegation to the negotiating table. Stuck up like all the rest of the nobility.
    \contact{\cPrince{}} The Curse Breaking teacher and a friendly rival of yours. As a noble, you know \cPrince{\theyare}n't as good at curse breaking as you. You expect to need to step in and help, assuming \cPrince{} will let you.
    \contact{\cBunker{}} A brilliant engineer who you hope to work with and talk magical theory with this weekend.
    \contact{\cMusic{}} The teacher in charge of the Ceremony of Excellence, and the person you have to convince that you deserve the speaking role.
    \contact{\cChupLeader{}} Your beloved \cChupLeader{\nibling}, with revolutionary tendencies. You last spoke shortly before the war began.
    \contact{\cJuniorStatesman{}} The commander of the \pShippie{} raiding party that killed one of your brothers and two of your niblings, now turned diplomat. 
\end{contacts}

\end{document}


