\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cWildCard{}}

You are \cWildCard{\full} (\cWildCard{\they}/\cWildCard{\them}), and 45 years old. You are ostensibly here to support \cEvil{\full}, represent the will of \cQueen{\full} in whatever negotiations the advisors attempt, and study the Relics of \pEarth{}. In reality you are more interested in protecting your surrogate daughter and gaining immortality — and everything you need to achieve it is here on this floating island.

You are a scholar from the \pFarm{} — one of the country’s best. You come from a wealthy, noble family — not as old as some, but not newly landed either. Your family’s lands are coastal and northerly, a hub of trade, and an area well known for its stone fruit. As a teenager, you were the calm to your twin Lorraine’s chaos. She always wanted to be out partying. You wanted to study, pursuing whatever esoteric question had captured your attention at that moment. Despite these differences, the two of you always loved and supported each other. You loved to hear the wild stories she brought back, and she loved to hear the latest theory you had devised.

More days than you’d like to admit, you wonder to yourself if things might have turned out differently if you had agreed to go out partying with Lorraine that night. One night she went out, and just didn’t come back. When your family found out two days later that she had been killed in a bar fight, you were destroyed. Fearing that this was a targeted attack on your family, your parents forbade you to leave the house — as the only other heir, they could not afford to lose you. For an entire \emph{year}, you were kept on the \cWildCard{\formal} estate, mostly out of sight. The story was put out that both you and Lorraine had entered a period of intensive study. When the authorities finally determined that your twin’s death was probably a random act of violence, your parents formally announced Lorraine’s passing, and you were allowed to roam again. But your other half was gone. You felt so off balance and unstable. You miss Lorraine so much.

You clung to the comfort of the Church. Namely, that the souls of \pFarmers{} are eventually reincarnated. But since your soul and Lorraine’s have been separated by her early death, there’s no guarantee that you would reincarnate together. You couldn’t stand the idea of losing her forever. So you vowed to wait. However long it took. But in order to wait indefinitely, you would have to do something impossible — become immortal. It has become your life’s mission.

You attended the \pSchool{} as a young adult, heart heavy from the lack of your twin at your side. At the \pSc{}, you did make a few friend, \cWildCardFriend{} \cHistory{\formal}. You also became acquainted with \cWildCardFriend{}’s \cHistory{\sibling}, \cHistory{\full} on school breaks. \cHistory{} did not attend the \pSchool{}, so you did not become close friends until somewhat later.

Today you are an expert in the history and theory of magic. You probably also know more than most Clerics about the theories of how Deific power works. This means that unlike some, you know that there are many things that are still unknown about how magic works, or even how it came to be. You push the boundaries of what is possible in ways that few can even conceptualize. It’s a good complement to your friend \cHedonist{\full} who is a leading expert in the most niche and obscure details of practical magic.  You two met just after your time at the \pSchool{} and bonded over your interests in chasing down leads in archives, uncovering magical mysteries, and becoming lost in esoterica.  You also are both scions of noble families from the \pFarm{}, so you also shared gossip of the court while reading old tomes or playing a friendly game of chess. Some days you idly wonder why a mind as brilliant as \cHedonist{} did not attend the \pSchool{}, but you’ve never found a good time to bring it up.


After your time at the \pSc{}, you turned to research full time. You traveled all over \pEarth{} and met some of the best minds on myriad topics you thought might help your quest. You would also regularly stop by the \cChupStudent{\formal} estate, to catch up with \cWildCardFriend{\full} nee \cHistory{\formal}, who was now married to the head of the family. Over the course of these visits, you became fond of your friend’s \cChupStudent{\offspring}, \cChupStudent{}. \cChupStudent{\They} reminded you so much of Lorraine when she was that age — all curiosity, eagerness, and not a care in \pEarth{} for consequences.

During this time, you connected more closely with \cHistory{}, as \cHistory{} was \cChupStudent{}’s primary tutor. You both took delight in helping \cChupStudent{} while talking late into the night about your scholarship and debating theories about the creation of the world, the nature of the Gods, and the best way to quickly read through archival material. You even shared a few of your theories about the Divine Realm, wondering about its true nature. You two have kept in touch,discussing the latest discoveries and theories in long letters while visiting each other when you can. 

An invaluable contact who soon became another friend is \cLibrarian{\full}. The two of you have puzzled through questions that stumped scholars for decades. Between your keen intellect and \cLibrarian{\their} unparalleled research skills (and of course access to the most unique repository of knowledge in \pEarth{}) there is nothing the two of you haven’t managed yet. You don’t know a ton about \cLibrarian{\them} personally, but that is mostly because you have so much to talk about regarding each other’s research projects that there is never time to get into more personal matters.

There are a few, scattered stories of an ancient time when there was free and open passage between the realm of mortals and that of the Gods. And supposedly, tucked away in a little grotto somewhere, guarded by a chimeric beast, is a spring. From that spring bubbles the ambrosia of immortality. The stories say that the Gods bathed in this liquid, granting them their status out of time. If a human were to partake of that ambrosia either by bathing or imbibing, time would stop for them as well, and they would become as timeless as the Gods. . But no mortal was ever able to best the guardian, and in the time since, the Gods have severed all physical connections between the Divine Realm and \pEarth{}.

All other scholars believe, therefore, that the possibility of immortality is lost to humanity. You, however, know better. To achieve this, you must simply find a way to access the Divine Realm, and a way to best the guardian of the spring. The latter is\ldots if not easy, then at least obvious. 
The \iScythe{} is one of the \pFarm{} Relics that can be used for the Ritual to control the Storm. Normally it is stored in the Library of the \pSc{}, and is only accessible at the ``Time of Deciding.’’ Here on the island, so close to the building storm, the Relics absorb magical energy and become highly charged, allowing them to do things that would be impossible at other times. The \iScythe{} in such a state could be used to kill someone without risking retribution from the Gods. It could also be used to intimidate almost any \textbf{thing} — including the guardian of the fountain. If the \iScythe{} is used in the ritual, though, its power will be drained. Therefore, you must either ensure that the \iPitcher{} is used in the ritual instead so that you may take the charged \iScythe{} for yourself, or you must complete your quest before the Ritual is executed.

Finding a way to reach the Divine Realm has been a lifetime of work for you, and it is still not quite within your grasp. The mainstream Church of \cFarmGod{} has always maintained that the Gods must have cut the Divine Realm off for a reason — that if the Gods didn’t want humans in the Divine Realm, who were humans to dispute that? But not everyone has always thought like the mainstream Church. A cult splintered from the Church some 200+ years ago. They called themselves the \cDisneySect{}, and coalesced around the idea that the divide between the realms was a challenge humanity was meant to overcome.

They designed an ambitious ritual to transport themselves to and from the Realm of the Gods. Before the ritual could be realized, however, the mainstream Church caught wind of the plan, and brought to bear their full might. The \cDisneySect{} were wiped out, and their forbidden knowledge lost to time\ldots Or at least that’s what the Church \emph{wants} everyone to think. But some deep-rooted hope in you drove you to investigate anyway. Surely someone, somewhere, had preserved the knowledge you needed. Your long and laborious search finally led you to a collapsed, underground temple of some kind, in the very roots of the \pSpine{}. 

You carefully picked your way through the space, occasionally forced to literally dig in order to clear your way. You were hoping to find a book or scroll that had been magically preserved, and overlooked by the purge somehow. What you found instead was \cDisney{\full} in a glass box under an enchanted sleep. That was almost a year ago. Without hesitation, you set to work breaking the curse \cDisney{\they} \cDisney{\were} under. It wasn’t easy. The curse was old, using conventions uncommon today, and curses have never been your specialty — you are noble after all; your magic is mostly around making plants grow and thrive. But any time you would doubt your ability, you’d look at \cDisney{} and remind yourself that \cDisney{\they} didn’t deserve the fate of sleeping for eternity. You couldn’t even ask for help — you didn’t want to risk someone hurting this young \cDisney{\person}, just because they miraculously survived a massacre.

It took you almost three months, but you broke the curse and awakened \cDisney{} approximately 9 months before today. The poor thing was unsurprisingly lost and scared. Your heart ached with the desire to protect \cDisney{\them}, and give \cDisney{\them} a second chance at life. You have been serving as a mentor and supporter ever since. It was your influence that got \cDisney{} a place at the \pSchool{} this year — you hoped that \cDisney{} could make the same kind of lifelong friends there that you did.

When you questioned \cDisney{} about \cDisney{\their} knowledge of the ritual for how to reach the Divine Realm, \cDisney{\they} admitted to you that \cDisney{\they} did not remember. \cDisney{} was certain that at some point \cDisney{\they} knew, but now, that part of their mind is blank. Neither of you know whether this is due to the enchanted sleep, some error on your part in breaking said sleep, a protective trauma response, or simply the passage of time. You tried not to let your disappointment show — after all, it is not \cDisney{}’s fault \cDisney{\they} \cDisney{\do}’nt remember. Still, you can’t help but feel grateful that \cDisney{} and \cDisney{\their} friend \cTechStar{} have taken it upon themselves to try to restore \cDisney{}’s memories. You’ll be glad to help if they will let you.

If \cDisney{}’s memory cannot be repaired, you’ll have to find another way to access the Divine Realm. But here at the \pSc{} are some of the best minds in all of \pEarth{} — and you have reason to suspect that the answer is closer to home than you could ever have imagined. You are no spymaster, but you keep a wary eye out for commoners who upset carts. In this case, \cCurse{\full}, one of the other \pFarm{} advisors, has caught your attention. You suspect \cCurse{\they \are}working on a secret project that could allow access to the Realm of the Gods. \cCurse{} is about as magically powerful as a commoner can get, and while you are loath to rely on \cCurse{\them} more than you must, if \cCurse{\they} \cCurse{\have} the key to reaching the Realm of the Gods, then you are more than willing to hold your nose and work with \cCurse{\them} to see your plans come to fruition.

Honestly, your interest in the Gods goes back to long before Lorraine was killed. The balance of Deific power has always fascinated you. People tend to talk about the four Patron Deities like they are the only Deities — but they are not. There are \textbf{many} minor Deities, of all kinds of things. One throws salt over one’s shoulder to invoke a minor God of protection and so forth. And the hierarchy of the Gods is not as cemented as the Patron Gods would like mortals to believe. The Gods are \textbf{always} jockeying for position. And people like you know the signs to read. Some minor God is preparing something big. They've been preparing for a long time, amassing followers, and thus power. And you want in on it — as long as it can benefit you. You haven’t survived in \cQueen{}’s court for this long without understanding the need to judge risks and benefits. You’ve been seeking out this new Deity's elusive followers for several years now, but to no avail. Something is coming to a head this weekend, and you want to know what — and how to turn it to your advantage.

You've had a distressingly hard time finding any leads about the followers of the mysterious Fifth God, other than that this group bears the symbol of a \textbf{four-leaf clover} and is based out of the \pShippies{}. After considering your options, you decided to let other people do the work for you. You identified \cBunker{\full} as an individual who seems to know entirely too much about too many things to be \emph{just} an engineer. You suspect that \cBunker{\they} \cBunker{\are} a spy for the \pShippie{} Spymaster. In which case, if anyone were to have information about these followers of a Fifth God, it would be \cBunker{}. \cDisney{} has a convenient knack for getting into places \cDisney{\they} \cDisney{\do}n’t belong, so you asked \cDisney{\them} to help you get into \cBunker{}’s suitcase. As far as you know, \cDisney{\they} succeeded, so all you need to do is retrieve whatever \cDisney{\they} found.

But pet projects aside, technically you \textbf{are} here as an advisor. Your job is to support \cEvil{} at the bargaining table while the other advisors try to arrange a ceasefire or something. Frankly, you’d rather the peace talks failed and the war continue. War is good for business. Your family’s lands are lucratively positioned between the fertile farmlands of the \cChupStudent{\formal} family, and the border with the \pTech{}, albeit on the coast so pirates can be a problem. Importing weapons and exporting food fills your coffers. And for you personally, the war distracts the Deities, meaning no one is looking too closely at what you are doing. Because to be honest, you aren’t sure that they would approve of your quest for immortality. The morality of indirectly hurting or killing the idiots that started the war (the \pShip{}) doesn’t particularly concern you.

Still, an advisor must always be apprised of the current political situation, and in the viper's nest of Court in the \pFarm{}, a single wrong phrase could end a career. Knowledge is power, whether it be blackmail, favors owed, or even just the right tidbit of gossip — and you intend to accumulate as much of it as you can this weekend. One thing you recently learned is that \cQueen{\Monarch} \cQueen{} favors \cQueen{\their} \textbf{youngest} \cPrince{\offspring}, \cPrince{}, as \cQueen{\their} heir. Now, your family has never fallen over themselves to fawn at the \cQueen{\Monarch}’s feet, and one of the \cQueen{\Monarch}’s other children might have a softer touch (leaving more power for your family to amass), but \cPrince{} might also prove to be a valuable ally. Either way, something was supposed to happen a month ago. \cQueen{\Monarch} \cQueen{} sent \cPrince{} to visit Duke \cChupStudent{\formal}. You held your breath to see where the chips would fall. None fell. Something went wrong. With the idle curiosity of one whose life could soon depend on it, you’d dearly love to know what, and if you could turn it to your benefit.

Speaking of the \cChupStudent{\formal} family, their secondborn child, \cChupStudent{}, whom you fondly watched grow up on your myriad visits, is here at the \pSchool{}. You haven’t been in touch with \cChupStudent{\them} much in the past few years, but you know that your friend is worried about their \cChupStudent{\offspring}. You’ll have to see for yourself if anything seems off. In a bid for connection that might encourage \cChupStudent{} to trust and open up to you, and as an excuse to spend time with \cChupStudent{\them} this weekend, you wrote to \cChupStudent{\them} about your twin, and enlisted \cChupStudent{\their} aid in investigating what exactly happened the night your twin died. 

Some months ago, \cHeir{\full} wrote to you, on the advice of your friend \cLibrarian{}. \cHeir{} wanted to know if there was any way to magically look into the past. It was not a problem you had considered before. Your mind had always been on the future. But it was nevertheless an intriguing question. With some thought, the two of you guessed that \iMirror{}, one of the \pTech{} Relics might be manipulated to look into the past. With access to information from the Library, both from \cPresident{}, one of \cHeir{}’s friends, and from \cLibrarian{} for your own part, the two of you pieced together a ritual that you think might work for whatever \cHeir{} is looking for. When you were casting around for something to invite \cChupStudent{} to do with you this weekend, it occurred to you that just such a ritual might allow you to look back in time and learn what really happened to Lorraine! Hopefully \cHeir{} will have no trouble borrowing \iMirror{} from \cHeir{\their} \cDiplomat{\auncle}, \cDiplomat{\full}.

You didn’t actually expect to uncover anything — after all, this happened more than 20 years ago, and in the \pFarm{}, not at the \pSchool{}. But it was a compelling excuse. Until \cChupStudent{} met you when you arrived on the island with a plan. \cChupStudent{\They} had heard some fellow students discussing a ritual to manipulate \iMirror{} into revealing the past instead of the present at a different geographic location. You might actually be able to get some answers about what actually happened!

Thoughts of \cWildCardFriend{} inevitably lead you to thoughts of \cHedonist{}, who will actually be at the \pSchool{} this weekend. You haven’t had the opportunity to catch up with \cHedonist{} in person in years. You are quite looking forward to discussing philosophy and exchanging news (aka court gossip) like the good old days.


This weekend the goal of Immortality, something you’ve worked toward for many years, is within your grasp. Shake hands with him, charm her, and it’ll be yours. You just gotta make sure whatever the new God has planned isn’t going to screw with \emph{your} plans, and make sure that you and \cDisney{} survive whatever political machinations are afoot. Still, you intend to keep an open mind. Either one of these uncertainties could be an advantage for you to capitalize on.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Partake of the ambrosia of the Gods to become immortal. To do this, you will need to find a way into the Divine Realm, either by helping \cDisney{} recover \cDisney{\their} lost memories, or by capitalizing on whatever \cCurse{} is doing (assuming \cCurse{\they} \cCurse{\are} competent enough to finish it), and bring the attuned \iScythe{} with you to keep the guardian at bay while you approach the spring.
    \item Decide where you stand with \cPrince{} and support or hinder \cPrince{\them} as you deem appropriate.
    \item Figure out what this new Fifth God is planning. Their followers on \pEarth{} are probably your best lead. You just have to find them.
    \item Protect and support \cDisney{}.
    \item Work with \cChupStudent{} to seek out the truth of what happened to your twin, Lorraine, the night she was killed.
    \item Figure out what is up with \cChupStudent{}. Your old friend \cWildCardFriend{} is worried about \cWildCardFriend{\their} \cChupStudent{\offspring}.
    \item Look after the interests of the \pFarm{} and your own family. Prevent a peace treaty or ceasefire from being reached, and make sure the Storm does not get sent to your homeland.
     \item Catch up with \cHistory{}, \cHedonist{}, and \cLibrarian{} as much as you can.
\end{itemz}

\begin{itemz}[Notes]
    \item This is your first time as an Advisor at the \pSchool{}. You had to work hard to get here, though rescuing \cDisney{} certainly helped smooth your way.
\end{itemz}

\begin{contacts}
    \contact{\cDisney{}} A young adult you awoke from a magical slumber. You care deeply for \cDisney{\them}, and hope that \cDisney{\they} will be able to help you reach the Divine Realm.
    \contact{\cHistory{}} An old friend with whom you share a long and pleasant history. You look forward to catching up this weekend.
    \contact{\cHedonist{}} A very good friend since your time at the \pSchool{}. You regularly correspond via letter, and savor the rare opportunity to meet in person. 
    \contact{\cLibrarian{}} One of the most brilliant research minds you have ever had the pleasure of collaborating with. You do not believe a question exists that could stump your collective skill.
    \contact{\cEvil{}} The head of the \pFarm{} delegation; you are supposed to be \cEvil{\their} second at the negotiating table, but you expect to be quite busy with your other plans.
    \contact{\cCurse{}} A \emph{commoner}, but one who may have a way to reach the Realm of the Gods if \cDisney{} can’t help you
    \contact{\cPrince{}} The youngest \cPrince{\offspring} of \cQueen{\Monarch} \cQueen{}. \cPrince{} has designs on the throne and you haven’t made your mind up yet whether you support \cPrince{\their} bid.
    \contact{\cChupStudent{}} The \cChupStudent{\child} of your friend \cWildCardFriend{}. You fondly watched \cChupStudent{\them} grow up on your myriad visits, but now your friend is worried about \cChupStudent{} and has asked you to see if you can get \cChupStudent{\them} to open up to you about what is going on.
    \contact{\cBunker{}} The \pShippie{} engineer charged with maintaining the school’s magical Bunkers, whom you suspect of being a spy. You had \cDisney{} steal notes from \cBunker{\them} to see what could be learned.
\end{contacts}

\end{document}




