\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cLibAssist{}}

You are \cLibAssist{\intro}. At 21 years old, you are a second year student at the \pSchool{}. You have always been a loner, preferring the company of your thoughts and your books to other people; the worlds of your mind and those between the pages always seemed so much more expansive and exciting than the narrow world you were forced to occupy growing up. The only exception was your older sibling, Sage, who you were in awe of as only a younger sibling can be. You loved listening to their stories and adventures and telling them about which book you were currently relishing. The two of you grew up in the \pFarm{} as the children of a barely noble family. Your family was unlanded, and therefore pushed to the very margins of polite society — barely better than commoners. You and your sibling were taught from a young age to calculate every move to maximize benefit for the family. For generations, your family made up for their unlanded status by serving in the military with honor and distinction; granted, military posts in a nation where any form of violence was anathema were largely ceremonial, but it still brought the \cLibAssist{\formal} name some degree of respect and dignity. 

When the war began, demand for experienced officers surged, and your elder sibling was called up to help stave off \pShippie{} raids. Your family enjoyed a meteoric rise in the royal court as tales of their exploits spread. Sadly, it was to be short lived. One of the prototype trebuchets catastrophically misfired under Sage’s command, cursing or killing many soldiers from the \pTech{}. For purely political reasons, the ensuing court-martial held Sage responsible for the entire incident and they were dishonorably discharged, disgracing the \cLibAssist{\formal} name. Since then, your family has pinned their entire hopes on you. The pressure would have broken anyone of lesser character, but you have known hardship and sacrifice your entire life. Your family has given you everything they could, and you intend to pay them back by clawing your way to the top — by any means necessary. So you put your nose to the grindstone and set your sights on the \pSchool{}. Surely at the most elite institution in all of \pEarth{}, you would finally be able to gain enough power and influence to lift your family’s fortunes and clear your sibling Sage’s name.

Making friends in the \pFarm{} was rarely advantageous, so you mostly went it alone. Even when all of your hard work paid off (okay, okay, and a lucky break) and you were selected for a spot at the \pSchool{}, you spent most of your first year in office hours and in the library, studying. You had to be the best student you could be, and with the best of the best of the entire continent here to compete with, that was no easy task. You were in the process of struggling to keep your grades up when the Librarian, \cLibrarian{\full}, took you under \cLibrarian{\their} wing. At first, you told yourself it was just advantageous to you to buddy up to \cLibrarian{\them} — but time soon led to a real friendship forming instead (or so you thought). You and the Librarian spent many enjoyable hours researching the Relics stored in the library, The \iLariat{}, The \iNet{}, and The \iScythe{}. Within your first year at the school, you had risen to the position of First Library Assistant, something you took great pride in.

You didn't mind when \cLibrarian{} appointed \cPresident{\full}, the student body president, to be the Second Library Assistant under you. You had already been cozying up to \cPresident{} for political gain for some time, given \cPresident{\their} popularity, student government position, and relation to the prominent Wave Rider diplomat \cHeadDiplomat{\full}. At least, it started out that way. \cPresident{} is just so earnest and authentically kind and caring that it is hard not to find yourself genuinely liking \cPresident{\them} in spite of yourself. Now \cPresident{\they} hang\cPresident{\verbs} out with you, defer\cPresident{\verbs} to your authority in the library, and sometimes confide\cPresident{\verbs} in you. While you're a little jealous of how easily success seems to come for \cPresident{}, you have also seen how \cPresident{\they} struggle\cPresident{\verbs} with anxiety; it is easier to like someone when you know they aren't perfect. The two of you often study together in the Library.

You had a rude awakening when \cAmbition{\full}, a ruthlessly ambitious student in the same year as you and from the \pTech{}, was appointed to be a Library Assistant as well. \cAmbition{\They} started out under you, but you watched in cold fury as \cAmbition{\they} sucked up to \cLibrarian{}, weaseled \cAmbition{\their} way into \cLibrarian{}’s confidence, and ultimately supplanted you as First Library Assistant, despite your every effort to undermine \cAmbition{\them}. It is so unfair! You know for a fact \cAmbition{} stole a book from the restricted section of the library before the last school break, and you thought for sure that ratting \cAmbition{\them} out to the Librarian would get \cAmbition{\them} demoted if not dismissed, but \cLibrarian{} hasn't done a thing about it! That's when you knew for sure something was wrong. 

\cLibrarian{} has indeed been acting really strangely the last few days. Where \cLibrarian{\they} used to be open and welcoming, \cLibrarian{\theyare} suddenly distant and cagey. You've seen \cLibrarian{\them} wandering the stacks almost like \cLibrarian{\theywere} lost. Determined to get to the bottom of it, you began discreetly rifling through \cLibrarian{}’s papers, and stumbled upon something shocking: A letter from \cLibrarian{\their} parents explaining how, just several days ago during the school break, \cLibrarian{\they} had killed a pirate that was attacking \cLibrarian{\their} family. While the fact that it was self defense does mitigate things somewhat, murder is still murder, and anathema to both the Gods and their people. \cLibrarian{}’s strange behavior must be because they have been punished by the Gods with amnesia! You are unsure what to do with this information. You resent \cLibrarian{} for choosing \cAmbition{} for the head assistant position over you, but \cLibrarian{\theyhave} also been a mentor to you, and you know that letting word get out about this would mean \cLibrarian{\they} would be ostracized and almost certainly fired by the Principal. For the time being you have told no one and hung onto the letter while you decide on the most advantageous course of action. Getting \cLibrarian{} fired \emph{would} be sweet revenge and clear the path for your own advancement, but it could just as well backfire and see \cAmbition{} appointed to the Librarian position instead of you. Maybe you could use the letter as blackmail to force \cLibrarian{} to promote you and take the unorthodox step of officially naming you \cLibrarian{\their} successor?

As \pEarth{}'s foremost repository of magical items and tomes, the library is a surprisingly dangerous place. In fact, the Librarian before \cLibrarian{} was killed on the job by a deteriorated piece of spellwork that backlashed unexpectedly when \cLibrarian{\they} tried to move it. Not that you have let that stop you — you sneak down into the lower, older, more dangerous levels at least once a week, even though you are not supposed to. You think you might be the only one who noticed that the \iScythe{} went missing from the library about 2 months ago. Before you could work out how to tell \cLibrarian{} (since you shouldn't have been in that area of the library alone), it mysteriously reappeared (this was about a week later). You wonder what happened.

Still, not everything has been fraught in your second year at the \pSchool{}. You were not prepared for the fierce little ball of energy that was \cAdopted{\intro}. \cAdopted{} is in \cAdopted{\their} first year at the \pSc{} and \cAdopted{\theyare} pleasantly similar to you in temperament. \cAdopted{} is also ambitious, although with somewhat different aspirations. The two of you became the best of friends and have hatched more than one ruthless plan together to get your way. \cAdopted{} has been working on a particular scheme recently that you are excited to help with. \cAdopted{} is adopted, the \cAdopted{\offspring} of farmers, taken away to be raised by a noble family. While such adoptions are standard practice and benefit all parties involved, the callousness and cruelty with which the \cAdopted{\formal}s have been treating \cAdopted{} are \emph{not} okay, and fly in the face of noblesse oblige. \cAdopted{} \cAdopted{\have} also been kept away from \cAdopted{\their} birth family all these years and \cAdopted{\they} resent\cAdopted{\verbs} \cAdopted{\their} ill treatment deeply. The two of you have been working on a curse to put on \cAdopted{\their} dastardly adoptive family to teach them a lesson and force them to let \cAdopted{} see \cAdopted{\their} birth family. There are just a few final steps to complete the curse, and \cAdopted{} might need your help with them. There is precious little justice in this world, and you find it surprisingly gratifying to help your friend punish those who richly deserve it.

If there is one thing that your and \cAdopted{}’s experiences have taught you, it is that knowledge is power — the knowledge to craft a curse, the knowledge to blackmail one’s enemies, the knowledge to outshine one’s peers academically. And while the library is full of knowledge, it's mostly \emph{old} knowledge. There is also current knowledge — useful, up to date information. The kind of information that flows as currency on the Black Market. Oh yes, you know about the Black Market that thrives under the very noses of every government on \pEarth{}. You were recruited by \cChupSecond{\full} originally, to serve as liaison to a surprising source — \cEthics{\full}, the Ethics teacher! You are unsure whether \cEthics{} and \cChupSecond{} know who is on the other end of the deals. You have a healthy dose of respect for \cChupSecond{}, and if you're being honest with yourself, a healthy dose of fear. \cChupSecond{\Theyare} scary, and could make your life very difficult if you told anyone that you know \cChupSecond{} has connections to the Black Market. \cChupSecond{\Theyare} always happy to have you facilitate a new sale, though. You've even started to try your own hand at collecting and passing information as another means to claw your way up. 

One day, when your curiosity got the better of you, you opened one of the sealed packets you were carrying to read a message you are sure that neither \cEthics{} nor \cChupSecond{} knows. \cInterpol{\full}, the Combat teacher, is not actually a teacher at all. \cInterpol{\Their} entire history is fabricated! Put on the trail, you've spied on \cInterpol{} a bit, and are convinced \cInterpol{} is part of some kind of secret government agency - probably a spy! Can you use this to your advantage somehow? You won't know unless you confront \cInterpol{\them} with what you know.

Your clandestine activities go further still. One year ago, the History teacher, \cHistory{\full}, approached you with an intriguing proposal. Recognizing your keen mind, \cHistory{\they} recruited you to become \cHistory{\their} spy and informant among the student body, reporting any unusual or suspicious activity you came across. \cHistory{} is a high ranking noble in \pFarm{}, and has promised you that your services will be richly rewarded. While \cHistory{\theyhave}n't come out and admitted it to you, you suspect that \cHistory{\theyare} involved in your nation's spy network. The most recent tidbit you shared with \cHistory{\them} is the mysterious disappearance and reappearance of the \iScythe{} from the library a few weeks ago.

If \cHistory{}'s promises fail to pan out, you could try your hand at selling information to \cEvil{\full}, the ruthless and powerful head of your nation’s diplomatic delegation, or \cHedonist{\full}, a prominent \cHedonist{\cleric} of Luminary. Surely \cEvil{\they} would see the value of the information and clandestine services you can provide. You actually already know \cEvil{}, having started writing to \cEvil{\them} a few years ago as a desperate attempt to find someone, anyone in the royal court who would offer you their patronage after your family’s disgrace. To your surprise, \cEvil{\they} actually wrote back, and while \cEvil{\theyhave} yet to offer you patronage, \cEvil{\theyhave} given you a lot of really good advice about how to manipulate people and maneuver in the viper’s nest that is the royal court. A part of you hopes that if you can prove yourself useful enough this weekend (which is your first chance to interact with \cEvil{} in person), \cEvil{\they} will take you under \cEvil{\their} wing in a more official capacity.

Earning the most Voting Stones to direct the Storm would be another way to gain prestige that you can cash in for social advancement later; after all, each stone you you get is a vote of confidence from the teacher or advisor who gave it to you. Winning the most votes would also help you ensure that the Storm does not get sent to your homeland.

You might be thinking about your future, but even so, you've got one more year of school. And while you're here, it would certainly be nice to be at the top of the pecking order next year, i.e. voted student body president. Campaigns for that won't start for another few months, but among other things, being chosen to demonstrate your magical prowess as part of the Ceremony of Excellence will give you a boost toward that. You expect fierce competition from the \pTech{} students in particular, so you may need to get creative to ensure you stand out. You think you have a good shot at being chosen, especially if you can cozy up to \cMusic{\full}, the Music teacher. Unfortunately, you don't think \cMusic{} likes you very much. You're not sure why. Maybe it has something to do with the way you encourage \cMusic{\their} adoptive grand\cAdopted{\nibling} \cAdopted{} to stand on \cAdopted{\their} own two feet and choose \cAdopted{\their} own path, without being beholden to the ``family'' who kidnapped and abused \cAdopted{\them} in the first place?

With a few, specific exceptions, you don’t much care for the students from the other nations. Sometimes it is hard to separate an individual from their context. \cTechStar{\full}, from the \pTech{}, is one example. \cTechStar{\They} sit\cTechStar{\verbs} on the High Council of the \pTech{}. \cTechStar{} has a direct say in the policies of \cTechStar{\their} entire country. When the \pTech{} make decisions that hurt your home (like deploying unreliable trebuchets that misfire, get people killed, and ruin your family's reputation!), it's hard to believe that \cTechStar{} is really able to hold the impact of those decisions. Another example is \cWarlordDaughter{\full} from the \pShip{}. \cWarlordDaughter{} is the child of the \pShippie{} Warlord, \cLoud{\full}, and a \pShippie{} through and through. It's hard not to be reminded of the \cLoud{\person} who is driving the war effort when you look at \cWarlordDaughter{\them}. It is hard to set aside the hurts that the war has caused. It's hard to believe the war could be for the greater good of everyone. 

You aren’t the only one to hold these kinds of sentiments. Many of the students from the \pShip{} and \pTech{} hold your family accountable for all the death and harm that happened under the command of your sibling. You are grateful for your fellow \pFarm{} students who have rallied around you. \cAdopted{} is already your friend, but even \cChupStudent{\full} and \cDisney{\full} have stood up for you a couple of times. In particular, you'd like to get closer to \cChupStudent{}, both for political gain because \cChupStudent{\their} family is very powerful and influential, and because \cChupStudent{\their} lackadaisical attitude means \cChupStudent{\theydo}n’t pose much threat to you academically. 

You are likewise grateful for the myriad Advisors from your nation. Many of them gladly correspond with the students at the \pSchool{}, and \cEvil{\full}, \cWildCard{\full}, \cHedonist{\full}, and \cCurse{\full} will be present this weekend if you need any advice in person about the best course of action, whether that is prioritizing protecting your home, or weighing the pros and cons of actions that might trade short term consequences for the long term betterment of the world.

This weekend is your one big shot in a lot of ways, so you can't mess it up. You're going to do your family proud and get the respect and position you deserve. You aren't afraid to break the rules to do it either. A win is a win, after all — a quick and dirty one counts for just as many points as a clean and fair one. All that matters is that you and the small handful of people you truly care about come out on top, and that you can finally restore your family to their rightful place of prestige in the royal court! 

\begin{itemz}[Major Goals]
    \item Gain power and social advancement for yourself and your family, by any means necessary. In so doing, clear your sibling Sage’s name and restore your family’s honor. Possible avenues include but are not limited to:
    \begin{itemize}
        \item Leveraging the fact that the Librarian is secretly a murderer and amnesiac.
        \item Feeding intelligence to \cHistory{}.
        \item Earning the most Voting Stones to direct the Storm, and making sure it doesn't get sent to the \pFarm{}.
        \item Gathering and selling information and items on the Black Market through \cChupSecond{}. \cEthics{} is an especially good source of information.
        \item Leveraging your knowledge that \cInterpol{} is some sort of spy.
        \item Trying to prove your usefulness to \cEvil{} and \cHedonist{}, two powerful advisors from your nation.
    \end{itemize}
    \item Help \cAdopted{} get revenge on \cAdopted{\their} adoptive family.
    \item Support your friend \cPresident{} with whatever \cPresident{\they} need\cPresident{\verbs}; it’s nice to have someone outside of the \pFarm{} who doesn’t blame you for what happened with Sage.
   \end{itemz}

\begin{itemz}[Minor Goals]
     \item Reclaim the 1st Assistant Librarian position from \cAmbition{}.
     \item Convince \cMusic{} to let you participate in the Ceremony of Excellence as one of the students doing the magical exhibition.
     \item Get to know \cChupStudent{}. The \cChupSecond{\formal} family is very powerful and would make good allies for you.
\end{itemz}

\begin{itemz}[Notes]
    \item Your extensive time in the Library gives you advantages over others when navigating the Library.
\end{itemz}

\subsubsection*{Contacts}
\begin{contacts}[The Black Market]
    \contact{\cEthics{}} The ethics teacher who you often run Black Market errands for, including carrying messages and valuable items to and from \cChupSecond{}.
    \contact{\cChupSecond{}} The economics teacher and your connection to the \pEarth{}n Black Market. Not to be crossed lightly. 
\end{contacts}

\begin{contacts}[The Spies]
    \contact{\cHistory{}} The history teacher, and apparently some sort of spy for the \pFarm{}? More importantly, a powerful noble with connections who can elevate your position if you continue to feed \cHistory{\them} secrets.
    \contact{\cInterpol{}} The magical combat teacher and apparently another spy? You've been shadowing \cInterpol{} and trying to decide how best to use this knowledge. 
\end{contacts}

\begin{contacts}[Personal Contacts]
    \contact{\cLibrarian{}} A formerly good friend among the adults at the school, until \cLibrarian{\they} betrayed that trust by giving the head assistant position to \cAmbition{}. Secretly a murderer and amnesiac.
    \contact{\cAdopted{}} Your best friend among the students. \cAdopted{\Theyare} ambitious and devious and you are happy to help \cAdopted{\them} with \cAdopted{\their} plans.
    \contact{\cPresident{}} The current student body president and 3rd Assistant Librarian (under you), whom you started out cozying up to for political gain but now genuinely like.
    \contact{\cAmbition{}} Your chief rival and a pathetic sycophant, unfairly promoted to 1st Assistant Librarian over you.
    \contact{\cMusic{}} The teacher in charge of the Ceremony of Excellence, whom you have to impress if you want to get chosen to demonstrate your skills. Unfortunately, \cMusic{\theydo} not seem to like you much, maybe because \cMusic{\theyare} a member of \cAdopted{}’s adoptive family and think\cMusic{\verbs} you are a bad influence?
    \contact{\cEvil{}} The ruthless and powerful head of your nation’s diplomatic delegation, with whom you’ve been exchanging letters for a few years.
    \contact{\cHedonist{}} A prominent and influential \cHedonist{\cleric} of \cFarmGod{}.
    \contact{\cChupStudent{}} A fellow student who is a member of a powerful noble family whom you would like to get closer to.
\end{contacts}

\end{document}
