\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cHedonist{}}

You are \cHedonist{\intro}, and 48 years old. You are a \cHedonist{\cleric} of \cFarmGod{}. While you perhaps indulge in the benefits of the position a little more than is strictly proper, it’s really just your just reward for all of your hard work. You do your duty, and do right by your country and the next generation. So what if you indulge a little while you pursue your own research projects?

You are told that your place in the Priesthood was assured from a very early age. Your family is quite powerful in the Priesthood (and consequently in the nobility), and your magical prowess supposedly manifested very young. According to your parents, this made life quite easy for you, as you sailed through most challenges. The truth is that you don’t actually remember your youth. You’ve been given to understand that you were quite a wild teenager, and drank to excess on more than one occasion. Somehow or another, this culminated in your family’s servants scooping you off the street in the middle of the night. You had been wandering aimlessly for hours, if not days. Not that you recognized them. You didn’t recognize anything. Your memory was gone — completely. You must have killed somebody. But no one knew who, or even exactly when. The gift of the Gods.

Eager to avoid the scandal that would come of your condition becoming widely known, your path into the Priesthood was expedited, and you were soon ensconced in your own ivory tower, left to research whatever your little heart desired. At first it was \emph{boring}. You were restless for\ldots something that you honestly couldn’t remember. Which was stupid. So by sheer force of will, you compelled the studies to become interesting.

And it worked, for the most part. You settled into a quiet life of study, meditation, researching the most obscure things, and serving the \pFarmers{}. You are now one of the foremost experts on  the most niche and obscure details of practical magic. It’s a good complement to your friend \cWildCard{} who is a leading expert in the history and theory of magic. You two met just after \cWildCard{\they} graduated form the \pSchool{} and bonded over your interests in chasing down leads in archives, uncovering magical mysteries, and becoming lost in esoterica. You also are both scions of noble families from the \pFarm{}, so you also shared gossip of the court while reading old tomes or playing a friendly game of chess. You are grateful that \cWildCard{} has never asked why you didn’t attend the \pSc{}. You’d hate to lie to your friend, but the truth is too embarrassing to face.

You tried not to dwell on the massive gap that was your entire life before the age of 17. You made new friends through correspondence, and found fulfillment. Mostly. You corresponded with clerics from all over for your research and scholarship, like \cEbbPriest{\full}, a cleric of \cEbb{}. But the austere life of most clerics rankled you. You craved beauty, luxury, and a touch of excess. Was that such a crime? No! \cFarmGod{} values \emph{life}. Surely \cFarmGod{\They} would not begrudge you a comfortable one.

So, you started acquiring nice things. There has always been a Black Market on \pEarth{}. For much of its existence, it has been a tiny thing, moving niche items like obscure historical, magical, and religious tomes, and various small time contraband at a rate too low to attract the ire of any government. You found it convenient for acquiring materials for whatever research project had most recently captured your fancy. Once the war began, however, legally acquiring tech from the \pTech{} and art from the \pShip{} became much harder. How convenient for you that the Black Market you were already well acquainted with stepped up to fill the gap. It's easy enough to trade a few minor curses (they are easy enough to purchase in the \pFarm{}) and tidbits of court gossip in exchange for whatever your heart desires. Of course, the \pFarm{} Spymaster probably wouldn't think it's just harmless gossip, but whoever they are, they haven't caught you yet.

Your most recent acquisition is a particularly nice ring. You bought it about a month ago from your Black Market contact, \cChupSecond{\full}. It goes splendidly with your terracotta colored robes, but that’s not why it quickly became an item you didn’t wish to let out of your sight. It has an enchantment on it — a powerful one. You don’t know enough about this type of magic to do more than guess that it is an illusion spell of some kind. What is this item really? Who lost it, and how? You’re desperate to know. And in the viper’s nest of \cQueen{\Majesty} \cQueen{}’s court, it could be a bargaining chip that saves your life someday.

For your next purchase, you have your eye on an \emph{automatic scribe}, which will allow you to efficiently make copies of written text, an invaluable tool for your important work preserving tomes of ancient wisdom. Honestly, something like this is a great example of how stupid the \pTech{} export laws are. What harm would this really do to be freely available beyond their borders? They are just stingy, difficult, and short sighted. You don’t feel the least bit bad about leveraging the black market to get access to this kind of thing.

To be clear, it's not that you are opposed to work — just that you are opposed to \emph{unnecessary} work. And there is a lot of \textbf{necessary} work to be done this weekend. As a \cHedonist{\cleric} of \cFarmGod{}, you have responsibilities. Primarily this entails bringing the \iPitcher{}, one of the \pFarm{} relics for controlling the Storm, and ensuring the Relics are not tampered with. Secondly, it is your responsibility to look after the spiritual wellbeing of the followers of \cFarmGod{}. You are expected to provide counsel and guidance to students and advisors alike, and are charged with initiating anyone desiring to take up \cFarmGod{} as their Patron Deity who demonstrates proper commitment to the faith. 

Further, as a \cHedonist{\cleric} of \cFarmGod{}, it is your responsibility to safeguard the sanctity of music and the healing magic that comes with it. The other nations simply do not understand that music is sacred and belongs in the hands of the Priesthood, and you are concerned that the moral fiber of the students from the \pFarm{} may be eroded by their heretical ideas. If anyone was free to learn the healing songs, every pirate, malcontent, and political rabble-rouser would seize on the opportunity and quickly destabilize the delicate balance of power in the \pFarm{} — unthinkable! You are grateful that at least \cMusic{\full}, the music teacher, is from the \pFarm{}, and seems to hold the proper reverence for music; hopefully \cMusic{\theyhave} been instilling such care and respect in the students.

An unofficial duty is to keep an ear out for people asking about the Giant Hummingbirds. The Priesthood has known for some time that fewer and fewer of \cFarmGod{}'s Avatars have been appearing as of late. In the past decade, there have been a distressing \textbf{zero} verified sightings, and only 4 total in the previous decade. If the masses knew, it would incite a panic that \cFarmGod{} had forsaken the country, which is not something a country at war can afford. It would also signal a vulnerability that the \pShippies{} might try to capitalize on, or even cause your \pTech{} allies to desert you. So far the Priesthood has had no luck determining the cause of the decrease, and your standing orders are to divert anyone attempting such a line of investigation.

Normally, you would be assisted in this massive list of duties by another cleric. One who taught at the \pSchool{}, or another advisor. Unfortunately for you, that colleague resigned after the mess with the dead students six years ago. You can’t really blame them. It must have been absolutely horrible. But it does mean that you are stuck with a particularly \emph{complicated} assistant. Technically \cDisney{} is a full \cDisney{\cleric} of \cFarmGod{}, not just an initiate, but \cDisney{\theyare} also rumored to have been part of a dangerous splinter group 200 years ago. How exactly \cDisney{\they} still look\cDisney{\verbs} like \cDisney{\theyare} 20, you have no idea. That’s above your pay grade.

That splinter group called themselves the \cDisneySect{}. They are said to have attempted a blasphemous ritual to access the Realm of the Gods itself! The details are fuzzy, but that information was dangerous enough that the Church chose to wipe out the faction some 200 years ago; evidently, they didn't quite finish the job. You really hope that \cDisney{} doesn't know the ritual, or if \cDisney{\theydo}, that \cDisney{\theyhave} the good sense to keep it to \cDisney{\themself} — otherwise, you might have to do something to contain the information. 

And you really don’t want to have to examine the morality of all of that mess. Was it really necessary to stoop to \emph{killing} dozens (if not more) Clerics in cold blood? The massacre was premeditated. You’ve seen the \emph{very carefully} concealed records that the Church keeps. They tried \emph{everything} to stop the \cDisneySect{}, to talk sense into them, to derail or distract them, but nothing worked. Several Relics, including the \iScythe{} and the \iNet{} are kept under lock and key in the \pSc{} library for a reason. In the wrong hands, in hands with enough power (like a few of the students here at the \pSchool{}), they could be used to wound, or maybe even kill a Deity. Access to the Divine Realm would mean a path to killing the Gods. And when all reasonable avenues are exhausted\ldots Oh the burden of responsibility. You really, really hope you can keep \cDisney{} out of trouble this weekend, so you don’t have to make any hard choices.

Speaking of morally questionable choices, the betrayal that started the war was predicated on a promise from the \pTech{} that they were close to finding a permanent solution to the Storms. That solution hasn’t materialized in six years. You fervently hope that the presentation scheduled for this weekend has actual answers.  If it's true, then your countries can come together and implement their solution, and finally be done with the whole thing. The sacrifice of the \pShip{} will have all been worth it. And you and the rest of the advisors can get around to talking them down from the ongoing war.

But you've been nearly swindled by knockoffs of fancy things before — and that makes you inherently suspicious of anything that sounds too good to be true. You feel it only prudent to vet any proposed solution as best as you are able. You hope it won’t come to this, but if necessary, you could go as far as interrogating the scientists under either a Truth-Telling Curse or — if you can manage it — under the power of the \iLariat{}. The \cCurse{\formal} family lives on the \cHedonist{\formal} lands along the West coast of the \pFarm{}. Due to the proximity of your families, you and \cCurse{\full} have maintained a long correspondence and even begun to meet up in person regularly. You have spent long hours discussing what little is known of the \pTech{} plan to end the Storms, debating whether or not it's actually possible, and what the cost might be if it is. The two of you have decided to work together this weekend to get to the truth once and for all. 

 But you must also be prepared for whatever you discover. If the \pTech{} cannot actually end the Storms, or if ending the Storms comes with a cost too high to pay, then what? Where do you go from here? How does one even begin to make amends?

Whatever the answer ends up being, the Storms won't be ending in time for at least this one last ``Time of Deciding’’. Therefore, you've got a responsibility as an advisor to support and guide the students, especially those from the \pFarm{}. The students here at the \pSc{}, particularly the 12 who stay this weekend to participate in controlling the Storm, bear a huge responsibility. And when they graduate, they will go on to be movers and shakers in their countries. The teachers shape these minds day in and day out. As an advisor, your one big chance to shape minds is the Advisor's Speech at the Ceremony of Excellence. \cMusic{} is in charge of arranging the roster this year, and you intend to have \cMusic{\them} give you the task of giving the speech. Naturally, there will be other contenders for the honor, but you are prepared to compete — and win. Your primary competitor is your friend \cCurse{}, but what's a little healthy competition between friends?

\cHedonist{\Cleric} though you may be, you are still also Nobility of the \pFarm{}. That requires a certain base level of social and political maneuvering. You have contacts among all three cohorts here this weekend that you need to connect with for one reason or another. Aside from keeping a wary eye on \cDisney{}, there is one other student that could benefit from your attention.

\cLibAssist{} is probably the sharpest of the entire cohort of students. The reputation of the \cLibAssist{\formal} family took quite a hit a few years ago when one of \cLibAssist{}’s siblings, who was serving as a general in the war, made an absolute fool of themselves (and got a number of people hurt, and an important defensive installation destroyed). The loss of status seems to have hit \cLibAssist{} particularly hard, and \cLibAssist{\theyhave} become intensely ruthless and cutthroat, absolutely without any qualms about who might get hurt by \cLibAssist{\their} behavior. While that attitude might thrive in the court of \cQueen{\full}, and probably impress \cPrince{}, it’s a lonely and exhausting life. You wonder if you might not be able to offer \cLibAssist{} an alternative. \cLibAssist{\Theyare}’nt particularly religious, but as your own life has proven, being strongly religious or spiritual is not necessary to thrive in the Clergy of \cFarmGod{}. Perhaps you could offer initiation into the Church as a\ldots redirection from more aggressive ways to climb back up the social ladder.

You also need to make proper social overtures with \cPrince{\full}, youngest child of \cQueen{\full}, ruler of the \pFarm{}. The two of you have played chess (both literally and metaphorically) for years, and you are rightly proud of your ability to hold your own in those games. No one thrives in the viper’s nest of \cQueen{}’s court like \cPrince{} did, before \cPrince{} took a job at the \pSchool{} five years back. You found that an odd development, especially with rumors that \cPrince{} is secretly favored by \cQueen{} as the heir apparent — above \cPrince{\their} older siblings, but who are you to question the career path of royalty? If nothing else, at least \cPrince{\theyare} a great source of courtly gossip that you can sell on the Black Market (though you don't tell \cPrince{\them} that). 

You are also looking forward to meeting a pen pal of yours, \cAntiChup{\full}, in person for the first time. Years ago, as part of your priestly training, you were tasked with striking up a correspondence with a member of the clergy of another nation — \cAntiChup{}. The two of you have had many lively theological discussions over the years, and you both deeply value the traditions that form the foundations of the Church. You never would have guess that your old pen pal would ultimately rise to become the High \cAntiChup{\Cleric} of the \pTech{}, \cTechGod{}’s Grace, but you are happy for \cAntiChup{\them} and honored to call such an illustrious individual a friend.

People say that compromise is part of life — but you've never found that to be the case. You've always been able to have your cake and eat it too. This weekend, that means indulging your desire for rare tomes and beautiful, fancy, and exquisite quality goods (regardless of the legality of their acquisition), alongside fulfilling your priestly and advisory duties. It might be a lot to do, but you've always been able to handle challenges without breaking a sweat. Why should this weekend be any different?

\begin{itemz}[Major Goals]
    \item Fulfill your Cleric duties, including protecting the Relics, distracting anyone who asks too many questions about the Giant Hummingbirds, and ensuring \cDisney{} doesn’t do anything stupid or reckless.
    \item Get in contact with the Black Market to acquire an automatic scribe and anything else that strikes your fancy; \cChupSecond{} is your current contact. You have curses (purchased from NPCs before coming to the \pSchool{}) and court gossip to sell in exchange.
    \item Work with \cCurse{} to verify the science the \pTech{} is touting to end the Storms once and for all. One means of doing so would be to compel the scientists to speak truthfully with either a Truth-Telling Curse or the \iLariat{}.
    \item Make sure the Storm does not get sent to the \pFarm{}.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Support and guide the students of the \pFarm{}, especially \cLibAssist{}, who seems determined to bite off more than \cLibAssist{\they} can chew in terms of making political enemies.
    \item Land a role speaking at the Ceremony of Excellence by convincing the teacher in charge, \cMusic{} of the value of what you wish to say.
    \item Find out what the enchantment on the ring is concealing.
    \item See how you can support \cWildCard{}, \cPrince{}, and \cAntiChup{} in their various endeavors this weekend.
\end{itemz}

\begin{itemz}[Notes]
    \item This is your second time at the \pSchool{} as an advisor. The first time was three years ago.
    \item Some potential gossip you could trade on the Black Market (this list is not exhaustive):
    \begin{itemize}
   	 \item The existence and nature of the \cDisneySect{}, and the rumor that one of them is here as a student.
   	 \item Details on the disappearing Giant Hummingbirds, though that getting out would strike a serious blow to the Church, so you are loath to part with it.
   	 \item \cPrince{} is currently favored to inherit the throne of the \pFarm{} when \cQueen{\Their} Majesty dies.
    \end{itemize}
\end{itemz}

\begin{contacts}
    \contact{\cCurse{}} A frequent pen-pal and fellow \pFarm{} advisor who is working with you to investigate the \pTech{} science. Also your primary competition for the speaking role at the Ceremony of Excellence.
    \contact{\cChupSecond{}} The Economics teacher from the \pShip{}, involved with the Black Market, and a contact you've used before to acquire many of your rarer technologies from the \pTech{}.
    \contact{\cWildCard{}} An old friend and occasional drinking buddy. Fun to be around, and surprisingly easygoing.
    \contact{\cPrince{}} A friend, chess partner, teacher at the \pSc{}, youngest \cPrince{\offspring} of \cQueen{\Monarch} \cQueen{}, and currently favored to inherit the throne.
    \contact{\cDisney{}} A student at the college who is rumored to be a \cDisney{\cleric} from the heretical splinter faction known as the \cDisneySect{}, thought to have been stamped out 200 years ago.
     \contact{\cLibAssist{}} A student that you believe reaches for cruel and malicious solutions more often than necessary. Maybe you can provide \cLibAssist{} with a less destructive way to reclaim social standing by joining the Church?
    \contact{\cAntiChup{}} An old pen pal of yours who has risen through the ranks of the Church of \cTechGod{} to become \cTechGod{}’s Grace. You are happy and honored to finally be meeting \cAntiChup{\them} in person this weekend.
\end{contacts}

\end{document}
