\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cDisney{}}

You are \cDisney{\intro}, and 21 years old. Well\ldots{}technically more like 221, but you were asleep for most of that. You are a first year student at the \pSchool{}, a full \cDisney{\cleric} of \cFarmGod{\intro}, and you grew up in the \pFarm{} two centuries ago. As you have endured 200 years of enchanted sleep and only awoke nine months ago, the world is strange to you. Common people have access to technomagical creations, the upper class walk around in clothing woven with magic, and traveling ``circuses'' from the \pTech{} share art and music freely amongst the \pFarmers{}. You also hold a deadly secret you dare only share with those you trust deeply (details below). 

You grew up very poor, forced into pickpocketing, begging, and scrounging for scraps to stay alive. You spent a few dark years on the streets — until a kindly old \cDisneyMentor{\cleric} named \cDisneyMentor{\intro} found you and took you in. Your life rapidly improved after that. You learned to read and write, and got a much more cheery outlook on life, though you never quite forgot your skills at getting into places where you didn't belong. Fortunately, that suited your mentor just fine, as \cDisneyMentor{\theywere} a member of a minority religious sect within the Church of \cFarmGod{} known as the \cDisneySect{\intro}. The \cDisneySect{} believed it was their destiny to enter the Realm of the Gods and commune with them directly about the creation of the world and other theological questions. It sounded so exciting! You studied under \cDisneyMentor{} to become a Cleric, where your idealism and desire to help others could really shine, and after years of study, you were ordained. Only a few days later, all of the prayer and research of you and your fellow \cDisneySect{} came to fruition when you attempted the most magnificent feat ever embarked upon by humankind. You had finally figured out a ritual to travel to the Divine Realm!

Unfortunately, before it could be realized, the ritual and the rest of your world came crashing down — you think. You don't actually remember except for hazy fragments. The rest you have pieced together from what \cWildCard{\intro} has told you. The mainstream Church caught wind of the ritual and condemned it as heresy. They broke into the temple where the ritual was being attempted just in time to stop it, killing all the Clerics therein. At the last moment, \cDisneyMentor{} hid you in the Crypt below the Temple, in a glass box, lying in a sleep like death, where you remained for two hundred years. 

You were awakened by \cWildCard{\full}, who had worked for years to unravel a puzzle that eventually led \cWildCard{\them} to you. \cWildCard{} has become almost a new \cWildCard{\parent} to you, gave you your first introduction to the modern world, and even sponsored your attendance at the \pSchool{}, and you are eternally grateful. The only item you have left from your earlier life is a locket that was given to you for safekeeping by \cDisneyMentor{}, which shines with the light of \cFarmGod{} when you open it. \cDisneyMentor{} told you that the \iLocket{} is a holy Relic, on par with other ``official'' Relics used in the ritual to direct the Storm, and you treasure it.

You've begun to make friends in your short time at \pSchool{}: \cPirateChild{\intro}, \cTechStar{\intro}, and \cAdopted{\intro}. You admire \cPirateChild{} for \cPirateChild{\their} loyalty, tenacity, and always saying what is on \cPirateChild{\their} mind instead of beating around the bush, though \cPirateChild{\they} can sometimes be a little too irreverent. You love \cTechStar{}’s idealism, enthusiasm, and sheer ingenuity, but \cTechStar{\they} can sometimes get tunnel vision and not think through all the implications. And \cAdopted{} is so passionate, clever, and devoted to the common good, but you worry about how much bitterness and resentment \cAdopted{\they} carr\cAdopted{\verby} towards \cAdopted{\their} adoptive family. \cAdopted{} was adopted into a noble family at a young age, and is deeply resentful about it. You don't understand why — you'd have given anything to be adopted into a family that loved you. \cDisneyMentor{} was kind, and the monastery was home, but it wasn't a loving family like \cAdopted{} and so many of your other new friends have.

The four of you are always getting into all sorts of pranks and mischief. You argue constantly too, but that doesn't mean you aren't the best of friends, right? Maybe you can trust them? You have always considered yourself something of an idealist and dreamer, and hate having to carry so much of your secret alone. When you were awakened by \cWildCard{}, and subsequently invited to attend the \pSchool{}, you hoped that the additional learning would allow you to both find your own place in this modern world and help others in the process.

You've told two of your best friends, \cPirateChild{} and \cTechStar{}, a little about your history, but hope that they won't spread the details too far. It's not that you meant to leave \cAdopted{} out, it just kind of happened that way. There never seemed to be a good time to come out and say, ``by the way, I'm a member of a heretical splinter faction of the Church of \cFarmGod{}.'' Maybe you hesitated because, unlike your other two friends, \cAdopted{} is from the \pFarm{}and therefore might look askance at your unorthodox religious affiliation.

You’ve also found a pleasantly kindred spirit in the \cInterpol{\intro}, the magical combat teacher at the \pSc{}. Most people in positions of power dismiss you and your optimism. They call you naive when they are being polite, or stupid when they aren’t. But \cInterpol{} is kind, and understanding, and supports your desire to find the best way forward for everyone. \cInterpol{\They} seem\cInterpol{\verbs} to really believe that you will go far and improve the world. It’s nice to have someone nearby who supports you. \cWildCard{} is great, but you are rarely able to see \cWildCard{\them} with all of your time at school.

Perhaps because of the catastrophic failure of the ritual with the \cDisneySect{}, it is very important to you to be heavily involved and ensure the success of the Ritual to Control the Storm this weekend; you do not want to see the same thing happen to your new friends. Aside from your role as a voting student and the actual execution of the ritual, there is the preparation, which is always a joint effort between the students and the teachers. You intend to make yourself useful to whichever teachers are in charge of the ritual this year.

A number of things are different now than they were 200 years ago, but most concerning to you beyond the current war is the absence of the Giant Hummingbirds, Avatars of \cFarmGod{}, which were so common in your time. The Hummingbirds used to be a cornerstone of daily life, appearing with messages of hope, faith, and inspiration to anyone who needed them. While you are perplexed at their current scarcity, you are even more alarmed by the fact that nobody seems willing to talk about it, especially given that the nations are currently at war. Of course the wars and great successes and failures of mortals influence the power of the Gods, and the success of their divine labors. You are determined to discover why \cFarmGod{}'s messengers have abandoned your people in what is clearly a time of great need. You consider it your duty as \cDisney{\cleric} of \cFarmGod{}, even if the mainstream Church did brand you and your fellow \cDisneySect{} as heretics.

You've been asking around discretely for some time about the missing Hummingbirds, but people keep reacting with shock and horror as though it is some big secret; as far as you can tell, the Church is trying to keep it under wraps — yet another decision by the mainstream Church that you disagree with. Close to despairing of finding any leads, or even help in your search, you wrote to several international entities known for their discretion, including \cHeadDiplomat{\intro} — if no one in \pFarm{}would do anything about it, then maybe someone from another nation would. It wasn't \cHeadDiplomat{}, but their apprentice, \cJuniorStatesman{\intro}, who replied. Despite being from the \pShip{}, \cJuniorStatesman{\they} share\cJuniorStatesman{\verbs} your concerns about the missing Avatars. The two of you have been searching for several months to no avail. If only you could reach the Divine Realm like the \cDisneySect{} originally planned, you could ask the Hummingbirds, or even \cFarmGod{} \cFarmGod{\themself} why the Hummingbirds have departed. But the plan to reach the Divine Realm got a lot of people you called family killed, so you aren't sure you would condone another attempt\ldots{} even if you could remember how the ritual goes. But if you could reach the Divine Realm and decide to go there, you certainly would bring \cJuniorStatesman{} along. You can’t wait to meet \cJuniorStatesman{\them} in person this weekend!
 
As a perhaps more immediate concern, your friend \cPirateChild{} has found a Dragon's egg, and (perhaps misguidedly) smuggled it into the school about a month ago to give to you as an early present for your birthday, which is on Sunday. You are touched by the gesture\ldots{}if a little troubled by the practicalities. You aren't sure \cPirateChild{} really thought this through in terms of what you should do with such a creature in the long term, but you know \cPirateChild{\they} meant well, and you can’t say it isn’t typical behavior for \cPirateChild{\them}.

At first, everything was going smoothly. You'd gotten \cAdopted{} to cast an enchantment to disguise the egg as an innocuous stuffed animal — but of course, the little creature hatched, which dispelled the enchantment. Probably just as well — it's not like a moving stuffed animal would be a very convincing disguise. Now you have a smart, adorable, ravenously hungry little baby Dragon to keep hidden (in a secret compartment behind a bookshelf in the student lounge) and fed. And to top it off, the poor thing seems to be sick, and keeps sneezing! You are determined to preserve this precious, albeit someday terrifying, creature, because the Dragons, also known as Sea Serpents, can become the Avatars of \cEbbFull{\intro} and \cFlowFull{\intro}. And the poor thing has no family, much like yourself\ldots{}And because it is so, so sweet. You think you could make it through this current predicament with a little luck and ingenuity.

You were recently asked a favor by \cWildCard{}, who is apparently looking for information on the existence of a Black Market. \cWildCard{\They} think\cWildCard{\verbs} that \cBunker{\intro} might have important information, so \cWildCard{\they} asked you to sneak into \cBunker{}'s room and steal paperwork from a briefcase this afternoon. You haven't stolen anything in a long time, but you trust that \cWildCard{} has a good reason. It was a challenge, but you succeeded and now have the papers the briefcase contained! You don't know what they mean, but \cWildCard{} probably will. You intend to ask \cWildCard{} to explain them to you when you turn them over, though. It's not fair to take risks and not even learn anything from them. Maybe \cWildCard{} is a secret agent, trying to take down the Black Market? That would be exciting! Maybe you can become a secret agent too! 

You also know that \cWildCard{} — and probably other far less worthy individuals — would like to know more about the ill-fated ritual that you and the other \cDisneySect{} tried to cast to gain entry to the Realm of Gods. While you would never reveal this information if you thought anyone would try to misuse the ritual that led to the deaths of all those in your Temple, \cWildCard{} is the person you trust most in this new world. Unfortunately, your memories of the ritual itself are scattered at best. You aren't sure if the memory was locked away deliberately by \cDisneyMentor{} after \cDisneyMentor{\they} put you to sleep, or if it just got lost in the 200 years you slept. Even if you can remember it, though, you still have misgivings about sharing it, even with \cWildCard{}; you are terrified that something terrible might happen to \cWildCard{\them} if \cWildCard{\they} tried to perform the ritual, and you can’t bear to lose someone you love again like that. Alas, to complicate matters, you retain a deep curiosity about theology and the creation of \pEarth{} from your time with the \cDisneySect{}, and traveling to the Divine Realm to speak with the Gods themselves would be the surest way to learn such fundamental truths. For now, though, it is a moot point — you've tried and tried to remember, but have come up empty. You are so frustrated you vent about it to your friend \cTechStar{} all the time, and \cTechStar{\theyhave} been so kind as to offer to help you regain your memories. If anyone can solve this dilemma, it’s your genius friend \cTechStar{}!

Speaking of \cTechStar{}, just this afternoon you overheard someone talking about \cTechStar{\them} on the other side of a closed door. On your way out from stealing the papers from \cBunker{}, you passed by the advisor's lounge, to which the door was closed. That was unusual enough that you stopped for a moment to contemplate. Then you heard someone muttering to themselves. Now, you don't normally like to snoop without good reason (but you are quite good at snooping when you need to), but hearing \cTechStar{}'s name seemed like a good enough reason to get close to the door and listen in. The mutterings were indistinct, but you're certain you heard them say something about getting control of \cTechStar{}’s creation, the VidCom technology, no matter the cost. The voice sounded serious. Deadly serious. Just what \cTechStar{\have} \cTechStar{\they} gotten \cTechStar{\themself} into? Like yourself, \cTechStar{\theyare} an idealist, and genuinely want\cTechStar{\verbs} to help others with \cTechStar{\their} technology — so whoever the voice belongs to is definitely a bad person.

Still, sometimes it is hard to separate an individual from their context. \cTechStar{\They} sit\cTechStar{\verbs} on the High Council of the \pTech{}. \cTechStar{} has a direct say in the policies of \cTechStar{\their} entire country. When the \pTech{} make decisions that hurt your home (like betraying the \pShip{} six years ago and dragging your nation into this terrible war), it's hard to believe that \cTechStar{} is really able to hold the impact of those decisions. You want to trust your friend and see the best in \cTechStar{\them}, but sometimes it is hard to separate the person from the big issues \cTechStar{\they} oversee\cTechStar{\verbs}. Another example is \cWarlordDaughter{\intro} from the \pShip{}. \cWarlordDaughter{} is the \cWarlordDaughter{\child} of the \pShippie{} Warlord, \cLoud{\intro}, and a \pShippie{} through and through. It's hard not to be reminded of the \cLoud{\person} who is driving the war effort when you look at \cWarlordDaughter{\them}. It is hard to set aside the hurts that the war has caused. Perhaps in a similar vein, many of the students from the \pShip{} and \pTech{} hold \cLibAssist{\intro}’s family, from your own nation, accountable for all the death and harm that happened under the command of \cLibAssist{}’s older sibling over the course of the war. Even though you don't know \cLibAssist{} particularly well, you feel the urge to stand up for \cLibAssist{\them} when someone from one of the other nations gives \cLibAssist{\them} a hard time. 

One notable event happening this weekend amidst many is that the current Principal, \cPrincipal{\intro}, is choosing \cPrincipal{\their} successor. \cMusic{\intro}, your favorite teacher, is vying for the position with \cBeetle{\intro} and \cChupSecond{\intro}. You think \cMusic{} would be a great principal and you hope \cMusic{\they} win\cMusic{\verbs}! \cMusic{} hails from the \pFarm{} like you and carries a profound reverence for music, deep wisdom, patience with sometimes overexcitable students such as yourself, and a lot of compassion. The two of you have had many great conversations about musical theory and theology.

This weekend there are mysteries to unravel, friends to help, and the all important Ritual to Control the Storm to prepare, the main event of the weekend. As a budding \cDisney{\cleric}, you are thrilled to be included in this vital work, and despite the many other priorities on your plate, you feel this is the most vitally important of all. Your contribution and subsequent vote will help, or harm, more people than you ever dreamed possible, and helping others is at the very core of your being. This is the most important weekend of your new modern life, and you can just feel that it is going to work out perfectly. You'll make sure of it!

\begin{itemz}[Major Goals]
    \item Ensure that the Ritual to Control the Storm goes flawlessly.
    \item Recover your memories of the ritual that allows travel to the Divine Realm. Then decide if you are going to tell \cWildCard{} or not. Hopefully \cTechStar{} can help?
    \item Keep your baby Dragon a secret, take care of it with \cPirateChild{}'s and \cAdopted{}'s help, and give it the perfect name.
    \item Work with \cJuniorStatesman{} to discover what happened to the Avatars of \cFarmGod{}, the missing Giant Hummingbirds.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Protect your friend \cTechStar{} — someone is plotting to steal \cTechStar{\their} VidCom technology, and \cTechStar{} might get hurt in the process.
    \item Pass off the papers you stole from \cBunker{}'s briefcase to \cWildCard{}. Don't let \cWildCard{\them} cut you out of whatever \cWildCard{\they} find\cWildCard{\verbs} out, though! If you're going to take risks for \cWildCard{\them}, you want to get part of the payoff.
    \item Help \cMusic{} become the next Principal of the \pSchool{}.
\end{itemz}

\begin{itemz}[Notes]
    \item You are a first year student.
    \item You have the \iLocket{} which shines with the light of \cFarmGod{} when opened. It is a religious artifact as powerful as any of the known Relics.
    \item There is a greensheet associated with the Bookcase in the Student Lounge where the baby dragon is hidden. This greensheet will explain how to take care of the baby over the course of the weekend. Your S-Score (1) allows you to freely view the sign hidden by the Bookcase sign, and access the greensheet.
\end{itemz}

\begin{contacts}
    \contact{\cWildCard{}} Your rescuer, benefactor, and parental figure, who saved you from two hundred years of enchanted sleep.
    \contact{\cTechStar{}} A good friend and classmate from the \pTech{}. An idealist who wants to help the world, and who bears the heavy responsibility of being on the High Council of the \pTech{}.
    \contact{\cPirateChild{}} Your good friend and classmate from the \pShip{} who gifted you a Dragon egg. Maybe not always good at thinking through consequences, but very enthusiastic\ldots
    \contact{\cAdopted{}} Your good friend and classmate from the \pFarm{}, who kindly cast an illusion to temporarily conceal the Dragon egg \cPirateChild{} gave you. You feel a sense of kinship to \cAdopted{\them}, even though your temperaments are so different. 
    \contact{\cMusic{}} Your favorite teacher, and you're excited that \cMusic{\theyhave} a chance at becoming the next Principal! You'll be rooting for \cMusic{\them}!
    \contact{\cJuniorStatesman{}} A \pShip{} diplomat who is helping you find the missing Avatars of \cFarmGod{}.

\end{contacts}

\end{document}

