\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cAdopted{}}

You are \cAdopted{\intro}. At 19 years old, you are a first year student at \pSchool{}. You grew up in the \pFarm{}, but your family life is\ldots{}complicated. Forcibly adopted into a noble family at a young age, you yearn to undo the despicable norms in your country that led to your kidnapping by the Nobility who could supposedly provide better for you than those who truly love you, and you'll do anything to find your birth family. You are determined to punish the ones who took you, and use the great magical potential that you were born with to better the lives of the farming families across the \pFarm{} whether the \cQueen{\Monarch} and the Nobility like it or not.

You were born into a poor family that farmed the lands under the rule of \cAdoptedParentOne{\intro}, but when your magical potential was discovered when you were barely a teenager you were promptly ``adopted'' into the Noble \cAdoptedParentOne{\formal} family. Your new so-called family told you it was for your own best interest and that they could give you a life and education that your birth family could never provide. In reality, you never felt truly included — your new siblings made it clear to you that you were there for your magical potential alone and your other relatives always treated you as second best. Never did they make you feel truly welcome or loved, like a real family would. Your adoptive parents would often lecture you on how lucky you were to be chosen and how you needed to work twice as hard to ``earn” your place among them. Both they and your tutors were always quick to berate and to punish should you fail to meet their lofty expectations; praise for your accomplishments was virtually nonexistent, let alone genuine affection. You hate the people who kept you from your birth family and the love and belonging you've craved all your life, and you've got plans for revenge. 

After so many years apart from your birth family and in the hands of people who never truly loved you, you are starved for the feeling of connection and being a part of something. You've felt this sense of something missing all of your life, but have never had much opportunity to explore a remedy. Out from under your adopted family's careful watch for the first time here at the \pSc{}, this has led to the increasingly strong desire to reconnect with your birth family and repudiate your kidnappers. You know that \cAdoptedParentOne{} would never approve, and the rest of the family would conspire to prevent you from doing so, so you must work in secret. You have heard rumors of these things called VidCom devices in the \pTech{}. These devices are not yet available to the general public even in the \pTech{}, but allow for communication between two people who each hold one of the devices. If only you could get your hands on a pair, you could keep one for yourself, and smuggle one to your birth family. Finding such items when they aren't generally available will be tricky — you'll probably have to either find a way to access the Black Market or get them from their inventor, \cTechStar{\intro}. And then there's the matter of money. While you aren't exactly hurting for pocket money, you suspect that the Black Market is likely to trade on things other than \pFarm{} currency. You are more than prepared to sell curses, break rules, or take on personal sacrifice to make this happen. You may also be able to convince \cTechStar{} directly, as \cTechStar{\theyare} mutual friends with your friends \cDisney{\intro} and \cPirateChild{\intro}. But you two are not close and you have no idea how \cTechStar{\they} would respond to such an illegal idea or how much \cTechStar{\they} would charge.

After you have the devices, all you need to do is find your birth family (\emph{OOC: that would happen in epilogue}) to give them one of the devices and convince them to take it, keep it secret, and love you again. That part might be more of a long term project\ldots{} They have to want to do that, though, right? After all, if you can't belong with them, there isn't anywhere else you really belong\ldots{} right? The desire to be with your birth family again is like an ache in your chest, but part of you knows you should keep your eye out for any other community you might be able to belong to — because if this doesn't work, and you haven’t found something else, you don't know WHAT you'll do. You do have friends here at least, but how many of them accept you for you and not your magical potential and adopted family name?

Beyond the immediate goals of finding and communicating with your birth family, you feel driven to improve the lives of your family and all those like them, who are so often ignored, neglected, or abused by the Nobility. Healing magic, which comes in the form of enchanted music, is strictly regulated by the Priesthood, and usually only licensed to be distributed by Clerics. If only you could devise a way to record the healing music and get it into the hands of the farmers who truly need it, you could improve the lives of so many — even save lives the next time The Storm hits the \pFarm{} again! The Nobility remain safe within their walls, a dedicated Cleric always on hand, while those who actually \emph{work} \cFarmGod{\intros} land face the Storms unprotected. You won't let the fact that these ideas are ``heretical'' stop you.

That is where \cMusic{\intro} comes in. \cMusic{} is the music teacher, and also happens to be the \cMusic{\auncle} of your adoptive ``father.'' \cMusic{\Their} music class is your favorite class. \cMusic{} has taught at the \pSchool{} almost since you were born; certainly since before you were ``adopted.'' So \cMusic{\theywere}n’t able to be around much when you were growing up, but \cMusic{\they} always showed you true kindness. You wish that \cMusic{} could do something to rescue you from the rest of \cMusic{\their} awful family, but short of \cMusic{\them} changing adoption laws, you sadly are stuck. But maybe you can leverage \cMusic{\their} connection with you to recruit \cMusic{} to the cause of sharing healing music with the masses, at least. As the music teacher and someone with ties to the Church of \cFarmGod{}, this could turn out to be crucial to your success. You'll have to tread carefully with this project, though, since many adults will likely look askance at what you are trying to do, including \cMusic{} \cMusic{\themself}, and \cHedonist{\intro}, the \cHedonist{\cleric} of \cFarmGod{} who you have heard will be here this weekend.

You have some hope that the Magical Combat teacher, \cInterpol{\intro}, might be willing to help. \cInterpol{\Theyhave} a lot of sympathy for your very reasonable fear of being hurt in combat class and you have overheard \cMusic{} and \cInterpol{} talking rhapsodically about the joy of music. This could prove either a boon or a hindrance, but at least \cInterpol{\they} may understand. 

You have only told one person so far about your plans to share music with the masses. You've been connecting recently with one of your classmates, \cScholarship{\intro}. Normally sort of a loner, \cScholarship{\theyhave} opened up to you about how much \cScholarship{\they} can't stand and want\cScholarship{\verbs} to get away from \cScholarship{\their} \cAntiChup{\cleric} mentor, \cAntiChup{\intro}, who is always making \cScholarship{} do \cAntiChup{\their} dirty work. \cScholarship{} hasn't gone into details, but you get the impression that the ``dirty work'' is often unethical, maybe even illegal. You deeply empathize with \cScholarship{\their} plight and recognize a fellow good person caught in a bad situation, determined to escape from it by any means necessary. You have thought about asking  \cScholarship{\them} to help with a curse you have been working on (more on that later), but you don’t want \cScholarship{} to have to do more shady stuff. But \cScholarship{} is positioned to do well in the church, with or without \cAntiChup{}, and the \pTech{} doesn’t have the same strictures on music as your homeland. So you have asked for \cScholarship{\their} help connecting to folks in the \pTech{} as you daydream over music box designs and talk about the unfairness of life. 

During these conversations, it dawned on you just the other day that your feelings go beyond compassion and respect — you are crushing on \cScholarship{\them} pretty hard. You haven't told \cScholarship{} yet and are still deciding what you want to do, but a part of you is desperate to find out if \cScholarship{\they} return\cScholarship{\verbs} your feelings. You are pretty sure you two could make beautiful music together.

You have another personal, somewhat more sinister goal — getting revenge for the wrongs done to you by your kidnappers. You've come up with a plan to curse your entire adoptive family's line with a wasting curse. This curse will render food tasteless, bland, and most importantly, devoid of nutrition. Until you decide to lift the curse, the entirety of the \cAdopted{\formal} family above the age of 15 will slowly waste away, despite their best efforts, and perish after months or years of agony. You don't intend to actually let them die, though — just make them confront their own helplessness in the face of a greater power, just like you have had to, and perhaps provide you some concessions in order to release them. 

Even with all your practice, the arrival and assistance of \cCurse{\intro}, who is a commoner just like you, will provide a key component of your plan, and is the biggest reason you have to complete it this weekend; the College's resident curse expert, \cPrince{\intro}, is \pFarm{} royalty, and therefore unlikely to be sympathetic to your cause. You have been exchanging letters with \cCurse{} for some time and have found \cCurse{\them} to be brilliant cursemaker and an excellent, albeit curmudgeonly, mentor; you are hopeful that \cCurse{\they} will be willing to give you the help you need, though you have not told \cCurse{\them} about your plan yet. It's not that you dislike \cPrince{} personally. \cPrince{\Theyhave} been an excellent Curse Breaking teacher and something of a mentor too; you just don't trust royalty. The biggest wrinkle in this plan is that your kidnappers are, of course, related to \cMusic{} and now that you've had the chance to get to know \cMusic{\them} more, you find you like \cMusic{\them} very much. As such, you've gone to significant trouble to start the preparations for a counterspell for \cMusic{\them} that can shield one person from the effects of the curse. No need to punish the good with the bad.

You have confided in your best friend \cLibAssist{\intro} about your plans to curse your “adoptive family,” and \cLibAssist{\theyhave} supported you all the way. \cLibAssist{} comes from a disgraced noble family and is every bit as bitter about \cLibAssist{\their} lot in life as you. \cLibAssist{\Theyare} devious, ruthless, and ambitious, but seem\cLibAssist{\verbs} to genuinely care for you as a kindred spirit, and you care for \cLibAssist{\them} in turn. You two know that power is something that you have to take into your own hands, as life will constantly work to defeat you. You have hatched other plans together before, but this is the most serious. 

Of course, to hold on to any advances you make, and to make it through the defeat of your ``adoptive family,'' you'll need to start building your own base of authority outside of them. Many of the most powerful and successful people in the \pFarm{} are alumni of the \pSchool{}. Earning the most Voting Stones for where to send the Storm would indicate that you have the favor of the teachers and advisors. You'd be well on your way to carving out a place for yourself in \pFarm{} society, from which you could implement all kinds of improvements. Which is to say nothing of how much peace of mind it would give you to be able to personally direct the Storm away from your homeland. After all, the common folk who work the land will always bear the brunt of the harm.

And then there is the matter of your friends \cDisney{} and \cPirateChild{}. The three of you have become fast friends during your time at the \pSchool{} and get up to all sorts of mischief. \cDisney{} is just so innocent and idealistic, hails from a commoner background just like you, and truly wants to help people. And \cPirateChild{} is full of passion, irreverence, and bitterness about the ways \cPirateChild{\their} own society (the \pShip{}) is broken and unjust, so the two of you see eye-to-eye on a lot of things. Both of them approached you a month ago with a ridiculous dilemma. They had gotten ahold of a sea serpent egg, and actually decided to keep and hatch it! You can't leave those two alone for five seconds before they manage something preposterous. The magically inclined members of your ``adopted'' family specialize in charms of protection, primarily illusions of the highest quality that make one thing look like another. Willingly or not, you learned the family trade, and are adept both at creating such charms and spotting them on objects, though breaking such enchantments is something you are still practicing. To keep \cDisney{} and \cPirateChild{} from getting in trouble, you agreed to use your magic to disguise the sea serpent egg as a stuffed animal. The illusion took a week to make and cast and worked quite well as long as the egg remained an egg. But now it has hatched! Casting illusions on living things is \emph{much} harder, and takes even longer. The illusions also don't last nearly as long (not fair), and anything the creature does will be modeled in the illusion. Your stuffed animal illusion has already faded, so it's best to keep the sea serpent hatchling hidden in the secret compartment behind one of the bookcases in the student lounge for now.

\cDisney{} and \cPirateChild{} aren’t the only ones who have approached you for magical assistance. You have become known at the \pSchool{} as an excellent cursemaker and breaker, and as a student you are often a friendlier face than the cursebreaking teacher, \cPrince{}. Still, your correspondence with \cCurse{} has taught you never to undercharge when the rich and privileged are involved. You know some students resent this. Take \cInitiate{\intro}, a third year Wave Rider student, for example. From a deeply privileged upbringing, when \cInitiate{\they} came to you with a bad luck curse asking for help, you of course asked for quite a high rate. \cInitiate{} seemed affronted you would not just help \cInitiate{\them} out of the goodness of your heart and a desire to ``stick it to the \pFarm{} nobility.'' \cInitiate{\They} would not be more specific than that for some reason, and you don’t want to not get what you are worth. You think \cInitiate{\theyare} probably upset at you, but as \cLibAssist{} reminded you, that is the price of doing business. 

Speaking of people you don’t get along with, \cDisney{} is also friends with \cTechStar{\full}, a brilliant inventor and, as the winner of the Tech Star Competition, a member of the High Council of the \pTech{}. You try to be polite for \cDisney{}’s sake, but it's hard not to dislike someone who is so embedded in traditional power structures. The \pTech{} dragged your nation into this terrible war, and you hold its government responsible along with your own for the death and destruction that has ensued. Not that the \pShip{} themselves are blameless here either. The Warlord's \cWarlordDaughter{\offspring}, \cWarlordDaughter{\intro}, attends the \pSchool{} too, and it's hard to look at \cWarlordDaughter{\them} without feeling your blood boil by mere association. 

You do try not to judge someone by their family, but it’s hard, even though you certainly wouldn't want to be judged by your adoptive ``family’s” behavior. Especially by \cEvilNemesis{\intro}’s behavior, the family’s most ruthless power broker who purportedly ordered a rival’s house burnt down twenty or so years ago and got someone killed. Even though \cEvilNemesis{\they} got a taste of \cEvilNemesis{\their} own medicine some eight years go, \cEvilNemesis{\their} legacy lingers and the \cAdopted{\formal} family is feared and revered in equal measure across the \pFarm{}. And you know that the students from other nations sometimes give your best friend \cLibAssist{} a hard time because of some of the things \cLibAssist{\their} siblings did while serving on the warfront. You know that is wrong and you stand up for \cLibAssist{} whenever you can. Honestly, it makes you two closer than ever, knowing your families both have issues that are neither of your faults, but yet you must suffer the consequences.

All in all, despite the various obstacles and troubles, you're hopeful that you'll be able to make meaningful connections with your real family, improve their lives with healing magic, and punish those who have wronged you. All you've got to do is survive the Storm, and not get kicked out for helping to hide a baby sea serpent!

\begin{itemz}[Major Goals]
    \item Finalize the Curse against your kidnappers with \cLibAssist{}’s help and ensure that \cMusic{} will be immune. If you end up needing the help of an advanced cursemaker, you’ll have your choice between \cPrince{} and \cCurse{}.
    \item Find a place to belong.
    \item Create a way to record music that will retain its healing magic. Maybe you can convince \cInterpol{} to help you finish the invention? To really make healing more widely available to the masses you will also need a way to mass produce your invention. For that you will need to find help from the \pTech{}.
    \item Decide what to do about your romantic feelings for \cScholarship{}, and see if there is some way you can help \cScholarship{\them} escape \cScholarship{\their} terrible mentor, \cAntiChup{}.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Acquire a pair of VidCom devices either directly or indirectly from \cTechStar{} and leave game with them so you can reconnect with your birth family \emph{(OOC: such reconnection would happen in in epilogue)}.
    \item Acquire as many Voting Stones as possible and make sure that the Storm does not get directed at the \pFarm{}.
    \item Help \cPirateChild{} and \cDisney{} with the newly hatched sea serpent baby. You all could get in huge trouble if it were to get loose or fall into the wrong hands, so it’s up to you to be the responsible friend!

\end{itemz}

\begin{itemz}[Notes]
    \item You are a first year student.
    \item There is a greensheet associated with the Bookcase in the Student Lounge where the baby sea serpent is hidden. This greensheet will explain how to take care of the baby over the course of the weekend. Your S-Score (1) allows you to freely view the sign hidden by the Bookcase sign, and access the greensheet.
\end{itemz}

\begin{contacts}
    \contact{\cMusic{}} The Music teacher, and extended family to your ``adopted'' family. \cMusic{\They} will be hit by the curse you are preparing unless you can do something to prevent it, and while \cMusic{} can be a little annoying (e.g. you can tell \cMusic{\they} disapprove\cMusic{\verbs} of your friend \cLibAssist{}), \cMusic{\Theydo}n't deserve to be cursed.
    \contact{\cLibAssist{}} Your best friend and accomplice in the plot to curse your adoptive “family.”
    \contact{\cPirateChild{}} Your reckless \pShippie{} friend. \cPirateChild{\They} smuggled a sea serpent egg into the school as a gift for \cDisney{}.
    \contact{\cDisney{}} Your idealistic \cDisney{\cleric} friend. Received a sea serpent egg as a birthday gift from \cPirateChild{}, which has now hatched!
    \contact{\cTechStar{}} A brilliant inventor and member of the High Council of the \pTech{} whom you are not overly fond of. Still, you may need \cTechStar{\their} help if you are going to secure a pair of \cTechStar{\their} VidCom inventions which would allow you to communicate with your birth family. 
    \contact{\cScholarship{}} A student from the \pTech{} whom you have been connecting with over having emotionally abusive guardians you both want to escape from. \cScholarship{\They} also happen\cScholarship{\verbs} to be super cute and you find yourself developing romantic feelings for \cScholarship{\them}.
    \contact{\cInterpol{}} The Magical Combat teacher, whom you think might be sympathetic to your goal of making magical healing available to the masses without reliance on the Clergy.
    \contact{\cPrince{}} The school's Curse Breaking teacher and an occasional mentor of yours, though you don't entirely trust \cPrince{\them} due to \cPrince{\their} royal pedigree. 
    \contact{\cCurse{}} The greatest cursemaker in all of \pEarth{}, a fellow commoner, and solid mentor of yours whom you feel you can rely on.
\end{contacts}

\end{document}
