\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cInterpol{}}

You are \cInterpol{\intro}, a 32 year old secret agent who is glad to be back in the field. You are a high ranking member of the Order of the Black Crocus, under cover at the \pSchool{} as the Combat teacher. Your current, crucial mission is to infiltrate the \pGoaties{} and stop their plot. This would be easier if you didn't find yourself agreeing with the \pGoaties{} more often than not.

You know their words are propaganda, but even so, they're hard to resist. They speak about how \cFarmGod{} has forsaken the common people, and you're not sure you disagree. Too often, the prayers of the common people go unanswered, while the nobility seem to receive a glut of divine favor, making it very clear that the system is out of balance. Not that balance is everything (that's a very \pShippie{} belief), but surely a \cFarmGod{\God} owes something to all of \cFarmGod{\their} followers — not just the ones who can afford the biggest tithes. The \pGoaties{} seem to be offering a nearly perfect solution, true equality for all people. Such a lofty ambition seems a little\ldots{}too perfect, and the group has been rumored to have its fingers in a \emph{lot} of shady business — everything from assassinations to black market curses. But still, that's why you are here — to find out if it really is too good to be true.

In your early years, you were a moderately powerful magic user from a moderately powerful family — nothing particularly special. You loved (and still love) music, and even briefly considered joining the Priesthood for the monopoly they hold on the musical art of healing magic. Ultimately, it was that very monopoly that changed your mind — while you will always revere music as something sacred, you couldn't help but feel that if healing magic was available to the masses, it would be better for everyone. You didn't want to be part of a system that kept such a basic human need in its own tightly clenched fist. Ah, the idealism of youth. 

So instead, you followed the path of least resistance, working hard in school and the game of courtly intrigue. An unexpected twist came when you were recruited by the Order of the Black Crocus, a secret international law enforcement entity with jurisdiction across all three nations. Your questioning of the status quo and hope for a more just world no doubt helped, as the Order frequently operated outside the strict letter of the law in favor of pragmatism and justice. Given access to equipment and information, you accomplished a number of rather remarkable things. Single handedly saving an orphanage and shutting down an organized crime ring — it was all in a day's work for you. But you were too effective for your own good. Your superiors pulled you off of field work much too soon, and stuck you behind a desk managing other agents.

But then the war happened, and the Order of the Black Crocus, previously an international organization, splintered. Greatly reduced in personnel and resources, you've struggled somewhat since to find direction. To your chagrin, direction was imposed on you when the Spymaster of the \pFarm{} absorbed the local remnants of the Order of the Black Crocus into their own spy network. You are now expected to collect secrets on the other nations and report them to the Spymaster. Fortunately, the Spymaster is also concerned about the rising threat of the radical religious cult known as the \pGoaties{}, a clear and present danger to the current power structure. With no one better suited to the task of intelligence gathering and your roster as diminished as it was, you managed to assign yourself the field position on this case. All the threads seemed to be leading towards the \pSchool{}, so four years ago you forged the papers you'd need to infiltrate the school as the magical combat teacher.

You soon found that you aren't as rusty as you feared. It quickly became clear that the \pGoaties{} are quite active at the school. You've got some pretty good leads on infiltrating the \pGoaties{}, although it took a few years. This group is good at covering their tracks. Very good. Your top three suspects are \cChupInventor{\full}, the Political Science teacher, \cHistory{\full}, the History teacher, and \cPirate{\full}, the Shop and Crafting teacher. \cChupInventor{} frequently sneaks off to the Old Wing of the \pSc{} carrying magitech parts and smuggles contraband in and out of the college. \cHistory{} smuggles clandestine messages in and out of the college and is alarmingly good at sneaking around undetected. And \cPirate{}, despite dating \cPrince{\full}, clearly has radical leanings, as well as a forged identity. You have also figured out that the group's symbol is a four-leaf clover. Now that you have some leads, it's time to take the dangerous but necessary step of actually infiltrating the \pGoaties{}.

To combat the fact that you have no history with the group up to this point, you've prepared yourself to pose as an Avenger. An Avenger is an obscure concept, talked about only in the quietest whispers — a person who kills on behalf of the God \cGenesis{} and is forgotten by others instead of forgetting themselves. Your cover story is that you have been killing so many targets for the group that even the group's members have forgotten you — and, conveniently, you're just one assassination away from being forgotten by existence entirely, and are understandably reluctant to take that last step.

With this cover, you hope that you can determine the true intentions of the \pGoaties{}, and fast. Your sources suggest they are planning something big for this weekend. If they mean to elevate \cGenesis{} to the same rank as the other Patron Deities as a \cGenesis{\Deity} of Luck on the side of the common folk, that's something you can get behind. You may even be willing to risk your career to let it slide or even help them. But if they are up to something else — assassinating heads of government, destroying priceless artifacts at the \pSchool{}, or doing something that would make life harder for the masses — that you cannot allow. If you find that to be the case, you must bring them back to the \pFarm{} for interrogation. Dead people don't talk, and leads released into the custody of other nations have a distressing tendency to escape before you get your turn. If you are unable to capture the \pGoaties{}, then foiling any plans they have that would harm the masses and successfully infiltrating the group so you are a properly embedded double agent will suffice.

One of the scenarios that scares you the most this weekend is someone absconding with or misusing one of the six Relics, the most likely culprits being the \pGoaties{}. Each one is powerful and dangerous in its own right, and if at least three of them aren't on hand for the Ritual to Control the Storm, the destruction could be catastrophic. It is therefore of paramount importance that the Relics stay present, attuned, and intact. The \iScythe{} especially is a potent weapon, capable of killing almost any entity that meets its blade, no matter how powerful.

Additionally, you know that if someone wanted to interfere with the ``Time of Deciding,’’ another vulnerable point is the bunkers that protect those who remain at the school from the Storm Surges. If the bunkers were to be damaged, it would jeopardize the safety of all who remain on campus. You have no idea how people managed before the bunkers were created and installed. Therefore, you intend to do what you can to keep an eye on the bunkers, and help their designer, \cBunker{\full}, maintain them this weekend. Anyone trying to interfere with such processes should be viewed with suspicion.

Posing as a teacher has come with its own set of challenges. You knew being a teacher was hard work, but you weren't prepared for the students to require so much reassurance and guidance. Some students you have become quite fond of. Others test your patience daily.

You have found yourself with a favorite student, \cDisney{\full}. \cDisney{} is just so\ldots{}pure and innocent, full of idealism and hope for a better world. \cDisney{\They} remind\cDisney{\verbs} you of yourself when you were younger, and you intend to support \cDisney{\them} however you can. One way of doing so would be to give \cDisney{\them} your Voting Stone. \cDisney{} is one of the few people you would trust to make a truly selfless decision about where to send the Storm, and just try to do whatever will serve the common good. Another student who has garnered your special attention, though for entirely different reasons, is \cAdopted{\full}. \cAdopted{} struggles greatly in your class, and is terrified of combat. You continue to help \cAdopted{\them} as much as you can, and believe \cAdopted{\they} hold\cAdopted{\verbs} great potential if \cAdopted{\they} can learn to overcome \cAdopted{\their} fears. 

On the opposite end of the spectrum is \cPirateChild{\full}, a student who is clearly also a thief, and a good one at that. Good enough to get in and out of \cChupInventor{}'s office undetected — something even you have yet to manage. Maybe \cPirateChild{} could be persuaded to help you somehow in your investigations? At least then \cPirateChild{\their} mischief would be serving a purpose. And then there is the shady behavior of \cLibAssist{\full}. You're not sure why, but you're certain that \cLibAssist{\theyhave} been shadowing you. You need to find out what \cLibAssist{\they} know\cLibAssist{\verbs} (or thinks \cLibAssist{\they} know\cLibAssist{\verbs}) and find a way to keep it from getting out if \cLibAssist{} somehow knows something inconvenient. Either that, or give \cLibAssist{\them} a better offer and recruit \cLibAssist{\them} to the Order of the Black Crocus. You have to admit, the kid’s got skills.

You've also made friends in your time here, such as the Music teacher, \cMusic{\full}. While \cMusic{\theyare}n't a \cMusic{\cleric} \cMusic{\themself}, \cMusic{\they} understand\cMusic{\verbs} music's value and its place in religion. \cMusic{\Theyhave} a special dispensation from the Church to teach music even though \cMusic{\theyare} not a Cleric. The two of you have bonded over your shared reverence for music. You're happy to help \cMusic{\them} if they need something, or just be a listening ear. 

You also established a rapport with the Librarian, \cLibrarian{\full}, from nearly the beginning. \cLibrarian{\Theyare} wise, compassionate, and deeply dedicated to both the preservation of knowledge and the mentoring of future generations. Over time, the two of you seamlessly transitioned from casual friendship to close friendship to, just in the past year, lovers. You even found yourself moved to break Rule Number 1 of spycraft and reveal your secret identity and true purpose at the school, and \cLibrarian{\they} didn’t reject you when \cLibrarian{\they} found out. Still, you both wanted to take it slow and didn't tell anyone else about the relationship. 

Everything seemed perfect with \cLibrarian{}, until just last night when you both returned from the pre ``Time of Deciding’’ break. The blank look on \cLibrarian{\their} face when \cLibrarian{\they} saw you told you everything you needed to know — your beloved partner had been afflicted with amnesia. When you asked \cLibrarian{\them} point blank, \cLibrarian{\they} admitted to having lost \cLibrarian{\their} memories. Amnesiacs are often discriminated against as murderers (which they almost always are, but nuances like self defense often get lost in the court of public opinion). Since that day, your thoughts have been in turmoil. Could \cLibrarian{} really have killed someone? The person you know and love would only have done that as an absolute last resort, and only in self defense or defense of another. As a seasoned spy and combat teacher, you are well acquainted with violence and split second decisions. You resolved to help \cLibrarian{} however you can, including keeping \cLibrarian{\their} amnesia a secret. Maybe the gods will be merciful and restore \cLibrarian{\their} memories in time. In the meantime, you have to decide what to do about your relationship. Do you even have a relationship if the other party can't remember it? You haven't told \cLibrarian{\them} about it, and you're not sure you should. It breaks your heart to start from scratch, but you can see that \cLibrarian{\theyare} still the same beautiful person you fell in love with. If it was truly meant to be, then it will form again organically. You hope.  

This will be a busy and trying weekend. Not only do you need to infiltrate a cult (and decide what to do once you're there) and keep your own secrets under wraps, but you also need to look after your amnesiac lover and try to rebuild your relationship. It will be a lot to handle, but you're used to that. You're the best of the best, and you intend to prove it.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Infiltrate and assess the true intentions of the \pGoaties{}. Stop their plan if you deem it unjust, and capture the group members to bring home for interrogation if you can.
    \item Help keep \cLibrarian{}'s amnesia under wraps, help \cLibrarian{\them} recover \cLibrarian{\their} memories if you can, and try to rebuild your relationship.
    \item Keep the Relics safe; they are needed for the Ritual to control the Storm, and each one could prove incredibly dangerous in the wrong hands.
    \item Help \cBunker{} maintain the Bunkers that protect against the Storm.
    \item Find out what, if anything, \cLibAssist{} has on you, and possibly recruit \cLibAssist{\them} and/or \cPirateChild{} to the Order of the Black Crocus.
    \item Decide which student to give your Voting Stone to.
    \item Support anyone trying to make magical healing more readily available.
\end{itemz}

\begin{itemz}[Notes]
    \item You are the magical combat teacher at the College of the Gods.
    \item You are relatively new to the school, having taught here for only four years. You were too junior three years ago to be selected to stay for the ``Time of Deciding,’’ but this year you made damn sure you would be present.
    \item International espionage is a thriving trade these days, and given the pivotal events happening this weekend, you would not be at all surprised if spies from all three nations are present, presumably among the advisors.
\end{itemz}

\begin{contacts}
    \contact{\cChupInventor{}} The Political Science teacher, and one of your top three suspects for being a member of the \pGoaties{}. Frequently sneaks off to the Old Wing of the college carrying magitech parts and smuggles contraband in and out of the college.
    \contact{\cHistory{}} The History teacher, and one of your top three suspects for being a member of the \pGoaties{}. Smuggles clandestine messages in and out of the college and seems to be alarmingly good at sneaking around undetected.
    \contact{\cPirate{}} The Shop and Crafting teacher, and one of your top three suspects for being a member of the \pGoaties{}. Despite dating \cPrince{\full}, \cPirate{} clearly has radical leanings, as well as a forged identity.
    \contact{\cLibrarian{}} The school’s wise and compassionate Librarian, your former(?) lover, and now, a total amnesiac. 
    \contact{\cMusic{}} Your teacher friend who you share your love of music with.
    \contact{\cAdopted{}} The student who struggles the most in your magical combat class. You believe \cAdopted{\they} hold\cAdopted{\verbs} great potential, though.
    \contact{\cDisney{}} Your favorite student, a hopeless idealist who reminds you of your younger self.
    \contact{\cPirateChild{}} A mischievous student who is clearly a thief, and whose services you are interested in employing for your espionage work.
    \contact{\cLibAssist{}} A sneaky student who has been shadowing you. You want to figure out what \cLibAssist{\their} game is, and if possible, recruit \cLibAssist{\them} to the Order of the Black Crocus.
\end{contacts}


\end{document}


