\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cAmbition{}}

You are \cAmbition{\full} (\cAmbition{\they}/\cAmbition{\them}), and 20 years old. It's your second year at the \pSchool{}, and you feel like that should mean you have things figured out, but you are still very much trying to find your place in this world. You pride yourself on your ambition and drive, and you're smart enough to play your cards right, but you wonder if the \pTechies{} will ever fully recognize you or let you reach your full potential. The \pSchool{} is where you can find out where you truly belong, and grab your destiny with both hands. Hopefully.  

You grew up in an upper middle class family,  but knew you were adopted as a baby.  You were the oldest, adopted when your parents thought that they could not have children.  After you were adopted though, they had two of their own.  While your parents took care of you materially as best they could, you felt that they always favored your younger siblings.  You don’t hate them, but it left you alone, emotionally isolated, and feeling separated much of your teenage years.  The desire to know who your parents were, to speak to them, to know why they gave you up,  and to tell you that they still loved you, has always been there, haunting your mind. Perhaps they are no one, but you feel in your bones that they are someone important to the world, to society. Maybe this is because of the great magical talent you possess, and the deep drive you feel, which you used to get yourself to the \pSchool{}.   Perhaps it is because your parents admitted to you on your last break that an anonymous donor has been helping to pay your tuition to the \pSc{}. Regardless of why, you know that you are meant for great things, and that finding your parents will only help you on your journey.  

You met your best friend \cHeir{\full}, the heir of the elite \cHeir{\formal} family, after arriving at the \pSc{}. Where you have always wondered about what your destiny would be, \cHeir{} has known from birth, and always felt trapped by it. (Well, technically \cHeir{\their} destiny changed 6 years ago, but we’ll get to that; it still involves a place in the \cHeir{\formal} family.) Despite your wildly different relationship to fate, when you met \cHeir{\them}, it felt as if you were finding a missing piece of your own life. \cHeir{\They} hated being tied down, stuck in an arranged marriage, at the whim of their deeply powerful family. You two bonded over your feelings of being out of place and deep interest in other cultures of \pEarth{}. 

Best friend or not, it still shocked you when a few months ago \cHeir{}, seriousness etched in every line of \cHeir{\their} face, asked you to take the position in \cHeir{\their} place. You asked \cHeir{\them} why, but \cHeir{\they} simply said it was because \cHeir{\they} knew you would do right by the family and \cTechGod{}. \cHeir{} explained that if the two of you could get the right pieces in place, there was a ritual that would make you into an equivalently valid heir to the family. Then it's just a matter of convincing \cHeir{}’s \cDiplomat{\auncle} and representative of their family, \cDiplomat{\full} to officially recognize you on behalf of the family. This will free \cHeir{} to live life \cHeir{\their} way, and place into your hands the power to run the industry leading \cHeir{\formal} Tech and Manufacturing Company. Better still, the position comes with the \cHeir{\formal}'s seat on the government's Council, meaning you would be a central part of your country's government. And best of all, a clear place to belong.

This seems far too perfect to be true. You have met \cFaledonParent{\full}, \cHeir{}’s \cFaledonParent{\parent} before on a few occasions when you attended a \cHeir{\formal} family dinner as \cHeir{}’s guest, and the two of you had sleepovers after. The dinners were uncomfortable, as \cHeir{}'s \cFaledonParent{\parent} seemed to not trust you. But having you there made \cHeir{} feel better, and you were happy to support your friend. \cDiplomat{\full}, \cHeir{}’s \cDiplomat{\auncle}, on the other hand, seemed to be very curious about your time at school and your future. You found yourself greatly admiring \cDiplomat{\them} and at the most recent dinner almost trusted \cDiplomat{\them} with your and \cHeir{}’s plan about the heirship. But \cHeir{} is adamant that \cDiplomat{} is tight with \cDiplomat{\their} \cFaledonParent{\sibling} and would not support the plan. It’s almost funny to think of a 50 year old \cDiplomat{\person} snitching on \cDiplomat{\their} \cHeir{\nibling} to \cHeir{\their} \cFaledonParent{\parent}. But \cHeir{} has known \cDiplomat{} \cHeir{\their} whole life, and you have only met \cDiplomat{} a handful of times over dinner. You trust \cHeir{}’s judgment.

Still, you worry about the plan to take over as heir if you cannot get \cDiplomat{} on your side. An uncooperative \cHeir{\formal} family could stymie your efforts and those of your friend. \cDiplomat{} will be at the \pSchool{} over the ``Time of Deciding,’’ so this is your big chance. You've got to get in on whatever meetings are occurring and contribute in such a way that \cDiplomat{} will take note and be impressed by you. The treaty talks are probably a good place to start since \cDiplomat{\they} forged the treaty between the \pTech{} and the \pFarm{} eight years ago. \cDiplomat{\They} will surely have a vested interest in any talks happening this weekend.  You don’t quite know how to get involved in the treaty talks, but \cHeir{} might know a way?

For the first year after \cHeir{} proposed it, you were sure that the one and only answer to your problem was to take over as heir. However, attending the \pSchool{} has broadened your horizons and  made you aware of so many more interesting places and people. You have been making friends with many of the students, trying to answer the question, if the \cHeir{\formal} family can’t be your home, then what could? You know that if you backed out of taking over for \cHeir{\them} that \cHeir{\they} would be very disappointed and maybe even upset at you. But if it’s clear that taking over as Heir isn’t going to work out, you hope that \cHeir{} will still support you in finding a place to call home.


The \cAmbition{\formal} family was never particularly pious, so you didn’t grow up close to the \pTech{}’s religion but you have started regularly studying and attending services with your fellow student,  \cScholarship{\full}. You feel a bit distant from the Church’s magitech focus, as you are no great engineer. But you have bonded with \cScholarship{} (who isn’t particularly engineering minded either, and still has a place) and you have begun to wonder if you could find a family within the faith. The two of you had not dis-similar starts in life. \cScholarship{} was just adopted into the Church Youth Program, instead of into a private family. 

As part of exploring faith as a possible found family, you would need to speak with the Clerics. It would be amazing to talk to \cAntiChup{\full}, who is literally \cTechGod{}’s Grace - the head of the church! But \cScholarship{} seems reluctant to introduce you to \cScholarship{\their} mentor. Still, maybe if you can catch \cAntiChup{\them} and \cScholarship{} in the same room, \cScholarship{\they} can arrange a positive introduction. 

You also have heard that the \cBeetle{\Cleric} of \cTechGod{}at the \pSc{}, \cBeetle{\full}, and \cAntiChup{} don’t always see eye to eye. \cBeetle{} does not seem to like your friend \cScholarship{}. You can’t possibly fathom why; \cScholarship{} is great. Maybe \cBeetle{} is just jealous of \cAntiChup{} and is taking it out on \cScholarship{}? This makes you not trust \cBeetle{}, and maybe if you decide that the priesthood is for you, you could prove your worth by bringing \cBeetle{} down a notch. You know \cBeetle{\theyare} running for principal, and that may be an angle of leverage. Besides, from what you can tell, \cBeetle{\they} had one of those charmed lives of love and belonging. \cBeetle{\They} don’t understand what life is like for people like you or \cScholarship{}.

There is, of course, also the matter of voting for where to send the Storm and conducting the ritual to control it, which is the whole reason for this weekend's events and guests. Rituals impress religious folks, right? You've already volunteered to help with the preparations for the ritual, overseen by the Librarian, \cLibrarian{\full}. This is a prime opportunity to earn recognition and hopefully connections. Something that gives you a leg up in this is being the 1st assistant librarian. You will be able to help your fellow students and even your teachers navigate its dangers.

 When you first started hanging out in the library, you didn’t expect to find yourself growing very fond of the Librarian, who, of all the teachers, has acted as a friend, advisor, and voice of kindness. If there was not the call in your heart for recognition and fame, maybe you could be a librarian yourself. You knew you were spending an unusual amount of time in the library for a student when you almost walked in on \cInterpol{\full} and \cLibrarian{} kissing late one night. I guess teachers also can like each other?

 Since returning from this last school break, you have grown concerned with the Librarian’s behavior. \cLibrarian{\They} seem\cLibrarian{\verbs} to be relying on you and \cLibrarian{\their} two other assistants, \cPresident{\full} and \cLibAssist{\full}, for far more of the daily functions of the Library, and you found \cLibrarian{\them} wandering in a particularly dangerous area of the stacks aimlessly this morning.  The sudden distance between you and \cLibrarian{} is disconcerting and you don’t like it. 

Aside from wanting to reconnect and figure out what happened since you care about \cLibrarian{} as a friend, helping  \cLibrarian{\them} would probably help you keep your position as First Assistant.  The Second Assistant \cLibAssist{\full} is constantly trying to undermine you. You think that \cLibAssist{\they} want to be the School Librarian once \cLibrarian{} retires and are waiting to pounce. \cLibAssist{\They} actually almost succeeded once. \cLibAssist{} accused you of having used your library privileges to take a book from the 3rd Tier just before the last school break of the library and not return it. It's not a full lie — you did it because you needed to find some research on a project you are helping \cFlowPriest{\full} with, but you always intended to return it. You just can’t right now, because you apparently used all your luck getting into that space the first time. 

You need to make sure the book is returned before the Librarian finally follows up on \cLibAssist{}’s accusations. And then you can turn it all around on \cLibAssist{}. \cLibAssist{\They} shouldn’t have been down in that part of the library alone either. Maybe it is a touch petty , but you know things that \cLibAssist{}’s family has done that led to trebuchet malfunctions and unnecessary harm and death in the war, and it gives you little tolerance for \cLibAssist{\their} attempts to undermine you. 

You have even begun considering whether your place might lie beyond the borders of the \pTech{}. You know this possibility would perhaps not be looked upon favorably by your fellow \pTech{} students, but you have started to talk more and more to some of the \pShip{} teachers, especially \cFlowPriest{\full, the mathematics teacher and cleric of \cFlow{}.  \cFlowPriest{} encouraged your exploration, and you started to have regular tea.  


The more you hear about what \pShippies{}’ families are like — large, ever changing but caring, with space to move — the more you wonder if this is a place you could belong. But you know that emigration is hard, and with the war on, it would be seen as an act of betrayal to the \pTech{}.  }\cFlowPriest{} has also explained the precepts of \cEbb{} and \cFlow{}, and honestly they seem more your style than those of \cTechGod{}, especially their focus on “for every action, a reaction,” and equality. And the  Is that blasphemous? They are all Patron Deities, all part of the same pantheon, but nations and patrons are synonymous. So you’re back to square one on needing to immigrate if you wish to take up the philosophies of \cEbb{} and \cFlow{}. . You would need to do something major for the \pShippies{} to welcome you, but surely you can think of something, and the \pShippie{} advisors can advise you if you choose to pursue this possibility.


Seeing your interest in \cFlowPriest{\their} religion and open mindedness, as well as how hard you work, \cFlowPriest{\they} let you in on a plan \cFlowPriest{\they \ have} apparently been working on for years. It sounds impossible, but if it works it may solve all your problems. It is well known that the Gods live in the Divine Realm and no human can reach them. At least, that is how it currently stands. But \cFlowPriest{} hopes to change this. \cFlowPriest{\They \have} been working on magically manipulating beans that could grow overnight and create a bridge to the Realm of the Gods, thus allowing people to speak directly to them! And \cFlowPriest{\they} want\cFlowPriest{\verbs} your help on this important — and very secret, very not very legal — work. You very much want to be one of the first to use this to travel to the Divine Realm. But you are smart enough to keep your participation quiet, lest this fail and you are left with a mark against your name. Surely you will succeed, though, as your collaborators include one of the most skilled Cursemakers in all of Cengea, \cCurse{\full}, and a brilliant young \pTech{} scientist, \cAssistantScientist{\full}. If you can get to the Divine Realm, maybe you can finally figure out what path you should tread. If anyone knows, it would be the Gods, right? 

You're also looking forward to the opportunity to participate in this year's Ceremony of Excellence, which the music teacher \cMusic{\full} is organizing. The combat demonstration presents a great opportunity for you — not only as a way to present your prodigious magical skill to the world, but also to demonstrate your ability to exert the influence needed to get selected. You'll need to be proactive to make sure you are one of the students chosen by \cMusic{}. Perhaps you can get your good friend \cChupStudent{\full} to participate as well? You are tired of \cChupStudent{}’s charade of not being particularly intelligent.

At first glance \cChupStudent{} seems not particularly intelligent — but in reality, \cChupStudent{\they} \cChupStudent{\are} much stronger and smarter than \cChupStudent{\they} let\cChupStudent{\verbs} on. You know this because you saw \cChupStudent{} after class one day, engaged in a complex and deeply nuanced conversation with \cChupSecond{}, the economics teacher. You don't understand this stance in the least — what benefit does someone get by hiding their true competence and missing out on the opportunities that competence can bring? You confronted \cChupStudent{\them} about this, and \cChupStudent{\they} admitted that \cChupStudent{\they} prefer\cChupStudent{\verbs} to just coast by if possible except when needed. Since then you two have had many fascinating conversations, and \cChupStudent{\they \have} even asked for your help with some library research (just secretly getting down to some of the deeper, more dangerous parts of the library without the Librarian finding out. You know, the kind of thing that could get you dismissed from your position as library assistant if you get caught. Maybe you should have asked why \cChupStudent{} needed this before sticking your neck out for \cChupStudent{\them}?) \cChupStudent{\They} owe\cChupStudent{\verbs} you for keeping quiet about this for so long, and you want to have everyone finally see how smart \cChupStudent{\theyare}.

As \cChupStudent{}’s family is a powerful noble house in the \pFarm{}, whose support for the \cQueen{} is never in doubt, being in their orbit has also brought you into the orbit of \cPrince{\full}. \cPrince{\They} may not be the current ruler, but you admire \cPrince{\their} cleverness, \cPrince{\their} ambition, and \cPrince{\their} desire to do right by \cPrince{\their} people. You are fascinated by curse breaking, though it is an area that does not come naturally, and have done your best to impress \cPrince{\them} in class and make sure to have \cChupStudent{} speak well of you. Perhaps \cPrince{\they} would take you on as an envoy or a personal aid and let you find your place in the \pFarm{}? The \pFarm{} is much more connected currently to \pTech{} so unlike emigrating to the \pShip{}, it does not feel as much of a fresh start but you love the focus on family and if you could get into a noble position through your efforts, maybe you would not have to worry about your position or even your descendants. 

This weekend is set to be the deciding moment for the most crucial pieces in the puzzle that is your young life. It will take everything you've got to bring this all together. You hope that \cDiplomat{} along with the other advisors who you have not met in person like \cAntiChup{}, and \cAssistantScientist{\full}will see your brilliance and advise in person about the best course of action, whether that is prioritizing protecting your home, or weighing the pros and cons of actions that might trade short term consequences for the long term betterment of the world. Make your offerings, get to work, and you can claim more than was ever in the cards for one such as yourself. And perhaps you may even find a place where you truly feel like you belong.  

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Complete a ritual with \cHeir{} to become the \cHeir{\formal} Heir.
    \item Talk to your friends in the \pShip{} and \pFarm{} and, using these connections, see if there is a place where you can belong in another nation.
    \item Assist \cFlowPriest{}, \cCurse{}, and \cAssistantScientist{} with the project to reach the Divine Realm.
    \item Convince as many teachers and advisors as you can to give you their voting stone. Decide where you think the Storm should be sent. 
    \item Get involved in the meetings \cDiplomat{} attends and make a positive impact and a good impression.
    \item Figure out what is going on with the Librarian, help \cLibrarian{\them}, and make sure that \cLibAssist{} does not take away your role as 1st Library Assistant.
    \item Prove your worth and skill by taking a lead role in preparations for the Ritual to Control the Storm.
    \item Distinguish yourself during the selection process to get yourself, and perhaps \cChupStudent{}, selected for the combat demonstration during the Ceremony of Excellence.
\end{itemz}

\begin{itemz}[Notes]
    \item Your extensive time in the library gives you advantages over others when navigating the library.
\end{itemz}

\begin{contacts}
    \contact{\cHeir{}} The \cHeir{\formal} Heir, and your friend, with whom you have a plan to trade fates, so to speak.
    \contact{\cDiplomat{}} The Diplomat from \pTech{} who originally formed the treaty with the \pFarm{}. \cDiplomat{\They} \cDiplomat{\are} one of the most important people for you to impress this weekend.
    \contact{\cScholarship{}} A friend of yours with whom you share a lot in common (including being adopted), who is helping you find a spiritual path.
    \contact{\cWarlordDaughter{}} Your main friend among the \pShippies{}, who is trying to forge their own path amidst huge expectations.
    \contact {\cLibrarian{}} Your boss, who has been acting strangely since you all returned from break, and who you want to help.
    \contact{\cLibAssist{}} Your rival for the top Library Assistant position who has tried to ruin your reputation.
    \contact{\cPresident{}} The third assistant librarian. Generally stays out of your competition with \cLibAssist{}
    \contact{\cChupStudent{}} A friend and confidante who adopts a perplexing facade of weakness and stupidity. It's probably time to break \cChupStudent{\them} out of that shell.
    \contact{\cFlowPriest{}} Your spiritual mentor among the \pShippies{}, who has given you an opportunity of a lifetime: to speak to the Gods directly.
    \contact{\cPrince{}} A \pFarm{} teacher who could really jumpstart your life in the \pFarm{} if you impress \cPrince{\them} and choose to go that route..
\end{contacts}

\end{document}


