\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cHeir{}}

You are \cHeir{\intro}, and 21 years old. It's your third and final year at the \pSchool{} — which means that this is your last chance, for so many things. As the reluctant Heir to the elite \cHeir{\formal} family, a family with an exclusive Council seat and a tech and manufacturing empire, your future is all but written in stone, whether you like it or not. At least, that's what they think! You've got a plan they'll all hate but will earn you your freedom, and probably save the company from your own disinterest. You have no desire to run the family business, and would rather enjoy your future in freedom, even if you aren't entirely sure what you'd do with it.

The \cHeir{\formal} family is messed up. From their obsession with power, to the lengths they are willing to go to keep it. Even now you aren’t sure you know the full extent of it, but what you do know only fuels your desire to escape. From the day you were born, your life has been dictated for the benefit of the family. You were betrothed from a young age to the second child of a powerful \pFarm{} noble family, \cChupStudent{\full} - a \cChupStudent{\kid} you hated from the first moment you laid eyes on \cChupStudent{\them}. You studied what your family demanded, foregoing a budding interest in the Church and dismissing fantasies of running away to the \pShip{}. You never questioned your \cFaledonParent{\parent} \cFaledonParent{}, your \cDiplomat{\auncle} \cDiplomat{\auncle}, or your older \cHeirSibling{\sibling} \cHeirSibling{}. That is until six years ago. (You did still resent \cDiplomat{} for arranging the betrothal though!)

Of course, you wouldn't be the \cHeir{\formal} Heir if your older \cHeirSibling{\sibling}, \cHeirSibling{\full}, was still alive. \cHeirSibling{\Theywere} a student at the \pSchool{} six years ago, and died under mysterious circumstances along with \cHeirSibling{\their} best friend, \cKidScientist{\full}, and ten other students right after voting to direct the Storm — the Storm that broke the treaty between the three nations by being sent to the \pShip{} out of turn. 

Six years ago, you suddenly felt a magical compulsion fade. It was a bizarre experience - you’d been under that compulsion your whole life. And now it was suddenly gone. You didn’t understand how or why at first. When your \cFaledonParent{\parent} explained about the generation-spanning blood magic ritual that compels younger members of the \cHeir{\formal} family to have complete loyalty to the family, you were furious! Of all the stupid, illegal, underhanded ways to try to ensure a dynasty! You didn’t speak to your \cFaledonParent{\parent} for a month, even though you were both grieving your \cHeirSibling{\sibling}’s passing.

Your \cFaledonParent{\parent} assured you that you would grow into your new role, and that you would come to understand the necessities of the family’s actions. You never did. Two years later, you fled the \cHeir{\formal} estate and took refuge in \cTechGod{}’s main temple and attempted to join the Church. That lasted only a few weeks until your family forced you back, but in that time you met \cBeetle{\full}, one of the kindest people you know, who was a keeper of the Celestial Beetles of \cTechGod{}. \cBeetle{\They} protected you from your family, and even went to bat for you, though it was for naught in the end. You still wonder if you could get out of all this responsibility, would you return there? Or would that just be trading one prison for another?

Even though the culprits were never found, you are sure that your \cHeirSibling{\sibling} and the students were murdered to cover up some conspiracy. The rest of the world may be content to sweep it under the rug, but you will not leave this school without discovering what really happened to your \cHeirSibling{\sibling} and bringing \cHeirSibling{\their} murderer(s) to justice. You suspect that the one(s) responsible will be here again at this crucial juncture, and you're not going to let them get away \emph{this} time. You and your friend \cPresident{\full} have made preparations to do a ritual that will allow you to gaze into the past with \iMirror{} that will let you see firsthand who orchestrated the Betrayal and murdered all those poor students. (More on \cPresident{} later). You just need to get \iMirror{} away from \cDiplomat{} who is in charge of it.

You never would have even known about the mirror if you had not asked \cLibrarian{} for assistance.  \cLibrarian{} did not ask questions, but pointed you towards \cLibrarian{\their} old friend, and apparently a prominent scholar on magical artifacts, \cWildCard{\full}.  You wrote to \cWildCard{} expecting nothing in return, but instead \cWildCard{\theyhave} been an invaluable help and seem\cWildCard{\verbs} to have taken a personal interest in the project, despite how vague you have been as to what exactly you want to look at in the past. 

It was \cWildCard{} who initially speculated that \iMirror{} might be manipulated to show the past, not just the geographically distant present. The two of you corresponded for months, your theories supplemented with invaluable insights from \cPresident{}, whose skill at navigating the library never ceases to amaze you. Eventually you finalized the ritual you plan to use! You know \cWildCard{} is going to be here this weekend, and, if you think you can fully trust \cWildCard{}, you may ask \cWildCard{\them} to help you actually execute the ritual.

But even if you can find justice for \cHeirSibling{}, the succession to the \cHeir{\formal} empire still falls to you. For now. Barrier one to escaping is that stupid blood curse. Apparently, a distant ancestor of yours wanted to make REALLY sure that there would never be competition for, or absence of, a \cHeir{\formal} Heir. That spell ensures that the oldest child, the Heir, is stuck with the job, and that any full siblings are made too magically loyal to the family to undermine them in any way. Luckily for you, they neglected to make the \emph{Heir themselves} magically loyal to the family in the same way. Their arrogant assumption was that any risk to the Heir would come from the outside, and that the compulsory loyalty of their siblings would help protect them. It never occurred to them that the Heir themself would wish to orchestrate their own removal. 

Your family would like you to believe it's impossible to escape this bond — but through extensive research (in the library of course), you've discovered a way. You can complete a modified version of an obscure ritual involving blood magic (your eyes hurt from rolling so hard at the pearl clutching you expect from the very people who used blood magic to create this mess in the first place). The ritual will allow you to transfer the heirship to another \cHeir{\formal}, and away from you. The ``cost’’ is that you will no longer be part of the bloodline. Some cost! That just means that you won’t go back to being magically compelled to support the family. Seems like a win-win to you.

Of course, the only other \cHeir{\formal} you knew until very recently was \cDiplomat{\full}, your \cDiplomat{\auncle}. You need someone of your generation to take over as heir.  Besides,\cDiplomat{\they} seem\cDiplomat{\verbs} to be doing something \cDiplomat{\theyare} really good at. \cDiplomat{} in \cDiplomat{\their} current role is crucial for the entire world’s chances to survive. You know that \cDiplomat{} has been working with \cHeadScientist{\full} and \cAssistantScientist{\full} to end the Storms forever, and have heard a bit about how that is going, which is surprisingly well. You do want to make sure \cDiplomat{} can finish that work.

This left you in a bind for a few years. But then you met \cAmbition{}, when \cAmbition{\they} arrived at the \pSc{} a year after you. The two of you quickly became best friends. \cAmbition{} even comes over for dinner and sleepovers on school breaks. \cAmbition{\Theywere} raised in a middle class family but you clicked perfectly. No one in your life has ever understood you more, and given your supreme disinterest in the family business, and \cAmbition{}’s brains, you knew almost immediately that \cAmbition{\they} would do a much better job of leading the family and the business than you. The only issue was that only someone of the \cHeir{\formal} bloodline can lead the family, and \cAmbition{} was not related. Or so you thought.  

After the most recent of those family dinner parties over the last school break, you decided to snoop on a conversation between \cDiplomat{} and \cFaledonParent{}. You hoped to learn more about what was actually happening with the Storms and the research into ending them, but you heard something very different. Your \cFaledonParent{\parent} was expressing worry about your \cDiplomat{\auncle} spending time around \cAmbition{}, who you regularly invite to family gatherings when \cAmbition{\they} don’t want to go home for the entire break. You were about to storm in and give your \cFaledonParent{\parent} and \cDiplomat{\auncle} a piece of your mind for being awful about your friend, when you heard your \cFaledonParent{\parent} say, “I will not risk what might happen if \cAmbition{} found out that \cAmbition{\theyare} \emph{your} \cAmbition{\offspring}. Stay in your lane with your pet scientists. You owe the family that glory. Damn your youthful indiscretions that I’m still cleaning up!” 

As you stood in the dark hallway outside the study, your heart pounded in your chest. \cAmbition{} was your cousin! No wonder you were such good friends. Maybe this was even \cTechGod{}’s will that the two of you had met? A chance to restore \cAmbition{}’s rightful place in the family? Although it’s not like the \cHeir{\formal} family is one worth celebrating being a part of.  For a heartbeat you wondered if the two of you ought not run away together and leave the \cHeir{\formal} family high and dry without any heir at all! 

You haven’t told \cAmbition{} the truth yet. You know how very desperate \cAmbition{\theyare} for a place to belong. You fear that this will only feed \cAmbition{\their} feelings of abandonment and having no home. You don’t want \cAmbition{} to spiral out this weekend. There’s no reason you can think of that the \cHeir{\formal} family would have had to give a child up for adoption. Ugh, now you dislike \cDiplomat{} even more. How could \cDiplomat{\they{} \have} done this to your best friend? Maybe you can tell \cAmbition{} after the ritual to transfer the heirship? Or better yet, maybe \cDiplomat{} would feel obligated to admit the truth to \cDiplomat{\their} own \cAmbition{\child} at that point?  

Since you can’t tell your family about any of this, and blood magic is deeply frowned upon in both your homeland and the \pFarm{} (where such magic originates), you'll need to be sneaky about actually executing the ritual. This will be especially complicated this weekend, since your \cDiplomat{\auncle} will be here and your \cFaledonParent{\parent} has written to tell you \cDiplomat{\they} will be conferring the family's Heir Seal (signet ring) upon you. Only one Seal is crafted per generation, and it is permanently bound to the Heir when it is conferred. You need to get the blood ritual with \cAmbition{} completed before \cDiplomat{} can catch you for the Seal ritual, because once that happens it will be too late to trade places. 

Of course, instead of sneaking around, you could open up to \cDiplomat{} about \cAmbition{} and your desires and try to convince \cDiplomat{\them} that \cDiplomat{\their} own \cAmbition{\offspring} would be best for the job. But that would require a lot of trust that you don’t have and maybe some bargaining that you aren’t very good at (and admitting you were eavesdropping). And if it didn’t work, your plan would be dead in the water. Is it worth the risk? 

If you do succeed, you still need to make sure that \cDiplomat{} knows how impressive \cAmbition{} is. Even if \emph{you} don’t like \cDiplomat{\them}, \cDiplomat{\theyare} renowned the world over. \cDiplomat{\Their} endorsement would catapult \cAmbition{} into the perfect spotlight. To accomplish what you expect to be an impossible task, you need to help \cAmbition{\them} get as many teacher and advisor Voting Stones, win a chance to demonstrate \cAmbition{\their} skill in the Ceremony of Excellence, and getting more people, especially prominent \pTech{} officials like \cAntiChup{\full}, the current head of \cTechGod{}’s church, to vouch for \cAmbition{\them} to \cDiplomat{}. 

Towards this goal, you have been pushing \cAmbition{} to write to powerful people, especially those who will be here this weekend. You are a bit worried that your perfect plan may have hit a tiny snag though though, as \cAmbition{} has really taken to the general idea, and has started to spend more and more time working to gain favor with teachers and students \emph{outside} of the \pTech{}. You think that cultural division is garbage, but you also need \cAmbition{\them} to want to stay in the \pTech{} and take over as Heir, or you’ll once again be ``down the mineshaft with no rope‘’ as it were.    

With \cDiplomat{} here, you are worried about how much that means your family will be watching your every move. \cDiplomat{} was involved in the treaty (a.k.a. the Betrayal of the \pShippies{}) that was revealed the week before \cHeirSibling{} was murdered. You don’t want to suspect your \cDiplomat{\auncle} of doing anything to \cHeirSibling{}, as you are sure \cDiplomat{\they} preferred \cHeirSibling{\them} to you, but you know \cDiplomat{\they} would also do anything to keep the family and the \pTechies{} on top. Surely the blood-bond would have prevented \cDiplomat{} from hurting \cHeirSibling{}? You hope your fear is ill-founded. 

As if that's not bad enough, \cDiplomat{} also arranged your betrothal so many years ago to \cChupStudent{}. The \cChupStudent{\formal}s are powerful \pFarm{} nobility, and hold lands on the border with the \pTech{}. They are profiting from the war due to imports and exports between your nation and theirs, and your family believes they will make powerful allies. Much as you resent being used as a political pawn, your feelings about the arrangement have recently become\ldots complicated. As children you and \cChupStudent{} were like oil and water, blaming one another for the betrothal forced on you both by \cDiplomat{} and your parents.

When \cChupStudent{\they} arrived at the \pSchool{} this year, it was more of the same. You loathed every moment of forced proximity, and have not hesitated to make your displeasure known. \cChupStudent{\Theyare} lazy, coasting on impressive raw magical talent, and a winning smile. But they are \emph{hot}. Oh \cTechGod{}, \cChupStudent{} is drop dead gorgeous. It’s not fair! How can someone so wrong for you look so perfect? And on top of it all, you both are in close proximity a lot!  At most meals even!  Because it just so happens that \cAmbition{} and \cPresident{}, your two best friends at the school, also happen to just think \cChupStudent{} is a joy to be around.  And sometimes, sometimes you hear \cChupStudent{} say something that is so insightful, so sharp that it takes your breath away.  You even have caught yourself smiling at \cChupStudent{} (and then quickly making sure to frown at \cChupStudent{\them}.  UGH.  \cChupStudent{\Do}n’t \cChupStudent{\they} hate you?  

This all came to a head this morning, when \cDiplomat{} came to you with a letter from your family. Apparently, in their \emph{infinite} wisdom, they have decided that you're getting married to \cChupStudent{} — this Monday! You weren't even remotely ready to face your feelings (shit, you caught feelings, didn’t you?) yet, and you resent being forced into this without your consent. Even if you might have chosen to pursue \cChupStudent{} eventually without the pressure, you're deeply conflicted about accepting under these circumstances — particularly with your imminent plans to leave your position behind. You aren't sure how either family, or \cChupStudent{} for that matter, will respond to your abandoning the Heirship. Wouldn't that be the most ironic turn of events? You come around to the idea of marrying \cChupStudent{} only to have your family take it away from you after trying to push it on you for so long. 

If you decide not to pursue \cChupStudent{}, or doing so goes poorly, you could always try with \cPresident{\full}. You and \cPresident{} initially bonded over your desire to know what happened to the students six years ago. \cPresident{\Theyare} one of the most charismatic, driven, passionate people you know.   Student body president, smooth talker, and easy on the eyes as well; you  found yourself wondering what life would be like with \cPresident{} instead of \cChupStudent{}. In the past few months,you've caught \cPresident{} sneaking glances at you from across the room many times. In a fantasy world, you could maybe be with both at the same time somehow, but that just isn't done where you come from. At least, not without scandal when whichever one is the extramarital affair is discovered and publicized. Besides, you're all from different walks of life, and different nations to boot. , And, of course, with the ongoing war a relationship with \cPresident{} would be across battle lines.

Speaking of across battle lines, if it were up to you, you would never talk to \cWarlordDaughter{\full}, except you and \cWarlordDaughter{} struggle in mathematics, and have therefore found yourselves often the last ones up, banging your heads against the same problems. You often find yourself not trusting or even just getting annoyed with \cWarlordDaughter{}. \cWarlordDaughter{\Theyare} the \cWarlordDaughter{\offspring} of the leader of the war effort on the \pShip{} side. \cPresident{} \emph{always} stands up for \cWarlordDaughter{\them}, even when you are right and \cWarlordDaughter{} is wrong, which you find frustrating. 

Still, you can’t be study partners for nearly a year and not eventually get to talking about yourselves.  You have made vague comments about how controlling your family is.  One very late night, in response,  \cWarlordDaughter{} confided that  \cWarlordDaughter{\their} \cLoud{\parent} used to be different — peaceful, kind, patient. And that \cWarlordDaughter{} wishes \cLoud{\theywere} still that way, and hates living in the shadow of such a violent and intense figure. You understood immediately, even though you didn’t want to - you can’t help but sympathize with feeling trapped by the circumstances of one’s family. Part of you wants to help \cWarlordDaughter{} , but you still don’t trust \cWarlordDaughter{\them}. 

So you decided to propose essentially a trade instead of just sticking your neck out for someone who might be lying to you. You asked \cWarlordDaughter{} to get the \iMirror{} from \cDiplomat{} (basically taking the fall if there’s trouble) this weekend. Doing so would help \cPresident{} and you with the ritual to look into the past. It would make sure that you don’t end up drawing more of the attention of \cDiplomat{} when it is discovered.In return, you agreed to help \cWarlordDaughter{} discover and reverse what happened to \cWarlordDaughter{\their}  \cLoud{\parent} \cLoud{}. You were pleasantly surprised when \cWarlordDaughter{\they} readily agreed to your terms. 

When your brain is swirling with so many conflicting thoughts, you are very thankful for \cAssistantScientist{\full}. You met \cAssistantScientist{\them} a few years ago at one of your family’s parties. The two of you gravitated toward each other as being some of the youngest people in attendance, with the least interest in posturing and politics. \cAssistantScientist{} is about the age \cHeirSibling{} would have been. It's a little like having an older sibling again. \cAssistantScientist{} has yet to pull you into trouble like \cHeirSibling{} may have, but you feel honored that \cAssistantScientist{} talks to you so much, and the two of you keep up a fevered pace of correspondence. \cAssistantScientist{\Theyare} usually quiet and serious, focused on the work of ending the Storms, but when \cAssistantScientist{\theyare} alone with you, \cAssistantScientist{\they} relax\cAssistantScientist{\verbes} and almost seem\cAssistantScientist{\verbs} like a different person — caring, funny, and thought provoking. 

\cAssistantScientist{} is a great sounding board for your romantic tribulations. You’ve confided your growing attraction to \cChupStudent{} and \cPresident{} to \cAssistantScientist{\them}, and \cAssistantScientist{\theyare} adamant that you will figure it all out. You’ve complained endlessly about \cWarlordDaughter{} as well, and \cAssistantScientist{} has had some good advice about how to tolerate people you don’t actually like but are stuck working with. You hope that this weekend the opportunity might present itself for you to return the favor to \cAssistantScientist{} and support \cAssistantScientist{\them} with whatever social challenges \cAssistantScientist{\they} might face.

You're also interested to see the presentation \cHeadScientist{\full} and \cAssistantScientist{} are giving this weekend. The treaty \cDiplomat{} made with the \pFarm{} relies completely on the promise that the \pTech{} will provide a technological way to permanently end the Storms. You've heard \cDiplomat{} speaking with the two scientists at length, often pulling them away from the parties for hours at a time. (Why bring them to the parties if you're just going to monopolize their time anyway?). What strikes you as odd is that your company has not yet been approached to manufacture anything, and you've got the market basically cornered on manufacturing. You are worried this may mean that the scientists have either bad news, or nothing to show yet. This is the one thing that \cAssistantScientist{} refuses to talk about with you. Maybe, just maybe, you’ll learn something that you can use against \cDiplomat{} to get \cDiplomat{\them} to agree to switch the Heirship.

In between everything else going on this weekend, you hope there'll also be enough time for you to also get involved in the Ceremony of Excellence that \cMusic{\full} is organizing. You'd really like to take the opportunity to showcase your skills — and maybe catch the interest of certain individuals — by being one of the combat demonstrators during the show. You are, of course, the most qualified individual, as you've been schooled in magical combat from a very early age, so it will be a win-win for the school. You'll need to be proactive to ensure you are the one chosen, though. Your ideal scenario would be both you and \cAmbition{} get chosen and have a breathtaking sparring match that makes you both look marvelous!

This weekend is your chance to leave the powerlessness of childhood behind and grab your own destiny with both hands. Maybe some freedom will even let you figure out what it is you DO want to do with your life! Whatever it is, wherever, and with whomever, your future will be your own once you can get closure for your \cHeirSibling{\sibling}'s murder and free yourself from the family lineage. Not to mention how happy it would make \cAmbition{} to take over the yoke of leadership that you loathe. Your \cFaledonParent{\parent} may not like it at first, but you know that everything you are doing this weekend will ultimately benefit the Faledon family as well.  

\begin{itemz}[Major Goals]
    \item Work with \cPresident{} to find out what happened to the students — most importantly \cHeirSibling{} — six years ago.
    \item Escape the \cHeir{\formal} family by making \cAmbition{} the Heir in your place, and help smooth the transition as best you can. Don’t let \cDiplomat{} interfere with your escape.
    \item Find love on your own terms with \cChupStudent{} or \cPresident{}. If only you could find a way to be with both\ldots{}
    \item Help \cWarlordDaughter{} figure out why \cLoud{} changed in exchange for \cWarlordDaughter{\their} help with getting \iMirror{}.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Assist \cAssistantScientist{} the scientist with anything \cAssistantScientist{\they} need\cAssistantScienist{\verbs} to stop the Storms and return \cAssistantScientist{}’s kindness around navigating social situations.
    \item Win a spot as a combat demonstrator in the Ceremony of Excellence and then impress everybody with your skill.
\end{itemz}

\begin{itemz}[Notes]
    \item You are graduating this year.
\end{itemz}

\begin{contacts}
    \contact{\cDiplomat{}} Your \cDiplomat{\auncle}, who you don’t exactly hate but see as an obstacle to your plans. As the creator of the treaty forged six years ago that brought about the Betrayal of the \pShip{} by the \pTech{} and the \pFarm{}, \cDiplomat{} is ultimately responsible for the current war between the nations.
    \contact{\cAmbition{}} Your close friend and secret cousin who has seen you through thick and thin. As an actual \cHeir{\formal}, \cAmbition{} is the perfect substitute Heir.
    \contact{\cWarlordDaughter{}} Due to \cWarlordDaughter{} being the \cWarlordDaughter{\offspring} of the Warlord leading the \pShippies{} so successfully into battle, you don’t trust \cWarlordDaughter{\them}, but you have found yourself studying together occasionally and have forged a mutual arrangement that should help you both out. 
    \contact{\cChupStudent{}} Your intended future \cChupStudent{\spouse}, and as such has been your childhood irritation from the start. That's all changed now, though, and you'd like to start over with a clean slate and get to know \cChupStudent{\them} as they are now, hopefully romantically. If only \cChupStudent{\they} felt the same\ldots{} and you two could take this at your own pace instead of being forced to marry in a few days.
    \contact{\cPresident{}} Your primary collaborator in finding out what happened to the students six years ago. Charming to say the least and possibly returns your romantic interest. Why is love so complicated??
    \contact{\cAssistantScientist{}} A friend you rely on as a safe space to sort out your various feelings about fellow students. Something of a surrogate older sibling. \cAssistantScientist{\Theyare} an assistant scientist on the project to end the Storms.
\end{contacts}
\end{document}
