\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cScholarship{}}

You are \cScholarship{\intro}. You are 21 years old and very magically talented. As an orphan from \pTech{}, you were only able to attend school, and now be here at the \pSchool{} on a religious scholarship granted to you by your mentor, \cAntiChup{\intro}. Because of that, your position here is distressingly precarious.

You never knew your parents. Instead, your first memories are from the orphanage. It wasn't bad as such, but neither was it a home. Your interest in religion initially spawned from the comfort that your spirituality brought you when times were hard, and you ended up working and volunteering at the small temple near the orphanage. When the Church agreed to take you in full time to their Youth Program when you were 13, you were overjoyed. Unfortunately, that joy faded shortly after \cAntiChup{}, who even then was a major figure in the Church of Kero, came into your life. After taking an interest in you thanks to your religious devotion and strong magical potential, \cAntiChup{} took charge of every aspect of your upbringing, curating your education and eventually starting to use you as an errand runner. Over the course of several years, the errands became more difficult, important, and dangerous — but none took you far from \cAntiChup{}'s watchful eye for long. You know that \cAntiChup{} did make sure you had a better life than you could have, so you are grateful for that. You think in \cAntiChup{}’s own way \cAntiChup{} may even actually care for you. You just wish you knew for certain.

You hoped things would change once you reached the \pSchool{}. \cAntiChup{} had been wildly supportive of your desire to attend the \pSc{}, and at first you were so happy for \cAntiChup{\their} support, but the motive behind it soon became clear — \cAntiChup{\they} wanted an agent on the inside. And with \cAntiChup{} in charge of the scholarship that allows you to attend, your position is contingent on continuing to please \cAntiChup{\them}. 

Still, at the \pSchool{} you got your first taste of something that resembled freedom, as well as the friendship of your frequent study partner, \cTechStar{\intro}, and you want \emph{more} of it. \cTechStar{} is a dreamer like no other, and you love to listen as \cTechStar{\they} wax\cTechStar{\verbes} poetic about the ways \cTechStar{\they} want\cTechStar{\verbs} to change the \pTech{} for the better. \cTechStar{\Theyhave} confided in you that \cTechStar{\theyare} deeply frustrated with the restrictions imposed by the Council and Church upon \cTechStar{\their} brilliant invention, the VidCom device. You often commiserate with \cTechStar{\them} about your own frustrations and lack of agency. Yet you are careful to remind \cTechStar{} that the Church is not the same as \cTechGod{\intro}. You often have to remind yourself of this fact as well, but you know it in your heart, in a way you can’t really describe. You guess that is what the word faith means, knowing something is true but not necessarily knowing why.

Speaking of \cTechStar{}, you know that sometimes students from the other nations give \cTechStar{\them} a hard time for being on the High Council of your nation and therefore partially responsible for overseeing the war. You know \cTechStar{} is a good person doing the best \cTechStar{\they} can and isn't responsible for everything the Council does, so you try to stand up for \cTechStar{\them} whenever you can. Still, sometimes it is hard to separate an individual from their context. \cWarlordDaughter{\intro} is the child of the \pShippie{} Warlord, \cLoud{\intro}, and a \pShippie{} through and through. It's hard not to be reminded of the \cLoud{\person} who is driving the war effort when you look at \cWarlordDaughter{\them}. It is hard to set aside the hurts that the war has caused. Another student you can’t stand is \cPresident{\intro}, the Student Body President and member of a prominent but loving Wave Rider family. Maybe it is petty of you, but \cPresident{} seems to have lived such a charmed life and had everything handed to \cPresident{\them} on a silver platter, whereas your life has been filled with struggle, hardship, and people trying to control you. It’s hard to look at \cPresident{} without feeling some jealousy and resentment.

In addition to \cTechStar{}, you have also made a good friend in \cAmbition{\intro}, who, like you, is adopted and trying to find \cAmbition{\their} own place in the world. \cAmbition{\Theyhave} expressed interest in joining the clergy and you have been happy to help \cAmbition{\them} explore this, though you want to make sure \cAmbition{\theydo}n't end up under \cAntiChup{}’s thumb like you are. This is challenging, as \cAmbition{\they} seem\cAmbition{\verbs} very interested in meeting your mentor this weekend. You wish you could be more open about why you don’t think this is the best idea.

\cAntiChup{} has grand plans for your future, and you like the general direction planned for you, but you're not as \emph{grateful}, or as blindly devoted, as you've been given the impression that you should be. You see signs now and then that \cAntiChup{} genuinely cares for you like a surrogate parent should, and you really are grateful for all \cAntiChup{\theyhave} done for you, but it is hard to ignore the fact that \cAntiChup{\theyare} also always plotting and tasking you with carrying out \cAntiChup{\their} dirty work. Under \cAntiChup{}'s orders, you ``borrowed'' the \iScythe{} from the \pSc{} Library, and on a school break two months back and hunted down the Avatar of \cEbbFull{\intro} — one of the two \pShip{} Avatars — and killed it. You felt sick the whole time (you are not a violent person at all), but also do want \pTech{} to be safe. The action has given the \pTech{} the upper hand in the war by eliminating the connection between the \pShip{} and one of their Goddesses, but it also broke the connection between the \iScythe{} and the \pFarm{}. You managed to sneak the \iScythe{} back into the Library, but to your surprise, and now terror, someone else was there in the depths of the library, ripping a page out of a very old and important looking book. They ran away before you could be fully sure, but you were pretty sure it was \cChupStudent{\intro}, a first year from the \pFarm{}. What you do know is it is very likely \cChupStudent{\they} know\cChupStudent{\verbs} you took the \iScythe{} and can destroy you with this information. You need to do what you can to keep \cChupStudent{\them} quiet, but hope mutually assured destruction if anything gets out will do the trick.  

Now the \iScythe{} needs to be reattuned to the \pFarm{} before anyone else finds out and traces the crime back to you. To do that, you'll need to make sure the ritual to renew the Ley Lines happens as soon as possible, as it is a prerequisite. The principal, \cPrincipal{\intro}, is traditionally the one in charge of that ritual, though you have heard that it has been delegated to \cBeetle{\intro} this year. Even if you can reattune the \iScythe{}, though, you still can’t completely cover your tracks — you had to shatter the wards on the reliquary where the Relics are stored in order to borrow the \iScythe{}, and try as you might, you lack both the time and the training to single-handedly restore them. You’ll just have to hope that \cChupStudent{} stays quiet.

While assassinating a God's Avatar was the most traumatic, this is hardly the first crime \cAntiChup{} has forced you to commit, and that pattern is exactly why you don't intend to answer to \cAntiChup{} forever. In fact, you have plans to end that this very weekend. The sticking point is the ``\iScholarship{},'' which is currently made out in \cAntiChup{}'s name. You need to find a way to convince \cAntiChup{} to sign it over to another member of the Church of \cTechGod{}. You know and like \cBeetle{\full}, the religion teacher at the \pSc{}. Alas, \cBeetle{\theydo}n't seem to like you very much. \cBeetle{} is of course a \cBeetle{\cleric} of \cTechGod{}; \cBeetle{\they} wouldn't be able to take on your scholarship otherwise. Being the only other Cleric of \cTechGod{} here, \cBeetle{\theyare} kind of your only option right now. If another opportunity presents itself, though, you'll take whatever you can get — short of emigrating. You love the \pTech{} and have no interest in moving to a different country. 

Of course, you will have to convince \cBeetle{} to become your new patron. You plan to accomplish that by helping \cEbbPriest{\intro} with \cEbbPriest{\their} research on the Creation of \pEarth{}. Ever since \cAntiChup{} mentioned \cAntiChup{\their} correspondence on the topic with \cEbbPriest{}, you have been fascinated. \cEbbPriest{} may not know you in person, but you plan on working with \cEbbPriest{\them} this weekend, without \cAntiChup{}’s knowledge. The Creation is a hotly contested topic among religious scholars across \pEarth{}, and \cBeetle{} is a premier scholar. Discovering something previously unknown about the beginning will surely impress \cBeetle{\them}. You also hope that helping with the ritual to renew the Ley Lines will ingratiate you to \cBeetle{}. You will have an uphill battle, as \cBeetle{\theydo}n't like \cAntiChup{} (sarcasm: you can't imagine why!) and seem\cBeetle{\verbs} to have painted you with the same brush. Convincing \cBeetle{\them} that you are different will be challenging, but crucial.

You are accompanied in your quest to impress \cBeetle{} by \cHeadScientist{\intro}, the brilliant scientist leading the research into how to end the Storms. As \cAntiChup{}’s protege, you regularly crossed paths with \cHeadScientist{} at official functions. You know that \cAntiChup{} brought you to these functions to take care of you in \cAntiChup{\their} own way, but both you and \cHeadScientist{} hated all the hobnobbing and politicking at such events. During many awkward cocktail hours, you found that you both preferred to be off pursuing your passions, so despite the difference in age, you felt a certain sense of comradery and would keep each other company. You noticed early on that despite \cHeadScientist{\their} very technical mind,  \cHeadScientist{} seemed to have a deeply spiritual side as well, and your conversations about religion and science would help while away the hours. The two of you kept in touch after you left for the \pSchool{}, and \cHeadScientist{\they} confided in you recently that the research into how to end the Storms was not going well and \cHeadScientist{\theywere} looking for a potential exit strategy. You agree with \cHeadScientist{\their} assessment that all the blame would be thrust onto \cHeadScientist{\their} shoulders if the research didn’t yield something useful. You agreed that your friend needed an out. 

You proposed the Church, and \cHeadScientist{\they} really took to the idea. Flash forward to the present: \cHeadScientist{} let you know that \cBeetle{} asked \cHeadScientist{\them} to work with \cEbbPriest{} on the research into the Creation of \pEarth{}, with the goal of impressing \cBeetle{} enough to be admitted into the Clergy, and \cHeadScientist{} wants you to help, which is perfect! What a way to bring everything together. You look forward to working with \cHeadScientist{} and seeing what \cHeadScientist{\their} brilliant analytical mind can uncover about such an important theological question. 

As if \cAntiChup{} has not already asked too much of you, \cAntiChup{\theyhave} also asked you to accompany \cAntiChup{\them} and sometimes even take \cAntiChup{\their} place at the treaty negotiations happening this weekend. Once again an “excellent learning opportunity” which also lets \cAntiChup{} get out of anything \cAntiChup{\they} find beneath \cAntiChup{\them}. You are supposed to sit at the table with all of the most prestigious delegates from all three nations and represent \cAntiChup{}, the Church, and the \pTech{}. Talk about weight on your shoulders! Still, you worry that if you don't at least try, some agreement will be made that will lead to immense suffering of the \pTech{}. Your people aren't remotely prepared to receive the Storm this year. How many would die if it were to be unleashed upon them? You cannot sit idly by and allow that to happen — you must try to protect your people, no matter how small you feel sitting at that table. At least there will be one seasoned diplomat from the \pTech{} sitting beside you, \cDiplomat{\intro}.

Besides \cAntiChup{}'s plans for the weekend, you have plans of your own too, thank you very much! You know that voting authority for where to direct the Storm involves convincing teachers and advisors to give you their Voting Stones. Having the most votes toward where to direct the Storm will be a solid first step toward building your own power, and will help ensure the Storm doesn’t get sent to your homeland. Surely there must be favors you can do or things you can say to persuade the teachers and advisors that you are the best candidate. You have not done enough to impress \cBeetle{} yet, but if you can impress \cBeetle{\them} before \cBeetle{\they} give \cBeetle{\their} stone to someone else, that would really stick it to \cAntiChup{}! Working with \cHeadScientist{}, especially if you discover something world changing, could also convince \cHeadScientist{\them}, at least.  


As it turns out, you are not the only one at the school trying to escape a manipulative and controlling guardian. You've been connecting recently with one of your classmates, \cAdopted{\intro}, who was kidnapped from \cAdopted{\their} birth family in the \pFarm{} because of \cAdopted{\their} magical talent and raised by a noble family that treats \cAdopted{\them} badly. Apparently, this is standard practice in that nation, but it seems wrong to you. You find yourself deeply empathizing with \cAdopted{\their} plight, and recognize a fellow good person caught in a bad situation, determined to escape from it by any means necessary. \cAdopted{} carries a lot of anger but has a good heart, just like you, and you want to help \cAdopted{\them} however you can. \cAdopted{\Theyare} clever, passionate, and deeply loyal to those \cAdopted{\they} love\cAdopted{\verbs}. 

You feel really honored, but also nervous, that recently \cAdopted{\they} trusted you on a project that \cAdopted{\theyare} working on that is amazing, but really dangerous. Part of you thinks you should tell \cAdopted{} to just not do it, that maybe those rules on healing magic and music in Children of the Sun are there for a reason, but then \cAdopted{\they} look\cAdopted{\verbs} at you and starts talking about how many lives it could save. So you agreed to help \cAdopted{\them} develop a device that can record music and bring it to the masses, quietly, as much as you can. Your main order of business is to see if you can help \cAdopted{} make inroads with some of the magitech folks in the \pTech{}. You don’t really know why you agreed to all of this, until just the other day. That is when it dawned on you that your feelings for \cAdopted{} go beyond compassion and respect — you are developing romantic feelings for \cAdopted{\them} too. You haven't told \cAdopted{} yet and are still deciding what you want to do, but a part of you is desperate to find out if \cAdopted{\they} return your feelings.

If everything goes well, by the end of this weekend, you will be free of \cAntiChup{}'s control, and well on your way to establishing your own power base in the Church. If you can keep your reputation from being tarnished by the revelation of your part in the death of \cEbb{\intros} Avatar, so much the better. The \pSchool{} has finally given you a taste of what it means to be your own person, and you intend to solidify that here and now.

\begin{itemz}[Major Goals]
    \item Get free of \cAntiChup{}’s control so you can be your own person and do what you feel is right, not someone else’s dirty work. To that end, convince another member of the \pTech{} clergy, presumably \cBeetle{}, to take over your scholarship. You will need to impress \cBeetle{} by helping \cEbbPriest{} and \cHeadScientist{} research the creation of Cengea.
    \item Reattune the \iScythe{} before anyone discovers what you did and keep \cChupStudent{} quiet about \cChupStudent{\them} seeing you with the \iScythe{}. The ritual to renew the Ley Lines must be completed in order to do this.
    \item Collect as many Voting Stones for directing the Storm as you can, and make sure the Storm does not get sent to the \pTech{}. You hope to count on \cHeadScientist{} for this.
   \item Decide what to do about your romantic feelings for \cAdopted{}, and see if there is some way you can help \cAdopted{\them} escape \cAdopted{\their} abusive adoptive family.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Sit in on the peace negotiations with \cAntiChup{}'s, and advocate for the \pTech{} as best you can.  
    \item Help \cAdopted{} with the music box \cAdopted{\theyare} crafting, even though it is blasphemous to \cFarmGod{\intro}.
    \item Check in with your friends \cTechStar{} and \cAmbition{}. The Time of Deciding is intense, and you are all going to need to support each other. Make sure that \cPresident{}’s naivety does not end up hurting you or your friends.
\end{itemz}

\begin{itemz}[Notes]
    \item You are in your second of three years at the \pSchool{}.
\end{itemz}

\begin{contacts}
    \contact{\cAntiChup{}} Your shady mentor and sort-of foster \cAntiChup{\parent}. You owe \cAntiChup{\them} a lot, and you care for \cAntiChup{\them}, but you need to be your own person. And hopefully be forced to commit fewer crimes.
    \contact{\cBeetle{}} Another member of the \pTech{} clergy who seems much nicer than \cAntiChup{}. You hope to convince \cBeetle{\them} to take over sponsoring your scholarship.
    \contact{\cHeadScientist{}} The brilliant scientist researching how to end the Storms, who is concerned about how the research is going and is looking for a way out. You convinced \cHeadScientist{\them} to pursue a spiritual path, and now you are both working together on studying the Creation of \pEarth{}.
    \contact{\cTechStar{}} A good friend you often study with, who you feel like you can rely on.
    \contact{\cAmbition{}} Another good friend who is adopted like you and trying to find \cAmbition{\their} place in the world.
    \contact{\cEbbPriest{}} A \pShippie{} \cEbbPriest{\cleric} of \cEbb{} who is studying the Creation of \pEarth{}. You are helping with \cEbbPriest{\their} research in order to impress \cBeetle{}.
    \contact{\cAdopted{}} A student from the \pFarm{} whom you have been connecting with over both wanting to escape toxic guardianships. You also happen to find \cAdopted{\them} incredibly attractive, and wonder if \cAdopted{\they} feel\cAdopted{\verbs} the same way about you\ldots{}
    \contact{\cPresident{\full}} The Student Body President and political scion who has lived a charmed life and seems to have everything \cPresident{\they} want handed to \cPresident{\them}. You are more than a little jealous.
\end{contacts}

\end{document}
