\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cChupInventor{}}

You are \cChupInventor{\intro} — brilliant 45 year old inventor and Diplomacy and Political Science Teacher at the \pSchool{} — but most importantly, a devoted member of the \pGoaties{} and supplier of the infamous black market. You have channeled all of your rage against your home country, the \pTech{}, into ever more fervor for your God, \cGenesis{}. This weekend is the culmination of almost a decade of work in the shadows — and you don't intend to let this chance pass you by.

You've known that inventing was in your blood since you were young. As a citizen of the \pTech{}, however poor, your parents encouraged your passion from day one, as did your best friend \cHeadScientist{\full}. The two of you spent days inventing, daydreaming, and supporting one another. As you grew, your confidence did also, as your inventions became more impressive and practical. You went from inventing magic-propelled paper airplanes to a scale that could measure weight with tremendous precision to, finally, your magnum opus: a new type of magical food preservation that could revolutionize your country. The power of these ``refrigeration coils'’ could not be overstated. While magically intensive, if you could leverage the massive industrial potential of the \pTech{}, it would be a practical solution to your country's food circulation problems. Understanding all of this, you were of course excited to share your invention with the world — and to receive the proper adulation for your hard work. Unfortunately, that all came crashing down in an instant 12 years ago.

With the support and encouragement of your childhood best friend \cHeadScientist{}, whose research you had drawn on for your refrigeration coils, you submitted your invention to be considered for production to the Temple — just as all inventors are required to. You'd never considered one of your previous inventions to be enough, so despite your prolific inventing, this was your first time here. As the door opened, you looked up with confidence as the \cAntiChup{\cleric} approached you — only to deliver the devastating news that your invention was rejected. Not rejected for revisions — rejected outright, because it was too ``expensive'’ to put into production. You don't remember the next moments. Later, people told you that you were kicked out of the Temple after you tried to attack the \cAntiChup{\cleric}. That didn't sound like you, but then again, neither did failure. When you came back to yourself, though, you were faced with the cold, hard reality that not only had your best work been rejected, but you had been banned from ever setting foot in the Temple again.

You were almost destroyed by this news. Your very reason for existence was being denied — for no good reason. That short-sighted \cAntiChup{\cleric}, \cAntiChup{\full}, couldn't see how much time and money and effort would be saved by your invention. The only reason you could think of to reject your invention was simple classism — you came from a poor family, and apparently those with a higher status wanted to keep you that way. Two months later, your suspicions were validated. An invention very similar to yours but with even less efficiency and a smaller capacity was greenlit. The only thing this invention had going for it over yours was that it was invented by the daughter of a Council Member. It was class warfare in its most distilled form. And this news was what broke you.

The next few years were spent in a dark cycle of rage and regret. You built things, then destroyed them, got jobs, then quit after the first annoyance. Your whole worldview had been torn down, and you didn't know how to cope — so you spun your wheels. That was, until 8 years ago when \emph{\cChupLeader{\they}} came along to give you a second chance — the founder of the \pGoaties{}, \cChupLeader{\full}. Apparently, \cChupLeader{} had heard of how poorly treated you were by \cTechGod{} and understood your anguish. It didn't take much to convince you to renounce \cTechGod{} and \cTechGod{\their} entire structure that handed power only to the lucky few. \cGenesis{}'s message of true equality for all resonated with you strongly, and you believe in \cChupLeader{}'s ability to bring that vision to life.

It was with great fervor that you helped build the \pGoaties{}. You were only too happy to lie, cheat, and steal your way up the ranks through the society that had wronged you. You did a lot of good for the group in many areas, feeding information and covering for the budding black market. With them, unlike in your inventing career, your efforts were quickly recognized. In just two short years, you were elevated to the top supplier of the black market in the \pTech{}, a crucial position, as the bulk of the cult’s funds come from black market sales. With this new position came a new charter — infiltrate the \pSchool{}, assist with the administration of the black market operations there, and await the time to implement your leader's masterstroke — whatever that might be. You studied hard and obtained the qualifications necessary to become a teacher in less than a year. After that, with the resources of the cult at your back, it was a simple matter to spoof the board and get the job of Diplomacy and Political Science teacher at the \pSc{} just months after the Storm six years ago. You know it is not a coincidence that you happened to arrive at the same time that the leader of the black market, and second in command for the \pGoaties{}, \cChupSecond{\full}, also came to the \pSc{} to teach economics. The death toll of that Storm among the \pShip{} was a great tragedy, but the ensuing influx of recruits to the \pGoaties{} has been, well, a godsend.

You've been working towards this moment all this time. Finally, this weekend, all the pieces are in place to execute your masterstroke, and finally reveal the \pGoaties{} to the world. To that end, the \pGoaties{} have produced a Relic — the \iHorseshoe{} — that is currently attuned to the \pSchool{}. If the \iHorseshoe{} or any other Relic attuned to the \pSc{} is used in the Ritual to Control the Storm, it will allow the Storm to be targeted at the \pSchool{}, and in doing so, destroy it utterly. Destroying the \pSc{} will not only serve as a powerful symbol that a new Deity has entered the upper echelons of the Pantheon, but also be a crushing blow to the current, corrupt political structures of all three nations. What's more, the word of \cGenesis{} is that destroying the school will end the Storms forever, ensuring that you and your fellow Followers will be hailed as heroes. To achieve this result, you must either install the Relic you have constructed into the Ritual, or corrupt one of the existing Relics in order to cause it to be attuned to the \pSc{} instead of its home nation; if you can attune more than one Relic to the school, the odds of the Storm striking it will be even higher. 

Each \pGoatie{} is playing a part in this plan, and making sure one or more Relics attuned to the \pSc{} ends up in the Ritual to Control the Storm is yours. You know that others are working on making sure enough student votes go to directing the Storm at the \pSc{} (though you can help by giving your Voting Stone to a student who is loyal to the cause, namely \cChupStudent{\full}). ChupStudent{} is a true class traitor, the \cChupStudent{\child} of a Duke in the \pFarm{}. You you have gotten to know \cChupStudent{} this past year, and underneath a facade of being a slacker, \cChupStudent{\theyhave} prodigious talent and a quick mind. You can see what a relief it is for \cChupStudent{\them} to be able to be who \cChupStudent{\they} really \cChupStudent{\are} to you in the brief conversations you have alone.  

Your contributions to this weekend’s plans go further still. Over the past few weeks, you worked closely with \cChupSecond{}, the efficient and competent second in command of the \pGoaties{}, to sabotage the Bunkers that protect against Storm surges. You are glad for the bit of extra time working with \cChupSecond{}. Due to you both being \pGoaties{} you try and not be too close in public, but the times — often in your secret lab — that you two can relax and speak freely give you strength to continue in your work. Repairing this sabotage will serve as a distraction for your enemies from the group's true purpose this weekend. And even if they are fully repaired, the Bunkers will be unable to protect everyone here from the full might of the Storm when it strikes the school. You and your fellow Followers intend to make sure the right people — \cAntiChup{\full} and other corrupt clergy and politicians — are trapped outside the Bunkers when the time comes. You have been assured that the luck of \cGenesis{} will protect you and your fellow faithful from harm. However, \cChupStudent{} is likely too young and naive to understand how sabotaging the Bunkers and using the Storm to assassinate the group’s enemies serves the greater good, so \cChupStudent{\theyhave} been kept in the dark about those details. Probably best to keep it that way. Even with all the pretending \cChupStudent{} does, \cChupStudent{\they} seem\cChupStudent{\verbs} to have made real friends here. Maybe you can help \cChupStudent{} with conversion efforts?

While installing at least one Relic attuned to the school in the Ritual to Control the Storm is your most crucial goal by far this weekend, you have a lot more to keep you busy. You have been heavily involved in the black market since its inception and are the head of the \pTech{} arm of the organization. You have been using your position to undermine the intellectual property laws of the \pTech{} as hard as you can out of well justified spite. You source a lot of highly sought after goods, including advanced weaponry. Your main contact in this is \cChupSecond{}, who clearly thinks \cChupSecond{\theyare} the lynchpin of everything related to the black market, but you're not a bad hand at this yourself. \cGenesis{} forbid something happen to \cChupSecond{}, but if it did, you are more than capable of stepping up and managing the market yourself. At any rate, your duties to the black market this weekend are simple — buy, sell, or steal as much valuable information and as many goods as you can.

As the black market liaison for the entire \pTech{}, you've handled many unique and fascinating items over the years. Most of these things come from your contacts in the \pTech{} or directly from \cChupSecond{}, who sources them from the \pShip{}. Recently you have sold such things as a mechanical bird to a representative of the \cQueen{\Monarch} of the \pFarm{} and a full wedding party's worth of Tech clothing to a fleet in the \pShip{}. \cHedonist{\full}, a \cHedonist{\cleric} from the \pFarm{}, is one of your best repeat customers, always willing to trade a bit of gossip or some small curses for hard to find books, magitech, and even tech infused clothing. Your best export has always been your personally developed technology, especially your refrigeration tech.

To circumvent \cTechGod{}'s laws on activating your own technology, you have been using a set of magical stones that store power, and the skills that \cGenesis{} taught you. These stones are highly illegal all over \pEarth{}, but especially in the \pTech{}. You have no idea how \cHeadScientist{} got \cHeadScientist{\their} hands on them six years ago, but they are the kindest gift anyone has ever given you. You intend to keep them very secret to protect both of you. Okay, maybe you have some idea how \cHeadScientist{} got \cHeadScientist{\their} hands on the stones. You can't help but notice that they look a lot like the official voting stones for directing the Storm, and that the ``Time of Peace’’ treaty was broken the year \cHeadScientist{} gave them to you. But it's best not to look a gift horse in the mouth, and the less you know, the less trouble you can get in if anyone does find out about them. Regardless, the stones are crucial to your work, but are fading in power — you can still use them for small charges of magical energy, but nothing as grand as when you first got them. You aren't particularly concerned, though. Once \cGenesis{} rises to power, you will no longer have to hide from \cTechGod{}'s wrath and can activate and sell all of the tech you like.

\cHeadScientist{} was one of your few childhood friends, and the only one you've kept in touch with. \cHeadScientist{\Theywere} your most trustworthy ally before your life changed, and \cHeadScientist{\theyare} coming to the school as an advisor this weekend. As close as you are, you haven't had much chance to meet — you've been busy working with the \pGoaties{} and \cHeadScientist{\theyhave} been just as busy with \cHeadScientist{\their} work. Having the chance to meet in person is an unexpected blessing, but also a burden — what if \cHeadScientist{} volunteers to stay outside the Bunkers when the Storm strikes the school and is killed? You would never be able to live with yourself. You \emph{must} find a way to get \cHeadScientist{} out of harm's way. The easiest way to protect \cHeadScientist{\them} would be to bring \cHeadScientist{\them} into the fold, as one of the \pGoaties{}. Of course, that could be challenging, as in the course of \cHeadScientist{\their} work to end the Storms, \cHeadScientist{} has been involved directly with \pTech{} bigwigs like \cHeadScientist{\their} boss \cDiplomat{\full} whom you would not mind seeing perish. Maybe you can appeal to \cHeadScientist{}’s desire to end the Storms and help \cHeadScientist{\them} see that the only true way to do so is through \cGenesis{}.

But \cHeadScientist{} is far from the only non-\pGoatie{} you are concerned about this weekend. You would hate to see any harm come to your students or many of your fellow teachers (though you won't shed any tears if \cPrince{}, the conniving \cPrince{\heir} of the \pFarm{}, perishes). In particular, you feel somewhat protective of your favorite student, \cTechStar{}, a brilliant young inventor and winner of this year’s TechStar Competition. You might resent \cTechStar{\their} lofty status were it not for the fact that \cTechStar{\they} clearly chafe\cTechStar{\verbs} against the corruption and cowardice of the Council of the \pTech{} and the Church of \cTechGod{}. The Council narrowly voted to severely restrict production and access to \cTechStar{}’s brilliant invention, the VidCom device, which enables long distance communication. You have carefully stoked the flames of \cTechStar{\their} resentment at this decision, and believe \cTechStar{\they} will soon be ripe for recruitment to the \pGoaties{}, which would also protect \cTechStar{\them} from the Storm when it strikes. As for the VidCom technology, you would dearly love to secure a prototype pair or even the blueprints themselves from \cTechStar{}, both to sell on the black market and for the \pGoaties{}’ own use. You and \cChupLeader{} are working together towards this end.

At the last ``Time of Deciding’’ three years ago, you also struck up a friendship with \cBunker{\full}, the brilliant engineer who designed and maintains the Bunkers. You initially did this as a cover for gaining a better understanding of the Bunkers in preparation for sabotaging them, but you soon found that \cBunker{\they} seem\cBunker{\verbs} like a good sort, and you have greatly enjoyed talking shop with \cBunker{\them}; moreover, \cBunker{\they} seem\cBunker{\verbs} to hold little faith in the Patron Gods, which only makes you respect \cBunker{\them} more. The two of you have kept up a correspondence, and you even recommended \cTechStar{} to \cTechStar{\them} as a potential intern. Still, there is something a little off about \cBunker{} that makes you suspect there is much \cBunker{\theyare} hiding, so you've been cautious about getting too close. You plan to help \cBunker{\them} ``maintain the bunkers’’ this year as well, and delay the necessary repairs as long as possible.

Your last bit of business this weekend is somewhat personal. You checked the guest list, then did a double take when you noticed the name of one of the advisors from the \pTech{}: \cAntiChup{\full}. The very \cAntiChup{\cleric} who denied your invention all those years ago — and a name you will never forget. You have long wondered what you would do if given the opportunity to have your revenge — and at long last, you have the means to do so. Killing \cAntiChup{} outright wouldn't do — that would cost you all your memories and accumulated knowledge. No, you need to expose \cAntiChup{\them} for what \cAntiChup{\they} truly \cAntiChup{\are} — and destroy the position that \cAntiChup{\they} used against you so long ago. \cAntiChup{} has surely committed more evil in the time you've been away, but prying those secrets from \cAntiChup{\them} won't be easy. Perhaps the easier way to strike at \cAntiChup{\them} is through manipulating those around \cAntiChup{\them} — a person as vile as \cAntiChup{} can't have TRUE friends. \cAntiChup{} has an initiate named \cScholarship{\full} whom \cAntiChup{\they} no doubt sorely mistreat\cAntiChup{\verbs}. If you can use \cScholarship{\them} against \cAntiChup{\them} in some way, that would be sweet revenge, though full recruitment may not be possible - \cScholarship{} seems to be properly dedicated to \cTechGod{}. If that fails, you can always try to make sure  \cAntiChup{} ends up outside the Bunkers when the Storm strikes, as noted earlier. 

This weekend will be busy. You hope to find some personal time to save \cHeadScientist{} and \cTechStar{} and to extract your revenge. But above all else, you need to make sure that your work for the last 8 years comes to fruition. You will not let the cruel, utterly unfair status quo beat you down again.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Ensure the \pGoaties{}' plan to destroy the school, elevate \cGenesis{} to the rank of Patron God, and end the Storms forever goes off without a hitch. This will require incorporating at least one Relic attuned to the school into the Ritual to Control the Storm. You can also help by giving your Voting Stone to a student who is loyal to the cause, and by recruiting as many new members to the \pGoaties{} as possible.
    \item Protect and support your best friend, \cHeadScientist{}, as well as your favorite student, \cTechStar{}.
    \item Get revenge on \cAntiChup{} any way you can; convincing \cAntiChup{\their} apprentice \cScholarship{} to betray \cAntiChup{\them} might be a good angle, but making sure \cAntiChup{} is outside the Bunkers when the Storm strikes the school would work too.
    \item Run the black market, together with \cChupSecond{}.
    \item Delay and disrupt the repair of the Bunkers as much as you can.
    \item Secure a prototype or blueprints of a VidCom device from \cTechStar{}, ideally by convincing \cTechStar{\them} to join your cause. 
\end{itemz}

\begin{itemz}[Notes]
    \item You teach Diplomacy and Political Science at the \pSchool{}.
    \item You have been teaching at the \pSc{} for five years, and so were not present for the mysterious deaths of twelve students at the Time of Deciding six years ago. You began teaching around the same time as \cPrince{} and \cChupSecond{}.
\end{itemz}

\begin{contacts}
    \contact{\cHeadScientist{}} Your best friend and a brilliant scientist. \cHeadScientist{\Theyare} giving an important presentation this weekend on how to end the Storms permanently. Little \cHeadScientist{\do} \cHeadScientist{\they} realize that the \pGoaties{} already have their own solution to the Storms.
    \contact{\cChupLeader{}} The charismatic and inspiring leader of the \pGoaties{}. You have followed \cChupLeader{\them} for eight years, and \cChupLeader{\theyhave} yet to steer you wrong.
    \contact{\cChupSecond{}} The incredibly organized and competent second in command of the \pGoaties{}. The two of you have run the black market together for several years. \cChupSecond{\Theyare} a little risk averse, though.
    \contact{\cChupStudent{}} is the youngest \pGoatie{} present, a student at the \pSc{}. \cChupStudent{\They} seem\cChupStudent{\verbs} deeply loyal, and \cChupStudent{\are} charged with earning and manipulating enough votes to direct the Storm at the school. You have been a mentor to \cChupStudent{}, have seen how clever \cChupStudent{\theyare}, and believe \cChupStudent{\theyare} up to the challenge. However, you must make sure \cChupStudent{\theydo} not find out you and \cChupSecond{} sabotaged the Bunkers. 
    \contact{\cAntiChup{}} Your worst enemy. \cAntiChup{\They} denied your most brilliant invention many years ago, only to approve a worse version from someone with higher social status. Perhaps you owe them a debt for opening your eyes to just how messed up the world is, but you still intend to extract your revenge.
    \contact{\cHedonist{}} A \pFarm{} advisor who has in the past sourced rare artifacts and expensive luxury items through your black market link.
    \contact{\cTechStar{}} A brilliant young inventor, this year's TechStar, and your favorite student. You believe \cTechStar{\they} may be ripe for recruitment to the \pGoaties{}. 
    \contact{\cBunker{}} The brilliant engineer who maintains the school’s bunkers, and a friendly acquaintance of yours. Still, you've avoided getting too close, as you suspect there is more to \cBunker{\them} than there seems\ldots{}
\end{contacts}

\end{document}