\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cHeadScientist{}}

You are \cHeadScientist{\intro}, and 42 years old. You are the premier scientist of the \pTech{}, a position you've held for almost six years. You like to think of yourself as a combination of fun loving approachability and dedication to your work. This weekend you are attending the \pSchool{} as an Advisor, an event you've been looking forward to, and dreading desperately in equal measure. Now you may be in for a challenging weekend, but at least you'll get to spend some time with your life long friend, \cChupInventor{\full}, so hopefully it won’t be a \textbf{total} loss.

As one of the top scientists in the \pTech{} scientist's guild, you are leading the national effort to invent a way to permanently eliminate the magical Storms that have long ravaged the three nations of \pEarth{}.  You've been at the forefront of this mission since you took over the decade-long project six years ago. Your first year was very rocky, plagued with equipment malfunctions and strange or missing datasets; it got so bad that you wondered if someone might be sabotaging your work, though you could never find any proof or leads. After the first year, though, things went more smoothly. Maybe it had something to do with the arrival of your capable assistant, \cAssistantScientist{\full}, in the second year of your running the project. It was almost as if \cTechGod{} was looking after you, sending someone with such incredible credentials your way. You are still paranoid that everything might suddenly start going wrong again though, since you didn’t know what caused the bad luck in the first place, or why it stopped.

Theorizing that the Storms were coming from somewhere outside the known world and could be stopped permanently by reflecting the Storm back to its source, your team was able to construct a network of relay stations along the Bones of the World that allows the Storm to be sent to other planes of existence (yes, those exist). The user interface is a portable Lightning Rod that must be used in the preparations for the Ritual to Control the Storm. You were also able to determine that the Storm is drawn to the largest concentrations of magical energy, which explains why it cannot be sent to uninhabited regions of \pEarth{} — most magic resides in people and the things they create, so heavily populated areas are like magnets for the Storm’s wrath. 

As for where and what the Storm’s point of origin is, the final test results only just came in as you were on your way to this Time of Deciding, and they are shocking: The Storm originates in the Divine Realm (the Realm of the Gods) at a location containing an enormous concentration of magical energy which you are referring to as Coordinate Zero. Your instruments have also detected another massive concentration of magic in the Divine Realm at a location you are referring to as Coordinate One. Without a way to reach the Divine Realm, there is no telling what exactly is at these locations or how Coordinate Zero is causing the Storm, but simulation after simulation has concluded that sending the Storm to \emph{either} location will destroy whatever is there and end the Storms for good.

You and \cAssistantScientist{} have brought your Lightning Rod with you to this ``Time of Deciding,’’ and it will need to be incorporated into the preparations for the Ritual to Control the Storm if the goal is to send the Storm to Coordinate Zero or Coordinate One in the Divine Realm. However, you have serious concerns about sending the Storm to either location without any idea what you would be destroying in the process. As ridiculous as it sounds, you are in desperate need of some means to visit the Divine Realm to scout those locations and see what's there. You vaguely recall some crackpot research proposal to develop a portal to the Divine Realm sent to you a few years ago by \cCurse{\full}, a prominent cursemaker; you dismissed it at the time as irrational and blasphemous and fobbed it off on \cAssistantScientist{}, but blasphemous or not, it now may prove crucial. So you’d better follow up with \cAssistantScientist{\them} to see what became of that research. 

As if you weren't under enough pressure already, you and \cAssistantScientist{} are scheduled to present the results of your research first thing Saturday morning! You haven't even had a chance to share your latest findings with your sponsor, \cDiplomat{\full}, or the members of your nation's High Council who are present, \cAntiChup{\full} and \cTechStar{\full}. They’ll surely want to hear your results and strategize about how to frame it to the other nations. Whatever is decided about where to send the Storm this time, it \textbf{must not} be sent to the \pTech{}, as doing so would destroy the relay stations your nation has spent the last six years building, and with them, your ability to end the Storms permanently.

You'll at least have a solid ally in \cChupInventor{\full}. You last saw \cChupInventor{\them} six years ago, shortly after the Time of Deciding, although you keep in frequent contact through letter writing. The two of you grew up together and while both of you grew up poor, you spent days inventing, daydreaming, and supporting one another. No matter what, you could always rely on each other. It was your own research that supported \cChupInventor{\their} greatest invention: refrigeration coils. You were the one that convinced \cChupInventor{} to take the invention to the Temple. You were disappointed when they rejected it, but \cChupInventor{} was absolutely crushed. You have done your best over the years to try to support \cChupInventor{}, but \cChupInventor{\they} nurse\cChupInventor{\verbs} a mean grudge against the Church to this day, especially against the \cAntiChup{\cleric} who turned \cChupInventor{\them} down, \cAntiChup{\full}. You are increasingly concerned about how fixated \cChupInventor{} remains on this.

Six years ago, you were supporting \cChupInventor{} in a different way. You were a junior scientist then, brought along to the ``Time of Deciding’’ at the \pSchool{} as a PR move, a poor kid who made good. You were supposed to stand around, look clever, and stay out of the way. But just before you traveled to the \pSc{}, an influential courtier from the \pFarm{} named \cEvil{\full} approached you and made you an offer you couldn't refuse. You were given replicas of the magical stones used for voting, and tasked with swapping them in for the real stones before votes were distributed, then swapping the real stones back in after the votes were counted and the direction of the Storm determined. The fake stones would then be a huge source of unregulated magic that you could do with as you pleased. As further incentive, you were told that performing this task ``would work wonders for your career.'' You were hesitant, but you knew that due to your family and less prestigious education in the eyes of those in power, this would be the only way you could achieve your dreams. So you agreed. You completed the mission without getting caught, and soon learned the horrifying results — the treaty between the three nations broken, war with the \pShip{}, and the 12 students who had voted to direct the Storm mysteriously dead. You returned home with a heavy heart, carrying the fake stones brimming with power from the 12 dead students, and gave them to \cChupInventor{} to empower some of \cChupInventor{\their} inventions even after being banned from the Temple. Even though you gave the stones away to a good cause, the guilt of your actions weighs on you. But who could you possibly tell? So you've told no one, carrying the burden alone.

The rest of your payment for swapping out the stones soon came through — \cDiplomat{\full}, an important \pTech{} diplomat who you had accompanied to the \pSchool{}, promoted you to a high station in the scientist guild (one that someone of your background could never have achieved otherwise) and put you in charge of stopping the Storms. You are grateful to \cDiplomat{} for all \cDiplomat{\their} mentorship and help to your career, but now you wonder if \cEvil{} hasn’t been laughing at you the whole time after the disastrous events that occurred with your help. Regardless, you have to steer anyone investigating what happened six years ago down some dead end or distract them. There is no denying your fingerprints are all over that mess, and losing your job would be the least of your worries if you get caught. Plus, \cChupInventor{} might go down with you, since \cChupInventor{\they} accepted the fake Voting Stones and as far as you know is still using them as power sources.

But this whole experience of being thrust to the pinnacle of society has been one harrowing gamble after another. You authorized the building of the array years ago, rolling the dice that it would end up being useful. At the time, it was a straight up guess that the Storm was coming from another realm. You also don’t actually know that your data is more reliable now than it was in those early days - maybe someone or something is still meddling and just got more subtle and harder to detect? Especially in the last six months, as things came down to the wire, and no answer had yet materialized, you began to panic. For \cTechGod{}’s sake, you didn’t actually know for sure that the Storm originates in the Divine Realm until today! And it’s still not a sure thing in your mind. What is at Coordinate Zero? Could something \emph{even worse} than the storms happen if you destroy it? Unless \cCurse{} has something, there’s no way to even check! It would be the biggest risk yet to send the Storm someplace and just\ldots{} hope.

So you started looking for a potential way out. You wouldn't have expected the Church to be your solution, but sometimes life takes you in unexpected directions. You got the idea from talking with a young Initiate of \cTechGod{}, \cScholarship{\full}, at the fancy social functions you are forced to attend as part of your lofty position. Both of you hate all the hobnobbing and politicking at such events and prefer to be off pursuing your passions, so despite the difference in age, you felt from the beginning a certain sense of comradery and would keep each other company. You haven't revealed anything about your crimes of six years ago, but you did express some doubts about the progress of your research into the Storms and desire for an exit strategy. Your young friend surprised you by encouraging you to pursue a career in the Church, and you surprised yourself by realizing that it called to a spiritual side you didn't know you had. And from a pragmatic standpoint, if you were a \cHeadScientist{\cleric} of \cTechGod{}, you'd be somewhat protected from the legal system of the \pTech{}. 

At \cScholarship{}’s encouragement, you wrote to \cBeetle{\full}, a Cleric of \cTechGod{} at the \pSchool{}, expressing interest in joining the Clergy, and were astonished when \cBeetle{\they} wrote back saying \cBeetle{\theywere} thinking of leaving the Priesthood in order to become principal of the \pSc{} and were looking for a successor. Of course, \cBeetle{}'s Cleric position is only available if \cBeetle{\theyare} selected as the next principal of the \pSc{}, so you need to make sure that happens. Otherwise, the best you could be is inducted as an Initiate, and Initiates don't have nearly the same legal immunities. And 42 is a little late to enter the game — you'll have to work very hard to convince \cAntiChup{\full} and \cBeetle{} that you actually want to become a \cHeadScientist{\cleric} for reasons beyond just saving your own skin, and are suited to the role. 

Part of that convincing is working with \cEbbPriest{\full}. \cEbbPriest{} is a scholar and \pShippie{} \cEbbPriest{\cleric} of \cEbb{} researching \pEarth{}'s creation story. \cBeetle{} has approved this as a project for you to work on to demonstrate your aptitude for theological work. You have asked your friend \cScholarship{} to assist with this work, as you know \cScholarship{} is unhappy under \cScholarship{\their} current mentor \cAntiChup{} and wants to switch to \cBeetle{}. \cBeetle{} for whatever reason does not seem to like \cScholarship{} much, so \cScholarship{} has asked you to keep \cScholarship{\their} involvement secret for now, so that \cBeetle{} doesn’t interfere. Regardless, it will be nice to work together on such an interesting field of research.

You haven't been back to the \pSc{} in six years. It feels a little surreal to be back, after you were whisked home and into your successful new life in the shadow of the deaths of 12 children. You were restless upon arriving, so you wandered off through the gardens. As you wandered, you fiddled with some of your technology. You always carry many small projects with you. Most of them are novelties — little more than fidget toys. But sometimes there really is no replacement for a self-mixing bowl and you are suddenly the most popular person in the room. On your way back to the rest of the \pTech{} contingent of Advisors, you (literally) ran into a stranger. \cChupAvenger{\They} introduced \cChupAvenger{\themself} as \cChupAvenger{\full}, gave you a warm smile, and waved off your apologies. As you continued on your way, you realized you felt a little lighter, almost giddy. \cChupAvenger{\Theyare} really cute; maybe \cChupAvenger{\they}'d be free for dinner sometime this weekend?

The last time you were at the \pSchool{}, you didn't pay much attention to the role of advisor, but now you are older and wiser. You feel like you’ve aged a lifetime, not just six years. You realize that the role advisors play in establishing voting authority can make or break a student's future career, and make or break international treaties. So you've taken a little time off of worrying about yourself to investigate the \pTech{} students who are staying for the ``Time of Deciding.’’ You already know \cScholarship{}, and you find \cScholarship{\them} trustworthy and intelligent. If \cScholarship{\theydo} manage to get out of sponsorship by \cAntiChup{}, \cScholarship{} likely will need any boon possible for the future. But if \cScholarship{} does not, you believe at least \cScholarship{\their} future should be secure.

As if you didn't have enough on your plate, you've noticed lately that you seem to have some odd memory gaps scattered across the last several years. You have plenty of memories of working in the lab, but your personal life seems\ldots{} thinned out somehow. It is a vague, subtle, yet troubling feeling that you haven't quite been able to shake. Thus far, you've been attributing it to stress and your abysmal work/life balance, but this off-kilter feeling persists.

This weekend is going to be a challenge. You've got to scramble for more data to inform your research into how to end the Storms and decide how to present the shocking results to those gathered here. You've got to keep an eye on \cChupInventor{} and support your friend. And you've got to make sure your plan to hide behind the protection of the Clergy is airtight. You aren't one to pray for luck, but you can certainly pray that \cTechGod{} grants you the skill and wisdom to see it all through.

\begin{itemz}[Major Goals]
    \item Decide with \cAssistantScientist{}, the Council Members (\cAntiChup{} and \cTechStar{}), and your patron \cDiplomat{} what to do with your research into how to end the Storms, and how to frame the results during your Saturday morning presentation. Should the Storm be sent to Coordinate Zero or Coordinate One in the Divine Realm, especially when you don’t know what is at those locations? If so, you'll need to perform a ritual to prepare the Lightning Rod before the Ritual to Control the Storm is conducted. Whatever happens, the Storm \textbf{must not} be sent to your homeland, or it will destroy all of your work of the past six years.
    \item Solidify an escape plan, either through \cBeetle{} or another way, in case it becomes necessary. To escape through the Clergy, you have to help \cBeetle{} win the Principalship so that \cBeetle{\their} Cleric position opens up for you to fill. To convince \cBeetle{} of your commitment to becoming a \cHeadScientist{\cleric} you need to work with \cEbbPriest{} and \cScholarship{} on questions surrounding the creation of magic, humanity, and \pEarth{} itself.
    \item Keep anyone from investigating what happened to the students six years ago too closely.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Get to know \cChupAvenger{} a bit. \cChupAvenger{\Theyare} cute and feel\cChupAvenger{\verbs}\ldots{} comfortable? Safe? Familiar? It is strange, but nice.
    \item Protect \cChupInventor{}, including possibly from \cChupInventor{\them}self.
\end{itemz}

\begin{itemz}[Notes]
    \item You were at the \pSchool{} six years ago as an advisor, and were secretly tasked with swapping out the voting stones for fakes by \cEvil{}. You had no inkling of the terrible events that would follow until it was too late.
    \item You have a fancy ring that you've been carrying in your pocket. The eerie thing is, it is not properly sized for you and you have no idea where it came from. You considered getting rid of it, but for some unknown reason the thought of doing so brings tears to your eyes and an ache to your heart.
\end{itemz}

\begin{contacts}
    \contact{\cAssistantScientist{}} Your primary assistant — reliable, smart, and dedicated, albeit a little closed off and distracted at times.
    \contact{\cChupInventor{}} Your closest friend for most of your life. \cChupInventor{} is a brilliant inventor, but \cChupInventor{\their} greatest invention was stymied by the Church. You aren't sure if you should continue to enable \cChupInventor{\their} grudge.
    \contact{\cBeetle{}} The \cBeetle{\cleric} who has offered to train you as a \cHeadScientist{\cleric}. It's a good escape plan if the public reaction to your Storm research goes poorly or your crimes from six years ago are discovered.
    \contact{\cEbbPriest{}} The head scholar on the creation myth project. You haven't met in person before, but \cEbbPriest{\they} seem\cEbbPriest{\verbs} competent, albeit a bit of a stickler for rules.
    \contact{\cEvil{}} The person who gave you the fake Voting Stones, both catapulting you to your current position and making you complicit in the greatest crime of the modern era. 
    \contact{\cDiplomat{}} A senior diplomat from the \pTech{} and the primary patron of your research into ending the Storms. 
    \contact{\cScholarship{}} A friend and student who turned you on to the possibility of joining the Clergy, and who seems very eager to help you and \cEbbPriest{} with the research into the creation of \pEarth{}.
    \contact{\cChupAvenger{}} A charming stranger you just met who seems to set your heart aflutter.
\end{contacts}

\end{document}
