\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}

You are \cTechStar{\full} (\cTechStar{\they}/\cTechStar{\them}), 19 years old and a technological prodigy. You are a first year student at the \pSchool{}, and come from the (usually) fair but rigid \pTech{}, whose \cTechGod{\Deity} \cTechGod{} inspires innovation. In your life and experience, however, the mortal church of \cTechGod{}, overseen by corrupt bureaucrats and religious figures, severely limits the benefits of progress to all. The one thing you want more than anything else is to follow your dreams of spreading your technology to the world, and you won't let anything stop you. An idealist to the core, you know you could use the tremendous opportunities of your new position as Tech Star, and the spectacular invention that won you the title, to help those less able to help themselves.

Growing up as the beloved only \cTechStar{\offspring} of a loving and moderately well to do family in the \pTech{}, you always knew you wanted to be an inventor. You began in the traditional way, dissecting the family suction cleaner, to your parents' delight. They dutifully provided you with materials, tools, and the education you would need to succeed, and you have exceeded their wildest expectations by inventing VidCom (Video Communication) devices, which allow two people to communicate remotely \emph{(OOC Note: Think of these like long distance walkie talkies with a video screen rather than a phone; they only work in pairs)}. This concept is mind blowing in a world of letter writing, and your invention easily won you the annual TechStar competition. You almost felt sorry for the other competitors, but you knew your invention could do the world the most good.  

Upon winning the competition you were granted the TechStar Council position on The Council for a year, and admission to the \pSchool{} due to your innate magical ability, as well as a number of prestigious job offers that will be open to you once your education is complete. It's hard to keep up with the Council's work alongside all your schoolwork, but you do your best, attending Council meetings when absolutely necessary, voting by proxy when possible, and abstaining when the matters at hand are not in your area of expertise.

However, this has made making friends outside of the \pTech{} challenging. You have experienced the distrust that many of the students from the \pFarm{} and especially the \pShip{} have towards you. It’s hard to miss the whispers that follow you through the halls. It’s not fair that some of them seem to associate you with the ruling class just because you are on The Council, especially when you try to use your position for good. Thankfully, many of your fellow \pTech{} students have your back, as well as a few students from other nations who have looked past your role to see the real you.

You do understand it, though — you often feel the same way about \cLibAssist{\full}. While the \pFarm{} and the \pTech{} are on the same side, \cLibAssist{\their} family cut corners with curse trebuchets and got folks on both sides killed. All due to greed and incompetence, two things you can’t stand. It’s hard to look past that, and reminds you about the consequences of being too trusting. You don’t hate \cLibAssist{}, for sure, but you are cautious.    

Unfortunately, despite your lofty achievements and position, you feel enormously disappointed with the way the \pTech{} has handled the development and distribution of your VidCom devices.  You'd assumed that they would immediately enter mass production and be given to people around the country, selling for a reasonable price, but this did not occur. First, the church, led by \cAntiChup{\full}, refused to magically enable more than a handful of the devices, stating the masses were not ready for such technology. You appealed to the High Council, but by a mere one vote margin, your fellow Council members rejected your appeal and sided with the church. The Head of the \cHeir{\formal} family, \cFaledonParent{\full}, was the swing vote, not deciding until the last moment. The Council claimed that your VidCom devices were ``too important'’ to the war effort, and that handing them to the public would inevitably lead to them getting into the hands of the enemy. It's ridiculous!  You know there's a war on, but surely people being able to communicate with their loved ones would boost morale and national pride? 

You don't trust \cFaledonParent{} to deal fairly, or have the best interest of the people at heart — \cFaledonParent{\they} only want\cFaledonParent{\verbs} what benefits \cFaledonParent{\them}. However, there is one person you may be able to ask for help.  \cDiplomat{\full} is \cFaledonParent{\sibling}, the preeminent diplomat for all of \pTech{}, and, despite all of that, stood up for your VidComs to \cFaledonParent{\them}.  It wasn’t a big public show, but you witnessed numerous discussions outside of the council chambers where \cDiplomat{} argued that the technology would prove how advanced the \pTech{} really was and boost the entire country’s morale.  You have not had a chance to speak to \cDiplomat{} about this, but you hope you have a chance this weekend.    

Though you deeply distrust \cAntiChup{} and the church, you've been lucky to have the help — and friendship — of \cScholarship{\full}, who's always happy to chat or help you with your schoolwork. \cScholarship{} is an initiate of the church of \cTechGod{} and it is through conversation with \cScholarship{\them} that you keep any of your own faith active and remember the good that is in \cTechGod{}. \cScholarship{\They} \cScholarship{\have} even assured you that it is not \cTechGod{}’s fault that your VidCom devices are not distributed. You know if the church had more people like \cScholarship{}, your devices would succeed. You have even thought about asking \cScholarship{\them} to plead your case to the church, especially \cScholarship{}’s mentor \cAntiChup{}, the High \cAntiChup{\Cleric} of the church of \cTechGod{}. You haven’t yet, mostly because you are still so mad at \cAntiChup{}.

You have met \cAntiChup{\them} serving on the Council, and you know it was \cAntiChup{\them}, not \cTechGod{}, who stopped your VidComs from being mass produced. \cScholarship{} is too afraid to confirm it, but you can sense it. Your time on the Council has let you see how \cAntiChup{\they} manipulate\cAntiChup{\verbs} everything towards war and stagnation. You want to help \cScholarship{} get out from under \cAntiChup{\their} thumb, which you might be able to do if you find anything that shows proof of \cAntiChup{\their} corruption. Besides, the war seems like a mistake in the first place. Why can't the nations work things out peacefully? Why shouldn't people of all nations come together through your VidCom devices and see that they are not three separate nations, but one people, sharing the same planet? You feel that all three governments have mishandled the war just like the Council mishandled your invention. You are going to fix it — by yourself if that's what it takes.

There have been \emph{some} good things to come out of your TechStar win. For one, you ended up meeting an up and coming researcher named \cAssistantScientist{\full}.  \cAssistantScientist{} is one of the researchers who is figuring out how to stop the Storms, a research effort led by the \pTech{}. \cAssistantScientist{}’ is a bright mind trying to save the world using unconventional means. That and the fact that \cAssistantScientist{\they} come\cAssistantScientist{\verbs} from a middle class family and rose to prominence resonated with you. You started writing back and forth, and unlike most scientists, \cAssistantScientist{\they} actually seem\cAssistantScientist{\verbs} interested in your VidCom devices as a means of peace. Maybe this weekend, when \cAssistantScientist{\they} \cAssistantScientist{\are} presenting on the fruits of \cAssistantScientist{\their} research, you can ask for advice on how to proceed with the vote for where to send the Storm and what to do about the restrictions placed on your VidComs. You can’t wait.  

Your entrance to the \pSchool{} has provided you many opportunities, and some of them are directly related to your goal of spreading your tech to the world. Most importantly, you've heard credible rumors about the existence of a black market that sells tech from the \pTech{} at the \pSc{} — and a black market that sells tech MUST be able to activate it without reprisal from \cTechGod{}. Rumor has it that \cLibAssist{\full} is a runner for the black market, so \cLibAssist{\they} will be your point of contact — which sucks, as you are not a huge fan of \cLibAssist{}, so maybe you can figure out how do something without \cLibAssist{\them}. Hypothetically, if you can set up a stable supply chain of production for your VidCom devices for the black market, you'll be one step closer to your dream. You do not plan to part with the blueprints for your device this weekend, though.  

Whoever has the blueprint is the only one able to make the VidCom devices, and you're not ready to release your monopoly yet, so you haven't even made a second copy of them.  Pursuant to manufacturing more VidCom devices, you've made arrangements with a stellar engineer from the \pShip{} named \cBunker{\full} to bring you supplies with which to build VidCom devices here (``Misc. Magitech Parts'’). You're not entirely sure how much \cBunker{\they}'ll be able to bring you, but you hope \cBunker{\they} \cBunker{\are} bringing at least some. You know that it would be a challenge, but you honestly hope to be able to continue your conversations with \cBunker{}. \cBunker{} and you have actually started a secret correspondence (you know that \cBunker{} should not be talking across enemy lines) in order to get these parts, and you two have been in conversation about magical technology and engineering for a few months. \cBunker{\They} \cBunker{\have} a dream job and could teach you so many things. You've volunteered to help with the planned maintenance and repairs to the Bunkers that will be happening soon, and you're thrilled at the chance to work with \cBunker{} —  You look forward to that honor. 

While that plan may get things rolling, you have higher aspirations. If you could get \cTechGod{}'s blessing to activate your technology yourself, you wouldn't need the black market in the long run. \cTechGod{} has granted the power to oversee the activation of tech to the Temple, but they're clearly not acting in a manner that honors \cTechGod{} or your people any more, because they are keeping your tech out of the hands of the people whose lives it could greatly improve. Like most successful inventors, you have the magical power it would take to activate VidCom devices yourself, but not the know-how. While you have not opened up about this frustration with many people, you have found a kindred spirit in \cChupInventor{\full}, the diplomacy and political science teacher who is also an inventor whose technology was deemed not important. \cChupInventor{\They} \cChupInventor{\have} been your mentor, helping you see how broken the system is, and hinting to you that \cChupInventor{\they} may even have a way to get around the restrictions on activating tech, and that \cChupInventor{\they} will help more this weekend. In exchange, perhaps you can give \cChupInventor{\them} a pair of VidComs of \cChupInventor{\their} own. Maybe you two can go into business together and subvert all of these systems?

When you're not busy working out how to change the fundamentals of the church and your country, you've also got a couple of personal projects on your plate. Your friend \cDisney{\full}'s birthday is coming up on Sunday, and you want to surprise \cDisney{\them}. You met \cDisney{} on your first day at the \pSc{}, and even though \cDisney{\they} \cDisney{\are} from the \pFarm{}, you quickly fell in love with \cDisney{\their} goodness, optimism, and core belief in doing the right thing. \cDisney{} grounds you. \cDisney{} has confided in you (in strict confidence) that — remarkably — \cDisney{\they} \cDisney{\were} actually awakened recently from 200 years of magical sleep! From what \cDisney{\they} remember\cDisney{\verbs}, \cDisney{\they} \cDisney{\are} a member of the \cDisneySect{}, a splinter sect of the Church of \cFarmGod{} that wanted to get to the Divine Realm but was violently destroyed by the mainstream Church. Only \cDisney{\they} survived. While \cDisney{\they} remember\cDisney{\verbs} bits and pieces of the ritual to reach the Divine Realm, there are still some major gaps in \cDisney{\their} memory, especially about how to actually complete the ritual! You're sure that with a little research and innovation you can figure out a way to recover these lost memories together. It's a perfect birthday gift, and you know \cDisney{\they}'ll be so happy.

Maybe you and \cDisney{}'s other friends, \cAdopted{\full} and \cPirateChild{\full}, could plan a party for \cDisney{\them} too? You don’t have any particular opinions about \cAdopted{}. You don’t spend much time together, since you really don’t have a knack for the curse breaking magic that \cAdopted{} excels at. It’s really only when you are both hanging out with \cDisney{} that you interact. Unfortunately, you and \cPirateChild{} don't get along — you don't see eye to eye on \emph{anything}. You aren't sure what \cDisney{} sees in \cPirateChild{\them}. \cPirateChild{\They} seem\cPirateChild{\verbs} to take nothing seriously, constantly getting into trouble in ways that are not the smartest, and just generally being aggravating. Besides, \cPirateChild{\they} \cPirateChild{\have} been asking a lot of questions about your VidCom devices, and you are sure \cPirateChild{\they} \cPirateChild{\are} not just trying to be friendly, it sets you on edge that there’s an angle here that you don’t see yet. You don’t know why, but \cPirateChild{} really seems to want to be close to you, even though you constantly argue.

Speaking of \cDisney{}, \cDisney{\they} \cDisney{\are} very close to \cDisney{\their} mentor \cWildCard{\full}. While \cWildCard{} might have been the one to wake \cDisney{} up and \cDisney{\they} \cDisney{\are} justifiably grateful for that, you're pretty certain that \cWildCard{\their} motives were (and are) more than \cWildCard{\they} let\cWildCard{\verbs} on.  \cWildCard{} comes from a scholarly background and — even knowing about the \cDisneySect{} — \cWildCard{\they \have} not done anything to hurt \cDisney{}. But \cDisney{} is so attached and is talking about sharing with \cWildCard{} how to get into the Divine Realm. It would mean a lot to \cDisney{} if you brought \cWildCard{} in on your plan to restore \cDisney{\their} memories, and so you plan to talk to \cWildCard{\them} this weekend and see if you can trust \cWildCard{\them}. If you can, \cWildCard{\their} knowledge would likely be invaluable. Honestly, it would be good to have someone other than just you and \cDisney{} trying to get \cDisney{\their} memories back, especially because you don’t trust \cPirateChild{}, who has also been encouraging \cDisney{} to look into \cDisney{\their} past. You have your own reasons for wanting to get to the Divine Realm as well, though you have not told anyone about that. If what \cChupInventor{} promises does not come through, you can always go directly to the source and plead with \cTechGod{} personally about the ill behavior of the church. Perhaps \cTechGod{} would give you a way to activate your technology without the mortal church’s blessing.

On top of all of this, you also have started to date someone that you never would have expected: \cWarlordDaughter{\full}. \cWarlordDaughter{} is the \pShippie{} Warlord, \cLoud{\full}'s \cWarlordDaughter{\offspring}, and a \pShippie{} through and through. At first, it was hard not to be reminded of the \cLoud{\person} who is driving the war effort when you looked at \cWarlordDaughter{\them}. But then \cInitiate{\full}, one of \cWarlordDaughter{}’s best friends, was frequently unable to study with them, and somehow managed to convince you both to be partners on pretty much every project together instead. So you got to know \cWarlordDaughter{} — passionate and outspoken with a deep conscience and a desire to end this war. You ended up friends in spite of it all and spent hours, sometimes more — occasionally with \cScholarship{} as well — discussing life.  \cWarlordDaughter{} has told you about \cWarlordDaughter{\their} own fears about \cWarlordDaughter{\their} \cLoud{\parent}, that something magical has happened to \cLoud{\them}. You agreed to help investigate and have been working with \cWarlordDaughter{\them} to uncover what happened and how to reverse it. 

You eventually realized you were starting to catch feelings for \cWarlordDaughter{}, more than friendship, but were too shy. You don’t know what you would have done without the help of \cInitiate{\full}, who not only gave you encouragement, but promised that \cWarlordDaughter{} felt the same way. It was embarrassing, but both of you ended up sending secret letters to each other on the same day that were very flowery, the kind of letters you would send someone when you were 14, not 19: ``Do you like me? Check yes or no,” kind of silliness. Happily, both of you checked the yes box!

It has been a few months now, and you have fallen for \cWarlordDaughter{} more and more. But there is a crack in your happiness, or maybe a few cracks. \cWarlordDaughter{} and you both have found yourselves the target of both distrust from the other nation’s students and protected by those of your nation due to your political power, either perceived or real.  \cWarlordDaughter{}’s training to be a \cWarlordDaughter{\cleric} also makes it interesting and delicate, as you may be expected to convert if things get serious. 

Neither of you wants to upset your friends or cause more tension, so you have decided to keep this relationship secret from everyone except \cInitiate{} for now, who you now realize was happily playing matchmaker this whole time. You also know that in general \pShippie{} culture is polyamorous, and you don’t know if that is something that \cWarlordDaughter{} wants. You want to be okay with it, but no matter how much the \pTech{} frustrates you sometimes, you never have experienced that kind of relationship. Don’t people get jealous? Would you get jealous? You don’t know if you should bring it up prematurely or just wait to see what happens.  

Another event you are interested in this weekend is the Ceremony of Excellence. You know that this ceremony traditionally involves a demonstration of magical power. As one of the most magically gifted and creative students at the \pSc{}, you believe that honor rightfully belongs to you. You intend to do whatever it takes to convince \cMusic{}, the teacher in charge of the ceremony, to pick you for the student combat demonstration.

At the end of the day, while there are a lot of things going on that deserve your attention, if you can secure a route to activate and distribute your VidCom devices safely, you'll leave happy — there's simply too much at stake there to not. If you can make sure that \cDisney{} remains safe and happy, so much the better. And you can always turn to the advisors from the \pTech{}, \cAssistantScientist{}, \cHeadScientist{\full}, and maybe even \cDiplomat{} for guidance as you decide how to move forward and what choices and sacrifices must be made. This will be your weekend — you can feel it.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Secure a solid path to activate and distribute your VidCom devices to as many people as possible, preferably without accumulating debt to the black market or anyone else.
    \item Prepare a great birthday present for \cDisney{} — restoring \cDisney{\their} lost memories, and decide if you should ask for the help of \cWildCard{}. In doing so, help \cDisney{} recover the lost ritual to reach Divine Realm so you can speak to \cTechGod{}.
    \item Assist your new romantic partner \cWarlordDaughter{} with investigating what really happened to \cLoud{}.
    \item Bring down \cAntiChup{} at least a peg or two, and in so doing, help the system become fairer and help \cScholarship{} get away from \cAntiChup{\their} influence.  
    \item Help \cBunker{} maintain the Bunkers, and learn as much as you can from \cBunker{\them}.
    \item Show your stuff as one of the combat demonstrators at the Ceremony of Excellence.
    \item Determine if you can and should keep your relationship with \cWarlordDaughter{} a secret.
\end{itemz}

\begin{itemz}[Notes]
    \item You are a first year student.
\end{itemz}

\begin{contacts}
    \contact{\cAntiChup{}} the High \cAntiChup{\Cleric} of the church of \cTechGod{} who to you represents everything that is wrong with \pTech{}.  You really do not like \cAntiChup{\them}. 
    \contact {\cAssistantScientist{}} A pen pal and young scientist whose background matches your own. You wonder if \cAssistantScientist{\they} can help you with your VidCom issue.
    \contact{\cDisney{}} Your friend and confidante who magically slept for two centuries. Sweet and innocent, with some memory issues.
    \contact{\cBunker{}} The brilliant engineer behind the \pSc{}'s Bunkers. Also bringing you supplies to manufacture more VidCom devices.
    \contact{\cChupInventor{}} Another disgruntled inventor and the school’s political science teacher.  \cChupInventor{\They} \cChupInventor{\are} helping you understand how you can fight against the corruption in \pEarth{}.
    \contact{\cWildCard{}} The \cWildCard{\person} who woke \cDisney{} from \cDisney{\their} enchanted slumber. 
    \contact{\cPirateChild{}} A friend of \cDisney{}'s who you don't like one bit. The feeling is mutual.
    \contact{\cScholarship{}} A friend you often study with, who you feel like you can rely on and want to help.
    \contact{\cLibAssist{}} A fellow student who helps out in the Library, and, more importantly, is a runner for the black market. Maybe \cLibAssist{\they} can help you distribute your VidCom devices?
    \contact{\cWarlordDaughter{}} You two have been dating for a few months now and you are smitten. But you are keeping things secret for now. It is a strain, but you also feel it is necessary to avoid drama with your fellow students.
    \contact {\cInitiate{}} WarlordDaughter{}’s close friend, and also the matchmaker behind bringing you and \cWarlordDaughter{} together. You owe \cInitiate{} but are not sure how to repay \cInitiate{\them}. 
\end{contacts}

\end{document}


