\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cBeetle{}}

You are \cBeetle{\intro}, and 43 years old. You are a \cBeetle{\cleric} of \cTechGod{\intro}, the patron \cTechGod{\God} of the \pTech{}, who inspires innovation and growth. You teach Religion at the \pSchool{}, and have for the last 18 years. You are incredibly knowledgeable about the Deities of \pEarth{}, and the religion derived from worship of the Pantheon, and enjoy sharing that knowledge with each new class of students. Still, you are ready to try for the next stage in your life, hopefully by taking over as Principal when \cPrincipal{\intro} steps down at the end of the weekend.

Your life growing up in the \pTech{} was wonderful. Your family was supportive of your interest in religion, and had the financial means to grant you easy access to the Church. In one program, you were assigned a pen pal from the \pFarm{} named \cMusic{\intro}. The two of you hit it off, and continued to correspond long after the program ended. You loved seeing music as sacred through \cMusic{\their} eyes, how eager \cMusic{\theywere} to help others and make the world a better place, and \cMusic{\their} courage in \cMusic{\their} insistence to always listen to \cMusic{\their} inner voice.

Your religious studies were tremendously fulfilling, and you entered the Clergy fairly young. You excelled in your studies, and were eventually granted the honor of taking care of the Celestial Beetles. With this new phase in your career came more time to study religion more broadly. You became deeply interested in the ancient history of the world and the creation myths of the various countries, which led to you starting a correspondence with a \pShippie{} scholar, \cEbbPriest{\intro}. This study also led you to learning about the connections between the Gods, and between the Gods and their Avatars. A God without their Avatar would have substantially less ability to affect \pEarth{} and protect their people. You have heard rumors in hushed tones that the Giant Hummingbirds of \cFarmGod{\intro} haven't been seen in over a decade, which explains why the Celestial Beetles of \cTechGod{} are so carefully protected. They are kept sequestered in the High Temple of \cTechGod{} with elite guards and dedicated clerics such as yourself watching over them day and night.

It bothers you that your deep devotion to \cTechGod{} and your respect for the truths of your religion are not universally shared among the Clergy, especially by \cAntiChup{\intro}, \cTechGod{}'s Grace \cAntiChup{\themself} (the leader of the entire Church). \cAntiChup{} seems less concerned with the will of \cTechGod{} and more interested in the power and intrigue involved in more worldly affairs, such as winning the war between the nations. You know this war and the Betrayal of the \pShippies{} can't truly be the will of \cTechGod{}, and you feel sure that \cAntiChup{} will someday be shown the error of \cAntiChup{\their} ways. Sadly, \cAntiChup{\their} protégé \cScholarship{\intro}, now a student at the \pSchool{}, is clearly following in \cAntiChup{\their} footsteps. \cScholarship{\They} run\cScholarship{\verbs} errands for \cAntiChup{} all the time, including off campus (which is a big no-no). You are sure that at least part of it is illegal. Sure, \cScholarship{} is deeply attentive in your classes and never has demonstrated any of \cAntiChup{}’s arrogance, but you still don’t trust \cScholarship{\them}. If only you'd been available to sponsor an initiate before \cAntiChup{} got \cAntiChup{\their} claws into \cScholarship{}. But now it is too late for \cScholarship{}, at least.

As your career grew and changed, you were selected to teach at \pSchool{}. When you got there, you found to your great delight that your childhood pen pal \cMusic{} was joining the faculty at the same time as you! While \cMusic{} can be good-naturedly nosy, \cMusic{\they} clearly \cMusic{\have} a good heart and always make\cMusic{\verbs} you laugh. You've never had a better friend. You honestly are not surprised that you both ended up finding your calling in teaching.

You also have a soft spot for \cHeir{\intro}, whom you met four years ago when you were back home on break looking after the Celestial Beetles. \cHeir{} is heir to the powerful but ruthless \cHeir{\formal} family, and as such has never wanted for anything except a genuinely loving family and the freedom to choose \cHeir{\their} own fate. \cHeir{\They} ran away from home to join the Church and spent weeks under your tutelage before \cHeir{\their} family forced \cHeir{\them} to come back. \cHeir{} is so bright, clever, and good-hearted, and you sympathize with \cHeir{\their} plight. You hope that \cHeir{\their} best friend, \cAmbition{\intro}, isn't too much of a bad influence; \cAmbition{\theyare} a rank opportunist and social climber who you fear is just using \cHeir{} because of \cHeir{\their} family name. You heard recently that \cAmbition{} is interested in joining the Clergy, which you oppose, as you don't trust that it is for the right reasons. Also, \cAmbition{} is friends with \cScholarship{}, and that means \cAmbition{} is likely also under the influence of \cAntiChup{}.

You are also in a stable, long distance polyamorous relationship with \cJuniorStatesman{\intro}. The two of you met on one of your trips back to the main temple of \cTechGod{}. As a teacher at the \pSchool{}, you do not get nearly enough opportunities to work with the Celestial Beetles as you would like. So you take them when you can get them, and about 8 years ago was one such opportunity. On your way out of the area of the temple where the Beetles are housed, you ran into a private tour and met \cJuniorStatesman{}. \cJuniorStatesman{\Theywere} polite and friendly, but you thought no more of the meeting until you went out to an eating hall that night for dinner. There was \cJuniorStatesman{}, eating alone at a table for two. The two of you made eye contact, and the rest is history. 

When \cJuniorStatesman{} first wrote to you about \cJuniorStatesman{\their} then current partner, your own heart broke a little. You hadn’t even realized you were crushing on \cJuniorStatesman{\them} until it became clear that a relationship was not an option. Except maybe it was? The \pTech{} is a firmly monogamous culture, ostracizing those who attempt to explore anything more deviant than a quiet, extramarital affair. But where the \pTech{} view relationships as these solid, unchanging monoliths, the \pShippies{} are more flexible. Like the difference between the mountains and the tides, their relationships ebb and flow, and polyamory is common. While the concept felt weird and foreign to you at first, when \cJuniorStatesman{} admitted \cJuniorStatesman{\their} growing feelings for you, you wanted to try it. Your romance quickly blossomed through your letters, but time in person wasn’t easy to arrange. And oh what a laugh the trickster god must have had when the war started less than 6 months later, drawing battle lines between the two of you. 

Six years ago, the two of you had elected to spend the ``Time of Deciding’’ at \cJuniorStatesman{}’s home, since the Storm was expected to hit the \pTech{}. That week was one of the most stressful of your life — the Storm hitting the \pShip{} when they weren’t prepared at all. The devastation and loss you witnessed personally — never mind the stories you’ve heard from elsewhere — shook you to your core. But in the short term, you first had to find a way to get back to the \pSchool{} without being recognized. No one could be allowed to find out that a \cBeetle{\cleric} of the \pTech{} was in 2nd Fleet during the Betrayal. There would be no questions, only retribution.

With the war on, your rendezvous have had to become increasingly more clandestine. Teachers at the \pSchool{} are supposed to be neutral entities, and publically dating a politician of the \pShip{} doesn’t exactly scream neutrality. You already push your luck by returning to the temple regularly to interact with the Celestial Beetles. You can’t imagine either the Principal of the \pSc{} or your fellow citizens of the \pTech{} would be too thrilled, but \cJuniorStatesman{} is worth the risk. 

Three years ago, \cJuniorStatesman{} came to the ``Time of Deciding’’ at the school. The two of you had been looking forward to spending as much time together as possible, especially because \cJuniorStatesman{} had broken up with \cJuniorStatesman{\their} previous partner about a year prior, so you were the only ones currently in each other’s lives. But when \cJuniorStatesman{\they} arrived, things became a touch more complicated. You’ve known \cEthics{\intro} since you started teaching at the school; \cEthics{\they} predate\cEthics{\verbs} you by two years, and you’ve been fast friends for over a decade. Like \cMusic{}, \cEthics{} is a bastion of compassion, care, and thoughtfulness. You two have debated everything, and even admitted to each other your quiet sympathies for the \pShippies{}. You share it all. So it was immediately obvious to you that \cJuniorStatesman{} and \cEthics{} were smitten with each other. The three of you sat down to talk about it. You had some feelings of loss about giving up part of your precious time with \cJuniorStatesman{}, but you’d never felt such a strong burst of compersion either. So with your blessing, \cJuniorStatesman{} and \cBeetle{} had themselves a little fling that weekend. While each seemed to enjoy the time, they have not pursued a relationship since. You aren’t sure why, since each has confided in you that they still like the other.

You wouldn't mind starting a second relationship yourself, but alas no one has currently expressed any interest. You don't meet a whole lot of new people, except on holiday, given that you teach at the \pSc{}. Sometimes it takes an outside force to shake things up and make you realize something you hadn’t noticed before, like how wonderful being around \cEthics{} makes you feel. \cJuniorStatesman{} may not be the only one interested in pursuing a romantic connection with \cEthics{}\ldots{} You and \cJuniorStatesman{} generally talk about changes to the relationship structure before implementing anything, though, so before you act, you want to chat with \cJuniorStatesman{} about it. That said, you do not have a relationship with veto power — it is possible to have conversations around making sure needs are still met despite a change in the relationship structure without anyone mandating the other's actions.

Having been a teacher of religion almost as long as you have been a \cBeetle{\cleric}, you are enormously honored and excited that \cPrincipal{} is considering you to be \cPrincipal{\their} successor as Principal of the \pSchool{}. It looks like you, your oldest friend \cMusic{}, or \cChupSecond{\intro} will be securing the promotion by the end of the weekend. Each of you has been given a task usually performed by the Principal, and yours is the management of the powerful ritual used to renew the Ley Lines that support the school and spread magic throughout the lands. You are an expert in wrangling people and ensuring that complex processes go off without a hitch, so you are confident that you can impress \cPrincipal{} and ensure that the Ley Lines are at full strength. Strengthening the Ley Lines will require a (temporary) sacrifice of magical power. You feel a bit salty about the fact that \cMusic{}’s and \cChupSecond{}'s assignments don’t require such a sacrifice, but the Ley Lines must be maintained and you are determined to impress \cPrincipal{}, so there is nothing for it. You are also a bit salty that \cChupSecond{}, a relatively new teacher, was put in charge of the most important task of all, ensuring the execution of the Ritual to Control the Storm, and a small part of you hopes that \cChupSecond{\they} will not be up to the task and will need to be bailed out by the Principal. Maybe you can assist as well, which should help your chances too.

Returning to the subject of religion, one year ago on a school break, you returned to the main temple (per usual every chance you get). One afternoon, while you were the only one in the room, you received a private message from one of the Celestial Beetles! You never would have thought yourself an appropriate recipient, what with your job at the \pSc{} meaning you had to mostly give up taking care of the Beetles (at this point you really just visit them once or twice a year), but apparently \cTechGod{} thought otherwise? The message simply said, ``bring me with you, but don't tell anyone,'' so you did. Smuggling the Beetle out past the guards wasn't easy, but you managed it.

The Beetle has provided you with many small messages this past year that have been helpful. One of the most noteworthy messages was that something is wrong with the Avatar of \cEbbFull{\intro}. You want to help somehow, but you aren't sure how to approach the \pShippie{} Clerics, \cEbbPriest{} and \cFlowPriest{\intro}. They are probably trying to keep the matter quiet, and would not be pleased that you know. After all, a sick or wounded Avatar is a situation many would love to capitalize on. But you want to help. \cFlowPriest{} has been a wonderful fellow teacher and for a long time you have had correspondence with \cEbbPriest{}, centered around collecting different creation myths of the world and analyzing the differences. This situation needs to be remedied quickly.

While all of the Beetle's messages have been useful, you have a sense that something about this weekend, the ``Time of Deciding,’’ is the true reason it is here with you. Afterward, it will have to go home. Of course, IF you become the principal, you can't be the one to take it home — it would be one of the downsides of becoming Principal. As long as you serve in that role, you cannot leave the school grounds without terrible consequences to the \pSc{}. In fact, you would even have to give up being a cleric of \cTechGod{}. (Hmm\ldots this also has some implications for your relationship with \cJuniorStatesman{} and anything you might start with \cEthics{} that you maybe hadn’t considered.) You would need to give the Beetle to another Cleric of \cTechGod{}, except you don't trust \cAntiChup{} or \cScholarship{}, who is still just an Initiate anyway. For the last week, you've been scouting around for a Cleric that you can trust to take the Beetle safely back to the \pTech{}, to no avail. There was no one you trust that you could manage to get on the advisor roster in time. 

However, you're in a unique position to recommend a replacement Cleric (must be at least 22 years old, which removes most of the students). If you find someone you deem worthy, you can essentially fast-track their religious career to replace you, without them having to go through years and years as an Initiate, and send the Beetle home with them. And you just may have a candidate for that solution — \cHeadScientist{\intro}. \cHeadScientist{} wrote to you a few months ago expressing interest in joining the Clergy after a meeting with an honest young initiate, and you have been pretty impressed with \cHeadScientist{\their} intellect and spirituality. If you can successfully induct \cHeadScientist{}, that takes care of returning the Beetle safely to your nation — IF \cHeadScientist{\theyare} trustworthy. To measure \cHeadScientist{}'s trustworthiness and faith, you have asked  \cHeadScientist{\them} to work with \cEbbPriest{} on a research project on the Creation of \pEarth{}. 

You also have recently talked to \cLibrarian{\intro} about some of your research, something you know you have talked to \cLibrarian{} about before, and which \cLibrarian{\they} always seemed interested in, but of course pulled in so many directions. But when you brought it up again this morning, to your surprise, \cLibrarian{\they} asked to be involved, so you also pointed them towards \cEbbPriest{}. The Creation necessarily lies in the ancient pre-history of \pEarth{} and it has always fascinated you. You and \cEbbPriest{} have long corresponded about it. You are eager to learn what the group discovers, but also intend to demonstrate your delegation skills to \cPrincipal{} by not micromanaging \cHeadScientist{} or \cLibrarian{} in the process.

This weekend will be a full one. Earning the principalship and all of the difficulty that goes with the new role will be one thing. Getting the Celestial Beetle home safely, and trying to figure out why it needs to be here this weekend, will be another. At the end of the day, though, the thing that will make you happiest is spending time with \cJuniorStatesman{} whenever you have the chance, and deciding what, if anything, to do about your newly recognized attraction to \cEthics{}.

\begin{itemz}[Major Goals]
    \item Keep an eye out for any suspicious activity that could disrupt this weekend’s crucial events — the ritual to restore the Ley Lines, the Ritual to Control the Storm, and perhaps the treaty negotiations. \cTechGod{} must have sent the Celestial Beetle here for a reason, and you intend to see it through! 
    \item Spend time with \cJuniorStatesman{} and decide whether you wish to start a romantic relationship with your friend \cEthics{} as well.
    \item Win the promotion to Principal. To this end, ensure the ritual to restore the Ley Lines is completed successfully. Your competition for the position is \cMusic{} and \cChupSecond{}.
    \item Find a Cleric of \cTechGod{} you trust to bring the Celestial Beetle back to \pTech{} with them. Right now, evaluating \cHeadScientist{}'s worthiness to become a \cHeadScientist{\cleric} of \cTechGod{} seems like your best bet since you don’t trust \cAntiChup{} or \cScholarship{}. Your evaluation hinges on \cHeadScientist{}’s ability to successfully work with \cEbbPriest{}. You can only make \cHeadScientist{} a \cHeadScientist{\cleric} if you win the principalship, but if you don't become the principal, you could always take the beetle home yourself.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Make sure the Storm does not get sent to the \pTech{}. To that end, help the \pTech{} students collect the most Voting Stones in order to direct the Storm by convincing the other teachers and advisors to give them their Voting Stones. By that same token, you \textbf{really} don’t want to see the Storm sent to the \pShip{} again either\ldots 
    \item Prevent \cAmbition{} from negatively influencing \cHeir{}.
\end{itemz}

\begin{itemz}[Notes]
    \item The ritual to restore the Ley Lines is critical for maintaining the School and ensuring that magic continues to flow throughout \pEarth{}. It would be terrible if something were to disrupt the ritual or endanger the Ley Line Nexus — magic throughout \pEarth{} could go haywire, or slow to a mere trickle, with devastating consequences. 
    \item You teach religion, covering all aspects of the worship of the Pantheon of \pEarth{}n Deities. You pride yourself on your objectivity when teaching despite being a \cBeetle{\cleric} of \cTechGod{}.
    \item You were not at the school six years ago when tragedy struck and twelve students perished. You had gone to \cJuniorStatesman{}'s home among the \pShip{} to spend time together.
    \item Any magitech device made by \pTech{} citizens must be empowered by a Cleric of \cTechGod{} according to Church doctrine. Any device that is activated by another means is both illegal and blasphemous. Sometimes you wonder if this doctrine is too strict, and stifles innovation, though. The much simpler magical items crafted by the \pShippies{} do not need to be empowered in this manner.
\end{itemz}

\subsubsection*{Contacts}
\begin{contacts}[Contacts Relevant to Finding the Next Principal]
    \contact{\cPrincipal{}} The Principal of the \pSchool{}. \cPrincipal{\Their} departure leaves big shoes to fill.
    \contact{\cMusic{}} A good friend from your youth and a fellow teacher, as well as your competition for the position of Principal.
    \contact{\cChupSecond{}} A relatively new teacher who is also competing with you for the Principal position. 
\end{contacts}

\begin{contacts}[Personal Contacts]
    \contact{\cJuniorStatesman{}} Your long time, long distance, romantic partner. You care about \cJuniorStatesman{\them} deeply.
    \contact{\cAntiChup{}} A fellow Cleric of \cTechGod{}, although ``fellow'' is the opposite of your feelings for \cAntiChup{\them}, as \cAntiChup{\they} twist\cAntiChup{\verbs} the religion you love for petty, personal reasons.
    \contact{\cHeadScientist{}} Your prospective replacement in the Clergy. You have been exchanging letters recently as you try to gauge \cHeadScientist{\their} suitability to join the Clergy.
    \contact{\cScholarship{}} One of your students, as well as \cAntiChup{}'s mentee. Sadly, \cScholarship{\they} seem\cScholarship{\verbs} to be following in \cScholarship{\their} mentor's footsteps.
    \contact{\cEbbPriest{}} A \cEbbPriest{\cleric} of \cEbbFull{\intro} who shares your love of history, particularly the pre-history of \pEarth{}, and is conducting research on that subject.
    \contact{\cEthics{}} The Morality and Ethics teacher at the school, and a dear friend for whom both you and \cJuniorStatesman{} seem to have romantic feelings. 
    \contact{\cHeir{}} Another favorite student of yours, with a good heart and a free spirit, who resists being the heir to the \cHeir{\formal} dynasty. 
    \contact{\cAmbition{}} \cHeir{}’s best friend and a rank opportunist, whom you think is a bad influence.
\end{contacts}

\end{document}
