\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cLibrarian{}}

You are \cLibrarian{\full} (\cLibrarian{\they}/\cLibrarian{\them}) from the \pTech{}, and the Librarian at the \pSchool{}. And\ldots that's about all you remember. You aren't even sure you remember that so much as your parents impressed these details upon you several days ago. You must be from the \pTech{}, as that is where your family is. You must be the Librarian, for you found your name on the office door. 

You could swear your parents sent you back to the \pSchool{} with a letter that provided more details about who you are and why you can’t remember anything, but now you can’t find it. You must have misplaced it in your confusion. How frustrating! Hopefully you can find it before it falls into the wrong hands. In your searching, at least you were able to find several cordial letters from a scholar of magical theory, \cWildCard{\full}, with whom you are evidently friends. The two of you seem to have corresponded about a variety of topics concerning the history and theory of magic, the Relics, and the Divine Realm.

You killed someone. You must have. Amnesia like this is the punishment the Deities dole out for murder. It was supposed to be a mercy; a way to make it easier to rehabilitate and reintegrate people into society. But how can you repent what you cannot remember? And the people of \pEarth{} have no love of amnesiacs. Many are still shunned by society, as if someone's desire to murder another human being were as innate as one's hair color, instead of a product of the circumstances in which they were raised or found themselves.

So at your parents’ (apparently\ldots that’s who they told you they were) urging, you are keeping quiet about it. You returned to your job at the \pSchool{}, and now you spend hours wandering the stacks when no one is looking, hoping to find so much as a single clue about who you were. You've found scraps. Just scraps for now, but if you keep looking, surely something will come together. You pray to \cTechGod{} in the quiet of your morning meditations, and you can't help but feel \cTechGod{\their} hand on you. \cTechGod{\They} want you to succeed. Some days you wish you could talk to \cTechGod{\them} face to face.

So what do you know? You know that you are patient and kind. Your office is full of plants that your body knows how to care for almost on an instinctive level — and though there are many, you feel at ease as you care for them. As for kindness, you can feel it in the way the students talk to you. They come to you for little things, or just to talk, and even the most trivial request fills you with joy to accommodate. They also, fortunately enough, seem to like you enough to tolerate your missteps as you learn to be yourself again. It's not much, but it's a start.

You've worked out that \cPresident{\full}, \cLibAssist{\full}, and \cAmbition{\full} are three students that you spent a lot of time with in the Library before. They seem to be your assistants, and have been a godsend in getting your work done — well, for the most part. You seem to be very good at reading people, and have noticed that while the other two are genuinely helpful and kind, \cLibAssist{} seems to do subtle things to undermine you or add to your confusion. Then again, you are so easily confused these days, so maybe you are being too harsh and it is just your imagination. You also have picked up that \cLibAssist{} and \cAmbition{} seem to have some sort of rivalry, though both get along with \cPresident{}. Regardless, all three of your assistants seem to know a lot about the Library, and you've learned a bit about how to navigate the place safely by claiming to want to test their knowledge. With how dangerous the library is, though, that isn't quite enough. Fortunately, just this morning, you felt yourself duck automatically to avoid a magical trip-wire that would have likely set off something unpleasant. Your body must retain some things that your mind doesn't — and that will be a huge help in keeping your secret.

The discovery of your instinctive ability to protect yourself from the dangers of the Library has given you the confidence you needed. One of your first thoughts was that the answer to your problem must lurk SOMEWHERE in the Library, but you are certain that searching for it in your current state would be suicide — how ironic. Since that incident, you've been delving deeper and searching for answers, but doing so with enough caution to not accidentally die is painfully slow. If only you had more time! This weekend, you will probably be under more scrutiny than ever. You need to find a way to reverse this memory loss as soon as possible. Seeking out others who are in a similar position could allow you to pool resources and search together, or maybe someone has already secretly solved this problem? Revealing your situation to the wrong person could be a career-ending disaster, however. You'll need to ask around subtly, or come up with a cover story, but with the best and brightest minds of \pEarth{} here this weekend, surely somebody knows something that could help you.

In addition to the three students, \cInterpol{\full}, the magical combat teacher, has also been a big help. When \cInterpol{\they} first approached you after the holiday, you were both nervous and strangely elated. \cInterpol{\Their} presence seemed…familiar? Comfortable? When \cInterpol{\they} asked point blank if you'd lost your memories after just a few minutes, you nearly died on the spot. But apparently, you were very close before. \cInterpol{} has been so kind and patient with you, and done a lot to cover for your missteps in the last few days. You are really grateful to have \cInterpol{\their} help — and \cInterpol{\their} presence has started to be your primary source of comfort. Being in \cInterpol{\their} presence feels right, and you wonder if there was more to your relationship than \cInterpol{} is letting on. But then again, you have been through a lot, so maybe you are reading too much into things. 

Another person you were apparently close friends with before you lost your memories is the school’s art teacher, \cChupAvenger{\full}. \cChupAvenger{\They} approached you yesterday, seriousness and regret etched in every line of \cChupAvenger{\their} face, and shared with you a terrible secret \cChupAvenger{\they} \cChupAvenger{\have} been carrying for years: Near the start of the war, \cChupAvenger{}'s anger about it caused \cChupAvenger{\them} to rashly renounce \cEbb{} and \cFlow{} and join a radical cult, the \pGoaties{}, even committing the primary taboo of this world — murder — in \cGenesis{}' name. Murders committed by Avengers (consecrated assassins) of \cGenesis{} don't have the same penalties as those imposed by the other Gods. Instead of the Avenger losing their own memories, others forget them instead. And so, one by one, the people in \cChupAvenger{}’s life forgot \cChupAvenger{\them}, until at last even the love of \cChupAvenger{\their} life, \cHeadScientist{\full}, did too. Consumed with grief for these losses and guilt for all the blood \cChupAvenger{\they} had shed in Genesis’ name, \cChupAvenger{\they} finally resolved to leave the \pGoaties{}. \cChupAvenger{\Their} first attempt to leave the cult peacefully had gone terribly wrong, and now \cChupAvenger{\they} \cChupAvenger{\are} desperate to escape the cult, atone for the harm \cChupAvenger{\they} \cChupAvenger{\have} caused, and find a way to rekindle \cChupAvenger{\their} relationship with \cHeadScientist{}. 

Could this be why you lost your memories? But no, that couldn’t be right, because you hadn’t just forgotten \cChupAvenger{}, you had forgotten \emph{everything}. You must have committed murder too and been punished by the Gods in the usual way. While you were shocked and horrified at what \cChupAvenger{\they} had done, you were hardly one to judge, and you were deeply moved by \cChupAvenger{\their} display of heartfelt remorse and the trust \cChupAvenger{\they} had placed in you. You resolved to help \cChupAvenger{\them} escape from that life, cover for \cChupAvenger{\them} in the meantime (as best you can), and help \cChupAvenger{\them} reconnect with \cHeadScientist{}. If the truth were to come out about \cChupAvenger{\their} actions, \cChupAvenger{\they} would be ostracized and probably imprisoned, just like you. There is not enough forgiveness in this world. That said, you know that \cChupAvenger{} will need to reconcile with \cEbb{} and \cFlow{} through \cChupAvenger{\their} actions this weekend, and then convince a Cleric to induct \cChupAvenger{\them} back into the faith.

Moved by \cChupAvenger{}’s trust in you, you almost decided to confide in \cChupAvenger{\them} about your situation too, but hesitated too long and the moment escaped you. You are still waffling about whether to tell \cChupAvenger{\them}. It would mean a lot to have the support of someone who understands what you are going through, but the more people who know, the bigger the risk of the wrong person finding out.

Back to business, though. Among the Librarian's duties are to lead the preparations for the Ritual to Control the Storm, but you can't remember what that entails! You will have to figure something out, and fast. Researching in the Library and talking with \cInterpol{} has at least reminded you of the most obvious part — keeping track of the Relics. There are three Relics that are stored in the Library for safekeeping: the \iNet{}, the \iLariat{}, and the \iScythe{}. These Relics must not be allowed to leave the island under any circumstances. You should also make sure that the Relics arriving with the advisors go home with whichever advisor they came with. 

And then there is the question of where the Storm should be directed. You've ascertained that as a teacher, you are supposed to help guide the students in this matter, and decide which one to give your Voting Stone to. Since your parents live on the northern coast, away from the massive cave networks that shelter much of the \pTech{}, and your nation has had no time to prepare, they would be at particular risk of dying. It is therefore imperative that the Storm go elsewhere — both because you love your parents, and because presumably they know much about your past and just haven't had a chance to impart that knowledge back to you.

Life at the \pSchool{} is actually quite idyllic. Most everyone gets along. The teachers are like one big extended family that transcends country divisions in a way not possible anywhere else on \pEarth{}. The students are inquisitive and clever, and you can see a bright future for \pEarth{} in their hearts and minds. Still, you have gathered that the decision of where to send the Storm is rather contentious, and you seem to have a Voting Stone that you are supposed to give to one of the students. How are you supposed to decide? You would rather not see the Storm go to the \pTech{}, since the people claiming to be your parents live there. You truly like all the \pTech{} students, but you of course don’t really know them, except \cAmbition{}. You trust \cAmbition{} to not send the Storm to the \pTech{}, but you want to talk more to \cPresident{} about \cPresident{\their} thoughts about where the Storm should go. You deeply appreciate that, while the other two compete with each other, \cPresident{} just wants to do what is best for the Library, for you, and as far as you can tell, the world. You know \cPresident{\they} \cPresident{\are} from the \pShip{}, but if \cPresident{} agreed to target the \pFarm{} instead of the \pTech{}, then maybe it would be best to give your stone to \cPresident{\them}?

Just this morning, you had a talk with \cBeetle{\full} about \cEbbPriest{\full}'s research into the creation of \pEarth{}. It sounds fascinating! You'd really like to be involved and chronicle whatever they find. Finding long lost history is kind of like finding long lost memories. Who knows — you might stumble upon something useful in the process. You'll have to chat with \cEbbPriest{} and let \cEbbPriest{\them} know you're interested in helping. Everyone would want a librarian to help, so you are sure \cEbbPriest{} will say yes.

This weekend is a race against time to see if you can piece together your missing memories before anyone finds out you are an amnesiac and kicks you out. In the meantime, you have duties for the Library and the \pSc{} to perform or fake as best you can. Fortunately, you're not alone — and if your reputation is as good as you think it is, you just might make it through unscathed.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Restore your memories, and avoid getting outed as an amnesiac until you do. You haven't found much yet, but surely there's something that can help you in the Library. Maybe if you can find the missing letter from your parents, that will provide some clues as well.
    \item Help prepare the Ritual to Control the Storm.
    \item Make sure the six Relics aren't tampered with, and end up where they belong after the Ritual to Control the Storm — the three from the Library should return to the Library, and the three with advisors should go home with those advisors.
    \item Explore your connection with \cInterpol{}. There is something in your heart and in \cInterpol{\their} eyes when \cInterpol{\they} look\cInterpol{\verbs} at you that tells you you were very close indeed\ldots
    \item Help \cChupAvenger{} escape the \pGoaties{}, atone for \cChupAvenger{\their} actions without being sent to prison, and perhaps rekindle \cChupAvenger{\their} romance with \cHeadScientist{}.
    \item Approach \cEbbPriest{} to help research the creation of \pEarth{}, magic, everything.
\end{itemz}

\begin{itemz}[Notes]
    \item You have learned that you were here at the school six years ago when 12 students mysteriously perished after voting to direct the Storm to the \pShip{}, but you have no memory of those experiences. You are somewhat thankful for that — it must have been terrible.
    \item The only person you have told about your missing memories is \cInterpol{}. You felt like you could trust \cInterpol{\them}, and you haven’t been disappointed. Maybe there are others you can trust with this knowledge, but it is a big risk.
\end{itemz}

\begin{contacts}
    \contact{\cInterpol{}} A close friend (and maybe more?) from before you lost your memory. You are grateful to have \cInterpol{\their} help now.
    \contact{\cLibAssist{}} A student who spends a lot of time in the Library and claims to be your assistant. Knowledgeable, skilled, and a real go-getter, but you could swear \cLibAssist{\they} sometimes add to your confusion on purpose.
    \contact{\cPresident{}} A helpful student who spends a lot of time in the Library and claims to be your assistant. Studious and thorough, but a little anxious.
    \contact{\cAmbition{}} Another helpful student who spends a lot of time in the Library and claims to be your assistant. Keen and ambitious, but a little lost about the eyes. You can relate.
    \contact{\cChupAvenger{}} A close friend from before you lost your memory, who has made grievous mistakes and desperately wants to atone for them and get \cChupAvenger{\their} life back on track. You can relate here too.
    \contact{\cEbbPriest{}} A Priest of \cEbb{} and \pShippie{} advisor who is researching the creation of the world. You are interested in this research! Has a reputation for being stern and traditional.
    \contact{\cWildCard{}} A scholar of the history and theory of magic with whom you appear to have shared a friendly correspondence. You do not know whether youC have ever met in person.
\end{contacts}

\end{document}








