\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cReligion{}}

%% Arike AKA FPF Teacher Religion

%%Start with a paragraph introducing the character (introduce at highest level): name, country of origin, role (student/teacher/advisor), what they think of religion, and what their #1 top priority should be here at game.  Important first impression of character.  Personality at top also, and how they perceive themselves

%%Spend 2-3 paragraph providing history and giving context/justification for why the character cares about what they care about. Introduce any contacts from this time in their life.  Ie: How did you become a teacher / what do you think about living in the CoS / why are you obsessed about destroying the status quo, what went wrong in your life to cause you not to like it.

%%Spend 1-2 paragraphs discussing the character's current life, problems, and priorities. Introduce any contacts from this time in their life. Current life and situation.   What they think about the most important contacts

%%Spend 1-2 paragraph talking about what this character sees for their future. Ground any goals here that haven't been introduced yet.  What are you doing next, what are you trying to accomplish, and why?

%%Spend 1 paragraph to conclude things. Reiterate the character's most important goals (one or two more important, probably one mentioned at the beginning), and most valuable contacts.  Who are they closest to?  Coherent last impression on character

%%No need to include abilities, etc - Tech will include automatically when we go to prod.

Teaches Religion

Priest

"Religious, studies beetles.  Is respectful of other religions and wants peace and equality.
Candidate for principal?"

On her return from "`visiting her family"' she brought the FPF avatar to the school secretly, in her pocket.

Set up the ritual, run religious aspects of stuff

Beetle mempack:  If x conditions are met find a place where you can commune with the Beetle, spend 5 min splattering ink, with beetle visible.  Then read the memo.

\textbf{Primary Plots:}

Preparing the Ritual*
https://docs.google.com/document/d/1xCN7BLfzBB3Tt237YSzGKusQj7cmi6nQxATP6aCLgEQ/edit?usp=sharing

Mechanics based item hunt plot around attuning, de-attuning, stealing, preserving the relics that are used in the ritual. Erica can reatune relics, is part of making the ritual happen, doing setup, etc.

Successsion for the Principality
https://docs.google.com/document/d/1aVTOkEIhoSKblYm4xwc-_BPsPNvjlzkUnjS9ZXKRrRo/edit?usp=sharing

The Ley Lines
https://docs.google.com/document/d/1Eea2ldlPpnp_LxW0KkHEjFFKn6ZceE_Q6JtAJgek0No/edit?usp=sharing

Arike's Replacement
https://docs.google.com/document/d/1Lax4I4DHm20dvKULZGIBqur-TiKBS_2vU9-_uHBKWBQ/edit?usp=sharing



\textbf{Secondary Plots:}

Resurrect the L'eau Avatar*
https://docs.google.com/document/d/13JWwHSUpGKjez2YLFkQf0XKcP2fyYYhZricUc0hGeoY/edit?usp=sharing

Wants to protech Shantih if it comes out that Shantih killed the Avatar.  She may find that out from the Beetle

Search for the Hummingbirds
https://docs.google.com/document/d/1fJ3F9bD-iPnq9AWnzmptV1i4-Fo7tFD3X4qETCA0Lcc/edit?usp=sharing

Poly Teachership
https://docs.google.com/document/d/1tUxzn9aptNal9x02jaSY_03gNNMcwQTwXlpYOVANmlM/edit?usp=sharing



\begin{itemz}[Goals]
	\item 
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
