\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cJuniorStatesman{}}

You are \cJuniorStatesman{\intro}, and 41 years old. You are an advisor from the \pShip{}, and while you weren't expecting to be here without your Boss, you feel surprisingly ready for the challenge. Your patron deities \cEbbFull{\intro} and \cFlowFull{\intro} are the Goddesses of balance — and time is a key element in creating that balance. Wrongs of the past can — and must — be righted in the present. The Treaty, the Storm, and the Avatars of the Gods are all just tools to accomplish that ultimate goal. It is your job as a diplomat to see the bigger picture, and to make the best use of the tools available to you — even in the face of those that cannot see that the ends justify those means. This weekend is going to be a big turning point for you and your country — you'll make sure of that.

As a child, you attended 2nd Fleet academy in order to study politics. You wanted for little, surrounded by care, love, and kindness. You’ve experienced the joy and community that forms under the teachings of \cEbb{\intro} and \cFlow{\intro} — like for like makes the whole world smile. Even when you moved to the 1st Fleet for your career, you have maintained deep ties to multiple ships and ports in the 2nd Fleet. As an adult, you have since spent most of your time working under \cHeadDiplomat{\intro}, aside from the sabbatical you took to serve in the war. 

The war broke out two years into your internship. At first you stayed by \cHeadDiplomat{}’s side, trying to find a peaceful, but fair resolution. Your people had been hurt, badly, and balance needed to be restored, but was war really the only option? After attending the ``Time of Deciding’’ three years ago, and butting heads with the advisors from the \pFarm{} and the \pTech{} directly, you accepted the hard truth that yes, war did indeed seem to be the only option — the only way to stop further hurt being rained down on your people, never mind a chance to balance the scales. You were filled with rage and anger that you felt like you had to burn off somehow.

So you took a sabbatical from your apprenticeship, and joined up with a 2nd Fleet ship that was conducting sea serpent raids on the \pFarm{} coast. A surprising number of the skills you had honed for politics translated to organizing and running a ship. Less than six months later, you were first mate on the 2nd Fleet, White Crest Ship. The ship operated mostly out of 8th and 9th Fleet waters, despite the risk posed by the \pWod{} and the pirates that work in those waters. The harsh realities of war quickly made the crew of the White Crest Ship feel like family. Which meant it hurt to lose them. 

Damn those trebuchets that have lost you multiple family members. And twice damn the cursemakers who supply the ammo. And thrice damn \cCurse{\intro} in particular. You are no expert in curses, but \cCurse{} is the best of the best in making them, and the \cCurse{\formal} family lives along the coast where the White Crest Ship worked. You have seen \cCurse{} staff the trebuchets with your own eyes. Your family would still be alive if not for \cCurse{\them}. Honestly? You might hate \cCurse{}. Maybe you should try to acquire a nasty curse just to break it over \cCurse{\their} head — a taste of \cCurse{\their} own medicine. Your raids may have killed some of the \cCurse{\formal} family and you almost hope you did. 

And while you’re at it, damn \cPrince{\intro} as well! \cPrince{\Theyare} \cQueen{\intro}’s youngest \cPrince{\offspring}. \cQueen{} is as ruthless and bloodthirsty as they come and you know that \cQueen{\theyhave} been a mastermind in the cruelty you have seen in the war. And if anyone is a chip off the old block, it’s \cPrince{}. When you thought that \cQueen{}’s eldest would inherit the throne, you retained a glimmer of hope that some day the \pFarm{} would become a far more reasonable place. But now rumors suggest that \cPrince{} has some scheme afoot to supplant \cPrince{\their} older sibling as the heir apparent. You wonder if there isn’t some way for you to interfere this weekend.

When \cHeadDiplomat{} wrote to you, urging you to return after you had been gone a year, you felt compelled to return. The rage and anger that had propelled you onto the decks of the White Crest Ship had been doused by waves of grief. So, back to the negotiating table you went, in hopes of convincing the \pFarm{} and \pTech{} that all the war was doing was digging graves. The sooner they surrendered to the \pShippies{}, the sooner \pEarth{} could figure out how to balance the scales and begin to heal.

While returning to work with \cHeadDiplomat{} felt like coming home, there was a rather unpleasant surprise waiting for you. In your absence, \cChupLeader{\intro} had been hired as \cHeadDiplomat{}’s secretary. No amount of skill with scheduling meetings will soften your dislike for \cChupLeader{\them}. \cChupLeader{\Theyhave} been undermining you at every turn, and you don’t even know why! The one time you tried to call \cChupLeader{\them} out for \cChupLeader{\their} shitty behavior, all you got was a sneered ``you have no proof.’’ Goddesses only know when \cChupLeader{} will decide whatever slight you supposedly did to \cChupLeader{\them} has been repaid. Hopefully \cChupLeader{} decides to put things aside this weekend to present a unified front and stops acting so childish. Do \cChupLeader{\they} not realize the world is at stake?

\cHeadDiplomat{} was one of the foremost diplomats of the \pShip{}, and a damn good one. You have seen \cHeadDiplomat{\them} broker compromises from impossible situations in the span of an hour, and no problem was ever too big, or too small, for \cHeadDiplomat{\their} personal attention. \cHeadDiplomat{} has the keenest sense for when those little things will sway someone to your side. While you could never fully fill those gigantic shoes, you have done your best to learn everything you possibly could from \cHeadDiplomat{\them}. This weekend was supposed to  be the culmination of your 8 year apprenticeship (7 years, interrupted), and your graduation from journeyman to master in your own right. But now \cHeadDiplomat{} has lost \cHeadDiplomat{\their} memories, and you and \cEbbPriest{\intro} are scrambling to fill the gap.

You woke up to the dreadful news only this morning, with a messenger boy pounding on your door. Everything happened so fast after that. \cEbbPriest{} called you and \cChupLeader{} to \cHeadDiplomat{}’s home the moment dawn touched the crest of the waves. Apparently someone had tried to assassinate \cHeadDiplomat{}! It was a frustratingly foolproof plan — while \cHeadDiplomat{} had physically survived the attack, \cHeadDiplomat{\they} had killed the assassin in self defense. Which means that \cHeadDiplomat{} has no memories or sense of self to speak of. Oh your blood boiled to think who could have done this, and why.

\cEbbPriest{} thought the answer was obvious — \cHeadDiplomat{} was trying to broker a peace treaty to end the war between the nations. Someone, from which nation was anyone's guess, must have sent the assassin in order to stop that. While the answer was easy and convincing enough on its face, somehow it didn't sit quite right with you. It was \textbf{too} tidy of an answer. Nearly seven years at \cHeadDiplomat{}'s side has taught you that the obvious answer is rarely the true one when international politics are involved. In the meantime, the story that you are supposed to tell is that \cHeadDiplomat{} became dreadfully ill last night, and couldn't make it. But in general, the fewer details spread around, the better. All questions are to be turned aside, or directed to \cEbbPriest{}.

\cEbbPriest{\They} think\cEbbPriest{\verbs} \cEbbPriest{\theyhave} this all under control. You aren't so sure about that. You intend to conduct your own investigation into the assassination attempt. You immediately disregarded instructions and wrote to \cHeadDiplomat{}'s \cPresident{\nibling}, \cPresident{\intro}, to tell \cPresident{\them} what happened and solicit \cPresident{\their} help. There hasn't been time for a response, but you intend to make contact as soon as you can get \cEbbPriest{} off your case. The only other people who know what happened to \cHeadDiplomat{} are \cChupLeader{} and the fourth \pShippie{} advisor, \cBunker{\intro}.

Still, someone had to show up at the \pSchool{} and make sure the \pTech{} and the \pFarm{} didn't continue to ride roughshod over the \pShip{}. As you contemplated whether you were really ready to step up and fill \cHeadDiplomat{}'s shoes, you realized that \cEbbPriest{} was going to have to come along. There simply wasn’t time to find someone else, and as a high ranking \cEbbPriest{\cleric}, the Advisors from other countries would be hard pressed to find fault with \cEbbPriest{\their} presence. So you set about giving \cEbbPriest{} a crash course in being an Advisor.

Now that you're here and not standing directly in your mentor's shadow, you're going to conduct yourself a little differently than your now amnesiac mentor would have. While you have a lot of respect for \cHeadDiplomat{} and \cHeadDiplomat{\their} strength of character, you feel the call of the Goddesses' balance leads you on a different path. You strongly believe that your country should extract as much worth as you can from the unjust aggressors from the continent before signing away your rights to make war. Whether or not the other side acknowledges it, this war is firmly in your favor — so the calls for peace between your nations are premature at best. Unless you can extract a large stable of concessions from the \pTech{} and the \pFarm{}, you are firmly against anything stronger than a temporary ceasefire (with an explicit end date) — and only because a temporary respite will allow the \pShippies{} to gather their strength for a crushing final blow. Still, a diplomat must be flexible in light of new information. If the tide of the war turns against you, or justice can be done and Balance restored some other way, you would be willing to consider peace.

Aside from work at the bargaining table, there is other important work to cover as well. Someone needs to be the students' primary contact and support regarding how to vote on where to direct the Storm. All are clever, though they vary on their commitment to Balance. Regardless, you have every intention of comporting yourself as a safe person to vent to, ask advice of, or whatever these youngsters end up needing.

You have known \cPresident{\full} since \cPresident{\theywere} young. As \cHeadDiplomat{}’s \cPresident{\nibling}, \cPresident{\they} attended many of the same social functions that you did, even before you began to work for \cHeadDiplomat{} directly. You have rarely met such an intelligent and observant young \cPresident{\person}. It is no surprise to you that \cPresident{\their} classmates look to \cPresident{\them} as a guiding light. But every lighthouse needs its foundation, and with \cHeadDiplomat{} indisposed, you intend to be that for \cPresident{}.


\cPirateChild{\intro} is a very recent acquaintance of yours. \cPirateChild{\They} originally wrote you out of the blue about the perennial plight of the 8th and 9th Fleets some months ago. How exactly a youth of the 5th Fleet would know so much escaped you, but you were moved by \cPirateChild{\their} compassion and the open and genuine way \cPirateChild{\they} spoke of the need for balance and justice internal to the \pShip{}, not just internationally. Remembering a favorite saying of \cHeadDiplomat{}, ``never ignore a tool provided by the Goddesses,’’ you have maintained an ongoing correspondence. Who knows? Someday knowing \cPirateChild{} may be the difference between you finding a peaceful solution to an issue, and things coming to blows.

You know \cWarlordDaughter{\intro} only through reputation. You know that \cWarlordDaughter{\they} care\cWarlordDaughter{\verbs} deeply for \cWarlordDaughter{\their} ship, and \cWarlordDaughter{\their} \cLoud{\parent}, \cLoud{\intro}. You hope that \cWarlordDaughter{} will not take it the wrong way if you offer your support to \cWarlordDaughter{\them} both in regards to the difficult decisions the students face this weekend, but also in protecting \cLoud{} and everything \cLoud{\theyhave} accomplished so far for the \pShip{}.

Of course, the tides of victory are flowing in your favor in large part because of the incredible strategic mind of Warlord \cLoud{\full}, a \cLoud{\person} whose work has quite impressed you. As one of the strongest military assets on the side of the \pShip{}, you have to do what you can to safeguard and motivate \cLoud{} to keep doing the good work that \cLoud{\theyare} doing. You fully expect the other nations to continue to conspire to assassinate the Warlord. You can't protect \cLoud{} directly from here, but you and \cWarlordDaughter{} can foil any plots being hatched here.

Another person you intend to ingratiate yourself with this weekend is \cBunker{\full}, your fellow advisor and the engineer who designed the school's magical Bunkers. \cBunker{} doesn't seem like much on the surface, but you know that \cBunker{\theyare} a longtime friend and confidante of \cHeadDiplomat{}, and therefore almost certainly more than \cBunker{\they} let\cBunker{\verbs} on. Your best bet to strike up conversation is probably to volunteer to help \cBunker{} with the maintenance of the Bunkers this weekend.

A bit further from home, there's \cDisney{\intro}. \cDisney{\They} wrote to \cHeadDiplomat{} some time back asking for aid in finding the Giant Hummingbirds — Avatars of \cFarmGod{\intro}. \cHeadDiplomat{} passed the letter along to you, knowing your interest in the Avatars. The two of you speculated that the disappearance of hummingbirds might indicate that \cFarmGod{} does not approve of the \pFarm{}’s participation in the war. If only you could prove it. So of course you agreed to help \cDisney{} find the hummingbirds. If it became widely known that they forsook the \pFarm{} because of the war, all support for it would crumble. Surely the \pFarm{} would sue for peace at that point, abandoning the \pTech{} to their depravity. But what started as a primarily diplomatic pursuit for you has become far more urgent.

One of the only tides flowing against you in this war has been the recent loss of one of the two \pShip{} Avatars. \cEbbPriest{} told you the devastating news just yesterday. While the clerics are understandably the primary ones in charge of resurrecting it, you have been at least made privy to the fact that doing this on the Mortal plane will be brutally costly. It is really unfortunate that the Gods themselves severed the connection between the Mortal Plane and the Divine Realm millenia ago. The whole situation is awkward given that the Church (all three Patron Deity branches of it) touts the line that the Deities must have severed the connection for a reason, and that mortals should not try to undo this. Talking about it is usually a good way to get yourself branded a heretic. Still, you hope to recruit \cDisney{}’s help (despite \cDisney{\them} being a \cDisney{\cleric}) in finding some way to reach the Divine Realm since that’s probably where the hummingbirds are too. And while you’re there, maybe you could talk to \cFarmGod{} and ask what happened?

In the midst of war, it can be easy to lose track of personal matters like love. You are currently in a stable, loving relationship with your \cBeetle{\partner}, \cBeetle{\intro}, and you wouldn't change that for the world. You met about 8 years ago, well before the war. It was a time when travel between the \pTech{} and the \pShip{} for pleasure was trivial enough. Ever an admirer of architecture, you sought out the main temple to \cTechGod{\intro} on one of your trips, and secured a private tour. In wandering those exquisite halls, you encountered one \cBeetle{}, stepping out from a room that was closed to the public. A warm smile, and brief pleasantries and \cBeetle{\theywere} gone. Yet \cFlow{} seemed to be inclined to you building something new. \cBeetle{} happened to go to dinner at the same eating hall that you did. A shy smile, a little wave, and you were no longer dining alone. And what a dining companion \cBeetle{} made. \cBeetle{\Theyare} a delightful conversationalist, kind, and insightful. \cBeetle{\They} too \cBeetle{\were} on something of a vacation at the moment, visiting the Temple for some of \cBeetle{\their} work as a \cBeetle{\cleric} that could not be conducted from the \pSchool{}. You did not eat alone again on that trip.

The two of you became immediate pen pals upon the ending of your trip, and absence does indeed make the heart grow fonder. Over the course of two years of correspondence, you grew to be close friends, and you eventually recognized in yourself budding romantic feelings. At first you were quite nervous to admit them to \cBeetle{}, since the \pTech{} don’t, as a whole, have a good opinion of polyamory, and you were already dating someone in the \pShip{}. But you took the risk and wrote to \cBeetle{\them} of your feelings. Oh what a laugh the trickster god must have had when the war started less than six months later, drawing battle lines between the two of you. 

The two of you had elected to spend the ``Time of Deciding’’ at your home, since the storm was expected to hit the \pTech{}. That week was one of the most stressful of your life — the storm hitting the \pShip{} when your country wasn’t prepared at all. The devastation and loss you witnessed personally, never mind the stories you’ve heard from elsewhere, ignited an unquenchable need for justice. But in the short term, you first had to find a way to smuggle \cBeetle{} back to the \pSchool{}. No one could be allowed to find out that a \cBeetle{\cleric} of the \pTech{} was in 2nd Fleet during the Betrayal. There would be no questions, only retribution.

Still you clung to the beautiful thing the two of you had, telling yourself that \cBeetle{} was not truly the enemy. The teachers at the \pSc{} are supposed to renounce their national loyalties when they join the faculty. So at least you weren’t completely alone when your other partner broke things off with you. They did not appreciate you leaving the White Crest Ship where they also served. So, for now, neither you nor \cBeetle{} have other partners.

Visiting the \pSchool{} three years ago gave you a rare opportunity to spend time with \cBeetle{} in person, so it was particularly nerve wracking to sit down and talk with \cBeetle{}, and \cBeetle{\their} fellow teacher, \cEthics{\intro} the first night. It was attraction at first sight between you and \cEthics{}, and while you wanted to spend time with \cBeetle{}, you didn’t want to miss this opportunity with \cEthics{} either. \cBeetle{} was gracious and understanding that you were interested in \cBeetle{\their} best friend of decades. You wondered briefly if you just had a type, but no, \cEthics{} is \cEthics{\their} own amazing person. 

The weekend was a delightful fling, but guilt clung heavy to you afterwards. Was \cBeetle{} really okay with you messing around with \cBeetle{\their} best friend? And could you really take on a second lover from the \pTech{}? Sure \cEthics{} was also a teacher at the school, but you could only lie to yourself so far about a teacher’s neutrality. And it’s not like either of them had the same excuse for you. You were a diplomat from the enemy nation. It could do much more than just destroy their career if anyone found out. Damn those two. Why did they both have to be such enticing, compelling people? And why couldn’t they be \pShippies{}?

So you reluctantly let the fling be just that, a weekend fling. You wrote to \cEthics{} only as an acquaintance and \cEthics{\they} followed your lead, never pushing. \cBeetle{} didn’t seem too upset either, so you breathed a sigh of relief, and sent your prayers to \cEbb{} that the \pTech{} would capitulate sooner rather than later and end the war so you might pursue your romantic endeavors freely. Because the more you got to know \cEthics{}, the more you realized that you may have found the only two \pTechies{} who were interested in justice for the \pShip{}. Maybe, just maybe, it’s time to stop denying your feelings and sit down for a proper conversation between \cBeetle{}, \cEthics{}, and yourself about if it is possible to establish a second relationship without putting \cEthics{} in danger. Including \cBeetle{} in these conversations is very important to you. You and \cBeetle{} always talk about changes to the relationship structure before implementing anything. That said, you do not have a relationship with veto power — it is possible to have conversations around making sure needs are still met despite a change in the relationship structure without anyone mandating the other's actions. 

And just in case this relationship needed any more angst, \cBeetle{} wrote to you just recently to say that \cBeetle{\theyare} being considered to take over the principalship of the \pSc{}. You want to support \cBeetle{\them}, you really do, but you still need to process your own feelings. The Principal cannot leave the island that the \pSc{} is built on. They are also immortal. Both leave you feeling like you’d just be left behind.

This weekend will be a tough one. Figuring out what happened to \cHeadDiplomat{}, ensuring that any ceasefire the other Advisors try to force is minimally ill-advised, finding the hummingbirds, and helping resurrect the \cEbb{} Avatar are important public duties — but if you can find the time, your love life is also in rather desperate need of time and attention. There's a lot at stake in these few days, but as a soon-to-be master diplomat, you intend to rise to the occasion.

\begin{itemz}[Major Goals]
    \item Protect the interests of the \pShip{}, and do right by your home country, her people, and her Goddesses. Sort out duties with \cEbbPriest{} and \cChupLeader{} (ugh!) and help ensure that any treaty that is signed is highly beneficial to the \pShippies{}. If the other nations won't acquiesce, the war can always continue, as long as the Warlord continues to lead you.
    \item With \cPresident{}'s help, investigate the assassination attempt on \cHeadDiplomat{}. Do so quietly — it wouldn't do for other nations to find out how close someone came to assassinating the \pShip{}'s most famous diplomat.
    \item Find the Hummingbird Avatars of \cFarmGod{} with \cDisney{} and learn why they haven’t been showing up on the mortal plane. This may involve finding a way to reach the Divine Realm. If advantageous for the \pShip{}, publicize what you learn. 
    \item Navigate adding \cEthics{} to your relationship with \cBeetle{}.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Support and advise the \pShip{} students through the difficult moral position they have been placed into. 
    \item Work with \cWarlordDaughter{} to discover and foil any attempts to hurt \cWarlordDaughter{\their} \cLoud{\parent}, \cLoud{}.
\item Put barriers in \cCurse{}’s way to pay \cCurse{\them} back for your dead ship family. Maybe giving \cCurse{} a taste of \cCurse{\their} own medicine would do nicely.
    \item Figure out who \cBunker{} really is. 
\end{itemz}

\begin{itemz}[Notes]
    \item You came to the \pSchool{} with \cHeadDiplomat{} as an advisor for the first time three years ago.
\end{itemz}

\begin{contacts}
    \contact{\cEbbPriest{}} An \cEbb{} \cEbbPriest{\cleric}, and a last minute addition to the delegation from the \pShip{} since \cHeadDiplomat{} has lost \cHeadDiplomat{\their} memories. You don’t know \cEbbPriest{\them} well, but \cEbbPriest{\they} seem\cEbbPriest{\verbs} calm and steady — something the \pShippies{} will desperately need this weekend.
    \contact{\cChupLeader{}} \cHeadDiplomat{}'s secretary. You resent \cChupLeader{\their} subtle and not so subtle acts of sabotage against you. 
    \contact{\cBunker{}} A fellow \pShip{} advisor, friend of \cHeadDiplomat{}, and the one in charge of maintaining the \pSc{}'s Bunkers. You are pretty sure \cBunker{\theyare} hiding something, so you don’t trust them fully.
    \contact{\cPresident{}} \cHeadDiplomat{}'s \cPresident{\nibling}, and a leader among the students.
    \contact{\cWarlordDaughter{}} The \cWarlordDaughter{\offspring} of \cLoud{\full}. You share the goal of protecting the Warlord. 
    \contact{\cDisney{}} A student from the \pFarm{} who is looking for the Giant Hummingbirds.
    \contact{\cBeetle{}} Your romantic partner, with whom you have a polyamorous relationship. \cBeetle{} is kind, funny, thoughtful, but also a \cBeetle{\cleric} of \cTechGod{} and bidding for the immortal principalship of the \pSc{}.
    \contact{\cEthics{}} The Morality and Ethics teacher at the school, who is dedicated to Balance (unusual for a non-\pShippie{}). \cEthics{\Their} thoughtfulness only strengthens your desire to try to figure out a relationship with \cEthics{\them}..
\end{contacts}

\end{document}
