\documentclass[char]{GL2020}
\usepackage[normalem]{ulem}
\parindent=0pt
\begin{document}
\name{\cEbbPriest{}}

You are \cEbbPriest{\intro}, and well along in years. You are a \cEbbPriest{\cleric} of \cEbbFull{\intro}, and an advisor from the \pShip{}. You treat the sacred duties of being a Cleric with all of the gravity they deserve, and bear up well under the weight of many responsibilities among the \pShippies{}. While you initially had no plans to attend the events at the \pSchool{} this weekend, it seems your \cEbb{\Deity} had other ideas.

You grew up in 7th Fleet, the child of Clerics of \cEbb{\intro} and \cFlow{\intro}. Though you traveled aboard several ships in your youth, you eventually returned to the Monastery at Southern Atoll to pursue studies in the priesthood. Very little fulfills you like the spirited debates of theology at the Monastery. The most compelling conversations root the theology in history. You have made a particular study of the creation story of \pEarth{}. It seems no one in recent memory has put much care into the small differences between the way the story is told in each of the nations. But some of the older stories are quite different from how the stories are told today, and the question of what really happened intrigues you deeply. You've corresponded at times with clerics from all over, including \cBeetle{\intro}, and \cFlowPriest{\intro}, who both work at the \pSchool{}, as well as \cAntiChup{\intro} from the \pTech{} and \cHedonist{\intro} from the \pFarm{}. All of these clerics have shared their own versions, and you have gathered quite a collection. \cBeetle{} and \cFlowPriest{} were particularly generous with their time and you greatly enjoyed conversations with them, and as such you still correspond. 

Still, no \cEbbPriest{\cleric} of \cEbb{} can live their entire life inside the Monastery. The work of the Goddesses is out among the people. So out you went, to help people learn to let go of the old, to make room for the new. For that is what \cEbb{} is all about: ends, closure, and moving on; cleaning up, learning lessons, and preparing for the next step. You ultimately settled on Fisher’s Cove, a small island close to the southern coast of the \pFarm{}, not too far from the monastery.

You were content there. You loved the people of the Cove, who traded often with the \pFarmers{}. Everything seemed perfectly in balance — until six years ago. You were out and about in your community, talking, laughing, and helping a few shipwrights tear down an old, worn out fishing vessel. The sea-birds raised the alarm first. They fled for the sea cliffs in droves, even species that rarely make landfall. The air was thick with their wings, and their frantic cries. Ever people of the sea and the wind, the \pShip{} looked to the horizon, to see the ominous black clouds of The Storm rapidly approaching. This wasn’t right! The ``Time of Peace’’ Treaty cycle said that the storm would go to the \pTech{} this year. No one was prepared. Houses had not been reinforced — that wood had gone to building new houses and ships this season. Crews were out to sea, fishing, sailing, and trading. Everything would be smashed to bits!

Already grieving the massive loss of life and livelihood, you took shelter with your school as best you could. (The \pFarm{} clerics might call their people ``flocks’’, but for the \pShip{}, people make up schools, just like fish.) When that terrifying week was over, you emerged to ruin worse than even you could imagine. The Fisher’s Cove community had nothing left. Desperate, you turned to the \pFarm{} — families your people had traded peacefully with for generations — only for your pleas to go unheard. The \pFarm{} closed its borders and refused to offer aid. When \cLoud{\intro} began to call for violence to repay the violence that had been visited upon the \pShip{}, you could only agree. You lent your voice and your authority to \cLoud{\their} cause, especially in the early days, getting \cLoud{} \cLoud{\their} first meetings with \cHeadDiplomat{\intro}, a prominent \pShip{} diplomat who had begun a deep, romantic relationship with your best friend some years back.

It has been nearly six years of war. Casualties and damages are building for the \pFarm{} and the \pTech{}, but while the war is probably sustainable for your people, they are just fighting for their survival at this point; they aren’t \emph{living}. Still \cEbb{} and \cFlow{} demand balance be restored. Only once every hurt, and loss, and pain have been repaid, can your people find peace. The scales were shifting back toward balance. The war has been serving its purpose to serve back what has been given to your people. But there’s fighting, and there’s fighting \emph{dirty}. 

Almost two months ago you were called back to the Southern Atoll Monastery from Fisher’s Cove. It seems that someone has managed the near impossible. The Avatar of \cEbb{}, has been killed, severing your connection to your \cEbb{\deity}. This is obviously foul play — Avatars don't simply die of natural causes. That means \emph{someone} killed it. Someone very strong in magic, who had some way to lure the Avatar to shore — or found a ship treacherous enough to carry them to deep waters, and a weapon capable of the deed. \cEbb{}’s influence is greatly reduced on \pEarth{} now, and you feel the loss as a visceral ache in your chest. You were asked to lead the work to resurrect them. It has been an emotionally and physically exhausting time, researching and preparing the work to right this wrong, wondering bitterly who committed this atrocity, and being separated from your school in Fisher’s Cove — but for the moment your work was at the Monastery, and in 1st Fleet, where the Council of Storm Watchers and the Head of the Church are. You communicate regularly with both as part of these preparations.

This past week you have been staying in a beautiful little villa clinging to the side of the cliffs surrounding Drova’s Landing, with your best friend and her \cHeadDiplomat{\spouse}, \cHeadDiplomat{}. The three of you had dinner together last night. It was such a lovely night of reminiscing and joy, even if it was quieter than dinners used to be when \cHeadDiplomat{}’s \cPresident{\nibling} \cPresident{\intro} and \cPresident{\their} friend, \cInitiate{\intro}, were also in attendance. But now both of them are off at the \pSc{}. You spent the night especially talking about these wonderful young people, as you remembered with fondness the long talks you had with \cPresident{} about balancing religion and politics and the honor you felt when \cInitiate{} told you about the appearance of the mark of the Goddesses upon \cInitiate{\their} skin. You still are pleasantly surprised \cInitiate{} told you before they told anyone else, in thanks for all your guidance, not just about the path of \cEbb{} but also about religions around \pEarth{}. You had said your goodnights and bade \cHeadDiplomat{} to send your best wishes to these young people you have had the pleasure to watch grow up and who now carry the hopes and fate of all of \pEarth{} on their shoulders.

In the wee hours of the morning, hours before nautical dawn, your best friend pounded on the door to the guest house where you were staying, sobbing. In a rush, you threw on a robe over your night things and came to see what had made your friend so distressed. There in the living room of the house was \cHeadDiplomat{}, covered in blood, with a dead body at \cHeadDiplomat{\their} feet. \cHeadDiplomat{\Their} eyes were clouded over with the fog of memory loss. It would be days before \cHeadDiplomat{\their} brain would begin remembering things again. In a heartbeat, \cHeadDiplomat{} was gone. There was only a person that looked like \cHeadDiplomat{\them} in your friend’s living room. You pulled your friend into a tight hug as she wept. Never have you been so glad to be a Cleric versed in supporting people through loss and grief as in that moment. 

But as much as you wished to stay with your friend for days or weeks as \cHeadDiplomat{\they} slowly pieced \cHeadDiplomat{\their} life back together, this was more than just a personal tragedy. It had the makings of a national emergency. Someone had to go to the \pSchool{}. Someone had to decide on and disseminate the public story of what happened. Someone had to tell \cHeadDiplomat{\their} friends and family. And that someone was apparently you.

Moving slowly out of respect for the weight of grief, you assessed the situation. The body on the floor was dressed in dark colors, and one hand still clutched a knife. A window was broken — the noise that had awoken \cHeadDiplomat{} who went to investigate while your friend had remained in bed. The overturned furniture indicated a struggle. The shallow cut from \cHeadDiplomat{}’s collarbone to hip revealed the murderous intent of the intruder. You sucked your teeth — self defense was still murder. \cHeadDiplomat{} \emph{might} regain some of \cHeadDiplomat{\their} memories, some day, but it was not guaranteed. And it certainly wouldn’t be soon enough for the ``Time of Deciding.’’ 

With a heavy heart, you contacted \cJuniorStatesman{\intro}, \cHeadDiplomat{}’s apprentice, and \cChupLeader{\intro}, \cHeadDiplomat{}’s secretary. You summoned them both to the house for a grim discussion over whatever breakfast the three of you might choke down. You knew \cJuniorStatesman{} better than \cChupLeader{}, but neither were complete strangers to you due to your political work and especially the dinners you all shared at \cHeadDiplomat{}’s house. You carry their grief as well. The three of you agreed upon a public story to put out: that \cHeadDiplomat{} had come down dreadfully ill last night and could not attend. You tried to impress upon the other two how important secrecy was in this — someone, or someones, had eliminated \cHeadDiplomat{} as a political figure. You believe it was an assassin sent by another nation, sent to quash the \pShippies{} greatest hope for a peaceful resolution to the ongoing conflict. If it weren’t for the loss of the \cEbb{} Avatar, there would be no reason for the \pShippies{} to consider a peaceful solution. Does whoever sent the assassin after \cHeadDiplomat{} also know about the Avatar? 

Regardless, it was a disgustingly foolproof plan, either \cHeadDiplomat{} would be dead, \cHeadDiplomat{\their} murderer unable to say anything about who had hired them, or \cHeadDiplomat{} would lose \cHeadDiplomat{\their} own memories. Either way, \cHeadDiplomat{\theywere} no longer fit to serve as the foremost Diplomat in all of the \pShip{}. You aren’t sure that either \cJuniorStatesman{} or \cChupLeader{} really understood. You can only hope.

Over the course of the morning \cJuniorStatesman{} and \cChupLeader{} gave you a crash course on what it meant to be an Advisor at the ``Time of Deciding.’’ Someone had to take \cHeadDiplomat{}’s place, and there was no time to find someone else — in reality, the Council would be hard pressed to find someone better qualified than you anyway. You might not be a diplomat, but as a very prominent \cEbbPriest{\cleric} of \cEbb{} there are plenty of skills you can lend to the situation.

Politics are a nearly impossible balance of half truths and hard choices. But your expertise is in bringing things to conclusion. As tragic as what happened to \cHeadDiplomat{} is, you can't shake the feeling that maybe you were \emph{meant} to be here this weekend. Someone needs to step up and mediate the treaty negotiations — and maybe that someone was meant to be you. Not that you intend to let the other nations get away without restoring balance — something must be done to balance the scales, and a new understanding regarding the Storm drawn up. One that spares the \pShip{} for long enough to rebuild; let the other nations take the Storm upon themselves for at least the next four or five cycles. That should begin to restore the balance that was destroyed with the original Betrayal. You expect to find a shrewd adversary in \cDiplomat{\intro}, the lead diplomat from the \pTech{}, and the author of the despicable alliance with the \pFarm{} that began the Betrayal. Come to think of it, \cDiplomat{} stood to gain quite a lot from \cHeadDiplomat{} being taken out of the picture. Could it be that \cDiplomat{\they} sent the assassin? You, \cJuniorStatesman{}, and \cChupLeader{} will need to present a strong, united front this weekend.

There is no rest for an albatross, of course. For all of three waves you thought you’d have to pass off ongoing preparations for resurrecting the \cEbb{} Avatar. But no, if anything, access to the \pSchool{} completely disrupted your carefully laid plans in a good way. Instead of facing at least another month of preparations, you might be able to pull the timeline in and get the Avatar resurrected \emph{this weekend}! The \pSc{} is the highest concentration of magic and powerful magic users in all of \pEarth{}, with access to Relics from all three nations, and your counterpart, \cFlowPriest{\full}.

It can't be just chance that one of your longtime correspondents, \cFlowPriest{}, a highly respected and powerful \cFlowPriest{\cleric} of \cFlowFull{\intro}, is a teacher at the \pSchool{}. Of course, there remain complications of which the answers have yet to reveal themselves. Chief among them is the central problem — where are you supposed to get a live sea serpent to act as a host? The cost of the ritual also will be quite steep (OOC: see details in greensheet). It is just so hard to concentrate enough divine energy on the mortal plane. You are pretty sure that if you resurrected the Avatar in the Divine Realm that it would be much less taxing, but that is both impossible and quite blasphemous. Not far behind these two concerns is the matter of how to keep things quiet. If word should get out as to what you are trying to do, the other nations would surely try to stop you, as being short an Avatar puts the \pShippies{} at a grave disadvantage in the war. You have explained the situation to your fellow \pShip{} advisors, and are grateful to have them on hand to assist you.

While you are here at the \pSc{}, you are also still a \cEbbPriest{\cleric} of \cEbb{}. You have a duty to the \pShippies{} and indeed to anyone who expresses a need for support or council. Chief among those requiring your attention will be \cInitiate{\full} and \cWarlordDaughter{\intro}, two initiates to the religion of \cEbb{} and \cFlow{}, who have yet to pick their Path and take their final vows. As with every other initiate, they bear the mark of the Goddesses upon their persons. No one is allowed to try for the priesthood without it \emph{(OOC: represented as a temporary tattoo either on the player's body, or tucked into their badge holder)}. Becoming a member of the clergy is not a decision to take lightly, and you intend to test for yourself whether these two are truly ready for the life they purport to want.

You have known \cInitiate{} since \cInitiate{\theywere} very young, but \cWarlordDaughter{\full} is much newer to you. \cWarlordDaughter{\They} struck up a correspondence with you a few years ago, after the war started. Your heart goes out to the \cWarlordDaughter{\child}. \cWarlordDaughter{} received \cWarlordDaughter{\their} mark of the Goddesses not long before the war broke out. With \cLoud{} as \cWarlordDaughter {\their} \cLoud{\parent} however, it seemed to \cWarlordDaughter{\them} pursuing the clergy was out of the question. You thought \cWarlordDaughter{\their} assessment premature — a door closed too soon. You encouraged \cWarlordDaughter{} to pursue studies, even if formal study at the 1st or 7th Fleet Academy was not possible. And look where \cWarlordDaughter{\theyare} now! In \cWarlordDaughter{\their} second year at the \pSchool{}, and well on \cWarlordDaughter{\their} way to becoming a full \cWarlordDaughter{\cleric}. You know you cannot induct anyone into the service of \cEbb{} (or the path of Balance) while the avatar is dead, but you especially have hope that \cWarlordDaughter{} may follow in that path. This is why you have trusted \cWarlordDaughter{} with the secret of the Avatar’s death and asked for \cWarlordDaughter{\their} help. Since arriving at school, you have also learned that \cFlowPriest{} has asked \cInitiate{}’s assistance as well. How both handle this very serious task will prove their readiness for being a cleric certainly. You also have one Voting Stone to give out, and depending on how \cInitiate{} and \cWarlordDaughter{} perform, you very likely will give it to one of them.

As the only cleric in the Advisor delegation, you also bear with you the ``\iChalice{},'' one of the two Relics of the \pShip{} which might be used for the ritual. It is yours to protect, or entrust someone to protect, until it is ready to return to its protections at the 1st Fleet Monastery. You also have the ability to assess the state of the Relics for the ritual — sometimes people are too enamored of the powers a Relic has to care about the consequences of them becoming de-attuned in the usage.

If the goddesses smile upon you, and your allies are stalwart and true, you might even have the opportunity to indulge your fascination with history. You’ve never had the chance to peruse the library of the \pSchool{}. You never expected to have a chance to meet up with so many of your cleric pen pals in person, let alone at the same time! Truly, the Goddesses work in frustrating and obscure ways. \cBeetle{} has shown the most interest in your research, your attempt to discover the truth of how \pEarth{} was created, once and for all, and you had hoped to work with \cBeetle{\them} directly this weekend, but it would appear \cBeetle{\theyhave} decided to delegate the task to \cHeadScientist{\intro} as a ``learning opportunity.'' 

You are trying not to feel too disappointed, but honestly, what are you supposed to do with \cHeadScientist{}, who only seems to have taken an interest in religion in the past few months? And then \cHeadScientist{} said that \cHeadScientist{\theyare} having \cScholarship{\intro}, an initiate of \cTechGod{\intro} and student at the \pSc{}, work with you too. At least as an Initiate, this student will likely have more religious knowledge. Still, it's not \cBeetle{}, and you will need to curb your annoyance as it isn’t \cHeadScientist{}’s fault that \cBeetle{} isn’t available. You are not one to squander what is brought in on the tide, even if it is not what you had expected. If \cScholarship{} really is as bright as \cHeadScientist{} claims then this endeavor should be quite fruitful. And Goddesses know, maybe \cHeadScientist{} will turn out to have some insight that those of you who have been deeply immersed in theology your whole life have missed.

You would certainly like to think that the students know better than to send the Storm to the \pShip{} again this year. Anyone who actually cares about peace should understand that doing so would only prolong the war. If \cInitiate{} and \cWarlordDaughter{} do not seem up for the task, you can always consider \cScholarship{} as a candidate for your Voting Stone? Assuming of course that \cScholarship{\they} help\cScholarship{\verbs} discover the history of the world. Perhaps if this war ever ends \cScholarship{\they} might even deserve at least an internship with you. How non-traditional it would be to take on a cleric of \cTechGod{} as an intern, but the idea does amuse you.

So while your presence here this weekend was unexpected to you, and probably to most or all of your fellow advisors, it is obvious your Goddesses had a hand in it. Your role here is three-fold: to guide \pEarth{} to a proper closure on the war, to uncover the truth of the Creation of \pEarth{}, and to serve as a \cEbbPriest{\cleric} in all the ways you might be called upon to do it. This is your moment, and you intend to rise to the occasion.

\begin{itemz}[Major Goals]
    \item Work out with \cJuniorStatesman{} and \cChupLeader{} who will handle which of \cHeadDiplomat{}’s responsibilities from this weekend, including heading up treaty negotiations, and advising and supporting the students. Ensure that any treaty signed is properly balanced and accounts for the pain and suffering of your people.
    \item Work out with \cJuniorStatesman{} and \cChupLeader{} who will investigate if \cDiplomat{} or anyone else here knows anything about the plot to eliminate \cHeadDiplomat{} — you suspect that \cJuniorStatesman{} will be more keen on this; \cChupLeader{} strikes you as lazy and petulant. Ensure the three of you present a united front preventing anyone from finding out the truth about why \cHeadDiplomat{} isn't here.
    \item Research the truth of the world’s creation — this is your chance to find the truth long lost, with the help of \cHeadScientist{} and \cScholarship{}.
    \item Work with \cFlowPriest{} and other \pShippies{} to resurrect the \cEbb{} Avatar.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Guide \cInitiate{} and \cWarlordDaughter{} in their final steps to becoming full fledged clerics of \cEbb{} and \cFlow{}.
    \item Make sure the Storm doesn't get sent to the \pShip{}.
    \item Safeguard the \iChalice{} to ensure no harm comes to it.
\end{itemz}

\begin{itemz}[Notes]
    \item You have never been to the \pSchool{} before.
    \item In your work as a \cEbbPriest{\cleric}, you have heard whisperings of a heretical cult among the \pShip{}, known as the \pGoaties{}. You have few solid facts, but you know they have lured some of the faithful away from the path of the Twin Goddesses, and committed violent acts in the name of their false god, \cGenesis{\intro}.
\end{itemz}

\begin{contacts}
    \contact{\cJuniorStatesman{}} \cHeadDiplomat{}'s apprentice and assistant negotiator. \cJuniorStatesman{} carries \cJuniorStatesman{\their} grief admirably (perhaps to be expected from a fellow follower of \cEbb{}), and you expect \cJuniorStatesman{\they} will be able to push through and accomplish what is needed. 
    \contact{\cChupLeader{}} \cHeadDiplomat{}'s secretary. Organized, professional, but lacking self motivation. You dubiously hope that \cChupLeader{\they} will be able to help you fill the hole \cHeadDiplomat{} left behind.
    \contact{\cFlowPriest{}} A \cFlowPriest{\cleric} of \cFlow{}, who you intend to collaborate with to resurrect the \cEbb{} Avatar. \cFlowPriest{\Theyare} more lax about rules and strictures than you are, and this sometimes leads to trouble. The two of you don't always see eye to eye, even in matters of theology, but you do respect \cFlowPriest{\them}.
    \contact{\cInitiate{}} An initiate of the \pShippie{} religion and a childhood friend of \cPresident{}, the two of you crossed paths at \cHeadDiplomat{}’s dinner parties. As \cInitiate{\theyare} graduating this year, it is past time \cInitiate{} picks a path and comes into \cInitiate{\their} full power, or decide that this is not the life for \cInitiate{\them}. You suspect \cInitiate{\theyare} dragging \cInitiate{\their} feet for some reason. You were there at the beginning of \cInitiate{\their} journey, and hope you can be there now as well. 
     \contact{\cWarlordDaughter{}} An initiate of the \pShippie{} religion, and the Warlord's \cWarlordDaughter{\offspring}. \cWarlordDaughter{} is in \cWarlordDaughter{\their} second year at the school, and is clearly struggling to find \cWarlordDaughter{\their} own sense of self, independent of \cWarlordDaughter{\their} \cLoud{\parent}. \cWarlordDaughter{\They} desperately want\cWarlordDaughter{\verbs} to be a cleric. 
    \contact{\cHeadScientist{}} A \pTech{} advisor that \cBeetle{} has delegated the task of working with you on researching the Creation of \pEarth{}.
    \contact{\cScholarship{}} A \pTech{} student, and initiate of \cTechGod{} that \cHeadScientist{} has brought along to be part of the research into the Creation of \pEarth{}.
\end{contacts}

\end{document}
