\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cPrincipal{}}

%Zev AKA WR Principal

You are \cPrincipal{\full} (\cPrincipal{\they}/\cPrincipal{\them}). You grew up in \pShip{} more than 250 years ago and followed your aspiration as a teacher all the way to the \pSchool{}. At age 62, near what you thought was the end of your career, you were chosen to be the next Principal. As the head of this important institution, you have been granted immortality by the Gods until you name your successor and pass on your mantle -- something you have finally resolved to do. You are tired -- oh so very tired -- and it is finally time to lay down your burdens and let younger minds determine the course of the world.

The \pShip{} of your childhood doesn't look all that different from the one of a decade ago. The Council of Stormwatchers was smaller, the rituals less elaborate, and food was a little blander. Still, everything was mostly the same, except for one important thing -- the pirates. While it's true that when you took on the Principalship, you foreswore your ties to the \pShippies{}, and accepted the fate that as long as your bore the title you could not leave the island on which the school is built, you have watched from a distance as the scourge of piracy slowly overtook your homeland. Watching their rise has been the hardest thing about remaining impartial and devoting yourself to the \pSc{}, even more so than the recent war. Conflicts come and go -- societal rot is harder to root out. And so you worry for the \pShip{} daily.

One of your greatest trials as Principal was the events of six years ago. After the Ritual to Control the Storm was completed, the students were tired but jubilant. Someone proposed a private toast for the students, so they all adjourned from the Great Hall to the Student Lounge, leaving the teachers and advisors twiddling their thumbs. After nearly an hour of waiting, you, \cDiplomat{\full}, and \cMusic{\full} decided that you had better go check on the students. What you found was 11 dead bodies. A quick inspection indicated that it was probably the wine. But where was the twelfth student, \cKidScientist{\full}? \cKidScientist{\They} \cKidScientist{\were} unaccounted for. The three of you stood in that room, the shock washing over you. Was \cKidScientist{} responsible, or \cKidScientist{\were} \cKidScientist{\they} an innocent victim who somehow managed to escape? You spoke quietly, and ultimately agreed to keep the fact that \cKidScientist{} was not among the dead a secret. It was far more likely that someone else had poisoned the students, and \cKidScientist{} had escaped. Keeping it out of public knowledge that \cKidScientist{\they} escaped would avoid anyone continuing to hunt \cKidScientist{\them}. And if \cKidScientist{\they} wanted to surface and return to the public eye, that was \cKidScientist{\their} prerogative. 

As if this tragedy weren't enough, the Betrayal of the \pShip{} came hard on its heels, as the Storm was sent to your homeland out of turn. You can't help but suspect that the two events are linked, that someone must have somehow rigged the vote under your very nose and killed the students to cover it up, but the official investigation that followed yielded no suspects. Besides, you had your hands full with the wave of resignations that followed -- teachers who couldn't bear what had happened and chose to leave the school. The school board had to hire quickly to fill their positions, and you had to train all of them before the new school year began. \cPrince{\full}, \cChupInventor{\full}, and \cChupSecond{\full} are all among that wave of new hires. Finding a replacement combat teacher took 2 years and you were most grateful when \cInterpol{\full} applied.

The curse of immortality is watching those you care about pass on without you. The people you grew up with, taught with, laughed with, broke bread with, they are all gone. It's not that you don't value your current colleagues, it's just that with every passing year, you feel more distant from them, more removed from the world. Even your current oldest friend, \cBunker{\full}, who visits the \pSc{} every 6 years to maintain the Bunkers, will pass away long before you, unless you make a change.  It's been wonderful to watch your former student and current friend, \cDiplomat{\full} grow up and flourish, but looking on \cDiplomat{\them} when last you saw \cDiplomat{\them} at an event recently, aged almost 50 years, you feel older than ever, and it's not a burden you wish to continue to bear.

And so, at the beginning of the school year, you announced your intentions to retire, and called for nominations for your successor. Over the past few months, you have evaluated a number of candidates, most of whom were teachers at the school. You believe you've narrowed your decision down to 2 finalists: \cMusic{\full} and \cBeetle{\full}. You haven't yet spoken with them explicitly about the heavy weight of immortality and responsibility to the school, but you know that conversation will be essential to prepare them for this burden. They must be prepared to watch life pass them by. They must understand that once they become principal, they mustn't leave the island (your predecessor disregarded this, and it caused the entire Old Wing of the College to collapse. Those ruins have resisted any attempt to clean them up or rebuild them.)

As a test, you have also given each of of your candidates charge over one of the important activities in the last few days leading up to the Storm. \cMusic{} is in charge of the Ceremony of Excellence - a fitting challenge for someone who has struggled to manage logistics in the past. \cBeetle{} is in charge of the crucial ritual to Renew the Ley Lines that keep the school afloat and channel magic throughout \pEarth{}. You feel it will be a good test of whether \cBeetle{\they} can let go \cBeetle{\their} ties to the here and now since it involves a sacrifice of power. While you are reasonably sure these two are up to at least the basics of these tasks, you have not discounted the possibility that you'll need to step in to make sure the tasks are completed correctly. And you are not above considering a dark horse candidate, even at this late stage, if they prove themselves invaluable to the maintenance of the school.

The other preparation to be made for the Storm is the Ritual itself. In order for the votes cast by the students to do anything, the Ritual must be set up in exacting detail. It requires Relics and careful preparation, and cooperation on all sides. The Relics are powerful artifacts in their own right, able to perform miraculous feats when attuned. Several attempts have been made to steal Relics over the decades. Very early in the annals of the \pSc{}, one of the \pFarm{} Relics disappeared. It took years of fevered work by the priesthood to sanctify a new one. You are committed to safeguarding all six Relics, making sure they are not tampered with or stolen, and that they all end up where they belong at the conclusion of the weekend – the three Relics in the Library should remain at the school, and the three Relics being brought by advisors should go home with those advisors. The three  Relics that are stored in the Library are the \iNet{}, the \iLariat{}, and the \iScythe{}. You intend to impress the importance of safeguarding the Relics upon your successor, whoever you should choose.

All of these preparations – the Ritual to Renew the Ley Lines, the Ritual to Control the Storm, and the Ceremony of Excellence, are essential. The results would be distressing if any one of them were to fail. But if \textbf{all three} were to fail, the consequences would be truly catastrophic – the \pSc{} would very likely be destroyed by the Storm, which would in turn be disastrous for all of \pEarth{}. Funny how all these little traditions actually matter. Without the \pSc{}, there would be no way to control the Storm, and it would rage unchecked across the whole continent and beyond. Worse still, with the \pSc{} and the Ley Lines running through the island irreparably damaged or destroyed, magic would either go completely haywire, or more likely, cease to flow throughout \pEarth{}, which could mean an end to all magic – the magic that powers the technology of the \pTech{}, makes the crops of the \pFarm{} grow, and keeps the ships of the \pShip{} seaworthy and thier weapons able to pierce sea serpent hide. You shudder to even think of it. Only you know of this vulnerability, as it is a closely guarded secret to prevent anyone from realizing they could sabotage the \pSc{} in this way. You will have to tell your successor, but you are loath to tell anyone else.

The other half of this process is the voting. Students from each nation will get a certain number of votes to cast toward where to send the Storm. Both the teachers and the advisors play a role in deciding how many votes each student should get. And it is your unenviable task to make sure it all happens. Not only are you in charge of making sure all the teachers and advisors submit their rankings on time, but you also have to ensure the votes are passed out appropriately on Sunday morning, and that the students submit those votes by lunch time.

Among the current crop of teachers, you have found an unexpectedly close friend in \cEthics{\full}, the Morality and Ethics teacher. \cEthics{\They} \cEthics{\have} such a kind and gentle heart, always considering the impacts of \cEthics{\their} actions and what will serve the greater good. You have taken it upon yourself to mentor \cEthics{\them}, though after two decades of friendship, you find yourself learning at least as much from \cEthics{\them} as \cEthics{\they} \cEthics{\does} from you.

Your closest friend among the teachers, however, is \cChupAvenger{\full}. \cChupAvenger{} seems to uniquely bring a smile to your face with \cChupAvenger{\their} deadpan humor, and reminds you of yourself in your younger days. As of late, though, \cChupAvenger{} has been in some trouble of the religious variety. Over the last few weeks, you came to notice some odd behavior on the part of the teachers at your school with regards to \cChupAvenger{} - they had come to forget \cChupAvenger{\them}. It took serious research, among some of the most obscure texts in the library, to figure out what was really happening. 

Your suspicions were confirmed when you confronted \cChupAvenger{} about it and \cChupAvenger{\they} confessed the whole story. Near the start of the war, \cChupAvenger{}'s anger about it caused \cChupAvenger{\them} to rashly renounce \cEbb{} and \cFlow{} and join the \pGoaties{}, even committing the primary taboo of this world -- murder -- in \cGenesis{}'s name. Murders done by devotees of \cGenesis{} don't have the same penalties as the other gods. Instead of losing your own memories, others forget you instead. This was a shock to you when you found out, but in talking to \cChupAvenger{}, you have come to understand why \cChupAvenger{\they} did what \cChupAvenger{\they} did, and truly see the remorse \cChupAvenger{\they} \cChupAvenger{\have} for those actions. You have since taken it upon yourself to help \cChupAvenger{} escape from that life, and cover for \cChupAvenger{\them} in the meantime. If the truth were to come out about \cChupAvenger{\their} actions, \cChupAvenger{\they} would be ostracized and probably imprisoned. There is not enough forgiveness in this world. That said, \cChupAvenger{} will need to reconcile with \cEbb{} and \cFlow{} through \cChupAvenger{\their} actions this weekend, and then convince a Cleric to induct \cChupAvenger{\them} back into the faith -- which will be awkward, since publicly \cChupAvenger{\they} never renounced the \pShip{} religion. Of the two Clerics of Ebb and Flow available to you, you think \cFlowPriest{\full}, one of the teachers, is more forgiving than \cEbbPriest{\full}, one of the advisors with a sterner reputation. 

After this Time of Deciding is concluded, you just want to retire in peace. No longer immortal, you'll be able to visit each fleet in your homeland, and then live out the rest of your life somewhere, preferably far away from conflict. Even if the war still rages, your time can be spent in quiet reflection, pondering questions you've always found fascinating, but never had time for among all of your other responsibilities -- like piecing together the truth about the creation of Cengea. Each country tells it slightly differently, and there are dozens of versions throughout history, so you've always been idly amused by contemplating what really happened. Once it is safe for you to travel, you want to see the world, experience all of the sights you haven't been able to for hundreds of years, and spend time with friends in a way that will mean more than it has since you took on the mantle of immortality.

All that will take is a smooth transition to the next generation. If you can make it out of here with a strong successor picked, the Relics in their proper places, and your friends safe and sound you will be able to finally rest.

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Make sure that all the voting goes smoothly, the teacher remain impartial, the voting stones are distributed accurately, the students vote on time, and that the ensuing Ritual to Control the Storm goes off without a hitch.
	\item Make sure the six Relics are neither tampered nor absconded with; after the weekend's rituals are complete, the three Relics at the school should remain at the school, and the three being brought by advisors should go home with those advisors.
	\item Decide who should succeed you as the immortal Principal of the \pSchool{}. Enact the transfer of power before the Storm is sent \emph{(OOC: before end of game)}. To that end, keep an eye on \cMusic{} and \cBeetle{} as they complete the tasks you've set for them. You can step in if you need to, but these tasks are meant to be tests of their fitness to take your place.
	\item Help \cChupAvenger{} mend \cChupAvenger{\their} ways, and return to the good graces of \cEbb{} and \cFlow{}.
\end{itemz}

\begin{itemz}[Notes]
	\item You know that pirates often identify undercover agents with code phrases. Since many pirates call The Graveyard, off the eastern coast of \pEarth{}, their harbor, you expect these phrases to contain reference to rough or un-navigable waters, or to water untouched by the Goddess' feet (a reference to the \pShippie{} Creation Story).
	\item The Principalship has an emblem representing it, which you will physically pass on to your successor. Please feel free to select a costume component for this purpose that you don't mind lending to another player when you choose your successor.

\end{itemz}

\begin{contacts}
	\contact{\cChupAvenger{}} Your best friend in the current era. Has made some bad choices, but is a fundamentally good person.
	\contact{\cEthics{}} The Morality and Ethics teacher, a close friend, and someone you've mentored over the years.
	\contact{\cMusic{}} One of your two finalists for succession. A little scattered, but seems to be growing at a rapid pace.
	\contact{\cBeetle{}} One of your two finalists for succession. You think \cBeetle{\they} might be too attached to \cBeetle{\their} current role and powers, but \cBeetle{\theyare} otherwise extremely competent.
	\contact{\cBunker{}} Your oldest living friend. A competent engineer who built and maintains the Bunkers at the \pSc{}.
	\contact{\cDiplomat{}} A former student and current friend, as well as the foremost diplomat in the \pTech{}.
\end{contacts}

\end{document}




