\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cPresident{}}

You are \cPresident{\full} (\cPresident{\they}/\cPresident{\them}), and a 3rd year student at the \pSchool{}. Now 22 years old, you were elected the Student Body President this year, and as such, it is your (self appointed) job to keep your fellow students safe when the teachers and advisors won't. As an enrollee from the \pShip{}, you follow the ways of \cEbb{\full} and \cFlow{\full}, particularly \cEbb{}. \cEbb{}'s focus on selective pruning of things that are no longer needed in order to provide clarity, answers, closure, and a place for the new is wonderful to you. Unlike many of your countrymen though, you find that ``like for like’’ isn’t always the best way to bring resolution.

You were born in the 2nd fleet, and grew up with \cInitiate{\full}, your best friend, under the watchful eye of your \cHeadDiplomat{\Auncle} \cHeadDiplomat{\full} and eventually \cHeadDiplomat{\their} assistant \cJuniorStatesman{\full}. The two of you did everything together, including moving to Drova's Landing, a port town in the 1st fleet. That changed a little when it was time to go to school. \cInitiate{\They} went to 1st fleet academy in order to study religion. Meanwhile, you went to the 2nd fleet academy, which focused on politics, negotiation, and economic policy, as you hoped to follow in your \cHeadDiplomat{\auncle}'s footsteps and become a politician. You were encouraged in this by \cJuniorStatesman{}, who always tried to make time for you and especially encouraged your interest in \cEbb{}. 

The war breaking out in your fifth year of your schooling increased your fervor for your schoolwork. You believe that the only way out of this war was going to be with diplomatic solutions that emphasized justice and you are willing to consider reparations for past wrongs as an alternative to more traditional paying back in kind. In this you have some conflict with \cJuniorStatesman{}. While you share the conviction that you can’t let the two other countries get away too easily, the strength of their anger and seemingly bottomless desire for revenge makes you nervous. \cJuniorStatesman{} took a sabbatical from their apprenticeship as a diplomat to go to war after all, joining the White Crest Ship. You respect \cJuniorStatesman{\them} for following their convictions, but you also have seen the grief and anger \cJuniorStatesman{\they} carry and wonder if it's wise for a diplomat to get that close to the war itself.  

\cHeadDiplomat{} on the other hand has been calling for peace. \cHeadDiplomat{\Theyhave} been seeking peace and recognizing that this war cannot go on forever, or if it does, that it would be terrible for the \pShippies{}. But while \cHeadDiplomat{\they} seek\cHeadDiplomat{\verbs} a rebalancing of pain through things like the Storm being visited upon the other two nations for the next few cycles, \cHeadDiplomat{\they} also wish\cHeadDiplomat{\verbes} to find common ground and reestablish the care that once existed between the nations, before the Betrayal. You are not a cleric, but your ties to the \pShippie{} religion reminds you of the value in finding balance between different perspectives. 

On top of all of this, you have had the privilege of knowing \cBunker{\full}, the greatest engineer in all of the \pShippies{}. \cBunker{\Theyare} a family friend of your \cHeadDiplomat{\auncle} and you regularly had family dinners with them and \cInitiate{}, especially when you all returned to the 2nd fleet from school. \cBunker{\Theyare} practical and forthright, though no diplomat. Unlike many of your other influences, \cBunker{} attributes little of \cBunker{\their} success to the twin Goddesses. It is an unusual perspective to be sure, but you’ve occasionally seen nods of agreement from your \cHeadDiplomat{\auncle} when the two of them spoke late into the night, nursing glasses of expensive alcohol. You have wanted to bring that up, but never have had the chance.

At the \pSchool{}, this education and all of your deep connections have served you well. It has led you to become the Student Body President, a role that will in turn support your future political career. Reunited by the Goddesses' own good fortune with your best friend here at the \pSchool{}, the two of you are more or less unstoppable\ldots{} Or would be if \cInitiate{\their} luck would stop being utterly rotten for 10 seconds. Three months ago, \cInitiate{} received a letter from ``long lost family'' in the \pFarm{}. They demanded \cInitiate{\their} immediate return to the \pFarm{}, to take \cInitiate{\their} rightful place in the family. \cInitiate{} had no such inclination to do so initially, but the bad luck curse that came with the letter is really starting to wear down \cInitiate{\their} resolve. The two of you have been trying to find a solution, to no avail, but you're far from giving up. 

\cInitiate{}'s other friend, \cWarlordDaughter{\full}, seems oddly fixated on \cInitiate{} giving \cInitiate{\their} \pFarm{} family a chance. But \cWarlordDaughter{} is not a bad sort, all told, and if \cWarlordDaughter{\their} help breaking the curse could tip the balance, you'd happily welcome it. Even though you two seem to argue about everything, from the war to religion to, well, curse breaking. You are starting to wonder if \cInitiate{} has feelings for \cWarlordDaughter{} beyond just friendship. You just hope that \cInitiate{} does not do anything foolish regarding the curse due to a crush. 

With myriad responsibilities as the Student Body President, both those assigned to you and those you’ve given yourself, sometimes your social life has to take a back seat. But since you are graduating this year, as \cInitiate{} loves to remind you, it is past time you turn some attention in this direction. You kept meaning to approach \cHeir{\full} or \cChupStudent{\full} romantically, but have never quite gotten around to it. You think very highly of both of them. \cHeir{} knows what \cHeir{\they} want\cHeir{\verbs} and is willing to fight for it, even if it's going to be hard to achieve. \cHeir{} has a lot of compassion, and you sympathize deeply with \cHeir{\them} for the loss of \cHeir{\their} older \cHeirSibling{\sibling} six years ago. You initially bonded over your shared desire to find out what happened. In the time since, you’ve found \cHeir{} to be a free spirit who’s been kept in port \cHeir{\their} whole life and never allowed to explore the currents. It makes your heart ache. \cChupStudent{}, for \cChupStudent{\their} part, is really easygoing (some go so far as to call \cChupStudent{\them} a slacker), but no one knows how to ``go with the flow'' better. Something about \cChupStudent{\their} laid-back, relaxed manner just puts you at ease, and makes you want to spend long, lazy afternoons together on the beach. You have been helping \cChupStudent{} in the library a lot recently, and you have deeply enjoyed the chance to just be near \cChupStudent{\them}. You think that \cHeir{} and \cChupStudent{} may not like each other that much, or at least they don’t talk much when you all are having meals together (usually with \cHeir{}’s good friend \cAmbition{\full} or \cInitiate{}). Which makes things more complicated...

Given that you are graduating soon and considering all the uncertainties this weekend, now might be your last chance to tell one or both of them how you feel. Rushing the job might make things a bit awkward, but \cInitiate{} makes a great wing\cInitiate{\person}. Despite not having any current partners, you identify as polyamorous. Could you possibly be lucky enough that both \cHeir{} and \cChupStudent{} might be interested in you, and willing to try? Even when the \pFarm{} and the \pTech{} do not recognize polyamory as a valid relationship structure? Or could you really go the rest of your life not knowing what might have been?

Since becoming Student Body President, you've been thinking more and more about how to protect the students. This mindset has brought with it the intense desire to figure out just what happened at the \pSc{} six years ago — just before the war started — when a unanimous vote that sent the Storm to the \pShip{} was followed by the mass murder of every student who voted. How could the students from \pShip{} have ever voted to send the Storm there out of turn? They would have known that it disrupted the balance and that it would kill their families and friends. You know there was treachery, there simply must have been. While the Deities presumably saw to the punishment of the direct murderers, it is up to the people to see that justice is brought upon those who orchestrated it. It is up to you and \cHeir{} to find these answers. 

Together you and \cHeir{} began speculating on how you could find out what happened. You hit something of a roadblock until \cHeir{} thought to contact \cWildCard{\full}, a \pFarm{} scholar, about the problem. While being as vague as possible about why you wanted to look into the past, \cHeir{} coaxed a tremendous amount of help from \cWildCard{\them}. You contributed in your own way, regularly digging up esoterica from the Library that the other two needed to proceed with designing the ritual. And now you have the finalized ritual in hand. All you need is the ``\iMirror{}’’, which is arriving this weekend in the possession of \cDiplomat{\full} (OOC: see your Greensheet). Now you just have to hope \cDiplomat{\they} will be willing to let you use it and keep your investigation quiet. If \cDiplomat{\theyare}n't willing\ldots{} will you let it stymie your search for answers? How far are you willing to go to learn the truth? Would you steal from the second most powerful Diplomat of \cDiplomat{\their} generation (behind your \cHeadDiplomat{\Auncle} \cHeadDiplomat{\full}, of course)? This investigation is of the utmost importance. After all, what if whoever did this is still at the \pSchool{}? And what if they try to do the same again\ldots{}?

Uncovering the past isn't the only thing on your mind. You've also got to look to the future. For the good of your country, the student body in general, and for your friends among them, there are two things happening this weekend that you can't just leave the teachers and advisors solely in charge of. For the preservation of the \pSc{}, it is important that the Ley Lines be renewed every three years. As student body president, you feel it is your duty to assist. And then there is the all important Ritual to Control the Storm. After the voting, a ritual is enacted to channel the magic from the students into actually directing the Storm. The ritual requires the use of one Relic per nation. You anticipate that setting up the ritual will be the most challenging and involved of your tasks this weekend. You are determined to monitor the proceedings and make sure there is no foul play.

Something that may put the ritual in jeopardy is a problem related to one of the most important figures in the ritual — the fact that the Librarian, \cLibrarian{\full}, has been acting\ldots{} odd. Almost as if \cLibrarian{\they} can't \emph{remember} how to do \cLibrarian{\their} job. Maybe others don’t recognize this, but you have been the third assistant to the \cLibrarian{} for two years now. You don’t know exactly how to interpret this. Maybe \cLibrarian{} has just stopped caring? Maybe the Librarian has a lot of other things on \cLibrarian{\their} mind or is hiding something? Maybe some imposter is pretending to be \cLibrarian{\them}? Or maybe, and this is the most serious, maybe \cLibrarian{\theyhave} done something terrible and incurred the wrath of the Gods? You really hope it's not one of those last two options! You need to investigate the truth and make sure you know every detail before you do anything risky like publicly accuse the Librarian of being a fraud or a murderer. It's such a shame, too — you have always had the utmost respect for \cLibrarian{}.

With so many things this weekend requiring access to the Library (or at least the knowledge stored there), you expect to do a lot of what should be the Librarian’s job. You plan to leave the one-upmanship and maneuvering to \cAmbition{\full}, the first library assistant, and \cLibAssist{\full}, the second. Those two are constantly competing for \cLibrarian{}’s approval, and you just don’t have time for such games. Knowledge is the important part, not who has a certain title. You are as fond of both of them as you can be, given that they are from the \pTech{} and \pFarm{} respectively. You don't like the nastiness this competition brings out in them, but there's only so much you can do to keep the peace. \cAmbition{} is friends with \cHeir{} and you find that \cAmbition{\theyare} pleasant to be around and you both care deeply for \cHeir{}, which is a place you have bonded. \cAmbition{\Theyare} not friends, and have not opened up much to you, which is their prerogative. You just hope you have not somehow offended \cAmbition{\them}.

On the other hand, you often study with \cLibAssist{} and have even found yourself confiding in \cLibAssist{\them} at times. \cLibAssist{\They} can be quite ruthless when upset and are not someone to cross lightly, but you know \cLibAssist{\theyhave} had a hard life and a lot of the students give \cLibAssist{\them} shit for some bad stuff \cLibAssist{\their} family did during the war involving trebuchets. While you hate the trebuchets and the toll they take on your people, it's wrong to blame someone for what their family did when \cLibAssist{\they} had nothing to do with it. You think \cLibAssist{} is probably lonely and just needs more people to trust, and you are glad to be such a person. 

After realizing last night that the Librarian is acting weird, you felt the need to review the protections around the three Relics stored in the library — the ``\iNet{}', the ``\iLariat{}'', and the ``\iScythe{}''. You feared this could be part of some larger plot. You don't usually break rules, and students should not be that deep in the Library without supervision, but you had helped another friend, \cChupStudent{\full} sneak down into the third tier about two months ago, so you knew you could do it again. (That trip hadn’t gone so well. The two of you got separated, though \cChupStudent{\they} assure\cChupStudent{\verbs} you that \cChupStudent{\they} got what \cChupStudent{\they} needed.) . 

Upon reaching the Reliquary, you realized something terrible — the wards on the reliquary where it was normally stored had been crudely shattered! You are not exactly comforted by the fact that none of the Relics were missing. Why break the wards and not take them? Is this a trap? Part of a larger scheme? Did someone take one, do something with it, and bring it back? You spent all night trying to work out how to tell someone (since you shouldn't have been in that area of the Library alone). Could the breaking of the wards on the Relics be somehow connected to the Librarian acting so weird?

You also want to make sure that you get enough Voting Stones from teachers to make sure you can vote effectively and make sure the Storm does not go to the \pShip{}. You will be leaning heavily on two teachers you have become close to at school. One is \cChupSecond{\full}, the economics teacher. You knew you loved politics, but didn’t realize you would find economics so fascinating too! You have been doing an extra research project for \cChupSecond{\them} on the benefits and drawbacks of financial reparations. (Financial reparations are a very unpopular option among the \pShippies{} — The Twin Goddesses insist that proper balance can only be restored by returning harm of a similar kind and magnitude. A.k.a. You can’t just buy forgiveness.) Working with \cChupSecond{\them} has opened your mind to how privileged your position in the 2nd fleet really is, and how much economic inequality still exists. You still are considering how best to act on this new perspective. 

You also really respect the competence and quiet calm of \cPirate{\full}, the crafting teacher. Crafting is something that calms your mind and helps you focus, and while it is not something you would ever do for a living, you appreciate how different it is from the rest of your life. \cPirate{} has ended up being someone you feel that you can turn to not just about school but life as well. You hope that \cPirate{\they} will support you both emotionally and with \cPirate{\their} Voting Stone.  

While you have made a handful of friends, in general it is hard for you to connect with the students from the \pTech{} and the \pFarm{}, especially given the war. For example, \cTechStar{\full} sit\cTechStar{\verbs} on the High Council of the \pTech{}. \cTechStar{} has a direct say in the policies of \cTechStar{\their} entire country. \cTechStar{\They} literally vote\cTechStar{\verbs} to continue the war regularly, when \cTechStar{\they} could instead admit to the harm the \pTech{} has caused, and work toward making amends instead. 

That is not to say that you get along with everyone on the \pShip{}. You care deeply that the school is safe, and that the students are cared for, and you are easily frustrated with anyone who could put this in jeopardy. This weekend, \cPirateChild{\full}, a first year student from the 5th fleet, has you worried. \cPirateChild{\Theyare} constantly poking \cPirateChild{\their} nose into conversations and unattended teachers’ desks. You have seen \cPirateChild{\them} take random odds and ends, like pieces of fruit, from desks, which is not much, but is stealing! And except in a few classes, \cPirateChild{} is always mouthing off, or not paying attention or making a joke. You hope that \cPirateChild{\their} actions are just harmless pranks, but you can’t wrap your head why \cPirateChild{\theywere} even chosen for such an incredible duty as the Ritual to Control the Storm in the first place! You need to keep a very close eye on \cPirateChild{\them} this weekend.

The last, but certainly not least, thing on your mind comes in the form of figuring out what happened to your \cHeadDiplomat{\auncle}, \cHeadDiplomat{}. You were really looking forward to seeing your \cHeadDiplomat{\auncle} after a long absence, and getting \cHeadDiplomat{\their} advice on your troubles; the two of you have always been quite close, corresponding frequently since you’ve been at the \pSc{}, and \cHeadDiplomat{\they} never steered you wrong. But just this morning (mere hours before the advisors arrived), you received news from \cEbbPriest{\full} that \cHeadDiplomat{} won't be coming due to a ``sudden illness.'' The very next letter you opened was from \cJuniorStatesman{}, who told you the truth — your \cHeadDiplomat{\auncle} was attacked by an assassin and ended up killing them in self defense. \cHeadDiplomat{} is now a total amnesiac. \cJuniorStatesman{} asked for your help finding whoever sent the assassin — discreetly, since there is a good chance it is one of the advisors from the other countries, and you don't want to scare them off before you have proof. The public story is still that \cHeadDiplomat{} is suffering from a sudden illness, and \cJuniorStatesman{} asked that you not tell anyone what really happened yet. You are filled with grief over the loss of your \cHeadDiplomat{\auncle}'s memories, and determined to find those responsible. 

You hope that \cEbbPriest{} will also support you this weekend. \cEbbPriest{} is an old family friend through \cHeadDiplomat{}, and while the circumstances under which \cEbbPriest{} is attending (taking \cHeadDiplomat{}’s place) are not pleasant, you expect to be able to turn to \cEbbPriest{\them} for support should you need it. \cBunker{\full}, has always had a good head on \cBunker{\their} shoulders and is a good friend of \cHeadDiplomat{}. You are glad you have \cBunker{} here. You don’t know the other advisor, \cChupLeader{\full} as well, but \cChupLeader{\theywere} \cHeadDiplomat{}’s secretary, so \cChupLeader{\they} will probably also be happy to help you as well. Any of the advisors should be able to help you determine the best course of action in any situation, whether that is prioritizing protecting your home, or weighing the pros and cons of actions that might trade short term consequences for the long term betterment of the world.

This weekend at the \pSchool{} will be packed. You and your country both have a lot riding on your actions here. Your top priorities are to ensure that the rituals go smoothly, figure out what happened to your \cHeadDiplomat{\Auncle} \cHeadDiplomat{} as well as the students six years ago, and to maybe find love along the way. It will be a lot — but with your friends by your side, you know you are up to the challenge.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Find out what happened to the students six years ago with the help of \cHeir{}. Bring anyone responsible who hasn't been punished by the Gods to human justice and make sure they can't do anything like that to you and your classmates.
    \item Work with \cJuniorStatesman{} to investigate the assassination attempt on your \cHeadDiplomat{\auncle}, \cHeadDiplomat{}.
    \item Ensure the Ritual to Control the Storm and the Ritual to Renew the Ley Lines are set up correctly. Don't let anyone interfere with them.  
    \item Make sure the Storm doesn't get sent to the \pShip{} yet again.
    \item Help your friend \cInitiate{} get rid of \cInitiate{\their} bad luck curse, and with the decision whether to visit \cInitiate{\their} extended family in the \pFarm{}.
    \item Figure out if there's any chance of getting together with \cHeir{} and/or \cChupStudent{}.
    \item Learn the truth of what happened to the Librarian and the disappearance of the \iScythe{} and determine if they are connected.
\end{itemz}

\begin{itemz}[Notes]
    \item You are graduating this year.
    \item Your extensive time in the Library gives you advantages over others when navigating the Library.
\end{itemz}

\begin{contacts}
    \contact{\cInitiate{}} Your best friend since childhood. \cInitiate{\Theyare} under a bad luck curse that the two of you have had no luck breaking these past three months.
    \contact{\cJuniorStatesman{}} Your \cHeadDiplomat{\Auncle} \cHeadDiplomat{}'s apprentice and a mentor from childhood who wrote to you about the assassination attempt on \cHeadDiplomat{}, and has enlisted your help in finding the perpetrators.   
    \contact {\cBunker{}} An old friend of your family and one of the best engineers in the world, who is always good for a new perspective.
    \contact{\cLibrarian{}} The school Librarian. A normally kind person who has been acting extremely suspiciously since returning from break. You suspect amnesia, which probably means foul play. You need proof before making any public accusations.
    \contact{\cHeir{}} Helping you investigate what happened to the students six years ago. You also have a crush on \cHeir{\them}. Is it possible to start a relationship? Is \cHeir{} even interested?
    \contact{\cChupStudent{}} A ``go with the flow’’ type. You have a crush on \cChupStudent{\them}. Is it possible to start a relationship? Is \cChupStudent{} even interested?
    \contact{\cLibAssist{}} A fellow student, study partner, friend, and first assistant to the Librarian. \cLibAssist{\They} strike\cLibAssist{\verbs} you as a bit mercenary, but you're not going to hold that against \cLibAssist{\them}.
\contact{\cPirateChild{}}: A \pShippie{} student who you have seen acting suspicious before and who you worry will somehow cause an issue this weekend.  
    \contact{\cChupSecond{}} The economic professor at the \pSchool{} who has exposed you to new thoughts and understandings about inequality and justice.

\end{contacts}
\end{document}





