\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cInitiate{}}

You are \cInitiate{\full} (\cInitiate{\they}/\cInitiate{\them}) and a student at the \pSchool{}. At 22 years old you are an Initiate in the Clergy of \cEbb{} and \cFlow{}, with a life of meaning and devotion ahead of you. You have a passion for crafting and engineering as well, but religion is your first love. You are from the \pShip{}, but your parents ran away from the \pFarm{} before you were born and that history has made your life\ldots{} complicated of late. With the help of your best friend, \cPresident{\full}, there is a lot you intend to accomplish at the Time of Deciding this weekend.

You were born in the 2nd fleet and grew up alongside \cPresident{}. For many years, the two of you did everything together, including moving to Drova's Landing, a town in 1st Fleet — until the time came to go to academy. \cPresident{}’s family was very well connected, and you regularly attended dinner parties with movers and shakers, especially those in the orbit of \cPresident{\their} \cPresident{\auncle}, \cHeadDiplomat{\full}. \cHeadDiplomat{} is the premier diplomat of the \pShip{}. Your favorite was \cBunker{\full}, the best engineer in the \pShip{}. \cBunker{\they} encouraged your crafts and schemes, even made little notes on them and shared with you \cBunker{\their} own ideas freely. \cBunker{\They} may seem a curmudgeon, and can be a bit dismissive of the Twin Goddesses, but never once has talked down to you, instead always encouraging your dreams.  

You didn’t know \cJuniorStatesman{\full} nearly as well, as \cJuniorStatemsan{\they} started to visit later, after \cJuniorStatesman{\they} were named assistant diplomat to \cHeadDiplomat{} nine years ago. \cJuniorStatesman{\They} \cJuniorStatesman{\have} a great mind for politics and a deep understanding of how to win friends and arguments. You respect \cJuniorStatesman{} and \cJuniorStatesman{\they} even tried to convince you before you left for your religious studies to follow your friend and join politics, but you have little interest in such things. Sometimes you also worry that \cJuniorStatesman{} is a bit too interested in revenge, even for a \pShippie{}? You know \cJuniorStatesman{\they} went to war for a few years out of a desire to help, and this changed \cJuniorStatesman{\them}. How many others has this war driven to anger and revenge?

While \cBunker{} was your favorite, it was another of \cPresident{}’s dinner fellows who changed the direction of your life. \cEbbPriest{\full} was a close friend of \cHeadDiplomat{}’s partner and, when \cEbbPriest{\they} had the time to leave \cEbbPriest{\their} community to which \cEbbPriest{\they} ministered, \cEbbPriest{\they} came to visit. Wise, scholarly, and thoughtful, \cEbbPriest{} and you had long conversations about the precepts of \cEbb{} especially. Yet with all of this, \cEbbPriest{} was deeply wordly and told you much about other religions and lands, including the \pFarm{}. When your mark of favor appeared from \cEbb{} and \cFlow{}, \cEbbPriest{} was the first person you told, even before \cPresident{} or your family. \cEbbPriest{} was elated, and recommended you to the 1st fleet academy to study religion with the intent to enter the priesthood, while \cPresident{\they} went to 2nd fleet academy, to study politics and diplomacy. Ever since then, they have visited you regularly when they could, though the war has meant it happens less often. You can see how saddened \cEbbPriest{\they} are about the war. You hope as a \cInitiate{\cleric} you can help lead the \pShippies{} towards a brighter future, or at least no Storms for a while.

Now that you are reunited by the Goddesses' own good fortune with your best friend here at the \pSchool{}, the two of you are unstoppable! Unstoppable, that is, except for the bad luck. Three months ago, you received a ``\iCursedLetter{}'' from your long lost family, the Fairweathers, in the \pFarm{}. They demanded your immediate return to the \pFarm{} to take your rightful place in the family and continue the bloodline. You had no such inclination to do so initially — your immediate family immigrated to the \pShip{} to escape these people before you were even born, after all, so you have no connection or interest in them beyond the last generation's bad blood. However, the bargaining chip that the letter spoke of, a curse of bad luck, was inflicted on you by the letter itself — and its continued influence on your life has begun to wear you down. You trip and drop things frequently. You lose objects that you cherish, like the holy symbol your mother gave you when you left home to study as a \cInitiate{\cleric}. On one occasion, an errant gust of wind blew an essay you had just finished writing for class into the fireplace and you had to start all over!

Honestly, all of this makes you not want to trust folks from the \pFarm{} unless they really prove it. Take \cLibAssist{\full}, for example. While it may not be \cLibAssist{\their} fault, \cLibAssist{\their} family commanded trebuchets that killed not only \pShippies{} but also people on \cLibAssist{\their} own side. You don’t know how that happened, but you bet it was greed, which just seems so typical. To be fair, though, you don’t trust many people on the \pTech{} side either. But you reserve a special distrust for the \pFarm{}.  

You regularly stay up late talking with \cPresident{} and \cWarlordDaughter{\full}, another initiate to the priesthood who is here at the \pSc{}, about what to do. \cWarlordDaughter{} is surprisingly sentimental for someone who is the \cWarlordDaughter{\offspring} of \cLoud{\full}, the warlord who started and leads the \pShip{} war effort. You like \cWarlordDaughter{} a lot. You can tell that some of the other students from \pTech{} and the \pFarm{} seem to distrust \cWarlordDaughter{\them} due to who WarlordDaughter{\their} \cLoud{\parent} is, but you know \cWarlordDaughter{} to be compassionate, kind, and desperate to get out of \cWarlordDaughter{\their} \cLoud{\parent}’s shadow. 

Okay, you admit it, you have a crush on \cWarlordDaughter{\them}. Of course, this will never amount to anything because \cWarlordDaughter{\they \are} with \cTechStar{\full}, one of the few good \pTech{} students. And this was all your fault! You helped matchmake the pair after you saw how much they got along after you had to drop out of two group assignments due to, well, lots of bad luck. You even helped them with their awkward confessions of feelings via encouraging them both to exchange letters confessing their feelings on the same day. And, of course, there you go getting feelings yourself. You need to either let \cWarlordDaughter{} know or try and move on. Because you do get the feeling that \cWarlordDaughter{} may also be interested in you? But would \cTechStar{} be willing to consider polyamory? It’s not exactly a thing in the \pTech{} and you don’t want to disrupt their relationship. Further, those two have chosen to keep their romantic entanglement on the down low, not telling any of the other students. You don’t know why exactly, but you respect their decision and don’t want to spill a secret that isn’t yours.

All of this is to say, you were surprised about how \cWarlordDaughter{} often encourage\cWarlordDaughter{\verbs} you to at least give your family in the \pFarm{} a chance.  \cPresident{}, on the other hand, is convinced that if you went to your grandparents' place they would never let you leave. With their heavy handed efforts to get you back, you certainly see his point. Either way, you've got to get rid of this curse somehow! Then you can figure out if you want to go visit your grandparents.

The cursemaker teacher at the \pSchool{} says there is no easy way to break a bad luck curse; the only thing one can do is fulfill the requirements to end it that were stipulated in its creation — i.e. go to the Fairweather estate. Either that or somehow find the person who made the curse and convince them to release you from it. Or perhaps one of the Relics can help? Your investigations with \cPresident{} and \cWarlordDaughter{} haven't turned up much else  in terms of other leads, except a few errant whispers about a hidden group that follows a Deity of Luck instead of one of the Patron Deities. Maybe they could help you, if you could find them.

You tried to get a second opinion about the curse from \cAdopted{\full}, a student from the \pFarm{} who had a reputation as being a curse breaking prodigy. You hadn’t really talked to \cAdopted{\them} much — \cAdopted{\they} always seemed prickly — but you had heard that \cAdopted{\they} really resented \pFarm{} nobility. This seemed like a perfect project for \cAdopted{\them} to get back at the nobility while helping a fellow student out. But when you asked \cAdopted{\them} they had the audacity to ask for an exorbitant price. And claimed that \cAdopted{\they} didn’t work for free for rich kids. How heartless and rude! You are so angry at \cAdopted{\them}. Maybe you can transfer your curse to \cAdopted{\them}. You certainly feel that \cAdopted{\they} deserve it. 

There's another important decision to make this weekend — you've been putting off picking a path for your priesthood. You will need to pick one Goddess to primarily serve, and with both \cEbbPriest{\full}, a \cEbbPriest{\cleric} of \cEbbFull{\full}, and \cFlowPriest{\full}, a \cFlowPriest{\cleric} of \cFlowFull{\full}, here this weekend, it's a pretty good opportunity. In fact, if you end up deciding to stay with your extended family, it may be your ONLY opportunity — and a short lived one since you could not be a \cInitiate{\cleric} of \cEbb{} or \cFlow{} in the \pFarm{}. 
And, as a side benefit, it would be really nice to have access to the full range of power that a \cInitiate{\cleric} has. It is a tough decision. 

You have had such a long relationship with \cEbbPriest{}, but you are concerned about having to be a full time \cInitiate{\cleric}, fully devoted to \cEbb{}’s work. You also have started to feel a bit distant from \cEbb{}’s call of scholarship and looking for that which is lost, especially since maybe some lost things, like your grandparents, should not be found. During your time at school, you have found a mentor in \cFlowPriest{}. \cFlowPriest{} has a job as a teacher of mathematics, as well as \cFlowPriest{\their} \cFlowPriest{\cleric} duties. \cFlowPriest{} has such a presence of emotional support, of openness, a willingness to try new things and break a bit away from tradition. While you have not told \cFlowPriest{\them} about your bad luck curse, you have talked to them about your grandparents trying to get you back, asked \cFlowPriest{\their} advice countless times, and heeded \cFlowPriest{\their} counsel. And as you have learned more about the teachings of \cFlow{}, and the focus \cFlow{} has on creation (which touches on your interest in invention and generating new ideas), the more you are drawn to \cFlow{\them}. You'd love to be able to continue to follow your passion for engineering even after you join the priesthood. That particular concern is independent of the decision on which path to choose. But choose you must.  

\cFlowPriest{} recently confided in you that something terrible had happened that could also affect your plans to join the priesthood — the Avatar of \cEbb{} had been murdered! Setting aside the dire implications for the \pShip{} as a nation, on a more personal level, without the \cEbb{} Avatar alive and well, your only choice is the path of \cFlow{}. While \cFlow{} isn't a bad choice, you would like to actually be able to \textbf{choose}. That's why, when \cFlowPriest{} came to you with a surprising opportunity to resurrect the Avatar this weekend, you were excited to help. You just hope you can be of assistance in this important secret quest. You expect it will be really challenging, but have confidence that between you, \cFlowPriest{}, \cEbbPriest{} and probably \cWarlordDaughter{}, you will figure it out.

Before you get too lost in your future, though, it's worth engaging with the opportunities of the present. Chief among these is the chance to study with \cBunker{} when \cBunker{\they} arrive\cBunker{\verbs} with the \pShip{} delegation to inspect the Bunkers that keep people safe from the Storm Surges at the \pSc{}. You can’t wait to see \cBunker{} again for a few days, even in such trying circumstances. \cBunker{} is a person you can just talk to, and you really hope \cBunker{\they} can give you advice on the many questions you have, especially where your future may lie! \cBunker{} is primarily a follower of \cEbb{}} — and while not a priest, \cBunker{\they} could have some perspective on how to keep on doing both priesthood and engineering.  

You also intend to look out for what is best for the \pShip{}. You plan to keep an eye on, and take a hand in, setting up the Ritual to Control the Storm. You care for your homeland, and by making sure the ritual is arranged correctly, you can ensure no one is up to anything shady that might screw over the \pShippies{} again. You don't really care which students get more votes to direct the Storm, as long as they direct it away from the \pShip{}. However, you doubt folks from the \pTech{} and especially the \pFarm{} would think about helping the \pShip{}, especially with how much they rally around their own. So working to make sure it's mostly \pShippies{} who collect the most Voting Stones would be a good thing. Helping with the ritual will also be a good opportunity to work directly with \cEbbPriest{} and \cFlowPriest{} and observe how their different callings cause them to approach situations differently.  

Aside from your own plans, you are happy to support \cPresident{} in \cPresident{\theirs}. \cPresident{} is looking into what happened to the students six years ago, when the Storm was sent to the \pShip{} out of turn the first time. You suspect that investigation might end up requiring\ldots{} religious support, but without any way to guess which adults were involved in that mess, you're a much safer option — hopefully the power you have as an initiate will be enough.

Your sense of camaraderie with \cPresident{} even goes so far as to wing\cInitiate{\person} for \cPresident{\them} in matters of romantic attraction. Thankfully, this time you didn’t catch feelings for someone on the way like your matchmaking between \cTechStar{} and \cWarlordDaughter{}. This being \cPresident{}'s last year at the \pSc{} too, \cPresident{\they} \cPresident{\have} left it a little late, but such is the way of things. You think that \cPresident{} could make a good couple with either of \cPresident{\their} current crushes: \cHeir{\full} or \cChupStudent{\full} — or both of them! You just have to figure out how to get them all to open up to each other about their feelings. And deal with \cHeir{} and \cChupStudent{} being resistant to polyamory, of course; neither of their home nations condone it. While you give a bit of side eye to \cPresident{}’s choices, both from powerful families from the other nations, you have found \cHeir{} and \cChupStudent{} to be two of the ones you trust more. Possibly because they both seem to not like their families.  

Maybe romance is just in the air. You unintentionally learned that the Art teacher, \cChupAvenger{\full}, is having romantic problems of \cChupAvenger{\their} own. While \cFlowPriest{} has been your main mentor at school, \cChupAvenger{} is also a favorite. It's pretty impressive to be that incredible of an artist, and you are a bit in awe. Like \cBunker{}, \cChupAvenger{} encourages you and never talks down to you. You think you may also be one of \cChupAvenger{}’s favorites. This is why you want to help! \cEbb{} and \cFlow{} encourage their followers to give their prayers to the sea breeze, which will carry the prayer to the ears of the Goddesses. This sometimes means that other mortals overhear too. \cChupAvenger{}'s prayer to have \cHeadScientist{\full} remember their romance was carried to your ears. Maybe it was just coincidence, or maybe the Goddesses have sent you to be their instrument, and to help these two get back together. You have in fact insisted you are going to help and \cChupAvenger{} has agreed. You are trying not to think too hard about the question of what \cHeadScientist{} did to lose part of \cHeadScientist{\their} memories. But on the other hand, how wonderful would it be to help these two restore their relationship? As with many problems, the best place to start researching is probably the Library! Maybe the Librarian \cLibrarian{\full} has some ideas?

So this weekend is going to be busy. You have a lot of decisions to make about your own future, the future of your nation to protect, and the future of your friends to help build. You are grateful for your friends and for the advisors of the \pShip{}. You know you can trust \cEbbPriest{}, \cJuniorStatesman{}, and \cBunker{} for counsel as you face this weekend’s decisions around the Storm and you trust \cChupLeader{\full}, the other advisor, as well. Maybe together you can answer the burning questions in your life. Which Goddess will you choose to serve? Will \cPresident{} or \cChupAvenger{} find romance? And will you manage to break the bad luck curse without being forced to acquiesce to your \pFarm{} family's demands?

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Work with \cPresident{} and \cWarlordDaughter{} to find the followers of a Deity of Luck and see if they can help you break the Bad Luck Curse. Then decide whether you are going to visit your extended family in the \pFarm{}.
    \item Help the teachers prepare for the Ritual to Control the Storm, and make sure the Storm gets sent somewhere other than the \pShip{}.
    \item Choose your cleric's path, whether it be \cEbbFull{\full}, \cFlowFull{\full}, or the very difficult path of Balance, and have your promotion ceremony to full \cInitiate{\cleric}.
    \item Help \cFlowPriest{} and \cEbbPriest{} secretly resurrect the \cEbb{} Avatar. Without it, you cannot choose to follow \cEbb{}'s path.
    \item Decide what to do about your romantic feelings for \cWarlordDaughter{}, who is already dating \cTechStar{} thanks to your matchmaking efforts.
    \item Hang out with \cBunker{} and do your best to assist \cBunker{\them} in maintaining the bunkers.
    \item Help \cPresident{} out with \cPresident{\their} investigations into what happened six years ago, and if you can get \cPresident{\them} to put work aside for a minute, help \cPresident{\them} approach \cHeir{} and/or \cChupStudent{} as potential romantic partners.
    \item Help \cChupAvenger{} out with getting \cHeadScientist{} to regain \cHeadScientist{\their} memories of \cChupAvenger{}.
\end{itemz}

\begin{itemz}[Notes]
    \item You are graduating this year.
    \item Your lost holy symbol was a ring with two sea serpents entwined, each swallowing the other's tail.
\end{itemz}

\begin{contacts}
    \contact{\cPresident{}} Your best friend. Accomplished and confident — yet sometimes you wonder if \cPresident{\they} would be able to accomplish anything without your help.
    \contact{\cJuniorStatesman{}} A friend of \cPresident{}’s family who tried to get you into politics. You respect \cJuniorStatesman{\them} but do not necessarily get \cJuniorStatesman{\them}.  
    \contact{\cWarlordDaughter{}} A fellow initiate of the Goddesses. Great for late night chats about the meaning of life. You fully admit you have a massive crush on \cWarlordDaugther{\them}.  
    \contact{\cBunker{}} An old friend and the chief engineer who designed the bunkers that protect people at the school as the Storm intensifies over the weekend. You are so excited to study with them during the regular check of the bunkers and ask for their advice about life in general.
    \contact{\cFlowPriest{}} A \cFlowPriest{\cleric} of \cFlow{} and teacher at the school. \cFlowPriest{\They} \cFlowPriest{\have} a flexible and open minded interpretation of the faith and have been acting as a mentor.
    \contact{\cEbbPriest{}} A \cEbbPriest{\cleric} of \cEbb{}, an advisor at the school this weekend, and a full time \cEbbPriest{\cleric}. \cEbbPriest{} has been a mentor of yours since your youth. \cEbbPriest{\They} \cEbbPriest{\have} a somewhat stricter and more ``by the book'' interpretation of the faith.
    \contact{\cChupAvenger{}} One of your favorite teachers whose love, \cHeadScientist{}, has forgotten \cChupAvenger{\them}. You want to help if you can!
    \contact{\cTechStar{}} \cWarlordDaughter{}’s partner thanks to your matchmaking efforts, and a pretty decent person, despite the hard time some others from your nation give \cTechStar{\them} for being on the \pTech{} High Council.
\end{contacts}
\end{document}





