\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cChupSecond{}}

You are \cChupSecond{\intro}, and the mastermind behind the growing success of the \pGoaties{}. Your fellow teachers think you are just a bit of a loner who teaches Economics at the \pSchool{}, but you are so much more — you are the epicenter of the Black Market on \pEarth{}, and the power behind the throne of the \pGoaties{}.

Where \cChupLeader{\full}, the current leader of the group, is bombastic, you speak truthfully and realistically. Where \cChupLeader{} agitates for immediate action, you are patient and plan for the long game. Where \cChupLeader{} has \cChupLeader{\their} head in the clouds, you have your feet on the ground. \cChupLeader{} uses charisma magic to hoodwink people into joining the cause, you truly change hearts and minds.

You were very sick for a very long time when you were small. Through that haze, you actually don't remember much of your young life. You were always frail, and with little magic to call upon. While you may be frail, you were a quick study and an excellent planner. But even with this, your lack of magic made the kind of employment that could better your circumstances hard to find, and you bounced from ship to port, barely scraping by. Your first truly vivid memory is nine years ago when \cChupLeader{} pulled you out of the bilges of the poorest boat in the 9th Fleet, and spoke words to you that made you feel alive for the first time. Those words were the promise of a better life, for you and all of \pEarth{} — a world of true equity and inclusion. \cGenesis{} was a minor \cGenesis{\Deity} of luck at the time, but through \cChupLeader{}, you learned of \cGenesis{}' big plans to upset the whole Pantheon. It all came down to Magic.

Magic is a gift given to the people of \pEarth{} by the patron deities of the three countries — and it was a gift that you didn't get your fair share of. You are technically a magic user, but only barely. Things that others do without thinking are an incredible effort for you. You struggle to shape wood without tools. You struggle to light a fire when others can do it with barely a thought. And even still, you have it far better than those born without magic at all. Magic was no gift to humanity — it was a curse. \cGenesis{} has promised to undo that curse, while simultaneously bringing forth a new era where everyone will be judged on their merit and their actions, instead of on how much privilege they were born with.

You've been working for almost a decade to build the necessary groundwork for that change. You forged the necessary papers to become a teacher at the \pSchool{}, arriving just over five years ago, around the same time as \cPrince{\full} and \cChupInventor{\full}. You and \cChupInventor{} are both members of the \pGoaties{} and thus have had to keep some public distance, but it has been such a boon to have someone else you can be fully honest with when you two are alone. You worry how much \cChupInventor{\they} care\cChupInventor{\verbs} for magic, but you deeply respect \cChupInventor{\them} as a brilliant engineer and partner in this work. 

\cChupLeader{} thinks that now is the time to make the bid for power, and thus reveal the \pGoaties{} and their true intentions to the world. You, on the other hand, fear that the group may not be ready. Your group's ostensible goal this weekend is to destroy the \pSc{} as a blow against the Patron Gods and political structures of \pEarth{}, permanently ending the Storms in the process. In reality, the plan goes two steps further — sending the Storm to the \pSc{} will also drastically weaken all magic on \pEarth{} by destroying the Ley Line Nexus at the center of the island, and serve as an assassination of many of the assembled dignitaries. Those last two items are strictly on a need-to-know basis, and only you and \cChupLeader{} know the full plan; specifically, \cChupInventor{} does \textbf{not} know that magic will be weakened, and \cChupStudent{} does \textbf{not} know that the Storm striking the school will kill many of those assembled here. If you want to retain their loyalty, you had best keep it that way. While you know both are loyal, \cChupInventor{}’s life centers around using magitech and \cChupStudent{} is overly fond of many of the other students here. In order to direct the Storm at the \pSc{}, you and your fellow cultists are working to make sure that a Relic attuned to the school is used in the Ritual to Control the Storm; the group's own Relic, the ``\iHorseshoe{}'', would be one option, as would re-attuning one or more of the other Relics. 

But you'll also need to make sure that enough students vote to direct the Storm at the \pSc{}, and right now your only student operative is \cChupStudent{\full}. Hopefully recruitment this weekend will change that. Still, you'll only get one chance at this in a lifetime and getting it to work is already uncertain. And you are not a gambling \cChupSecond{\person}. It \textbf{would} be a masterstroke if it worked — but the problem you are preoccupied with is the aftermath. With so many of the highest ranking members held in the \pGoaties{} partly or wholly by \cChupLeader{}'s charisma magic, weakening magic right now could well end the cult too, and destroy everything you've built. You've devoted your life to this cause, and you won't let one overeager step bring it all to ruin. Someone has to be the adult in the room for this momentous decision. That's why you have planned for the long term and are prepared to take control if things go wrong.

Even \cChupLeader{} has acknowledged that the plan could fail, and has sanctioned your contingency plan if it does. If the group’s efforts to direct the Storm at the school this weekend are thwarted, you intend to disavow everything, let \cChupLeader{} take all the blame, and go into deep cover as the group's new leader. Pursuant to that goal, you put in your bid to become the new principal of the school when \cPrincipal{} retires, as holding that lofty position would make any future attempts much easier. It is a crowded field with your fellow teachers \cMusic{\full} and \cBeetle{\full} running against you, but you have the advantage of support from the other \pGoaties{}; you just need to consolidate that support and make sure they put in a good word for you with \cPrincipal{}. The principal has tasked each of the candidates with overseeing a different ritual this weekend in order to prove themselves, and you have been given the most important one — the Ritual to Control the Storm. While it is the responsibility of the students to craft the ritual and the Librarian to oversee the preparations for it, you are in charge of the execution of the ritual itself. This places you in a uniquely strong position to influence which Relics get used in the ritual, making it far easier to ensure that one of them is attuned to the school. 

Of course, if you do become principal, you both become immortal (a good thing in your opinion since you could wait several lifetimes before trying again) but also cannot leave the school, as doing so for more than a few days would bring the buildings crumbling down. You have looked into whether this would also destroy the Ley Lines, weaken magic, and end the Storm, but as far as you have been able to determine it would just destroy the buildings, unfortunately. \cChupLeader{} thinks that you need to find some loophole in this, but you feel that you could run the cult just fine from the \pSchool{}. You have been running a world spanning Black Market from here, after all.  

The Ritual to Control the Storm is not the only ritual you are charged with overseeing this weekend. For months now, you have been dreaming of wandering through the depths of the Library chasing after a white rabbit. The dreams always end in a marble cavern with glowing symbols of \cGenesis{} upon the walls, and the rabbit turning to you and uttering the words, ``At the Time of Deciding, Luck shall be made manifest. Summon me in this place of power, and Fortune will ever smile upon you.’’ You are certain that \cGenesis{} has chosen you to summon \cGenesis{\their} Avatar into the mortal world, elevating \cGenesis{\their} power to rival the Patron Gods! As a Bishop of \cGenesis{}, you already know the ritual to summon an Avatar, but the cult has always lacked a suitable place of power to perform it. You have scoured all three tiers of the Library for the marble cavern, but have not been able to find it, which means that the rumors of a secret fourth tier hidden beneath the third must be true. Now that the Time of Deciding is upon you, you \textbf{must} find that cavern before the weekend is over. Thus far you have only told \cChupLeader{} about your dreams, but you will likely need more help to find the cavern, and you will \textbf{definitely} need more help for the ritual itself. 

There is yet more you have been doing to prepare for this weekend. You have been working with \cChupInventor{} to sabotage the magical Bunkers that protect people at the \pSchool{} during the run up to the Storm, and finally finished your work this morning. This sabotage serves a twofold purpose: scrambling to repair the Bunkers will distract your enemies from the cult’s efforts to send the Storm to the school, and the sabotaged Bunkers will be unable to protect as many people when the Storm strikes. Even if the Bunkers are fixed, they will still not be able to protect everyone here from the full wrath of the Storm. You fully intend for the corrupt and decadent advisors from the three nations to be among those who don't survive, sending a powerful message to your enemies. Meanwhile, the luck of \cGenesis{} will protect you and your fellows from the Storm with or without the Bunkers. You just need to make sure \cChupStudent{} doesn't find out that the Bunkers won't be able to protect everyone until it is too late, or that \cChupStudent{\their} fellow cultists were behind the sabotage; \cChupStudent{\theyare} a loyal Follower, but too young and naive to understand that such sacrifices must be made for the greater good. 

Still, you respect \cChupStudent{}’s dedication to the cause, and \cChupStudent{\theyhave} shown a great deal of interest in your more radical economic theories. Born to one of the most powerful noble families in the \pFarm{}, \cChupStudent{\theyare} a true class traitor. You have tasked \cChupStudent{\them} with hunting through the Library and destroying any books which talk about what might happen to the Ley Line Nexus if the school were to be struck by the full wrath of the Storm, to keep your enemies and any new recruits with doubts from finding out it will be destroyed. Assisting \cChupStudent{\them} in this search has provided you with the perfect alibi for your own search for the cavern from your dreams. \cChupStudent{} let you know about 2 months ago that \cChupStudent{\theywere} able to find and destroy the only book on the subject, so that's one less thing to worry about.

But even with \cChupStudent{} on your side, the plan to direct the Storm at the \pSc{} will almost certainly fail unless more student votes are cast for that option. You can help with this by giving your Voting Stone to a student loyal to the cause, which at this point is just \cChupStudent{}, and by trying to induct more students into the \pGoaties{}. You find \cPirateChild{\full} to be particularly promising — \cPirateChild{\their} ability to view economic policy through a class lens quite akin to your perspective on magical ability fills you with pride. The kid’s clearly got a lot of passion, and resentment for the corrupt status quo, and you can't help but like \cPirateChild{\them}. 

And then there is \cPresident{}, one of your brightest students. \cPresident{\They} would be risky to recruit as \cPresident{\they} hail\cPresident{\verbs} from one of the wealthiest and most powerful families in the \pShip{}, but for that same reason winning \cPresident{\them} over would be a great boon to the cause. \cPresident{} has a sharp mind, an impressive aptitude for economics, and has even been doing extra research with you above and beyond \cPresident{\their} regular coursework concerning the pros and cons of financial reparations. (Financial reparations are a very unpopular option among the \pShippies{} — The Twin Goddesses insist that proper balance can only be restored by returning harm of a similar kind and magnitude. A.k.a. You can’t just buy forgiveness.) You try to sneak in subversive messages whenever you can.

While not exactly a matter of recruitment, you do also need to find your missing/forgotten Avenger and bring them back into the fold. Neither you nor your fellow cultists seem to remember them, so you will have your work cut out for you. This is a very bad sign, as it means that your Avenger may have gone rogue and killed someone they were not supposed to. You need to figure out who they are, and how to regain control of them if necessary. You could also swear that you had an informant who was feeding you intelligence on the \pTech{} research into ending the Storms and sabotaging anything that could interfere with the cult's plans, but you can't remember who that is either! Perhaps they are the same person and that's why you can't remember them. Your top three suspects are \cInterpol{\full} (who is clearly up to something shady and certainly has the combat skills to be an Avenger), \cChupAvenger{\full} (who has an awful lot of mysterious absences for a teacher, some of which coincide with assassinations the \pGoaties{} have conducted), and \cWildCard{\full} (who is also clearly up to something shady and has traveled in secret all over \pEarth{} for mysterious reasons, including at times which coincide with assassinations the \pGoaties{} have conducted).

An Avenger is a powerful tool in the right hands, but like any tool they can also be misused and cause more harm than good. That point was further driven home just yesterday when you learned through your informants that \cChupLeader{} sent an Avenger to assassinate \cHeadDiplomat{}, the head diplomat of the \pShippie{} delegation. The assassination attempt failed, but \cHeadDiplomat{} was forced to kill in self defense, and has therefore reportedly lost all \cHeadDiplomat{\their} memories, which is why \cHeadDiplomat{\theyare} not present this weekend. As a result of \cChupLeader{}’s rash decision, there was a massive crackdown by the \pShippie{} Spymaster, and many of your agents, whom you had carefully positioned within the \pShippie{} spy network itself over a span of years, were rounded up. You were \emph{so close} to uncovering the identity of the Spymaster themself! Years of work dumped overboard because of yet one more example of \cChupLeader{}’s recklessness. You haven’t confronted \cChupLeader{\them} about this yet, but nor do you intend to let it go. As for the \pShippie{} Spymaster, you were at least able to narrow down their identity to one of the Advisors — \cJuniorStatesman{\full}, \cBunker{\full}, or \cEbbPriest{\full}. You will need to be especially careful around these three, and do what you can to make sure they are neutralized as a threat.

You certainly manage a lot of things for the \pGoaties{} (\emph{someone} has to), and have a lot to keep an eye on this weekend. One of your most important ongoing responsibilities is managing and maintaining the Black Market. On \pEarth{}, the flow of goods, technology, and information is very tightly controlled. This leads to great demand among those who can't get things — particularly new technology from the \pTech{} since the war started. This, in turn, led to an opportunity for a thriving Black Market — and you put in the work to make it happen. Almost every serious technological gadget, weapon, resource, or snippet of information that is sold through the market passes through your hands. You take in supplies from all over, and send them out again. It's a lot of work, but it both maintains anonymity for as many people as possible while keeping transfer chains short, and ensures that no one can take that base of power away from you. Without you, the market would collapse within weeks, though not immediately — you do work closely with \cChupInventor{}, who helps supply many of the goods coming out of the \pTech{}, especially weapons. 

A lot of your Black Market information comes from a rather unexpected source, \cEthics{\full}, the Ethics and Morality teacher. \cLibAssist{\full} serves as an intermediary to maintain your anonymity. \cEthics{} is operating under the delusion that the things \cEthics{\they} provide\cEthics{\verbs} you with go directly and exclusively to support the \pShip{} war effort. In truth the war is moderately useful and you'd generally prefer it continue, since it so neatly distracts all of the governments from your activities, but you won't turn down a better deal to sell something elsewhere occasionally. Recently, however, the amount of information you are getting from \cEthics{} has slowed down. You are concerned that \cEthics{\they} may be sending it to another party, and would like to put an end to this.

From the many things you've passed along recently, you took a particular interest in a \emph{liberated} load of goods from the \pFarm{}. The contact who passed off the fancy little box works with pirates, and they often have the most surprising little things for you. This box was no exception. It had a charm on it to keep it from being opened — a very powerful, good quality one. Intrigued, you reached out to one of your contacts, a pen pal of sorts who is one of the best curse workers in the \pFarm{}, though quite eccentric. \cCurse{\full} was delighted to work on so challenging a puzzle. But when \cCurse{\they} got the box open, and you saw the glint of something shiny and even better quality than the box. You snatched it away before \cCurse{} could get a good enough look to identify it. Then you sold the fancy ring and its box to one of your most reliable customers, \cHedonist{\full}.

Another useful thing you've gotten off of the Black Market recently was a juicy piece of information — someone else seems to have designs on Avatars. There were unsubstantiated but credible rumors that one of the \pShip{} Avatars has been killed. This is valuable, pricey information that could sway the tide of the war in the right hands. Not only could that information fetch an incredible price on the Black Market, but it will give \cGenesis{} all the more of an edge. To complicate matters, however, you overheard \cFlowPriest{\full}, the \cFlowPriest{\cleric} of \cFlow{}, talking to \cInitiate{\full} about trying to resurrect the \cEbb{} avatar. That proved that the rumors are true, but also presented a problem — the \pShip{} clerics must be prevented from resurrecting the \cEbb{} avatar. You have also heard through the Black Market that no Giant Hummingbirds, the Avatars of \cFarmGod{}, have been seen in six years. Could they be gone too? If so, it would give \cGenesis{} an even greater advantage to have \cGenesis{\their} Avatar on \pEarth{} while other Deities lack an Avatar on the mortal plane.

This weekend is a crucial turning point for you and the \pGoaties{}. You have a Black Market to run, a ritual to subvert, and an Avatar to summon. Delegation will be your friend, so long as you can trust the people you are delegating to — and trustworthy people are hard to come by. This weekend will make or break the \pGoaties{}. It is your job to see the group through to the other side.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Send the Storm to the \pSc{}, in order to weaken all magic in \pEarth{}, empower \cGenesis{}, end the Storms forever, and assassinate the corrupt advisors gathered here. This will require incorporating at least one Relic attuned to the school into the Ritual to Control the Storm. You can also help by giving your Voting Stone to a student who is loyal to the cause, and by recruiting as many new members to the \pGoaties{} as possible, especially among the students. 
    \item Find the ``Cavern of Fortune’s Shadow’’ in the depths of the Library, and once there, lead the ritual to summon the Avatar of \cGenesis{}. 
    \item Prepare to take over the \pGoaties{} if the cult’s plans fail this weekend, and decide what to do about \cChupLeader{}, regardless. To that end, convince \cPrincipal{} to appoint you to be the new Principal. Lead the execution of the Ritual to Control the Storm in order to impress \cPrincipal{\them}, and garner as much support for your candidacy as possible.
    \item Uncover the identity of the \pShippie{} Spymaster and frustrate their designs, or better yet, work your way into their confidence as a double agent. You have narrowed down their identity to \cJuniorStatesman{}, \cBunker{}, or \cEbbPriest{}.
    \item Work with \cChupInventor{} to maintain the Black Market. The ``Time of Deciding’ ’is always busy with all the advisors here.
    \item Figure out who the Avenger and informant on the Storm research is/are and bring them back into the fold. Your top three suspects are \cInterpol{}, \cChupAvenger{}, and \cWildCard{}.
    \item Stop the \pShip{} clerics from resurrecting the \cEbb{} Avatar. If the opportunity presents itself to kill any other Avatars of the Patron Gods, you certainly won't turn it down either. 
\end{itemz}

\begin{itemz}[Notes]
    \item Regarding the effects of the Storm striking the school, \cChupInventor{} does \textbf{not} know that magic will be weakened, and \cChupStudent{} does \textbf{not} know that many of those assembled here will be killed or that \cChupStudent{\their} fellow cultists sabotaged the Bunkers. If you want to retain their loyalty, you had best keep it that way.
    \item You teach economics at the \pSchool{}. You started teaching here five years ago, and so were not present for the Betrayal of the \pShip{} and mysterious deaths of the 12 students six years ago.
\end{itemz}

\begin{contacts}
    \contact{\cChupLeader{}} The current leader of the \pGoaties{}. \cChupLeader{\Theyare} reckless and overzealous, and you see it as your job to curtail the worst of \cChupLeader{\their} excesses. A part of you wonders if the group would be better off under your leadership.
    \contact{\cChupInventor{}} Your second on the Black Market, \cChupInventor{} has been with the \pGoaties{} almost as long as you. You don't think \cChupInventor{\they}'d react well if  \cChupInventor{\they} knew that destroying the \pSc{} will weaken all magic in \pEarth{}.
    \contact{\cChupStudent{}} The youngest member of the \pGoaties{} present. Loyal to the cause, but you aren't sure how \cChupStudent{\they}'d react if \cChupStudent{\they} knew that destroying the \pSc{} will kill many of those present, and that \cChupStudent{\their} fellow cultists sabotaged the Bunkers.
    \contact{\cEthics{}} A useful source for goods and information to sell on the Black Market. Seems particularly keen to pass secrets and tech on to the \pShip{}.
    \contact{\cLibAssist{}} Your messenger in the Black Market, acting as a useful intermediary between you and prospective customers. Blissfully unaware that the market is controlled by the \pGoaties{}.
    \contact{\cCurse{}} Your best curse-breaking and making contact. Eccentric, but a decent enough sort.
    \contact{\cHedonist{}} A \cHedonist{\cleric} of \cFarmGod{} with a surprising taste for luxury contraband. As such, one of your best customers on the Black Market.
    \contact{\cPirateChild{\full}} A bright and outspoken \pShippie{} student who views economic policy through a lens of class conflict and systemic oppression, much like your views of magic. A promising candidate for recruitment to the \pGoaties{}.
     \contact{\cPresident{}} Your most dedicated economics student, from an influential \pShippie{} family. Recruiting \cPresident{\them} to the \pGoaties{} would be a great victory, though not without risk.
\end{contacts}
\end{document}
