\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cChupAvenger{}}

You are \cChupAvenger{\intro}, a 43 year old Art teacher from the \pShip{}, and, to your great regret, Avenger of \cGenesis{}. When the war began, you were overwhelmed by anger at the betrayal by your country's long-time allies, and made the rash decision to join the \pGoaties{}. Since then, you have calmed down, had a change of heart — and finally now, after bringing your existence to the brink of erasure, realized how desperately you need a way out.

You grew up on a loving ship amid a loving family in 4th Fleet, appreciating the beauty of the world around you. Your teenage years were primarily defined by travel as you toured many ships and ports, and eventually, the other countries, cultivating a love for the natural beauty of the world and honing your skills as a virtuoso in all kinds of art — the act of creating life from a mural, the art of carving away wood to reveal the beauty within, and the skill of shaping clay to your will. While the \pShippies{} do not embrace visual arts that do not also serve a functional purpose, you excelled at marrying form and function in your work, bringing beauty to otherwise mundane objects. You were also, admittedly, a thrill seeker, becoming extremely adept at hunting and slaying the sea serpents that threatened people’s lives and livelihoods — combat skills that would serve you well later, much to your regret. You collected trophies from your hunts and often incorporated them into your artwork, marveling at the beautiful patterns and colors of the beasts you had slain.

Just as you were settling down to a calmer life in your beloved \pShip{}, you were approached with a job offer to the prestigious \pSchool{} as the Art teacher. You started teaching at the \pSc{} 8 years ago, and have met many friends among your coworkers, including the Librarian, \cLibrarian{\full}. The Librarian was what you hoped to be as a teacher: kind, always there to help, curious, and also a great lover of art. You two bonded over the beauty of nature, especially plants, and you would always bring gifts back from your journeys. \cLibrarian{} really is one of the best people you know. You also stuck up a friendship with \cPrincipal{\full}, bonding over your shared love of the \pShippies{}, a place \cPrincipal{\theyhave} not seen in years due to the limitations placed on \cPrincipal{\them} by being Principal.

When the \pShip{} were betrayed, you were outraged. You, having seen the beauty that harmony had wrought in the world, could not fathom the sheer audacious evil of the other countries. You were back home on the 4th Fleet Pink Coral Ship when the Storm struck; the ship was nearly destroyed and a third of the crew perished. If you hadn't been in port at the time, none of you would have survived. As you made repairs and counted the dead and missing (taking a short sabbatical from your teaching to support your fellow \pShippies{}), a delirious, half dead young \cKidScientist{\person} staggered up to the gangplank, rambling about murder and betrayal. You were shocked to recognize \cKidScientist{\them} as \cKidScientist{\full}, one of your students who had been at the \pSchool{} for the ``Time of Deciding.’’ Intrigued and moved to pity by your own losses, your crew agreed to take \cKidScientist{\them} in and nurse \cKidScientist{\them} back to health. When \cKidScientist{\theywere} well enough, \cKidScientist{} explained that someone had tampered with the student vote to send the Storm to the \pShip{}, and then poisoned the wine used for the student toast; all the other students had perished except \cKidScientist{}, who had fled for \cKidScientist{\their} life. You vouched for \cKidScientist{\them} and your crew recognized that \cKidScientist{\theywere} as much a victim as they. 

\cKidScientist{} spent some time living with you on Pink Coral Ship, but \cKidScientist{\theywere} ill-suited to a life at sea, having grown up in the \pTech{} and the \pFarm{}. \cKidScientist{\They} became increasingly determined to work \cKidScientist{\their} way back into the \pFarm{} or the \pTech{} and find out who was responsible for the Betrayal. You and your crew wanted those answers too, and supported \cKidScientist{\them} the whole way. You helped \cKidScientist{\them} change \cKidScientist{\their} identity, obtain forged documents from the burgeoning Black Market, and remake \cKidScientist{\them} into \cAssistantScientist{\full} — the identity \cKidScientist{\they} still go\cKidScientist{\verbes} by to this day. You’ve kept in touch as much as you can (which isn’t much), and \cKidScientist{\theyare} still working undercover to unmask the perpetrators of the Betrayal. You vowed to keep \cKidScientist{}’s secret.

As for you, you were quickly recruited by your fellow teacher, \cChupSecond{\full}, to join with like-minded people who all wanted to do something about the Betrayal and the corrupt power structures that had led to it — the \pGoaties{}. You took a lengthy sabbatical to become one of their members. Because of your natural charm and experience with other nations, one of your first missions was to befriend \cHeadScientist{\full}, the head scientist on the project to end the Storms, in order to gain access to that research and sabotage any findings that threatened the cult’s plans. What exactly those plans were was on a “need-to-know” basis and you did not need to know. To this day, all you know is you were told to sabotage, steal, or destroy any data that mentioned the \pSchool{}, so that is what you did. You are no scientist so you never really understood what you were sabotaging, but you succeeded at your mission, at first. What you did not expect was that you would actually come to care for \cHeadScientist{} — \cHeadScientist{\their} brilliance, \cHeadScientist{\their} passion, \cHeadScientist{\their} earnest desire to make the world a better place. You fell head-over-heels in love. After one year, you couldn't bear to keep sabotaging \cHeadScientist{\their} work and stopped, though you never found the courage to confess what you had done. Since then, your relationship has been one of genuine caring and affection, built on love, trust, and mutual interests, though you still carry the guilt of your prior actions. You also never found a good time to confess to being part of a group that many would consider a heretical cult.

Because of your remarkable combat skills, you were also consecrated by the \pGoaties{} as an Avenger, a holy assassin who is forgotten by others instead of losing their own memories — a special ``boon'' of \cGenesis{} that would soon reveal itself to be the scourge of your existence. You slew many corrupt officials and enemy spies in \cGenesis{}’ name, rarely feeling an ounce of regret. But little by little, your world disintegrated around you. All of your family and most of your friends, including one of your oldest friends, \cPrincipal{}, have forgotten you by now. \cPrincipal{} still remembers you \emph{exist}, which is good because \cPrincipal{\theyare} your boss, but the years of friendship you shared are all gone. 

Fortunately, your two favorite students, \cPirateChild{\full} and \cInitiate{\full}, still remember you; their personalities are like night and day, but they both have a passion for the arts and self expression through crafting. \cPirateChild{} throws \cPirateChild{\themself} into art with such passion, like someone who may never get the chance again. Occasionally, \cPirateChild{} mentions how frustrated \cPirateChild{\theyare} that art is seen as a luxury, not a practicality on \cPirateChild{\their} ship. You understand that anger, though you no longer wish to foster that emotion in yourself. \cInitiate{}, on the other hand, is deeply talented, but a bit unsure of \cInitiate{\themself}. You do what you can to help this confidence, as you feel that \cInitiate{\theyhave} a bright future in bringing art into whatever path \cInitiate{\they} follow, including into the priesthood.

Of all the people who've forgotten about you as a result of your activities, though, \cHeadScientist{}, the love of your life, is the hardest. As of a few months ago, \cHeadScientist{\theydo}n't remember \emph{anything} about you. Not even your first date, on which you brought \cHeadScientist{\them} a dozen red roses (or the many subsequent bouquets of black crocuses after learning those were \cHeadScientist{\their} favorite). Fortunately, you have the help of \cInitiate{}, who knows that \cHeadScientist{} has forgotten you. You didn't mean for \cInitiate{} to find out, but perhaps it was meant to be. \cEbb{} and \cFlow{} encourage their followers to give their prayers to the sea breeze, which will carry the prayer to the ears of the Goddesses. Even though the Goddesses have no reason to answer your prayer since you forsook them, you sent one anyway. But sometimes other mortals overhear prayers sent on the wind. This time, \cInitiate{} overheard you, and is now determined to help. You can't help but wonder if \cInitiate{\theyare} the Goddess' answer to your prayers, unworthy though you might be. Still, the two of you haven't addressed the whale in the room yet of how \cHeadScientist{} forgot you in the first place. You'll have to figure out an explanation that avoids implicating \cHeadScientist{} or you in anything you can't talk your way out of. Regardless, you are grateful for \cInitiate{}'s help, and intend to repay \cInitiate{\their} kindness however you can, perhaps by giving \cInitiate{\them} your Voting Stone.

It was this particular instance of amnesia that finally woke you up to the true price you were paying. The \pGoaties{} may have a noble cause, and you have met many good people in the organization, but ultimately, it isn't a cause worth throwing away your life and legacy — let alone murdering people — for. Unfortunately, your first naive attempt to leave the group peacefully a few weeks ago ended violently after you were forced to kill the officer you spoke to about it in self defense. While you are quite certain that you managed to clean that mess up by framing the \pGoaties{}’ enemies, you think the death must have been noticed by \cGenesis{} \cGenesis{\themself}. In the wake of that killing, you discovered that every \pGoatie{} you knew had forgotten you, even the cult’s leaders, \cChupSecond{\full} and \cChupLeader{\full}, who as far as you were told, are not supposed to be able to forget Avengers. This development is a double edged sword — on the one hand, being forgotten \emph{should} make it much easier for you to extricate yourself from the cult, but on the other hand, suddenly forgetting who their Avenger is will surely alert \cChupSecond{} and \cChupLeader{} to the fact that something has gone wrong, and prompt them to search for you. You’ll just have to hope you can keep a low profile and avoid drawing their attention.

Desperate for help and close to despairing, you decided to take the risk yesterday and approached one of your closest friends who might be able to help, \cLibrarian{\full}. Compassionate, wise, and learned in ancient lore, you hoped that if anyone could help you extricate yourself from the \pGoaties{}, atone for your past actions, and find some way to rebuild your relationship with \cHeadScientist{}, it was \cLibrarian{\them}. \cLibrarian{} listened with patience and empathy as you unburdened yourself of the secret you have been carrying, and then, without hesitation, pledged \cLibrarian{\their} support.

Even with help, though, your task will not be easy — you must reconcile with \cEbb{} and \cFlow{}, and convince the Clerics to induct you back into the religion. That will be awkward, since publicly you never left the faith. The Clerics won't be able to tell if you've completed your reconciliation, but the Avatar summoned as part of the conversion will. Of the two Clerics of \cEbb{} and \cFlow{} available to you, \cFlowPriest{\full}, your fellow teacher, is more forgiving than \cEbbPriest{\full}, one of the advisors (at least by reputation; you've never met \cEbbPriest{} in person). You might be able to admit your situation to \cFlowPriest{} and get \cFlowPriest{\their} help, but it could easily backfire if \cFlowPriest{\they} tell\cFlowPriest{\verbs} \cEbbPriest{}. And while you are working your way back into the graces of the Twin Goddesses, you still desperately hope that you might be able to reawaken some of \cHeadScientist{}’s memories of you and your relationship. You are prepared to start from scratch if you need to, but it breaks your heart to do so.

But you need to. Shortly after the advisors arrived, you ran (literally) into \cHeadScientist{} in the garden. Your heart raced as you tried to hold it together and gave \cHeadScientist{} a warm smile, brushed off \cHeadScientist{\their} apologies, and introduced yourself with as much charm as you could muster. The smile \cHeadScientist{} gave you back made you almost cry, but also gave you hope. \cHeadScientist{} may have forgotten you, but you know that you will never stop loving \cHeadScientist{\them}.

After the Betrayal of six years ago, you feel determined to make sure this ``Time of Deciding’’ goes off without any outside interference. There is little doubt in your mind that agents from the \pTech{} and the \pFarm{} rigged the vote six years ago to send the Storm to the \pShip{} and then killed all of those poor students, and that those same agents will likely try to do so again. As such, you intend to keep a close eye on the proceedings, including making sure no one tampers with the Voting Stones or the Relics needed for the Ritual to Control the Storm, by volunteering to help with the preparations for said ritual. If you can catch any would-be saboteurs in the act and get justice for the Betrayal of the \pShip{}, so much the better. You are loath to kill anyone else and be forgotten by even more people, but if you can publicly expose their treachery or turn them over to the \pShip{} authorities \emph{(e.g. The advisors, or detaining the person for post game)}, that would suffice.

Overall, your current situation is extremely complex, and the only way you really see out is forward. Getting out of the \pGoaties{}, renouncing \cGenesis{}, and getting back into \cEbb{} and \cFlow{}'s good graces will not be trivial, but it's your most important goal this weekend. If you can manage them, preventing any tampering with the Ritual to Control the Storm and getting back into a relationship with \cHeadScientist{} would both take a load off of your mind as well.

\begin{itemz}[Major Goals]
    \item Get out of the \pGoaties{} and atone for your crimes in \cGenesis{}' name, \emph{without} betraying the rest of the group to the authorities, for their cause is righteous; you just cannot personally be a part of it anymore. You will need to be especially careful around \cChupLeader{}, \cChupSecond{}, \cChupInventor{}, and \cChupStudent{}. \cLibrarian{} has agreed to help.
    \item Rekindle your forgotten romance with \cHeadScientist{} and keep \cHeadScientist{\them} out of the \pGoaties{}'s way. \cInitiate{} has agreed to help with the first part.
    \item Make sure the Storm does not get sent to the \pShip{}. To that end, help \cInitiate{} and \cPirateChild{} collect the most votes to direct the Storm by giving one of them your Voting Stone and convincing your fellow teachers and advisors to do likewise.
\end{itemz}

\begin{itemz}[Minor Goals]
    \item Make sure no one tampers with the Voting Stones or the Relics needed for the Ritual to Control the Storm, and help the ritual go off successfully and without interference.
    \item Reconnect with \cAssistantScientist{} and make sure that \cAssistantScientist{\their} cover does not get blown. 
\end{itemz}

\begin{itemz}[Notes]
    \item You teach Art at the \pSchool{}.
    \item Different teachers stay for different Times of Deciding. Six years ago, you were still a fairly new teacher, and had no particular desire to stay anyway, so you were not present at the \pSc{} that weekend.
    \item You know that the \pGoaties{} are planning something big this weekend, but you don't know what — they all forgot about you before you could be briefed on the mission. Whatever it is, you want no part of it, but nor do you intend to interfere.
\end{itemz}

\begin{contacts}[The Followers of Genesis]
    \contact{\cChupSecond{}} The second in command of the \pGoaties{}, and the member who recruited you initially. Level headed and plays the long game skillfully, albeit reservedly.
    \contact{\cChupLeader{}} The head of the \pGoaties{}. Charismatic, bold, and a little reckless.
    \contact{\cChupInventor{}} Another \pGoatie{} here at the school. Awkwardly, also \cHeadScientist{}’s best friend.
    \contact{\cChupStudent{}} The one \pGoatie{} you know of among the students.
\end{contacts}

\begin{contacts}
    \contact{\cPrincipal{}} The principal of the \pSchool{}, and a close friend before \cPrincipal{\they} forgot about you due to your actions as an Avenger. 
    \contact{\cHeadScientist{}} Your former romantic partner, who no longer remembers you due to actions you took as an Avenger. Can you find a way to restore \cHeadScientist{\their} memories, or win \cHeadScientist{\their} heart anew?
    \contact{\cInitiate{}} A \pShippie{} student who wants to help you get back together with \cHeadScientist{}. \cInitiate{\Theyare} your best student, with a true appreciation of art and engineering.
    \contact{\cPirateChild{}} Another of your favorite students. Brash, outspoken, and a passionate artist. 
    \contact{\cLibrarian{}} A close friend who is trying to help you escape \cGenesis{} and reconnect with \cHeadScientist{}. 
    \contact{\cAssistantScientist{\full}} The false identity being used by your former student and survivor of the massacre of the students following the Betrayal, \cKidScientist{\full}. \cAssistantScientist{\Theyhave} been working undercover to unmask the perpetrators of the Betrayal, and you welcome this opportunity to discreetly reconnect and see what \cAssistantScientist{\theyhave} learned.
\end{contacts}

\end{document}
