\documentclass[char]{GL2020}
\usepackage[normalem]{ulem}
\parindent=0pt
\begin{document}
\name{\cPirate{}}

You are \cPirate{\full} (\cPirate{\they}/\cPirate{\them}). You have taught Shop and Crafting at the \pSchool{} for 18 years, and everyone knows you as genial and approachable. While you started life as a pirate aboard the 8th Fleet Silent Fog, nearly two decades on land have you questioning whether you actually want to go back. Either way, this weekend will be the culmination of many things you have long prepared for.

You grew up in 8th Fleet, bouncing from ship to ship. 8th and 9th Fleet struggle more than anywhere else in the \pShip{}, and youngsters are often sent on to the next ship when there isn't enough food to go around. It's not surprising, therefore, that many ships ultimately turn to piracy, preying on their fellow \pShippies{} as well as the \pFarm{} and the \pTech{}. The Silent Fog is the best pirate ship there is, and you were lucky to end up aboard her at the end of your drifting.

The Silent Fog was legendary for a reason — and it was in no small part due to her captain's ability to play the long game. Long enough to forge paperwork and send you to work at the \pSchool{} to see what secrets you could learn. And you learned so much — particularly about the Relics that are used to control the Storm. The Storms devastate wherever they hit, but pirate ships, with no safe harbor to anchor in, are often battered to pieces among the jagged shoals of \pWod{}. One Relic in particular, the ``\iNet{}'', was of interest. When attuned to the \pShip{}, and stowed aboard a ship, it can be used to directly control the tides and waves. With it, a ship could survive any Storm, no matter how bad, and would be nigh on uncatchable to boot. So you and the Captain hatched a plan to steal it. More on that later, though.

Maintaining your cover has been crucial, as \cPrincipal{\full}, the Principal of the school for the last 200 years, hates pirates with a burning passion and would quickly sink your plans if \cPrincipal{\they} caught wind of you being a pirate. As part of your cover, you made a point to get to know the other teachers, and the subset of Advisors who come to the school every three years. \cEthics{\full}, the Ethics teacher, took a surprising shine to you, and the two of you have been great friends almost since you first set foot on the Island. \cEthics{} is an incredibly intelligent \cEthics{\person}, and while you are very good at pretending, you are not entirely sure you have \cEthics{\them} fooled. But \cEthics{\they} \cEthics{\have}n't ratted you out yet, so maybe it doesn't matter. Still, you were quite surprised when \cEthics{\they} asked you a tremendous favor less than a year after you arrived. \cEthics{} had agreed to help an anonymous parent get an innocent baby to safety in the \pShip{}. You've always had a soft spot for children, so you agreed. You knew the Silent Fog could find a way to pass the \cPirateChild{\child} off several times over to some nice, calm ship in 3rd Fleet or something, making sure they would be untraceable.

On the advisor side, you've found a friend in \cBunker{\full}. \cBunker{} is an engineer who designed and installed the Bunkers that help protect the people at the school from the Storm as it builds in power. The two of you love to talk shop and trade tips and tricks on building things — even if \cBunker{\their} focus is on engineering and architecture, and yours is more on repair and crafting intermediate materials. Seeing as you are both \pShippies{}, you have the most delightful conversations about how the littlest details can make or break a project. Three years ago, \cBunker{} came as an advisor — a break in \cBunker{\their} normal pattern of attending the ``Time of Deciding’’ only every six years. You were sad to miss the opportunity to connect with \cBunker{\them} then, but no particular teacher stays every time. You look forward to helping \cBunker{} with the crucial and fascinating task of maintaining the Bunkers this weekend.

\cPrince{\full} started out as a friend — but three years ago, that relationship blossomed into romance. It's daunting to be romantically involved with a member of royalty, and from the \pFarm{} no less, but you've been together long enough that that nervousness has mostly worn away. \cPrince{} is not just attractive, but brilliant, pragmatic, kind, and, for a royal, very down to earth. Others may find \cPrince{} too focused on power, but you believe that \cPrince{\they} just want\cPrince{\verbs} what is best for the world and the \pFarm{} and \cPrince{\have} to put up walls to protect \cPrince{\themself}. You do hope that \cPrince{\their} love for you will cause \cPrince{\them} to be softer to the \pShip{}, at least if \cPrince{\their} dreams of ruling become reality.  

Unfortunately, \cPrince{\their} moderate dislike of pirates that most of \cPrince{\their} country shares has blossomed into a full blown hatred ever since \cPrince{\their} royal train was attacked and \cPrince{\they} \cPrince{\were} robbed about a month ago. So it might get a little\ldots{} awkward\ldots{} if you ever get around to revealing your origins. Maybe you can talk \cPrince{\them} around? Maybe you can find the right moment to tell \cPrince{\them} the truth? Or maybe it's enough to swear off pirating in the future? After all, it HAS been almost two decades since you were aboard the Silent Fog\ldots{} Or maybe you shouldn't bring it up at all and hope that \cPirate{\they} never find\cPirate{\verbs} out?

As for what you'd do if you weren't being a pirate, well\ldots{} In your time at the \pSc{}, you've come to admire \cFlowPriest{\full}, and \cFlowPriest{\their} devotion to \cFlow{}. You see the peace and belonging it gives \cFlowPriest{\them} and you feel called to that same place, and away from piracy. Normally, only those who bear the mark of the Goddess are allowed to even try to join the priesthood. The Goddess' mark almost never appears past puberty, and you do not bear the mark. If only you could talk to \cEbb{} and \cFlow{} face to face. Surely they would understand and grant you the mark. But after speaking earnestly with \cFlowPriest{} about your desire to become a cleric, \cFlowPriest{\they} agreed to take you on as an initiate anyway and \cFlowPriest{\have} been teaching you in secret. \cFlowPriest{\They} still seem\cFlowPriest{\verbs} uncertain about whether to ultimately ordain you as a full \cPirate{\cleric}, so you will have some convincing to do. The really hard part, though, will be convincing the \cEbbPriest{\cleric} of \cEbb{} who is here this weekend. \cEbbPriest{\full} has quite the reputation for being strict. Becoming a \cPirate{\cleric} would also be a convenient solution to \cPrince{}'s hate of pirates. Your relationship could continue, either long distance (probably), or if by some miracle you convince \cPrince{} to renounce \cPrince{\their} claim on the throne, \cPrince{\they} could either stay on as a teacher at the \pSc{}, or you could both retire to the \pShip{}. If you are allowed to become a \cPirate{\cleric}, you'd still need to decide which path to follow — \cEbb{}, \cFlow{}, or the difficult path of Balance. You know your friend \cBunker{}, though not very religious, follows \cEbb{}, and you are pretty good friends with \cFlowPriest{}, who follows \cFlow{}. Meanwhile, you wonder just how hard Balance really is\ldots{}

Becoming a \cPirate{\cleric} and renouncing piracy without fulfilling your initial mission would leave the Silent Fog high and dry, though — and though you may not necessarily return to the ship, you still owe a certain loyalty to your Captain. Correspondence with the Silent Fog is risky, so you try to limit how frequently you do it. The last message you received was 3 months ago: The captain wrote that all was in place for stealing the \iNet{}, and that your contact would be present at the ``Time of Deciding’’ — you assume the contact is one of the advisors. They are to find you by uttering the phrase, ``The Waters untouched are not abandoned,'' and you are to respond with, ``by those brave enough to chart the course.'' Once you find each other, the two of you must prevent the \iNet{} from being used in the Ritual to Control the Storm, as this will expend its magic, and smuggle it off the island.

Maintaining a cover this deep involves more than just making friends. You occasionally have to be seen making an effort above and beyond. In this case, you've settled on being picked to give the Teacher's speech at the Ceremony of Excellence. Every ``Time of Deciding,’’ teachers from a different country give the speech, and this year it is the \pShip{}’ turn. It's a nice, flashy, public thing you can do to maintain your charade. And when you sat down to try to write something up, you found yourself surprisingly impassioned. You drew on the inequalities you grew up with, and now you very much want to point the graduating students at the socioeconomic inequalities on \pEarth{}. The plight of the pirates will never change if those in power cannot understand that they are driven to it by desperation and a lack of opportunity. Maybe your speech (if you can convince \cMusic{\full} to pick you) will convince these young adults to do something to change the socioeconomic imbalances. Of course, you also have to be picked over \cFlowPriest{}, who also wants to give the speech. While you respect \cFlowPriest{} as a mentor, you know that \cFlowPriest{\they} would not be able to make as powerful — as vital — a speech.

But that's in the future — what of everyone suffering in the meantime? The \pShippies{} need a break from being battered by the Storm. As a teacher, part of your responsibilities this weekend are to help guide the students and to decide which student to give your Voting Stone to. You have been on the lookout for which student among the \pShippies{} has the strongest presence and will be able to convince students from other nations to vote to send the Storm somewhere other than the \pShip{}. You aren't sure you've found the perfect choice, but your choice at the moment is \cWarlordDaughter{\full}, \cWarlordDaughter{\offspring} of the \pShip{} Warlord, \cLoud{\full}. You should keep an eye out for another candidate if you can find one, though — while being related to the Warlord is a positive in the eyes of the \pShip{}, it certainly isn't looked on favorably by the \pShip{}'s enemies.

If \cWarlordDaughter{} isn't the answer, perhaps you can support one of your two best crafting students, \cPresident{\full} and \cPirateChild{\full}. \cPresident{} is the Student Body President and you admire \cPresident{\their} diligence and focus. \cPresident{\They} \cPresident{\have} dreams of being a diplomat and you know \cPresident{} cares deeply about the \pShip{}.  \cPresident{\They} \cPresident{\have} been coming to you for advice about everything from this weekend to romance and you trust \cPresident{\them} as much as you can trust a \pShippie{} from 2nd Fleet. \cPirateChild{}, in contrast, is full of piss and vinegar and frustration with the unjust status quo, which is just what is needed in a future leader. You try and encourage that anger and passion when you can.

This weekend will decide what your future looks like. Will you be going back to the Silent Fog? Will you succeed in becoming a \cPirate{\cleric} of \cEbb{} or \cFlow{}? Will you and \cPrince{} still be a couple when the dust settles? So many questions, and so little time — you'd better get down to answering them.

\begin{itemz}[Goals (in roughly descending order of importance)]
    \item Find your pirate contact from the Silent Fog and help them get the properly attuned \iNet{} off the island without getting caught. Don't let the \iNet{} be used in the Ritual to Control the Storm!
    \item Figure out what to do about your relationship with \cPrince{}. Is there any way to not have this relationship go down in flames?
    \item Decide if you still want to be a pirate, or if you want to try to become a \cPirate{\cleric}. If you do choose to try to become a \cPirate{\cleric}, you will have to find a way to get a real or fake mark of the Goddess to appear on your person.
     \item Decide which \pShippie{} student is the most likely to be able to build the coalition necessary to ensure the Storm is not sent to the \pShip{}, then give that student your Voting Stone. \cWarlordDaughter{} may fit the bill.
    \item Convince \cMusic{} to pick you for the Teacher's speech at the Ceremony of Excellence. Then give a speech that will inspire the new generation to address the socioeconomic inequalities in their countries.
    \item Help \cBunker{} maintain the magical Bunkers that protect people from the ravages of the Storm.
\end{itemz}

\begin{itemz}[Notes]
    \item You expect the undercover pirate here to help you liberate the \iNet{} to approach you with the phrase, ``The Waters untouched are not abandoned.'' The proper response to indicate you are the person they are looking for is, ``by those brave enough chart the course.'' You will have to be careful, though, as many people hate pirates. If the wrong person somehow knew the code phrases, or overheard you, it could blow everything.
    \item You usually try to go ``home'' to 3rd Fleet during the Time of Deciding, including six years ago, so you weren't present for the tragic incident in which 12 students died and the Storm was sent to the \pShip{} out of turn. You've only actually managed to make it back to the Silent Fog (your real home) once, and that was 12 years ago.
\end{itemz}

\begin{contacts}
    \contact{\cPrince{}} The love of your life. You know many people wouldn't understand your relationship, but where they see a ruthless, calculating royal scion, you see a sensitive visionary who is doing \cPrince{\their} best in the den of moray eels that is the royal court of the \pFarm{}. \cPrince{\They} \cPrince{\have} had to put up walls in order to survive, but with you \cPrince{\they} \cPrince{\are} always gentle and kind.
    \contact{\cEthics{}} Your first friend at the school. You hit it off almost immediately. \cEthics{\They} entrusted you to hide a baby among the \pShippies{}.
    \contact{\cBunker{}} A good friend and brilliant engineer. \cBunker{} shares your love of crafting and is in charge of maintaining the school's Bunkers.
    \contact{\cPrincipal{}} The principal of the \pSchool{}. \cPrincipal{\They} \cPrincipal{\are} vehemently anti-pirate and if \cPrincipal{\they} found you out, getting fired would probably be the least of your worries.
    \contact{\cFlowPriest{}} A \cFlowPriest{\cleric} of \cFlow{} that you respect, and who has been training you as an initiate of the faith in secret. You hope \cFlowPriest{\they} can be convinced to ordain you as a full \cPirate{\cleric}.
    \contact{\cEbbPriest{}} A \cEbbPriest{\cleric} of \cEbb{} with a reputation for being strict and traditional. \cEbbPriest{\They} would not be willing to ordain you as a full \cPirate{\cleric} without the mark of the Goddesses.
    \contact{\cWarlordDaughter{}} A student you've had your eye on for a while as a potential organizer of the student voting, for the good of the \pShip{} — if \cWarlordDaughter{\their} lineage doesn't poison the message.
    \contact{\cPresident{}} The Student Body President and one of your best crafting students, whose diligence and focus you admire.
    \contact{\cPirateChild{}} A rambunctious student whose frustration with the unjust status quo is palpable, and laudable. Also one of your best crafting students.
\end{contacts}

\end{document}




