\documentclass[char]{GL2020}
\parindent=0pt
\begin{document}
\name{\cChupAvenger{}}

%Joe Landolph AKA WR Teacher ChupAvenger 

%%Start with a paragraph introducing the character (introduce at highest level): name, country of origin, role (student/teacher/advisor), what they think of religion, and what their #1 top priority should be here at game.  Important first impression of character.  Personality at top also, and how they perceive themselves

%%Spend 2-3 paragraph providing history and giving context/justification for why the character cares about what they care about. Introduce any contacts from this time in their life.  Ie: How did you become a teacher / what do you think about living in the CoS / why are you obsessed about destroying the status quo, what went wrong in your life to cause you not to like it.

%%Spend 1-2 paragraphs discussing the character's current life, problems, and priorities. Introduce any contacts from this time in their life. Current life and situation.   What they think about the most important contacts

%%Spend 1-2 paragraph talking about what this character sees for their future. Ground any goals here that haven't been introduced yet.  What are you doing next, what are you trying to accomplish, and why?

%%Spend 1 paragraph to conclude things. Reiterate the character's most important goals (one or two more important, probably one mentioned at the beginning), and most valuable contacts.  Who are they closest to?  Coherent last impression on character

%%No need to include abilities, etc - Tech will include automatically when we go to prod.

\textbf{Primary Plots:}
 
Rescuing Joe  https://docs.google.com/document/d/1pn1RCDSTLRcF6wh123S6pxhYpeM1iCkjbLGpIWk2d5s/edit?usp=sharing

Marie, Marie, Do you know who I am?  https://docs.google.com/document/d/1q6WfXdgmNhCcJG1LGT1aCvlazhaTnZH9P0XZJ696xNA/edit?usp=sharing

Ev and Joe  https://docs.google.com/document/d/1lfYeHwSeLSwe3dI-YkQvAX3usw97P2U0JyCTw9_CepE/edit?usp=sharing

\textbf{Secondary Plots:}

Control of the FoG https://docs.google.com/document/d/1vbOTYybnnrH5pTKJOlkYHSKoEgiwbK8rY8ASwWNtFN0/edit?usp=sharing

Covering for a Murderer https://docs.google.com/document/d/1ccko996tpBDKIy44OXomCDIxChzn1WyCtMSvsgyVrwM/edit?usp=sharing

Revenge on Black (Chris)  https://docs.google.com/document/d/12NGWo-N_5xm3PyfXP8yXdxbquPdghRJ0upToSGseOK4/edit?usp=sharing

Amnesiac Relationship https://docs.google.com/document/d/1_hEBifEantaZLoeT5bTHwCLbiO0rzTn5ZRsJYgRP-bk/edit?usp=sharing

What, You're a PIRATE??? https://docs.google.com/document/d/1GkM-AooG2NSfY1WNXo_CNEDfFg0jse9uMgxhhG4gyB4/edit?usp=sharing  

Old teacher, convinced to become a chup as an avenger at the very start, then an avenger; now Jessie and Aaron have forgotten him, but Zev knows him well; took a sabatical. Knows that there'll be no leniency from Black. Killed a FoG who realized that he was trying to get out, which is why Jessie and Aaron forgot him.	Reluctant cultist; path to redemption through balance. Blinded by anger 6 years ago, joined up as a founding member. Has since realized the error of his ways. "Avenger" = assassin who get's forgotten by the world. Religious studies friends with Arike, share a spiritual connection across gods.	"
Former relationship with Marie (tension w/Chris and y/n join cult)"	looking for a way out, and to be forgiven for his sins!!

Art Teacher

\begin{itemz}[Goals]
	\item 
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
