\documentclass[blue]{GL2020}
\parindent=0pt
\begin{document}
\name{\bAdvisorBlue{}}

Being an Advisor sent to the \pSchool{} during the Time of Deciding is a tremendous honor and a tremendous responsibility. You are here to protect the life and livelihoods of your nation, and maybe forge a better future for all of \pEarth{}. Many of you have other tasks as well, not so grand or sweeping, but equally important in their niches. The roster of advisors turns over quite regularly. It is not common for an advisor to attend more than a few Times of Deciding in a row; \cDiplomat{\full} and \cHeadDiplomat{\full} are the notable exceptions here.

Advisors arrive at the \pSc{} just before the brewing Storm cuts off travel, some time in the mid to late morning on Friday. During a normal Time of Deciding, your one and only task is to ensure that the Storm is sent to the proper place. For the years of the Time of Peace treaty between all three nations, this was a relatively simple task of reminding the students of their duty, and then relaxing and enjoying each other’s company, maybe discussing some international business deals. But that lax attitude paved the way for the breaking of the treaty, and now you face a much more difficult task.

There is no clear answer where the Storm should be sent this time. Even if you adhere to the basic principle, ``not to my home nation,'' you still have two choices. And then there is the matter that you don't get to decide on your own. The students themselves get a vote on where to send the Storm, and the results of that vote are the strongest determining factor of the Storm’s destination. Besides choosing which student to give your Voting Stone to, all you can do is try to persuade, advise, cajole, and, if necessary, threaten and blackmail them into voting the way they should. Even the teachers, who control which Relics are included in the ritual, have a say.

Currently, the ``End of Suffering’’ Treaty holds sway, but a new treaty could be drawn up. Any attempt to do so will be a massive undertaking. Impassioned speeches to your fellow advisors here will not be enough — you will have to find ways to persuade the ruling bodies of the nations that your solution has merit as well. They will not let you wave away things your nation believes is owed to it. A new treaty will be hard, but not impossible. After all, you have the very best advisors and diplomats in all of \pEarth{} here. \emph{Any new treaty ratified by at least two nations will carry metaphysical weight and influence (but not solely determine) the Storm’s destination in the direction of whichever nation is stipulated to receive it in the treaty. The ``End of Suffering’’ Treaty says that the Storm should be sent to the \pShippies{}}.

A third role you can play at this Time of Deciding is that of a career mentor. The students gathered here represent the best of the best. Each of you has the option to select a student to serve as your intern or apprentice for at least the next three years. Both parties stand to gain in these arrangements — the students gain valuable experience and contacts, while the advisors gain the services of and chance to personally and directly influence some of the brightest young minds in all of \pEarth{}, the next generation of movers and shakers. While offering internships is a time honored tradition, not all advisors do so every time. Sometimes none of the students are a good fit this time around.

Some of you have personal business with each other, and the teachers and students, for good or for ill. Some have pet projects that require resources and knowledge found only at the \pSc{}. And you all have personal and national reputations to uphold — proving that you are better than your uncouth neighbors.

While the immediate future of \pEarth{} rests with the students, the greater future, spanning years or decades, is yours to shape. What are you willing to trade away to get what you want? Is there a price too high to protect your people? What will your legacy be?

\begin{itemz}[Goals]
    \item Decide which student to give your Voting Stone to based on whatever criteria you choose, including, almost certainly, whatever will best serve your and your nation’s interests.
    \item Negotiate with the other advisors and see if you can hammer out a new treaty that your home governments are willing to ratify — or have your nation go it alone if there is nothing to be gained from a treaty.
    \item Protect the interests of your nation, and uphold its dignity.
    \item If you find an acceptable candidate, offer your internship or apprenticeship to one of the students present this year.
\end{itemz}

\end{document}
