\documentclass[blue]{GL2020}
\parindent=0pt
\begin{document}
\name{\bDramatisPersonae{}}

\subsection*{The Advisors}
\subsubsection*{\pFarm{}}
\begin{itemize}
    \item \textbf{\cEvil{\full} (\cEvil{\MYcharpronouns})} \textit{[Played by: \cEvil{\MYplayer};\cEvil{\MYplayerpronouns}]}\\ A driven and influential career politician and leader of \cEvil{\their} nation's contingent of advisors.
    
    \item \textbf{\cHedonist{\full} (\cHedonist{\MYcharpronouns})} \textit{[Played by: \cHedonist{\MYplayer}; \cHedonist{\MYplayerpronouns}]}\\ A \cHedonist{\cleric} of \cFarmGod{}; traditional, scholarly, and very committed to \cHedonist{\their} duties.
    
    \item \textbf{\cWildCard{\full} (\cWildCard{\MYcharpronouns})} \textit{[Played by: \cWildCard{\MYplayer}; \cWildCard{\MYplayerpronouns}]}\\ A brilliant academic and high ranking noble specializing in the history and theory of magic.
    
    \item \textbf{\cCurse{\full} (\cCurse{\MYcharpronouns})} \textit{[Played by: \cCurse{\MYplayer}; \cCurse{\MYplayerpronouns}]}\\ An eccentric and clever commoner and one of the most skilled and sought after Cursemakers in all of Cengea.
\end{itemize}

\subsubsection*{\pTech{}}
\begin{itemize}
    \item \textbf{\cDiplomat{\full} (\cDiplomat{\MYcharpronouns})} \textit{[Played by: \cDiplomat{\MYplayer}; \cDiplomat{\MYplayerpronouns}]}\\ A driven career diplomat and one of the foremost negotiators on all of \pEarth{}. Leader of \cDiplomat{\their} nation's contingent of advisors.

    \item \textbf{\cAntiChup{\full} (\cAntiChup{\MYcharpronouns})} \textit{[Played by: \cAntiChup{\MYplayer}; \cAntiChup{\MYplayerpronouns}]}\\ The venerable, traditional, and outspoken High \cAntiChup{\Cleric} of \cTechGod{}.
    
    \item \textbf{\cHeadScientist{\full} (\cHeadScientist{\MYcharpronouns})} \textit{[Played by: \cHeadScientist{\MYplayer}; \cHeadScientist{\MYplayerpronouns}]}\\ A brilliant scientist and the lead researcher in the project to end the Storms permanently.
    
    \item \textbf{\cAssistantScientist{\full} (\cAssistantScientist{\MYcharpronouns})} \textit{[Played by: \cAssistantScientist{\MYplayer}; \cAssistantScientist{\MYplayerpronouns}]}\\ A young research assistant closely involved in the research to end the Storms permanently.

\end{itemize}

\subsubsection*{\pShip{}}
\begin{itemize}
    \item \textbf{\cEbbPriest{\full} (\cEbbPriest{\MYcharpronouns})} \textit{[Played by: \cEbbPriest{\MYplayer}; \cEbbPriest{\MYplayerpronouns}]}\\ A stern \cEbbPriest{\cleric} of \cEbb{}. The replacement leader of the \pShip{} advisors in place of \cHeadDiplomat{\full}, who is unexpectedly absent this weekend.

    \item \textbf{\cJuniorStatesman{\full} (\cJuniorStatesman{\MYcharpronouns})} \textit{[Played by: \cJuniorStatesman{\MYplayer}; \cJuniorStatesman{\MYplayerpronouns}]}\\ Apprentice to \cHeadDiplomat{}, and a skilled diplomat in \cJuniorStatesman{\their} own right.
    
    \item \textbf{\cBunker{\full} (\cBunker{\MYcharpronouns})} \textit{[Played by: \cBunker{\MYplayer}; \cBunker{\MYplayerpronouns}]}\\ The brilliant engineer who designed and installed the \pSc{}'s magical bunkers which protect against the Storm. Has been returning to the \pSc{} for many years to maintain them.
    
    \item \textbf{\cChupLeader{\full} (\cChupLeader{\MYcharpronouns})} \textit{[Played by: \cChupLeader{\MYplayer}; \cChupLeader{\MYplayerpronouns}]}\\ The charismatic and competent Secretary of \cHeadDiplomat{}.

\end{itemize}

\subsection*{The Teachers}

\begin{itemize}
    \item \textbf{\cPrincipal{\full} (\cPrincipal{\MYcharpronouns})} \textit{[Played by: \cPrincipal{\MYplayer}; \cPrincipal{\MYplayerpronouns}]}\\ The immortal Principal of the \pSc{} for the last two centuries, who has decided that it is time to retire and choose a successor. (\textbf{NPC})
\end{itemize}

\subsubsection*{\pFarm{}}
\begin{itemize}
    \item \textbf{\cInterpol{\full} (\cInterpol{\MYcharpronouns})} \textit{[Played by: \cInterpol{\MYplayer}; \cInterpol{\MYplayerpronouns}]}\\ The \pSc{}'s Magical Combat teacher, and one of the newest staff members.
    
    \item \textbf{\cMusic{\full} (\cMusic{\MYcharpronouns})} \textit{[Played by: \cMusic{\MYplayer}; \cMusic{\MYplayerpronouns}]}\\ The \pSc{}'s Music teacher, with a kind heart and a great reverence for music, who has been at the \pSc{} for many years. One of the contenders for the Principalship.
    
    \item \textbf{\cPrince{\full} (\cPrince{\MYcharpronouns})} \textit{[Played by: \cPrince{\MYplayer}; \cPrince{\MYplayerpronouns}]}\\ The youngest child of \cQueen{\full}, and the \pSc{}'s Cursebreaking teacher.
   		 
    \item \textbf{\cHistory{\full} (\cHistory{\MYcharpronouns})} \textit{[Played by: \cHistory{\MYplayer}; \cHistory{\MYplayerpronouns}]}\\ The \pSc{}'s History teacher, from a middling noble family.
\end{itemize}

\subsubsection*{\pTech{}}
\begin{itemize}
    \item \textbf{\cBeetle{\full} (\cBeetle{\MYcharpronouns})} \textit{[Played by: \cBeetle{\MYplayer}; \cBeetle{\MYplayerpronouns}]}\\ A kindly \cBeetle{\cleric} of \cTechGod{}, the \pSc{}'s Religion teacher, and one of the contenders for the Principalship.
    
    \item \textbf{\cChupInventor{\full} (\cChupInventor{\MYcharpronouns})} \textit{[Played by: \cChupInventor{\MYplayer}; \cChupInventor{\MYplayerpronouns}]}\\ The \pSc{}'s Diplomacy and Political Science teacher, and a brilliant engineer in \cChupInventor{\their} spare time.
    
    \item \textbf{\cEthics{\full} (\cEthics{\MYcharpronouns})} \textit{[Played by: \cEthics{\MYplayer}; \cEthics{\MYplayerpronouns}]}\\ The \pSc{}'s Morality and Ethics teacher, and informal student counselor, who has been at the \pSc{} for many years.
    
    \item \textbf{\cLibrarian{\full} (\cLibrarian{\MYcharpronouns})} \textit{[Played by: \cLibrarian{\MYplayer}; \cLibrarian{\MYplayerpronouns}]}\\ The \pSc{}'s Head Librarian of many years, learned in all kinds of lore.
\end{itemize}

\subsubsection*{\pShip{}}
\begin{itemize}
    \item \textbf{\cFlowPriest{\full} (\cFlowPriest{\MYcharpronouns})} \textit{[Played by: \cFlowPriest{\MYplayer}; \cFlowPriest{\MYplayerpronouns}]}\\ The \pSc{}'s Mathematics teacher, and an open-minded \cFlowPriest{\cleric} of \cFlow{}.
    
    \item \textbf{\cChupSecond{\full} (\cChupSecond{\MYcharpronouns})} \textit{[Played by: \cChupSecond{\MYplayer}; \cChupSecond{\MYplayerpronouns}]}\\ The clever and pragmatic Economics teacher at the \pSc{}, and and one of the contenders for the Principalship.
    
    \item \textbf{\cChupAvenger{\full} (\cChupAvenger{\MYcharpronouns})} \textit{[Played by: \cChupAvenger{\MYplayer}; \cChupAvenger{\MYplayerpronouns}]}\\ The \pSc{}'s Art teacher. A bit of a loner.
   		 
    \item \textbf{\cPirate{\full} (\cPirate{\MYcharpronouns})} \textit{[Played by: \cPirate{\MYplayer}; \cPirate{\MYplayerpronouns}]}\\ The Shop and Crafting teacher who has been at the \pSc{} for many years.
\end{itemize}

\subsection*{The Students}
\subsubsection*{\pFarm{}}
\begin{itemize}
    \item \textbf{\cDisney{\full} (\cDisney{\MYcharpronouns})} \textit{[Played by: \cDisney{\MYplayer}; \cDisney{\MYplayerpronouns}]}\\ A cheerful and idealistic \cDisney{\cleric} of \cFarmGod{} and first year student with no family, but being sponsored by \cWildCard{\full}.
    
    \item \textbf{\cAdopted{\full} (\cAdopted{\MYcharpronouns})} \textit{[Played by: \cAdopted{\MYplayer}; \cAdopted{\MYplayerpronouns}]}\\ An opinionated young noble and first year student from a middling noble family.

    \item \textbf{\cChupStudent{\full} (\cChupStudent{\MYcharpronouns})} \textit{[Played by: \cChupStudent{\MYplayer}; \cChupStudent{\MYplayerpronouns}]}\\ A young noble from a middling noble family, and first year student, with a laid-back reputation.
   	 
    \item \textbf{\cLibAssist{\full} (\cLibAssist{\MYcharpronouns})} \textit{[Played by: \cLibAssist{\MYplayer}; \cLibAssist{\MYplayerpronouns}]}\\ An ambitious second year student from a minor noble family, and one of the Librarian's student assistants.
\end{itemize}

\subsubsection*{\pTech{}}
\begin{itemize}
    \item \textbf{\cHeir{\full} (\cHeir{\MYcharpronouns})} \textit{[Played by: \cHeir{\MYplayer}; \cHeir{\MYplayerpronouns}]}\\ A third year student, and heir to the powerful Faledon family (and corporation).

    \item \textbf{\cTechStar{\full} (\cTechStar{\MYcharpronouns})} \textit{[Played by: \cTechStar{\MYplayer}; \cTechStar{\MYplayerpronouns}]}\\ A starry-eyed, young inventor, this year's Tech Star, and a first year student.

    \item \textbf{\cScholarship{\full} (\cScholarship{\MYcharpronouns})} \textit{[Played by: \cScholarship{\MYplayer}; \cScholarship{\MYplayerpronouns}]}\\ A second year student and Initiate of \cTechGod{} from humble origins and currently under the tutelage of High \cAntiChup{\Cleric} \cAntiChup{}.

    \item \textbf{\cAmbition{\full} (\cAmbition{\MYcharpronouns})} \textit{[Played by: \cAmbition{\MYplayer}; \cAmbition{\MYplayerpronouns}]}\\ An ambitious second year student eager to demonstrate \cAmbition{\their} talents to the world. One of the Librarian's student assistants.
    
\end{itemize}

\subsubsection*{\pShip{}}
\begin{itemize}
    \item \textbf{\cPresident{\full} (\cPresident{\MYcharpronouns})} \textit{[Played by: \cPresident{\MYplayer}; \cPresident{\MYplayerpronouns}]}\\ A third year student, and the level-headed student body President.

    \item \textbf{\cInitiate{\full} (\cInitiate{\MYcharpronouns})} \textit{[Played by: \cInitiate{\MYplayer}; \cInitiate{\MYplayerpronouns}]}\\ A third year student, Initiate studying to be a cleric, and skilled crafter.
   	 
    \item \textbf{\cWarlordDaughter{\full} (\cWarlordDaughter{\MYcharpronouns})} \textit{[Played by: \cWarlordDaughter{\MYplayer}; \cWarlordDaughter{\MYplayerpronouns}]}\\ A second year student and Initiate studying to be a cleric. Also the child of the Warlord leading the \pShip{} war effort.
   		 
    \item \textbf{\cPirateChild{\full} (\cPirateChild{\MYcharpronouns})} \textit{[Played by: \cPirateChild{\MYplayer}; \cPirateChild{\MYplayerpronouns}]}\\ A cocky and irreverent first year student.
   	 
\end{itemize}




\end{document}
