\documentclass[blue]{GL2020}
\begin{document}
\name{\bCult{}}

Religious and moral principles
\pCult{} follows the teachings of \cCultGod, the \cCultGod{\god} of fortune. The primary themes of their teachings are equality, fairness, and the nobility of self sacrifice. \pCult believe that all people should have the same opportunities and abilities, and that those who have more should donate their resources to those who have less. In particular, \pCult{} strives to eliminat economic inequality, which is otherwise impossible to escape from in the world at large.

In general, \pCult strive to be very open about taboos. Speaking against \pCult is frowned upon, but is outwardly embraced - freedom of speech being paramount. Respect for every identity, nationality, and social class is ingrained in \pCult teachings. The acceptance of those without means in particular is a strong means of recruitment in the more restrictive corners of external society.

As an organization \pCult largely look on people outside of the fold with pity, and always strive to find those that they can safely induct into their superior lifestyle.

% The bishops know that this is all about getting rid of magic, but the rank and file do not

% There are a few special cells that are working towards he end of magic, carefully curated. There are a lot of \pViking{} like that

% The \cCultLeader should be someone who really wants to do this - it's an important role

History of \pCult
The \pCult are a cult of personality, built around the immensely charismatic figure known only as \cCultLeader. While young, they have a nearly supernatural ability to sway people to their side. This persuasion is mostly natural charisma, but is bolstered by signature magical enhancements. As a citizen of the \pViking, \cCultLeader started the cult on their ship soon after developing these enhancements. With this freedom, \cCultLeader{\they} was able to visit and spread their teaching not just throughout \pViking territory, but start forays into \pTech and \pFarm. It was during these trips that \cCultLeader carefully selected two cardinals as their generals in other nations, individuals with enough charisma to start their own sects with enough obedience to never betray them. \cTechCardinal hails from \pTech and \cFarmCardinal hails from \pFarm.

\pCult has only officially been around for 6 years, having gained rapidly in popularity  in \pViking{} following the first time the storms went to \pViking unjustly and the world war began. In the last 3, their popularity and power has skyrocketed have they gained real popularity in \pViking.

Structure of \pCult
\pCult is built in cells that communicate only with the adjoining cells, passing information and orders via communication magic at specified times during the day. \pViking has around twice the number of cells of \pTech and \pFarm combined - these cells usually, but not always, map to boats. The leader of a cell is a Bishop, and ultimately, the Bishops report to the Cardinal of the country they are in, receiving their orders in a game of telephone from the previous cell.

\pCult are bold. On covert missions, they often operate in plain sight. When congregating as a cell, however, they are much more careful to avoid prying eyes, hiding in the forest, taking over a ship, or meeting in an abandoned warehouse as appropriate to their country of residence.

\pCult are keen for the chance to induct new members. They are particularly eager to induct the naive children who may end up controlling the vote.

External relations
\pCult have maintained a low profile throughout their short lifespan, but avoiding the notice of the governments entirely was impossible. Their profile is highest in \pViking, of course, and even average citizens are aware of the rumors there. Many \pViking{\people} are sympathetic to \cCult's message, even if they don’t participate themselves - their message of fairness and true equality strike a chord with many. However, if the full extent of their goals were revealed, they would become far less popular, so only inductees hear about their ambitions to destroy magic. Because of the democratic nature of \pViking, no strong resolution has yet been made to stop \pCult's criminal activities, though a growing faction has been trying to drum up support to prosecute them.

\pTech and \pFarm think of \pCult as criminals due to their contraband and theft of intellectual property. However, they have not made enough of a nuisance of themselves to be prioritized above other criminal organizations, allowing their foothold to spread.

The Black Market
\pCult raise funds primarily via a fast growing black market using the connections already put in place to transfer goods and services clandestinely throughout the three nations. Intermediate steps in the chain do their best not to know exactly what it is they are smuggling. However, one of the primary draws of \pCult{} is the ability to access technology you would never receive normally based on your social class. 

Examples of technology that members of \pCult{} receive from the other countries:
From \pTech{} - smartphones, wearable tech, and fancy clothes.
% Also takes in many inventors who are turned away by the temple, and helps them get mages to enable these inventions. The brilliant and the not super brilliant alike. Or they want to use higher class technology.
% There aren't a ton of magic users coming from Tech, but there are some. (rare) magic users who don't WANT to work for the Tech church

% Serfs from /pFarm as well - they want to OWN stuff!! And not be reliant on the nobility. They want magic
% Weapons from Leau - even soldiers backed by the government buy these in Tech country
% This all adds up to - need to give people tech within the cult
% They may not want to kill magic after this! Cells need carefully curated info
% Farm nation provides curses - items with curses in them or connecting with people for more powerful curses on key individuals. A book or a scarf with a curse in it?
% They also provide food to the other nations
% Farm nation peasants get promises of land and the ability to cast magic on that land.
% For Farm, they also smuggle messages from the magic peasants to their families

% There's also the promise of a commune of followers of genesis who live together idyllicly

Educational system
\pCult follow the standard cult playbook - ease the new recruit in with friendship and relatable worries and concerns, then slowly step up the radical messages until it reaches the level of brainwashing. Religious services are intense and mentally draining, in deliberate contrast to the tamer religious services available elsewhere. \pCult deliberately isolate members from their existing relationships in order to make the inductee as susceptible and dependent on the group as possible. Above all else, \pCult are encouraged to read the writings of \cCultLeader daily, which seems to have an almost hypnotic effect.

Technology and Magic
The technology available to \pCult{} is composed of the most useful technologies from other nations, which in practice means that it mostly resembles that of \pTech{}. However, \pCult{} also heavily encourages research into branches of magic deemed too dangerous and unprofitable by \pTech{}. This does not often yield results, but has done so several times in the past. The two most useful of these feats were: 

1. A means to probe a target's mind for their secrets at the cost of some of the target and caster's sanity. 
2. A way to transfer the caster's magic ability to another (something the bishops liberally solicit for their own power).

In addition, \cCultLeader has passed down several persuasive magical techniques to bishops, which they use to great effect.

Avengers
\pCult do not believe in the inherent wrongness of murder when the target is someone who hoards power or assists those who do. As an expression of power, \cCultGod has managed to twist the universal law against murder for \pCult. Instead of losing your own memories when you kill another, others lose their memories of you - until, finally, no one remembers who you are and you cease to be. This has led \pCult to train and use some extremely effective assassins in a world where career assassins are basically unheard of - and the evidence for those assassinations vanishes from the minds of those around the target. These religious assassins, known as Avengers, live a lonely life in service of their beliefs, but an effective one. It is unknown what happens to Avengers after they expire.

% 5-8 kills/avenger, based on how many people know them when they started.
% If we have an avenger character, they should have at least 5 kills and know that they don't have long left.
% The first kill is a chance, the second is a higher chance, the third kill is a guarantee
% "`If you see me, roll a d4. If you roll a 1, you don't know me, even if you did before"'
% Have a second one of these


School attendees
\pCult do not have official representation at the school. However, they have pulled a lot of strings and taken many risks to sneak a few of their highest ranking supporters into the ranks of those attending this conference. \cCultLeader is here as one of the lowest ranking students. \cTechBishop is a newly minted high ranking diplomat, ostensibly there to facilitate the agreement between \pTech and \pFarm. Various other lower ranking members were also snuck in, none of whom have met each other, including one masquerading as the sibling of \cAmnesiac{}.

% Someone from one of the three nations is infiltrating the cult and is trying to figure out who the cult leader is so they can off them
% Tech Bishop is newly minted high ranking official - they persuaded, informationed, and murdered their way up with the help of the cult.

Goals
\pCult's goal is to subvert the storm selection ceremony and to keep the storm at the school. Doing so will break the pact between the gods and remove magic from the world, bringing about a new world order of perfect equality that \cCultLeader desires.

Costuming
\pCult strive to maintain secrecy, and so always masquerade as a normal citizen of their nation of origin. However, they do keep a small item in the shape of a clover on their person at all times to prove their allegiance to others they may meet that they may have never seen before.

% The interpol PC in game has one of these pins, but doesn't have this bluesheet, so they don't know everything they need to masquerade fully. They get the bluesheet, but we should redact the LIVING SHIT out of it




Read this for ideas \/

Meeting notes 8/24
Soften how we think of how the fall of magic will affect everyone. The followers of genesis have to realistically think that it’s not that bad, especially for them.

The Chupacabrists are all about sacrifice. They think about ending magic as sacrificing the old work to get a better one.

Notes prior to 8/24
Chubacabraists - More liberal (out of rebellion against poverty). More likely to be young, except for the students of the school, as they are hand picked

Rise of Chubacabra religion is causing storms to be even stronger than should be, increasing amplitude - make the storm bad enough and stay at the school and it will destroy the conduit.  Only way to fix magic is with magic (like how Vikings were thinking of it)

Chupacabra want storm to go to school and to destroy religion
Magic is destroyed
School is destroyed
Agrarian famine - Technomancers also starve
Vikings unable to battle sea serpents
Technomancers - Unable to use magic for mining / trade / etc.  All technology stops working

Apocalyptic

Character idea - charismatic leader

Plot ideas - convert members to their group

Character ideas - prominent moles

Chupacabrists started with Vikings
Chubacabra - why don’t all of them jump on
Has to be more than traditionalist
Family that is in charge because have lots of magic is invested in magic not going away
Perhaps one of them has theory that ships go faster because magic - will go do research to prove it
A Viking kid who wants to go to school might run to go to school to prove / disprove thesis
Vikings initially sympathetic to Chubacabras but then backpedal
more likely to be part of Chubacabra religion because seen as option in part of restoring the balance.  Not endorsed by Vikings, just growing more easily there because of terrible conditions there

Chupacabra wild card
Steal / transfer / neutralize power of the children
Killing people?  Could have a handler
Creating potion of the river Lethe
Possibility that Chupacabra has different punishment to murder that isn’t wiping people’s memories
Could start game with a dead NPC - looking for murderer with missing memory but the murderer isn’t missing memory
Potentially have amnesiac character who is being framed for this
Does the Chupacabra God punish murder, what do they punish, and how do they punish?
Perhaps start to cease to exist in other people’s memory (ie: someone they care about back home forgets who they are) - being removed from reality.  Once person has nobody who remembers you, you cease to exist / fall off face of the planet and go to the realm of the Gods.
Belief makes power for Gods, removing belief in person who is being punished
No murder until X, etc
No weapons here, have to make poison going to use, etc etc


\end{document}
