\documentclass[blue]{GL2020}
\parindent=0pt
\begin{document}
\name{\bCultAvenger{}}

\section*{Who are the \pGoaties{}?}
The \pGoaties{} are a group of stark contrasts and contradictions, part cult and part political movement, torn between high-flung ideals and ruthless methods. The group follows the teachings of \cGenesis{}, the \cGenesis{\Deity} of Luck, Probability, Fortune, Underdogs, and Trickery. The primary themes of their teachings are equality, fairness, the nobility of self-sacrifice, and the value of facing one's fears and taking risks. The \pGoaties{} believe that all people should have the same opportunities and abilities, and that those who have more should give their resources to those who have less. In particular, the \pGoaties{} strive to eliminate economic inequality, which is otherwise difficult to impossible to escape from in the world at large. As below, so above - The \pGoaties{} reject the supremacy of the so-called Patron Gods, who hoard power and lord it over “Minor” Gods like \cGenesis{} who are every bit as important. They see the unjust hegemony of the Patron Gods and the corrupt power structures of the mortal world as integrally linked, and hope to topple both.

While the group ostensibly embraces freedom of speech, it is \textbf{seriously} frowned upon to voice \textbf{any} criticism of the leadership or the teachings of \cGenesis{}. The acceptance of those without means in particular is a strong method of recruitment in the more restrictive corners of society since respect for every person, regardless of identity, nationality, or social class, is ingrained in group teachings. Still, the \pGoaties{} largely look on people outside of the fold with pity, and always strive to find those that they can safely induct into their enlightened worldview. It is said that one day, the Chosen of \cGenesis{} will recreate \pEarth{} as a promised land — a commune of the faithful who will live together in harmony.

\section*{History of the \pGoaties{}}
The \pGoaties{} were founded and built up by the immensely charismatic leader, \cChupLeader{\full}, whose name and appearance are known only to the inner circle (and to enable this particular mission, the player characters in this cell). While young, \cChupLeader{\they} \cChupLeader{\have} a nearly supernatural ability to sway people to \cChupLeader{\their} side. As a citizen of the \pShip{}, \cChupLeader{}, also known as the ``Chosen of \cGenesis{}’’, started the group on \cChupLeader{\their} ship, converting the entire crew to the cause. With the freedom not to have to hide from friends and family, the Chosen was able to visit and spread \cChupLeader{\their} teachings, not just throughout \pShippie{} territory, but to the \pTech{} and the \pFarm{} as well. It was during these trips that the Chosen met those who would eventually be selected as Bishops to serve as the group's generals and spiritual leaders in other nations. Similar to the Chosen, the identity of the Bishops is secret even within the group. The \pGoaties{} popularity surged 6 years ago in the \pShip{} following the first time the storms were sent to the \pShip{} unjustly, riding the same tide of resentment that sparked the war and \cLoud{\full} used to surge into power.

\section*{Structure}
The \pGoaties{} are structured in cells that communicate only with the adjoining cells, passing information and orders between leaders via coded signals and dead drops. The \pShip{} has around twice the number of cells as the \pTech{} and the \pFarm{} combined. These cells often, but not always, compose the entire crew of a given ship. The leader of a cell receives orders in a game of telephone from the previous cell all the way from the Bishops or the Chosen.

If anyone in the group wishes to challenge the Chosen of \cGenesis{} for leadership, they can call a vote of no confidence at any time, provided the same individual has not called a vote in the last 24 hours. All known \pGoaties{} in the game \textbf{other} than Avengers (see Avengers section below for what those are) must be present for the vote (check with a GM). The vote is a simple 1 vote/person run-off between the current Chosen and a challenger; the person who called for the vote does NOT need to be one of the candidates. Candidates are first given the opportunity to speak to the assembled Followers. Once speeches are done, votes are made publicly via moving to stand with the candidate you support. A 2/3rds majority is required to elect a new Chosen. Anything less than that and the current Chosen will persist. While this is the protocol for electing a new leader, it has never been successfully exercised in the group's history; the current Chosen of \cGenesis{} has been the Chosen since the founding of the group. 

\section*{Methods}
The \pGoaties{} follow the standard cult playbook — ease the new recruit in with friendship and relatable concerns, then slowly step up the radical messages until it reaches the level of brainwashing. Religious services are intense and mentally draining, in deliberate contrast to the tamer religious services available elsewhere. The group also deliberately isolates members from their existing relationships in order to make the inductee as susceptible and dependent on the group as possible. Above all else, the \pGoaties{} are encouraged to read the writings of the Chosen daily, which are charismatic enough to energize and deepen faith.

Once someone fully embraces the cult, they describe the experience as that of a close, loving family. Everything they need is provided freely within the confines of the group. People find friends, mentors, and lovers, places to live, food to eat, and a purpose in life.

\section*{Membership}
The \pGoaties{} take all kinds. Some of their most valuable members are \pTech{} inventors with talent who are turned away by the Temple of \cTechGod{}. The group finds ways to help them to imbue their inventions, and in return reaps the benefit from the brilliant and the mediocre alike. Other members from the \pTech{} are also welcomed, mostly from the bottom rung of society who, unable to afford higher education and trapped in a cycle of poverty, are lured by the promise of a better life and a better future for their children.

Another source of recruits are commoners from the \pFarm{} who just want to have some agency in their lives and the right to real property, away from the oppressive hand of the Nobility. The \pGoaties{} have promised large swaths of land to its \pFarm{} recruits once \cGenesis{} comes to the fore.

The largest group by far, however, comes from the \pShip{}. Despite all the talk of Balance in the \pShip{} society, most wealth is concentrated in the hands of the 1st through 4th Fleets, and somehow it never seems to trickle down to the poorer fleets. Many \pShippies{} have become disillusioned with their free-wheeling, free market way of life, and are lured to the \pGoaties{} by promises of a more equitable and truly Balanced society. Others are drawn by anger at the rest of the world for the Betrayal of six years ago, believing the war does not go far enough. Regardless of what draws them, \pShippies{} are the base of power of the \pGoaties{}. It doesn't hurt that neither the governing Council nor the warlord, \cLoud{}, has yet to seriously crack down on the group, giving the Followers tacit legitimacy.

The \pGoaties{} do not, of course, have official representation at the school. However, they have pulled a lot of strings and taken many risks to sneak a few of their highest ranking members into those attending this Time of Deciding. Not all of the Followers on this mission have worked together before, so they may not have personal relationships yet.

\textbf{Recruitment remains a high priority for the \pGoaties{}, and this weekend is no exception. The group is very unlikely to succeed at its objectives without new recruits, especially among the students.} That said, not getting caught or exposing the group to the wrong person is also crucial, so every recruitment attempt is a calculated risk. Requiring new recruits to pass some test to ``prove they are serious'' and that they are ``ready for the risks involved'' can help mitigate this risk. To formally induct someone requires a Cleric of \cGenesis{} to perform a ritual of initiation. The earlier someone is inducted, the more value their aid will be.

\section*{External Relations}
The \pGoaties{} have maintained a remarkably low profile throughout their (relatively) short lifespan considering their methods, but avoiding the notice of the powerful entirely was impossible. Their profile is highest in the \pShip{}, of course, and even average citizens have heard whispers there. Many \pShippies{} are sympathetic to the group's message, even if they don't participate themselves. Because of the democratic nature of the \pShip{}, this has led to a lack of a strong resolution condemning the \pGoaties{}'s criminal activities, though a growing faction has been trying to drum up support to prosecute them.

The general public in the \pTech{} and \pFarm{} remain largely unaware of the existence of the \pGoaties{}. Many have heard of the black market (see below), but don’t know it is controlled by a religious cult. Spy agencies and the mainstream Church in these two nations, however, are increasingly on the hunt for the \pGoaties{}, seeing them as dangerous criminals due to their contraband, theft of intellectual property, general “rabble rousing," and rejection of the Patron Gods. A small handful of cells have been compromised and lost recently due to repression by these forces. It is all but certain that enemy spies will be present at this Time of Deciding among the Advisors, and perhaps even the Teachers. Every Cleric of one of the Patron Gods is a potential enemy informant as well.

\section*{The Black Market}
The \pGoaties{} raise funds primarily via a thriving black market, using the connections already put in place to transfer goods and services clandestinely throughout the three nations. Intermediate steps in the chain do their best not to know exactly what it is they are smuggling. However, one of the primary draws of the \pGoaties{} is the ability to access technology you would never have normally based on your social class. From the \pTech{}, \pGoaties{} can enjoy appliances and wearable technology. From the \pFarm{}, they can enjoy curses/blessings and cursed/blessed items, as well as exotic foods and expensive spices. And from the \pShip{}, they can find weapons, superior crafting supplies for many projects, and seafood. The black market pipelines are also used to deliver mail within the \pFarm{}, which otherwise wouldn't be able to travel between peasants born with magical talent (and subsequently ``adopted'’ into a noble house) and their birth families.

When executing solo or small group missions, they often operate in plain sight, relying on speed and shock to get their work done. When congregating as a full cell, however, they are much more careful to avoid prying eyes, hiding in the forest, having inducted a full ship, or meeting in an abandoned warehouse as appropriate to their country of residence.

\section*{Avengers}
The \pGoaties{} do not believe in the inherent wrongness of murder when the target is someone who hoards power or assists those who do. Therefore, \cGenesis{} has managed to twist the universal law against murder for specially consecrated individuals within the \pGoaties{}. For these individuals, known as Avengers, instead of losing their own memories when they kill another, others instead lose their memories of the Avenger — until, finally, no one remembers who they are. This has allowed the \pGoaties{} to train and use some extremely effective assassins in a world where career assassins are all but unheard of — and the evidence for those assassinations often vanishes from the minds of those around the target. These Avengers live a lonely life in service of their beliefs, but an effective one. To be called to serve as an Avenger is one of the highest honors that \cGenesis{} can bestow — it is a sacrifice, but it is greatly lauded within the community. It is unknown what happens to Avengers after everyone forgets their existence.

\section*{A Relic of Genesis}
Through extensive prayer, faith, and dedication, the Chosen of \cGenesis{} and \cChupLeader{\their} closest associates were recently able to consecrate a new Relic to \cGenesis{}, on par with the Relics of the Patron Deities — the ``\iHorseshoe{}''. While its exact properties are not disseminated to the rank and file, it is believed to confer supernatural luck, in keeping with \cGenesis{}' domain. The consecration of the ``\iHorseshoe{}'' is seen as a sign of \cGenesis{}' favor and rise in prominence, and the group's growing power and influence.

\section*{Costuming}
The \pGoaties{} strive to maintain secrecy, and so always masquerade as a normal citizen of their nation of origin. However, they do keep a small item in the shape of a four-leaf clover (the symbol of \cGenesis{}) on their person at all times, both to remind them of their faith, and to reveal their allegiance to other members of the cult whom they are meeting for the first time. This religious symbol is usually kept hidden, however, so as not to draw the attention of the group's enemies. You are welcome to bring your own four-leaf clover prop, or the GMs can provide you with a simple stand-in. You must have one or the other. Other symbols of \cGenesis{} include rabbits, lilies, horseshoes, playing cards, and dice.

\section*{Known Members}
This is a list of the \pGoaties{} who have been assigned to this particular mission. It is possible that other Followers may be here, working on other missions for \cGenesis{} without it being public knowledge to this cell.
\begin{itemize}
    \item \cChupLeader{\full} - The Chosen of \cGenesis{} and founder of the group.
    \item \cChupSecond{\full} - The second in command of the group, and a Bishop of \cGenesis{}.
    \item \cChupInventor{\full} - A brilliant inventor.
    \item \cChupStudent{\full} - One of the group's youngest operatives. Deeply devoted to the cause.
    \item \cChupAvenger{\full} - Unfortunately, you have been called upon to serve as an Avenger this weekend. Fortunately, none of your fellow cultists seem to remember who you are! For once being forgotten is working in your favor.
\end{itemize}

\end{document}