\documentclass[blue]{GL2020}

\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{ltablex}
\usepackage{tabularx}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
{\renewcommand{\arraystretch}{1.5}
\setlength{\columnsep}{1cm}

\parindent=0pt
\begin{document}
\name{\bPantheon{}}

The below table contains the pantheon of Cengea and some information about each god's domain and symbols. Do not feel like you need to memorize all of this information; it is simply there for your reference. While the Patron Gods (bolded) are known to everyone, the minor gods are more obscure, and have no officially sanctioned worshipers of their own. Someone might make an offering to a minor god if appropriate to the situation, but many people go through their lives without paying them much mind. This list is also not comprehensive. More minor gods exist, but they are even more obscure than those that made it into the table. 

Only the Patron Gods are powerful enough to have an Avatar in the mortal world. While the minor gods have various animals associated with them, the question of what form their Avatar would take is purely speculative.

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash} m{1.8cm} |>{\centering\arraybackslash} m{1.5cm} | X |X |}
\hline
\multicolumn{4}{|c|}{\textbf{{\large The Patron Deities}}} \\
\hline
	\textbf{Name} & \textbf{Pronouns} & \multicolumn{1}{c|}{\textbf{Domains}} & \multicolumn{1}{c|}{\textbf{Symbols and Avatars}} \\
\hline
	\cFarmGod{} & They/Them & \textbf{Patron of \pFarm{}}. Light, Fertility, the Sun, the Living World, Agriculture, Music.  & sunburst, hummingbird (Avatar), flowers in general, cornucopia, clay and terracotta, copper, musical instruments. \\
\hline	
	\cTechGod{} & She/Her & \textbf{Patron of \pTech{}}. Science, Engineering, Smithcraft, Inspiration, Ingenuity  & scarab beetle (Avatar), gears, obsidian, gold, forge, hammer. \\
\hline	
	\cEbbFull{\full} & She/Her & \textbf{Patron of the \pShip{}}. Ocean, Islands, Ships, the Ebb Tide, That Which is Lost or Taken. & waves, island, ships, golden sea serpent (Avatar), limestone. \\
\hline	
	\cFlowFull{\full} & She/Her & \textbf{Patron of the \pShip{}}.  Ocean, the Moon, Rain, the Flow Tide, That Which is Created or Given. & waves, falling raindrops, the moon, silver sea serpent (Avatar), limestone, moonflower. \\
\hline	
\hline	
\multicolumn{4}{|c|}{\textbf{{\large The Minor Deities}}} \\
\hline	
	\textbf{Name} & \textbf{Pronouns} & \multicolumn{1}{c|}{\textbf{Domains}} & \multicolumn{1}{c|}{\textbf{Symbols and Avatars}} \\
\hline	
	The Fates & She/They & \textbf{As a triumvirate}, Fate, Destiny, Mortality, Spinning and Weaving. \textbf{As individual aspects}, the Past (the Maiden), the Present (the Mother), and the Future (the Crone). & \textbf{Triumvirate}: spiders, spider webs, spinning and weaving implements. \textbf{Maiden}: measuring stick. \textbf{Mother}: distaff, spindle. \textbf{Crone}: scissors. \\
\hline	
	\cGenesis{} & He/Him & Luck, Probability, Fortune, Underdogs & rabbit, four-leaf clover, lily, horseshoe, playing cards, dice, marble \\
\hline	
	Noct & She/They & Darkness, Night, Fear, Doubt, Dreams and Nightmares (both positive [helping you face your fears and grapple with doubts] and negative aspects). & sand, labyrinths, stars, nightshade, obsidian, whippoorwill \\
\hline	
	Jade & He/They & Jealousy, Envy, wealth, and jewelry making. Often associated with Love or Lust, but does not actually rule over either. & emeralds, jade, snakes, cracked objects (like broken hearts, or shattered pottery), flame orchid \\
\hline	
	Whisp & All & A shapeshifter. Cleverness, duplicity, secrets (both harmless and major), sometimes piracy due to association with theft. & two masks, a coin, empty needle, keys, corvids (crows, jays, etc.), black crocus \\
\hline	
	Verit & They/Them & Deity of remembrance and history and all that contains-writing, memory, nostalgia, grudges, stories, truth & an open book, a quill, twilight, forget-me-nots, owl, stone flower \\
\hline	
	Aura & Ze/Zir & Deity of the spaces between: doors, travel, portals, illness (between life and death), reflections & a door frame, a walking staff, dogs, morning glory, faceted crystals, mirrors \\
\hline	
	Kalos & They/Them & Celebration, beauty, theater/dance, love/lust. & a ribbon, an open palm, swirling wind, a double knot, a butterfly, hollyhock \\
\hline	
\end{tabularx}


\end{document}

