\documentclass[blue]{GL2020}
\parindent=0pt
\begin{document}
\name{\bSchool{}}

\section*{What is the \pSchool{}?}
The \pSchool{} is the metaphorical center of \pEarth{}. It resides at the center of the continent on a tiny airborne island suspended in the sky by the twining Ley Lines of the world; in fact, every major Ley Line in \pEarth{} connects at this spot. It is accessible only by vehicles reinforced against the elements, which are lifted by thick cables (gondola style). The island sits above a placid lake. Like the island above it, it is not a particularly large lake, but it does have many unusual properties due to the Ley Lines that converge upon it. Unlike most other bodies of water in \pEarth{}, no fish, bird, or sea serpent has ever been recorded to reside in this lake, making travel to and from the school relatively safe except during the Time of Deciding.

No one knows for sure how old the \pSchool{} is. It is generally understood that it was built by humans, not created by the Gods, but the details of when are long lost to time. Given that this island is the only location from which the Storm can be partially controlled, it makes sense that humans would eventually build structures here to allow for permanent occupation. The school records indicate at least 6 principals have served the school since its founding, although 8 gravestones of similar shape rest in the school graveyard. Dates on all but the 3 most recent are weathered beyond legibility. Since the acting principal of the \pSc{} stops aging (effectively immortal) for as long as they hold the post, there is no telling how long each served and therefore how old the school might be.

The \pSc{} itself is part academy, part library, part archive, and part Temple to the Gods. The brightest, best connected, and most magically powerful from all three nations are sent to the \pSchool{} to finish their studies — and the best of those remain there during the Time of Deciding to participate in the Ritual to Control the Storm.

The current Principal of the \pSc{} is named \cPrincipal{\full}. The Principal bears the particular burden of being unable to leave the island without dire consequences to the structures built upon it. Like every Principal before \cPrincipal{\them}, \cPrincipal{} has been granted immortality by the Gods, both as a reward and as a way to ensure the \pSc{} remains under a steady hand. That immortality lasts as long as \cPrincipal{} remains Principal, but after 200 long years of service, \cPrincipal{\they} has announced \cPrincipal{\their} plan to retire. The Principal always chooses \cPrincipal{\their} own successor, and currently the three contenders are the Music teacher, \cMusic{\full}, the Religion teacher, \cBeetle{\full}, and the Economics teacher, \cChupSecond{}. Your character may or may not have opinions about which is the best candidate.

The \pSc{} maintains its independence from all three nations, and is in fact the only truly independent place on the continent. It maintains this balance with careful political maneuvering on the part of the teachers and Principal, financial strength from the staggering tuition, powerful magical defenses laid down over the ages, and protection from the Gods themselves. The \pSc{} is additionally funded partially by the three nations, even in this time of war, and donations from wealthy alumni.

\section*{Campus}
Even countless ages after its founding, the \pSchool{} is a wonder of magical construction. Each of the main buildings surpass the largest buildings on the continent, made of giant, unbroken slabs of granite, with Gothic pillars supporting wide roofs with painstakingly sculpted eaves. The buildings sport the continent’s first stained glass windows with fanciful depictions of figures of legend and the very Gods themselves.

The Library is a particularly awe inspiring building, sporting bookshelves that span multiple stories, accessible by a network of catwalks. A massive spiral staircase winds down into the very heart of the island, offering access to deeper, and more dangerous, levels for those who dare. This building is heavily magically warded and contains many of the most dangerous, forbidden, and ancient knowledge on the continent. It is not always clear whether the wards are meant to protect things in the Library from outsiders, or to protect outsiders from the things in the Library. The dangers of navigating the Library are great enough that specially trained Librarians need to pass down the knowledge of how to survive its maintenance and access its deepest secrets. It is said that the Gods themselves maintain the magical protections in the Library.

Other facilities are almost as impressive. The rooms in the student dormitories and staff housing are lavish, large, and well-maintained. There is ample space for the current class of 180 enrolled students (20 per nation per year) and the 100+ faculty and support staff. The school’s Temple of the Gods rivals any of the finest cathedrals in the three nations. Even the Abandoned Wing, ruined and rendered uninhabitable when one of \cPrincipal{}'s predecessors left the island for a week, retains remnants of its former grandeur.

\section*{Curriculum}
The curriculum of the \pSc{} is the most advanced in \pEarth{}. Over the three years of a student’s tenure, they are given the best education in subjects ranging from magical combat to mathematics to diplomacy. Students emerge from the \pSchool{} as well-rounded individuals, capable of and sought after for jobs in just about every discipline.

The most basic qualification for the \pSc{} is high magical power, and that gift is honed to perfection alongside the minds of its young wielders. As a person’s raw magical power level fades past approximately college age, it is no exaggeration to call the \pSchool{} the highest concentration of magically powerful people on \pEarth{}. Most magic users, of course, counterbalance this decrease in raw power with increasing finesse in their application.

\section*{The Time of Deciding}
It is presumed that ever since the development of the Ritual to Control the Storm, the \pSchool{} has hosted the ``Time of Deciding.’’ During this time, non-essential staff and students who are not chosen to participate are sent home for the duration, the bunker function of some buildings is activated to protect those who remain during Storm Surges, and the transport gondolas are shut down until the Storm passes. More information on the Time of Deciding is available in the \bWorld{} bluesheet.

\end{document}

