\documentclass[blue]{GL2020}
\parindent=0pt
\begin{document}
\name{\bStudentBlue{}}

Being a student at the \pSchool{} is a tremendous honor and a tremendous responsibility. You are \pEarth{}'s future leaders, in both a spiritual and secular sense. You were picked for excellence in academics, religion, magic, and more. You are the best of the best that \pEarth{} has to offer. You spend three years at the \pSchool{}. During that time, you take classes in a wide variety of subjects, and work on independent projects. You hone your skills, your critical thinking, and your magic. And at the end of it, you go on to be some of the most influential people in your nation.

Your time at the \pSc{} is one of learning, growing, and forging lifelong friendships. The connections you make here will help you for the rest of your life. But not everyone is friendly with each other, even from the same country. Things get even worse when national loyalty comes into play. Many things are on the line beyond the fate of the world. Advisors can offer those who impress them internships that can set you up for life. Teachers can choose you to participate in the Ceremony of Excellence, an honor that sets you above your peers. For those with the strongest ambitions, rivalries can become cutthroat.

Those of you who are present during the Time of Deciding have a particular set of challenges ahead of you. \textbf{You must decide where to send the Storm, design and execute the Ritual to Control the Storm, and then live with what you have done for the rest of your life.} The Storm is a cruel choice. People will die. Livelihoods will be destroyed. But you must choose. To choose not to choose is also a choice, and it is the bloodiest of all. Though it has not been tested since before the \pSc{} was founded, wisdom is that an uncontrolled Storm will kill many more than a controlled one as it rages across all three nations.

The burden is heavy, but you are not alone in it. Many of your teachers and advisors have participated in this ritual before. They have all learned to bear the burden. They may have advice for you — do not squander the resource their advice can be. And you have your fellow students here with you now — you will collectively share the responsibility for this year's Decision. You can and should discuss and debate amongst yourselves as well. Do not take this responsibility lightly.

But do not let it consume you either. Some of you are graduating this year. Some of you just started at the \pSchool{}. You have your whole adult lives ahead of you. You are young, and full of potential. \pSc{} is a time for joy, fun, connection, friendship, romance, and more. It is a time to try things, to make mistakes, and to grow and change. You are the future of \pEarth{}. What will you make? Who will you be? How will you change the future?

\begin{itemz}[Goals]
    \item Decide how you will vote for where to send the Storm. The Advisors and Teachers will have a lot to say on the matter, but the decision is ultimately yours on how to cast your vote(s).
     \item Gain the favor of Teachers and Advisors to get additional Voting Stones (each student starts with 1 and can hold a maximum of 5) and potentially accept an internship with one of the Advisors to help your future career.
    \item Design and execute the Ritual to Control the Storm. \emph{(OOC: There will also be a “default” version of the ritual you can fall back on if no one wants to design a new ritual.)}
    \item Attend the Ceremony of Excellence to be recognized, or support your fellow students.
    \item Make the \pSc{} proud.
\end{itemz}

\end{document}
