\documentclass[sheet]{GL2020}
\parindent=0pt
\usepackage[shortlabels]{enumitem}

\usepackage{fancyhdr}
\fancypagestyle{plain}{%
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{\sffamily\fontsize{24pt}{24pt}\selectfont\thepage} % except the center
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}
\pagestyle{plain}

\begin{document}

%%Title Page
\begin{center}\LARGE\bf\begin{tabular}{|c|}
  \hline The Library\\ Choose Your Own Adventure\\ START HERE\\ \hline
\end{tabular}\end{center}

\begingroup
\itshape
Welcome to the Library. Use this choose-your-own-adventure booklet to explore this space. How it works:
\begin{itemize}
  \item When you turn to a page, read the list of options, pick one, and follow its instructions. If you remain on that page, you can then pick another option. Repeat on the next page you turn to.
  \item Groups may explore the Library together as long as there is consensus on all decisions made. If there is disagreement, you must proceed separately.
  \item Some options require that certain conditions be met (e.g. a CR threshold). As long as anyone in your group meets the condition, the whole group may take that option; for CR thresholds, count everyone’s CR combined, and add the highest L-Score in your group. 
  \item Some options ask you to roll a d20; high rolls are usually more favorable. 
  \item Some locations give you an option to remove an item from one of the envelopes located here; do not remove items from these envelopes unless instructed to do so. 
  \item You cannot backtrack to a location you just came from unless there is an option to do so in the text. 
  \item If you want to do something that isn’t listed among the options, find a GM. 
  \item At any time, you may choose to \textbf{Flee Blindly} from the Library, which brings you back to page 1 and causes you to lose one CR token until the next meal; you must also return any items you obtained in the Library back to their original envelopes as you drop them in panic.
\end{itemize}
\endgroup

The Library of the College of the Gods is a wonder to behold, sporting bookshelves that span multiple stories, accessible by small catwalks. A massive spiral staircase winds down into the very heart of the island, offering access to deeper, and more dangerous, levels for those who dare. This building is heavily magically warded and contains many of the most dangerous, forbidden, and ancient knowledge on the continent. It is not always clear whether the wards are meant to protect things in the Library from outsiders, or to protect outsiders from the things in the Library. The dangers of navigating the Library are great enough that specially trained Librarians need to pass down the knowledge of how to survive its maintenance and access its deepest secrets. It is said that the Deities themselves maintain the magical protections in the Library. The Library has 3 tiers. The 1st/Low Tier is relatively safe and open to anyone, housing books on innocuous topics from basic magical theory to geography to engineering. The 2nd/Middle Tier houses more dangerous books and artifacts, and the 3rd/High Tier is home to the most dangerous and forbidden knowledge; it is in the 3rd Tier that the three Relics housed at the college are stored. Rumors abound of a 4th/Extreme Tier, but no one ever goes that deep, if it even exists in the first place.\\

%\vspace{3cm}

{\large \textbf{To begin exploring the library, turn the page to read page~\pageref{TierOneHub}.}}

\pagenumbering{gobble}

\clearpage

\pagenumbering{arabic}
\setcounter{page}{1}

\begin{center}\section*{\underline{Tier 1 Hub}}\end{center}
\label{TierOneHub}

Welcome to the 1st Tier. Blue will-o’-the-wisps drift lazily through the stacks, providing a source of light. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
	\item Browse the stacks. You can find any information available in your bluesheets. You may also ask the GMs a question, and if it is \textbf{common} knowledge, you will receive an answer.
	\item Leave the Library.
	\item Explore the Obsidian Corridor (turn to page~\pageref{ObsidianCorridor}).
	\item Read the Dedication Plaque at the entrance (turn to page~\pageref{LibraryDedication}).
	\item Descend the spiral staircase down to Tier 2 Hub (requires \textbf{CR 5} to overcome the wards; turn to page~\pageref{TierTwoHub}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Obsidian Corridor (Tier 1)}}\end{center}
\label{ObsidianCorridor}

A winding, dimly lit passage seemingly carved from solid obsidian branches off from the stacks, leading deeper underground. Reflections in the glossy stone make it hard to navigate or spot side passages. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
	\item Return to Tier 1 Hub (turn to page~\pageref{TierTwoHub}).
	\item Gaze at the dim reflections in the walls (turn to page~\pageref{AbyssGazesAlso}).
	\item Fumble your way further down the passage. If anyone in your group has an L-Score of at least 1, you may freely choose any of the options below without rolling. Otherwise, roll a d20.
	\begin{enumerate}
		\item If you roll a 7 or lower, turn to page~\pageref{ObsidianGreenhouse}.
		\item If you roll 8-13, turn to page~\pageref{HallofTinyDrawers}.
		\item If you roll 14 or higher, turn to page~\pageref{MeadowofBlackCrocuses}.
	\end{enumerate}
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Abyss Gazes Also (Tier 1)}}\end{center}
\label{AbyssGazesAlso}

You gaze into the dark reflections in the walls of the Obsidian Corridor. At first, nothing seems to happen. Then, it suddenly dawns on you that your reflection is staring back at you. Fear and bile rise in your throat as you lose all sense of time, rooted in place, the darkness gazing ever deeper into your soul. The reflections begin to shift, taking the form of your deepest doubts and fears\ldots{}

For the next two minutes, each person will continue to see their own doubts and fears in the walls of the passage. Role play accordingly. You may speak and act, but until the time has elapsed, you cannot leave this location. 

\textbf{If} you have encountered a mechanic that prompts you to search for ``glowing bricks,’’ look at ``\sBlueBrickEightEnvelope{}'' (if the envelope is not there, ignore this).

Once two minutes have passed, return to page ~\pageref{ObsidianCorridor}. 



\clearpage

\begin{center}\section*{\underline{The Obsidian Greenhouse (Tier 1)}}\end{center}
\label{ObsidianGreenhouse}

You pass through two pairs of glass doors and enter a muggy room full of bizarre plants. There are many plants in this room, some of which can be seen elsewhere on \pEarth{}, but some are completely unique to this space. These unique plants seem to grow from pots filled with volcanic rock, and everything from their stems to their flowers to their fruits seems to be made of obsidian.

Magical effects on the ceiling emulate the stars, the moon, the sun, and even weather patterns. In one corner, you can see a tiny thunderstorm raging.

Those unusual plants have \textbf{incredibly sharp edges} to their foliage. It would be easy to cut one’s self on the leaves if one is not being careful.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Search for something useful by checking ``\sObsidianGreenhouseEnvelope{}'' Each person in your group may remove 1 item of their choice from the envelope. Roll a d20; if the result is 5 or less, \textbf{one} person in your group cuts themself, losing 1 CR token until the next meal. \textbf{You may only choose this option once per visit to the Library.}
	\item Return to the Obsidian Corridor (turn to page~\pageref{ObsidianCorridor}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Hall of Tiny Drawers (Tier 1)}}\end{center}
\label{HallofTinyDrawers}

You find yourself in a room with shelves and shelves of tiny drawers, each containing minute supplies, from dried herbs to wooden fasteners. A great place to find small components you might need, but it could take a while to find. Why aren't any of the drawers labeled!?!

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Take an item from one of the drawers. Look through the items in ``\sHallOfDrawersEnvelope{};'' each person in your group may take 1 item of their choosing. \textbf{You may only choose this option once per visit to the Library.}
	\item Return to the Obsidian Corridor (turn to page~\pageref{ObsidianCorridor}).
	\item Open the tiny drawers in different combinations to see if anything interesting happens. Then:
	\begin{enumerate}
		\item If you have ever succeeded on the below roll, you may skip it and turn to page~\pageref{SecretPassage}.
		\item If you have not succeeded on this roll before, roll a d20 and add the highest L-Score in your group.
		\begin{enumerate}
			\item If the result is 14 or higher, you succeed and turn to page~\pageref{SecretPassage}.
			\item If the result is 13 or lower, nothing happens and you may not try again until you have \textbf{left the Library} and come back to this location.
		\end{enumerate}
	\end{enumerate}
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Library Dedication (Tier 1)}}\end{center}
\label{LibraryDedication}

A beautiful plaque hangs on the wall here, bearing the Library dedication, from when it was originally completed:

\vspace{0.5cm}

\begin{center}
``Those of us who built this space as a repository for all \pEarth{}n knowledge\\
Do henceforth dedicate this space to future generations.\\

May our skills, knowledge, and magical abilities\\
Be pillars of support, to raise them up to even greater heights.''\\
\end{center}

\emph{Turn to page~\pageref{TierOneHub}}

\clearpage



\begin{center}\section*{\underline{Tier 2 Hub}}\end{center}
\label{TierTwoHub}

The second tier of the Library lies deeper underground, housing some of the more dangerous volumes on magic and restricted lore. Green will-o’-the-wisps drift lazily through the stacks, providing light. Most people aren't allowed down here without a Librarian escort. Tread carefully. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Browse the stacks. Your \textbf{group} may ask the GMs one esoteric question under the following conditions: \textbf{You may only choose this option once per visit to the Library.} Spend 5 minutes role playing doing research. Then roll a d20 and add the highest L-Score in your group. If anyone in your group is a subject matter expert (e.g. a historian asking a history question), add 3. Lastly, add 1 per group member beyond the first.
	\begin{enumerate}
		\item If the result is 18 or higher, you will receive \textbf{an} answer (though not necessarily the answer you are looking for). 
		\item If you roll 1-6 (ignore modifiers), \textbf{one} person must draw a \textbf{random} Curse from ``\sCursedCodicesEnvelope{};'' they are now affected by the Curse they drew. 
		\item Otherwise, nothing happens.
	\end{enumerate}
	\item Return to Tier 1 Hub (requires CR 5 to overcome the wards; turn to page~\pageref{TierOneHub}).
	\item Visit the Curse Carrel (turn to page~\pageref{CurseCarrel}).
	\item Visit the New Philosophy Room (turn to page~\pageref{NewPhilosophy}).
	\item Wander deeper into the stacks (turn to page~\pageref{DeepStacks}).
	\item Descend the spiral staircase down to Tier 3 Hub (requires CR 10 to overcome the wards; turn to page~\pageref{TierThreeHub}).
\end{enumerate}
\endgroup

\clearpage


\begin{center}\section*{\underline{The Curse Carrel (Tier 2)}}\end{center}
\label{CurseCarrel}

The room here has a gold lettered sign reading ``Curse Carrel.'' Inside are dozens of bookshelves, packed to the ceiling with books on curses. From books of recipes to books on theory and design, there is no single place on \pEarth{} that has a greater collection of knowledge on curses. Those who pursue projects with \cPrince{\Heir} \cPrince{}, the cursemaking teacher, spend a lot of time in the little study desks scattered about the space. Most any answer you could have about cursemaking is probably in one of these books. You’d just have to find it. 



\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Browse the books. Spend 5 minutes at this location without taking any action other than conversation. You are now considered a ``subject matter expert'' on Curses. If you leave the Library, you lose this bonus. (Turn to page~\pageref{BookonGardening}).
	\item Return to Tier 2 Hub (turn to page~\pageref{TierTwoHub}).
	\item \textbf{If} you have encountered a mechanic that prompts you to search for ``glowing bricks,’’ look at ``\sBlueBrickElevenEnvelope{}'' If the envelope is not there, ignore this option.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{New Philosophy Room (Tier 2)}}\end{center}
\label{NewPhilosophy}

After the Old Philosophy Room was severely damaged in the Old Wing of the College, a new one was built in the Library, to house new treatises on many subjects. The College of the Gods boasts the most complete collections on Cengea of metaphysical writings, as well as theological theory regarding the nature of the Deities. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Browse the books. Spend 5 minutes at this location without taking any action other than conversation. You are now considered a ``subject matter expert'' on Theology and Metaphysics. If you leave the Library, you lose this bonus.
	\item Return to Tier 2 Hub (turn to page~\pageref{TierTwoHub}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Deep in the Stacks (Tier 2)}}\end{center}
\label{DeepStacks}

The bookshelves seem to go on forever in all directions. You can hear faint murmuring and rustling pages, but whenever you look, the noise stops. You could swear that some of the voices are whispering your name. Panic rises within you as it dawns on you that you aren’t sure how to get to the Tier 2 Hub. Out of the corner of your eye, you glimpse a small, nondescript door with a sign that reads, ``NO ADMITTANCE.'' In the opposite direction, you see a triangular door with the symbol of a spider carved on it; the hair on the back of your neck stands on end as you look at it, a palpable aura of fear is emanating from the doorway.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Try to find your way back to Tier 2 Hub. Roll a d20 and add the highest L-Score in your group: 
	\begin{enumerate}
		\item If the result is 11 or higher, turn to page~\pageref{TierTwoHub}.
		\item If the result is 10 or lower, turn to page~\pageref{LostintheStacks}.
	\end{enumerate}
	\item Pass through the doorway with the sign that reads, ``NO ADMITTANCE'' (requires an L-Score of at least 2, succeeding on a Difficulty 16 Lockpicking test, \textbf{or} CR 7; turn to page~\pageref{HallMisfiled}).
	\item Pass through the triangular doorway with a spider symbol on it (turn to page~\pageref{ChamberoftheFates}).
	\item Continue to wander aimlessly. Roll a d20 and add the highest L-Score in your group. 
	\begin{enumerate}
		\item If the result is 9 or higher, turn to page~\pageref{DeeperStacks}.
		\item If the result is 8 or lower, turn to page~\pageref{LostintheStacks}.
	\end{enumerate}
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{A Floral Portal (Tier 2)}}\end{center}
\label{FloralPortal}
You open the book to a beautiful illustration of a field of black crocuses. It is amazingly lifelike. As you gaze in admiration, it dawns on you that it is a little too lifelike. In fact, you feel a gentle breeze wafting from the pages, smell the flowers, and see them dancing in the wind. Suddenly, you are no longer holding the book, but are instead standing in that very field of flowers.

\vspace{0.5cm}

\emph{Turn to page~\pageref{MeadowofBlackCrocuses}}.

\clearpage

\begin{center}\section*{\underline{Secret Passage (Tier 1)}}\end{center}
\label{SecretPassage}

The floor suddenly opens up beneath you and you find yourself sliding down a dark tunnel. You lose track of time in the pitch blackness, until faint light appears ahead. You hear the grinding of stone and are blinded by the light of an opening racing towards you. Before you know it you are through and sprawling on the floor, the passage sliding shut behind you.

\vspace{0.5cm}

\emph{Turn to page~\pageref{NewPhilosophy}}.

\clearpage

\begin{center}\section*{\underline{The Chamber of the Fates (Tier 2)}}\end{center}
\label{ChamberoftheFates}

You find yourself in a strange, triangular room. Everywhere there are references to the number ``3,’’ and paraphernalia of spinning and weaving. In the very center of the room, on a low dais, rest some black wool, a set of hand carders to prepare wool for spinning, a drop spindle for spinning wool to thread, and a pair of gilt scissors. Above your head hangs a bizarre art installation. Thousands of threads of every color and material imaginable tangle and intertwine, leaving you with the sensation of a (poorly made) net about to drop on your head - or maybe a spiderweb. The thought sends a shiver down your spine, and you reflexively check the corners of the room for a lurking spider.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Go back through the triangular door (turn to page~\pageref{DeepStacks}).
	\item Use the items on the dais to spin some thread, then return them to the dais. Roll a d20 and add the highest L-Score in your group. If anyone in your group knows how to spin thread (most Children of the Sun do, but use your judgment), add 3. You may consume one Spiderweb per person in your group to add 3. 
	\begin{enumerate}
		\item If the result is 14 or higher, turn to page ~\pageref{SpinningThreadChamberofFates}.
		\item If the result is 13 or lower, you are unable to spin quality thread and nothing happens; you may not attempt this roll again until you have \textbf{left the Library} and returned to this location.
	\end{enumerate}
	\item Take the items on the dais and leave (turn to page ~\pageref{SpinningThreadChamberofFates}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Hall of the Misfiled (Tier 2)}}\end{center}
\label{HallMisfiled}

A long, dimly lit hallway stretches before you, both sides lined with piles and piles of books of every description. Many of them are in serious disrepair - titles faded, binding falling apart, pages damaged or missing. Beside the doorway, there is an ornate display case of rich, dark wood; it is full of what appear to be large lenses. There is a mournful aura to this place, the silence suffocating, the dust thick. The hallway stretches farther than you can see into the darkness, where a sense of foreboding lurks. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Exit the door to Deep in the Stacks (turn to page~\pageref{DeepStacks}).
	\item Press on down the hall, into the darkness and silence (turn to page~\pageref{IntotheDarkness}).
	\item Take a ``\iCrystalLens{}'' from the display case (remember Bulkiness rules). Each person in your group may remove \textbf{one} item from ``\sDustyCaseEnvelope{}.''
	\item If you have encountered a mechanic that prompts you to search for ``glowing bricks,’’ look at ``\sBlueBrickTenEnvelope{}'' If the envelope is not there, ignore this option.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{A Lonesome Volume (Tier 2)}}\end{center}
\label{LonesomeVolume}

You press on through the darkness, and gradually the hallway grows brighter. The passage opens into a small room with a plush, red carpet and luxurious desk and chair at the center, all covered in a layer of dust. The walls are lined with more piles of misfiled books, but they are in better condition than those at the entrance to the Hall of the Misfiled. On the desk, you glimpse a book you recognize, one that had personal significance to you in the past, and still does. It is a little worn, but perfectly legible. What’s more, you remember seeing an empty space in exactly the section it belongs in when you were Deep in the Stacks.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Keep the book. Feel free to make up a title and use some scrap paper to create an item card - it is \textbf{1-Hand Bulky}. Don’t let the Librarian catch you walking off with it, though.
	\item Take the book and go file it where it belongs on the shelves (turn to page~\pageref{RestoredRightfulPlace}).
	\item Go back down the hallway (turn to page~\pageref{HallMisfiled}).
\end{enumerate}
\endgroup

\clearpage



\begin{center}\section*{\underline{Tier 3 Hub}}\end{center}
\label{TierThreeHub}

The spiral staircase ends here. The third tier of the Library lies near the very heart of the floating island, housing some of the most dangerous volumes on magic and forbidden lore. Red will-o’-the-wisps drift lazily through the stacks, providing an eerie light. With only rare exceptions, no one is allowed down here unless they are with an experienced Librarian. More than a few people have disappeared or met their demise in the third tier. Tread carefully. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Browse the stacks. Your \textbf{group} may ask the GMs one esoteric question under the following conditions:\textbf{ You may only choose this option once per visit to the Library.} Spend 5 minutes role playing doing research. Then roll a d20 and add the highest L-Score in your group. If anyone in your group is a subject matter expert (e.g. a historian asking a history question), add 3. Lastly, add 1 per group member beyond the first.
	\begin{enumerate}
		\item If the result is a 16 or higher, you will receive \textbf{an} answer (though not necessarily the answer you are looking for). 
		\item If you \textbf{roll} 1-8 (ignore modifiers), \textbf{two} people in your group must \textbf{each} draw a \textbf{random} Curse from ``\sCursedCodicesEnvelope{}'' - they are now each affected by the Curse they drew. 
		\item Otherwise, nothing happens.
	\end{enumerate}
	\item Return to Tier 2 Hub (requires CR 10 to overcome the wards; turn to page~\pageref{TierTwoHub}).
	\item Follow the sound of running water (turn to page~\pageref{UpsideDownGrotto}).
	\item Wander deeper into the stacks (turn to page~\pageref{DeeperStacks}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Meadow of Black Crocuses (Tier 1)}}\end{center}
\label{MeadowofBlackCrocuses}

You enter an improbably huge chamber lit by skylights. Within it is an even more improbable scene - a vast field of black flowers, all crocuses from the looks of it. They appear to be real. A gentle breeze wafts through the cavern, sending ripples through the sea of dark flowers. A peaceful, if slightly eerie, scene.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Pick some of the flowers. Each person in your group may remove one item from ``\sBlackCrocusEnvelope{}'' \textbf{You may only choose this option once per visit to the Library}.
	\item Return to The Obsidian Corridor (turn to page~\pageref{ObsidianCorridor}).
	\item If you have encountered a mechanic that prompts you to search for ``glowing bricks,’’ look at ``\sBlueBrickNineEnvelope{}'' If the envelope is not there, ignore this option.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Deeper in the Stacks (Tier 3)}}\end{center}
\label{DeeperStacks}

The bookshelves seem to go on forever in all directions. Many of the books glow with an eerie light and are chained to the shelves. All around you, pages rustle, voices mutter, and chains clank as the restless codices strain against their restraints. You feel as though you are being watched - in some cases, literally, as some of these books have eyes that follow you as you pass. Voices beckon in all directions, murmuring enticements and secrets known only to you. Panic rises within you as it dawns on you that you aren’t sure how to get back to the Tier 3 Hub. You stumble upon an ornate door seemingly carved from a single block of white marble standing by itself, not attached to any wall; its center is carved in the shape of a diamond. At the end of a row of shelves, you see another door of rich, dark wood carved with symbols of the four Patron Gods. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Try to find your way back to Tier 3 Hub. Roll a d20 and add the highest L-Score in your group:
	\begin{enumerate}
		\item If the result is 14 or higher, turn to page~\pageref{TierThreeHub}.
		\item If the result is 13 or lower, turn to page~\pageref{LostintheStacks}.
	\end{enumerate}
	\item ``Open'' the white marble door with a diamond symbol in the middle of the room (turn to page~\pageref{WaxMuseum}).
	\item Open the wooden door with symbols of the Deities (turn to page~\pageref{HallofHeadlessGuardians}).
	\item Continue to wander aimlessly. Roll a d20 and add the highest L-Score in your group. If you have ever succeeded on this roll before, add 3.
	\begin{enumerate}
		\item If the result is 11 or higher, you succeed and turn to page~\pageref{StrangeEpigraph}.
		\item If the result is 10 or lower, turn to page~\pageref{LostintheStacks}.
	\end{enumerate}
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{A Book on Gardening? (Tier 2)}}\end{center}
\label{BookonGardening}

As you browse the books on Curses in the Curse Carrel, you stumble upon something out of place on the shelf - a book entitled \emph{Feeding a Little Life with Dried Tubers: A Gardener’s Guide to Bulbs}. A book on gardening in the Curse section? How odd. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Examine the book (turn to page~\pageref{FloralPortal}).
	\item Ignore the book (turn to page~\pageref{CurseCarrel}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Underground River (Tier 3)}}\end{center}
\label{UndergroundRiver}

You are swept along by an underground river, gasping for air every time you surface, bumping against rocks in the darkness. At last, you are disgorged into a small stream flowing through the Obsidian Greenhouse. You are wet, cold, and a bit bruised, but in one piece.

\emph{Turn to page ~\pageref{ObsidianGreenhouse}}

\clearpage

\begin{center}\section*{\underline{The Upside Down Grotto (Tier 3)}}\end{center}
\label{UpsideDownGrotto}

You find yourself in a small cavern filled with gently trickling waterfalls, the water dancing with iridescent color. The color is not all that is unusual about it - the water is flowing \textbf{up}, forming an underground lake on the ceiling. The spray from the waterfalls forms a fine mist, the droplets falling upwards in a gentle drizzle. The chamber is lit by softly glowing, bioluminescent mushrooms and ferns. There is a primeval energy to this place, an aura of boundless creation and rejuvenation. Perhaps a good place to rest. 


\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Rest and enjoy the calm of the grotto. For every five minutes you spend here, recover one lost CR token that has been lost in the library at any point.
	\item Go for a swim (turn to page\pageref{SwimminGrotto}).
	\item Eat one of the mushrooms (attempting to harvest them and remove them from the grotto will fail, as they immediately turn to mush if you take them from the chamber). \textbf{Each} person must draw a \textbf{random} Curse from ``\sCursedCodicesEnvelope{}'' they are each now affected by the Curse they drew. 
	\item Go through the narrow passage at one end of the cavern (turn to page~\pageref{TierThreeHub}).
\end{enumerate}
\endgroup

\clearpage


\begin{center}\section*{\underline{Swimming in the Upside Down Grotto (Tier 3)}}\end{center}
\label{SwiminGrotto}

The rushing, iridescent waters of the Upside Down Grotto are cool and refreshing. You find yourself enjoying them so much that you fail to notice getting swept up into one of the upside down waterfalls until it is too late. The current sweeps you into the lake on the ceiling of the cavern, where the whirlpool that drains the lake threatens to swallow you up.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Fight the current and swim for shore (requires CR 5; turn to page~\pageref{UpsideDownGrotto}).
	\item Follow the current and let the whirlpool pull you under. Roll a d20. 
	\begin{enumerate}
		\item If you roll 7 or lower, turn to page~\pageref{SlowBoatDarkRiver}.
		\item If you roll 8 or higher, turn to page~\pageref{UndergroundRiver}.
	\end{enumerate}
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Into the Darkness (Tier 2)}}\end{center}
\label{IntotheDarkness}

You walk down the dimly lit Hall of the Misfiled, flanked by heaps of dusty, crumbling tomes. The light gets fainter and fainter, until you are stumbling through total darkness. Suddenly, you feel something brush against your leg. You recoil just in time, hearing the snap of jaws closing on empty air. You are being attacked by Book Wyrms! Creatures of total darkness, they feed on decaying books of magic, but will also devour the magical energy of people if they can get it. 


\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Fight off the Book Wyrms (requires CR 9); you may consume one ``\iFlameOrchid{}'' per person in your group to gain +3 CR total for this fight. Then:
	\begin{enumerate}
		\item Press onwards down the dark hallway (turn to page~\pageref{LonesomeVolume}).
		\item Go back to the Hall of the Misfiled (turn to page~\pageref{HallMisfiled}).
	\end{enumerate}
	\item Fail to fight off the Book Wyrms. You are outmatched and forced to retreat, but not before the creatures drain some of your magical energy. \textbf{Each person loses one CR token until the next meal.} Turn to page~\pageref{HallMisfiled}.
\end{enumerate}
\endgroup

\clearpage


\begin{center}\section*{\underline{Spinning Thread in the Chamber of the Fates (Tier 2)}}\end{center}
\label{SpinningThreadChamberofFates}

You reverently take up wool, carders, drop spindle, and scissors from the dais in the Chamber of the Fates, and several minutes later, have a length of fine black thread to show for your efforts. As you place the items back on the dais, the thread you spun rises through the air and twines itself into the ragged tapestry or net above you. The aura of fear in the room eases, and you sense something almost akin to amusement. As you gaze at the ragged tapestry, it suddenly dawns on you that you can \textbf{see} the threads of destiny in its warp and weft, the intertwining of lives and choices. Your head swims, unable to contain the infinite yet unable to look away. Mercifully, the vision recedes, until you are left only with a firmer grasp of your own destiny.

\textbf{One} person in your group gains a ``Blessing of the Fates:'' Exactly once, when an instruction in this booklet tells you to roll a d20 and you do not like what you roll (low rolls are usually bad, high rolls are usually good), you may expend your ``Blessing of the Fates'' to reroll the die and choose which roll you want to keep. A group cannot have more than 1 ``Blessing of the Fates'' at a time. You lose your ``Blessing of the Fates'' the moment you leave the Library.

\vspace{0.5cm}

Turn to page\pageref{ChamberoftheFates}.

\clearpage

\begin{center}\section*{\underline{Looting the Chamber of the Fates (Tier 2)}}\end{center}
\label{LootingChamberofFates}

You take up the items on the dais in the Chamber of the Fates and move to leave. The temperature in the room drops precipitously, your breath visible and spiderwebs of frost forming on the walls. Before you can react, the netlike tapestry above you drops suddenly, tangling you in its warp and weft. The implements you stole rise from your hands into the air, spinning thread of their own volition, faster and faster. In the lashing thread you see visions - visions of your death, over and over again. Try as you might, you cannot break free of the net. All you can do is watch in growing horror as images of your doom flicker before your eyes.

\vspace{0.5cm}

\emph{For the next five minutes, everyone in your group is Restrained, and seeing the aforementioned visions. Role play accordingly. After the time has elapsed, the net releases you and you are violently ejected from the Chamber. You may not voluntarily enter the Chamber of the Fates again until your next visit to the Library. Turn to page\pageref{DeepStacks}.}

\clearpage

\begin{center}\section*{\underline{A Slow Boat on a Dark River (Tier 3)}}\end{center}
\label{SlowBoatDarkRiver}

You find yourself in a dark cavern with an underground river rushing through it. There is a small, stone dock where a half ruined boat is moored. The boat looks like it can barely float, and will only be good for one journey, if that. In contrast to the ramshackle boat, a set of polished silver double doors stand at one end of the cavern.


\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Pass through the silver double doors at the end of the cavern (turn to page 30).
	\item Attempt to pilot the rickety craft down the river. Roll a d20 and add the highest L-Score in your group. If anyone in your group has experience piloting boats (most Wave Riders do, but use your judgment), add 3. You may consume one Moonflower per person in your group to add 3.
	\begin{enumerate}
		\item If the result is 14 or higher, turn to page\pageref{ChamberofRelics}.
		\item If the result is 13 or lower, turn to page~\pageref{WetandBumpyRide}.
	\end{enumerate}
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{A Towering Tree (Tier 3)}}\end{center}
\label{ToweringTree}

You enter a brightly lit chamber, where a brilliant light is shining through a diamond shaped hole in the ceiling. Below it grows an improbably tall, spindly tree, bare of leaves and covered in red, tubular flowers. The flowers are slowly falling from the tree in a steady rain of crimson. Despite the beauty of the scene, there is an air of sorrow to this place.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Return to the Wax Museum (turn to page~\pageref{WaxMuseum}).
	\item Climb the spindly tree up to the hole in the ceiling (requires CR 12; you may consume 1 ``\iSunflower{}'' per person in your group to gain +3 CR total for this check; turn to page~\pageref{LightedPedestal}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Chamber of the Relics (Tier 3)}}\end{center}
\label{ChamberofRelics}

You reach a magnificent chamber, carved from solid bedrock in the College’s original gothic architecture. Glowing crystals of many hues jut from walls, bathing the room in a rainbow of light. The walls are decorated with stone reliefs depicting scenes from the founding of the College by the Gods themselves. There is a recent looking, large crack in the wall, through which a swift underground river is visible. Statues of the four Patron Deities stand at the center of the room, surrounding a pedestal upon which rests a richly carved wooden reliquary. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Spend 5 minutes studying the carvings on the wall. You are now considered a ``subject matter expert'' on the founding of the college. If you leave the Library, you lose this bonus. 
	\item Pass through the stone double doors at the entrance to the chamber (turn to page~\pageref{HallofHeadlesssGuardians}).
	\item Climb through the crack in the wall with the underground river and see where it takes you. Each person in your group separately rolls a d20. Then:
	\begin{enumerate}
		\item If you roll 11 or lower, turn to page~\pageref{WetandBumpyRide}.
		\item If you roll 12-17, turn to page~\pageref{UndergroundRiver}.
		\item If you roll 18 or higher, turn to page~\pageref{RiverofForgetting}.
	\end{enumerate}
	\item Open the reliquary. Examine the items in ``\sReliquaryEnvelope{}'' you may then:
	\begin{enumerate}
		\item Return the items to the envelope.
		\item Take one or more of the items (remember the Bulkiness rules).
	\end{enumerate}
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Lighted Pedestal (Tier 3)}}\end{center}
\label{LightedPedestal}

You enter a small, dim room, despite the brilliant light emanating from the opening you passed through to get here. The floors are covered with a deep, plush carpet, the walls are draped in curtains, and even the ceiling is hung with fabric. A single rune-infused light hangs down in the middle, illuminating only what is directly below it. In the center of the room sits a marble pedestal. On the pedestal is a green velvet cushion. On the cushion rests an ornate jewelry box. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Open the jewelry box and see what is inside. Look at the item in ``\sJewelryBoxEnvelope{}''
	\begin{enumerate}
		\item If you wish to take the item, do so.
		\item If you wish to leave the item, return it to the envelope.
		\item If the envelope is empty, turn to page\pageref{MemoryofLight}.
	\end{enumerate}
	\item Go back through the diamond shaped hole in the floor (turn to page~\pageref{TierThreeHub}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Wax Museum (Tier 3)}}\end{center}
\label{WaxMuseum}

At first glance, you seem to be in a crowd of people in an ornately carved, marble chamber with high ceilings, glittering chandeliers, and mirrors on the ceiling. But no one is moving. Closer examination reveals that the figures are uncannily lifelike wax statues. There are statues of some of the Avatars of the Gods too - Luminary’s hummingbirds and Ebb’s silver sea serpent. Carnival music is faintly audible wafting in from somewhere. The place has an aura of eerie stillness, yet you keep catching yourself glimpsing what you think is movement out of the corner of your eye. A shiver runs down your spine. Some of these statues are people you recognize - former teachers, students, and advisors at the College of the Gods who are not here today. Even likenesses of most of the 12 students who perished six years ago stand among the crowd of figures. One end of the chamber has double doors of silver, and the other end has double doors of copper. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Go through the silver doors (turn to page~\pageref{SlowBoatDarkRiver}).
	\item Go through the copper doors (turn to page~\pageref{ToweringTree}).
	\item \textbf{If} you have encountered a mechanic that prompts you to search for ``glowing bricks,’’ look at ``\sBlueBrickTwelveEnvelope{}'' If the envelope is not there, ignore this option.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Lost in the Stacks (Tiers 2 or 3)}}\end{center}
\label{LostintheStacks}

The murmuring of the tomes around you is a dull roar now, nor does it stop when you look. The books seem to be able to see into your very soul, your every secret laid bare. You are getting dizzy, your heart thundering in your ears\ldots or is that the roaring of the tomes? The floor rises up to meet you as the tide of panic engulfs you and everything goes black\ldots{}


\vspace{0.5cm}

\begingroup
\itshape
Roll your d20. Each person in your group must roll separately. Then:
\begin{enumerate}[A]
  \item If you rolled an odd number, draw a random Curse from ``\sCursedCodicesEnvelope{}'' you are now affected by this Curse. Then turn to the page number the die landed on. You can’t remember how you got to your new location; everything is hazy. 
	\item If you rolled an even number, you are \textbf{Knocked Out}. Turn to the page number the die landed on; this is where you will wake up. You can’t remember how you got to your new location; everything is hazy.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Restored to its Rightful Place (Tier 2)}}\end{center}
\label{RestoredRightfulPlace}

You make your way to the spot in the stacks where you believe the book is supposed to be filed and place it on the shelf. Its pages rustle, and you hear the words “thank you” in a voice like dry leaves that ripples outward through the stacks, a gentle susurrus of gratitude. The sound guides you out of the maze of shelves and back to Tier 2 Hub.

\textbf{One} person in your group gains a ``Tome’s Gratitude.'' As long as you have a ``Tome’s Gratitude,'' add +1 to your L-Score. \textbf{A group cannot have more than 1 ``Tome’s Gratitude'' at a time.} You lose a ``Tome’s Gratitude'' the moment you leave the Library. 

\vspace{0.5cm}

\emph{Turn to page~\pageref{TierTwoHub}.}

\clearpage

\begin{center}\section*{\underline{A Memory of Light (Tier 3)}}\end{center}
\label{MemoryofLight}

The jewelry box is filled with light - blinding, beautiful, almost tangible. It floods your senses. In the light you feel warmth, unconditional love, and unfathomable sorrow. Then the light fades, and you are standing once more before the Lighted Pedestal. The feelings take longer to fade. You have touched something powerful here, something pure, and it has left you with a gift.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item \textbf{One} person in your group gains a ``Memory of Light:'' Exactly once, when you turn to a page in this booklet and do not like what you see, you may \textbf{expend} your ``Memory of Light'' to ignore that page and return to the page you just came from.\textbf{ A group cannot have more than 1 ``Memory of Light'' at a time.} You lose your ``Memory of Light'' the moment you leave the Library.
	\item Turn to page~\pageref{LightedPedestal}.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{A Wet and Bumpy Ride (Tier 3)}}\end{center}
\label{WetandBumpyRide}

Well that didn’t go as planned; you encounter a series of rapids and soon find yourself swimming for your life. The current sweeps you along, banging you against rocks as you gasp for air. The river forks multiple times until you have no idea where you are. Eventually, you are able to fight your way to shore - battered, exhausted, and half drowned, but alive.

\vspace{0.5cm}

\begingroup
\itshape
Each person loses one item they obtained in the Library at any point in the past, not just from this trip (place it back in its original envelope; ask a GM if you don't remember which envelope it goes in). Each person loses one CR token until the next meal. Turn to page~\pageref{UpsideDownGrotto}.
\endgroup

\clearpage

\begin{center}\section*{\underline{The Hall of Headless Guardians (Tier 3)}}\end{center}
\label{HallofHeadlessGuardians}

You enter a long hallway lined on both sides with tall, headless suits of armor covered with gears, pistons, and glowing sigils. The mechanical guardians bear swords and spears crackling with magical energy. On the far end of the hall, you see another doorway. The moment you step forward, the guardians raise their weapons, blocking your path, and their sigils glow red.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Exit the way you came in (turn to the last page you were on, either~\pageref{DeeperStacks} or~\pageref{ChamberofRelics}).
	\item Talk your way through (requires someone with an L-Score of at least 3, that the current Principal be part of your group, \textbf{or} that at least one Cleric from each of the three nations be part of your group). Then:
	\begin{enumerate}
		\item Pass through the stone double doors (turn to page~\pageref{ChamberofRelics}).
		\item Pass through the wooden door (turn to page~\pageref{DeeperStacks}).
	\end{enumerate}
	\item Try to fight your way through (turn to page 36). Note: Being skilled in engineering will help.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Battling the Headless Guardians (Tier 3)}}\end{center}
\label{BattleHeadlessGuardians}

You engage with the mechanical warriors, bringing all your magical combat training to bear. You will need it -  they are powerful adversaries, their weapons moving with great speed and strength, unleashing torrents of magical energy. 

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Defeat the mechanical warriors (requires CR 15; if anyone in your group is an engineer [many from Free People’s Federation qualify, but use your judgment], add 3 to your CR total for this fight). You may then:
	\begin{enumerate}
		\item Pass through the stone double doors (turn to page~\pageref{ChamberofRelics}).
		\item Pass through the wooden door (turn to page~\pageref{DeeperStacks}).
	\end{enumerate}
	\item Be defeated by the mechanical warriors. Everyone in your group is \textbf{Knocked Out} and ejected from the hallway back to the room you came from (either page~\pageref{DeeperStacks} or~\pageref{ChamberofRelics}, whichever you last visited). Each person loses one CR token until the next meal.
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{A Strange Epigraph (Tier 3)}}\end{center}
\label{StrangeEpigraph}

You stagger onward for you know not how long, until deep within the bowels of the Library, your mind frazzled and hazy, you stumble upon a chipped and worn mosaic in the floor. Shaped like a sunburst and ringed by images of the Gods, the stacks radiate out from it like spokes on a wheel. At the center of the sunburst is a large tile of pure amethyst carved in the shape of a heart. Around the heart, dark tiles spell out a strange poem or epigraph:

\begin{center}
Spin thread like a spider\\
And behold endless tracks \\
\vspace{0.25cm}
Restore that which was lost\\
To its place in the stacks\\
\vspace{0.25cm}
Ascend the weeping tree\\
And receive sacred light\\
\vspace{0.25cm}
Then return to the heart\\
To descend into night\\
\end{center}

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Examine the heart shaped tile. Then:
	\begin{enumerate}
		\item Descend into night (requires expending \textbf{two} of the following three things: A ``Memory of Light,'' a ``Blessing of the Fates,'' and a ``Tome’s Gratitude;'' turn to page~\pageref{TierFourHub}).
		\item Otherwise, the tile wobbles slightly, but nothing else happens.
	\end{enumerate}
	\item Leave this place and brave the stacks once more (turn to page~\pageref{DeeperStacks}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{Tier 4 Hub}}\end{center}
\label{TierFourHub}

The amethyst heart at the center of the mosaic turns out to be an elevator that descends even deeper underground, below Tier 3. You find yourself in a natural cavern, its walls somehow fading upward into a starry night sky above. All manner of literary detritus is scattered around you - pens, ink pots, broken bookshelves, scraps of paper, leather bindings - but no actual books. There is even a shattered printing press heaped in the corner. The stars glimmer above, and there is a feeling of primordial energy in the air. You can hear the sound of rushing water down a side passage. Down another, you glimpse a swirling vortex of pages hovering in the air like a whirlwind.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Follow the sound of rushing water (turn to page~\pageref{RiverofForgetting}).
	\item Enter the vortex of pages (turn to page~\pageref{HeartoftheLibrary}).
	\item Step onto the amethyst heart and ascend back to the Strange Epigraph (turn to page~\pageref{StrangeEpigraph}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The River or Forgetting (Tier 4)}}\end{center}
\label{RiverofForgetting}

A vast underground river flows through this cavern, so wide you cannot see the other side. Stepping close to the river, you feel a strange but unmistakable mental sensation - memories could drift out of your mind here, leaving only confusion or peace in their place. You realize with a shock that this must be the legendary River Lethe which bears souls to the Underworld - the River of Forgetting.

\vspace{0.5cm}

\begingroup
\itshape
You may:
\begin{enumerate}[A]
  \item Scoop a handful of water from the river and drink it. Give up one memory you focus on, removing it completely and permanently from your mind.
	\item Scoop some water into a container (requires an ``\iGlassVial{}''). Water collected here will remove one memory when consumed - adjust the item card for the vial accordingly. This effect cannot be forced on another character against their will, as using it requires voluntary focus.
	\item Go for a swim.\textbf{ Be advised that this will have a permanent, major, game altering effect on your character.} If you still wish to do this, find a GM.
	\item Return to Tier 4 Hub (turn to page~\pageref{TierFourHub}).
\end{enumerate}
\endgroup

\clearpage

\begin{center}\section*{\underline{The Heart of the Library (Tier 4)}}\end{center}
\label{HeartoftheLibrary}

You stride up to the portal of swirling pages and let it engulf you. You expect to be buffeted by strong wind, but instead you just feel a soft tingling as your vision fills with dancing paper and script. When the pages part, you find yourself in a strange chamber composed entirely of books. At its center is one of the most beautiful things you have ever seen - a brilliant nexus of violet light, words and pages dancing through the air around it, the whole pulsing gently like a heartbeat. Words flow like lifeblood through veins from this focal point, out into the book-walls and beyond. You know instinctively that this is the Heart of the Library.

\vspace{0.5cm}

\begingroup
\itshape
You may reach out to the Heart and commune with the Library. Each individual does this \textbf{separately}.
\begin{enumerate}[A]
  \item If your intentions towards the Library and the School are \textbf{benevolent}, everything you have learned in reaching this point coalesces into a deeper understanding, and the Library gives you its blessing. You may:
	\begin{enumerate}
		\item Add \textbf{+2 to your L-Score}, permanently. You may ask the GMs one question about anything in game and you will receive \textbf{an} answer, though not necessarily the answer you are looking for. \textbf{You may only select this option once per game.}
		\item Turn the page to any location in the Library that you have previously visited, as you flow through the stream of words to your destination.
	\end{enumerate}
	\item If your intentions towards the Library and the School are \textbf{malevolent} (use your judgment), the Library senses this and rejects your communion. You are violently ejected to page 1. Note that there is no obvious way for anyone with you to know that you didn’t receive the Library's blessing and go there by choice.
\end{enumerate}
\endgroup

\clearpage

\end{document}
