\documentclass[white]{GL2020}
\parindent=0pt
\begin{document}
\name{\wWarlordResignationOfficial{}}

\emph{[This letter is sealed with the official seal of the Warlord, of which the Warlord has the only copy]}

\vspace{1cm}

\textsl{To the Members of the \pShip{} Diplomatic Delegation,}

\vspace{0.5cm}

\textsl{I, Captain \cLoud{\full}, write to inform you of my resignation from the position of Warlord, effective immediately. It has recently been brought to my attention that I have been laboring under a personality altering curse, now broken - a curse which warped my perception of Balance, clouded my judgment, and motivated me to swear vengeance upon the \pFarm{} and the \pTech{}, becoming the Warlord you have known.}

\textsl{But that is not who I truly am, or wish to be. I have had enough of the senseless bloodshed, nor do I see a future for our people in such violence. I have sent word of my resignation, and the reason for it, to the Fleets and the Council of Storm Watchers. While my deepest wish is for this war to cease, I am not so naive as to think that such is possible without a binding treaty, a task which I entrust to your capable hands. Regardless, I cannot be a party to the killing any longer.}

\textsl{Know that the Curse which changed me was not done out of malice, but a simple miscalibration. My own hubris is to blame - I sought the will to challenge the Council of Storm Watchers, whom I believed had failed us as a nation, and it went too far. For that, you have my deepest apologies. I cannot undo the past, but it is my hope that my resignation will help chart a better course for the future.}

\vspace{0.5cm}

\textsl{May \cEbb{} and \cFlow{} guide you safely to port,}\\
\textsl{\cLoud{\full}}

\end{document}

