\documentclass[white]{GL2020}
\parindent=0pt
\begin{document}
\name{\wWarlordResignationOfficial{}}

\emph{[This letter is sealed with the official seal of the Warlord, of which the Warlord has the only copy]}

\vspace{1cm}

\textsl{My Dearest \cWarlordDaughter{},}

\vspace{0.5cm}

\textsl{I cannot thank you enough for your letter, and the remedy you enclosed which has restored me to myself. My years as Warlord have been like a waking nightmare, a nightmare that has finally ended, thanks to you. I am resigning from the position of Warlord, effective immediately, and have sent word to the Fleets, the Council of Storm Watchers, and the \pShip{} advisors at the \pSc{} as well. While I have not forgiven the land dwellers for their betrayal, this path of violent retribution is wrong, and has been from the start. I cannot stop the war, but I will no longer be a part of it, and perhaps my resignation will aid the cause of peace.}

\textsl{You are probably wondering why in sea and sky we commissioned the curse from \cCurse{\full} to begin with. You know that we blamed the Council of Storm Watchers for the Betrayal of the other nations. \cQuiet{} and I requested the curse in an ill-advised bid to wrest political power away from the Council, but it worked too well, changed my personality too much. I never intended to become a warmonger, but whatever my intentions, the impact has been devastating.}

\textsl{I am so sorry for all the pain and turmoil this has caused you. I hope that you can someday forgive me. I have a great deal of atoning to do, both to you and to the world at large, and I hope that my resignation is a first step. I am as proud of you as a \cLoud{\parent} can be, my little \cWarlordDaughter{}. I know that you will continue to make us proud on this momentous occasion of the Time of Deciding, and send the Storm away from our people, who have suffered enough.}

\vspace{0.5cm}

\textsl{May \cEbb{} and \cFlow{} guide you safely home,}
\textsl{\cLoud{\full}}

\end{document}

