\documentclass[notebook]{GL2020} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nCreationTwo{}}

\begin{page}{first}
You are very interested in researching the creation of \pEarth{}. You have two allies in this investigation, \cEbbPriest{} and \cScholarship{}. Each of you has a different but related line of investigation that when combined all together should yield an exciting and interesting discovery. When the game starts, open \nbref{second}.
\end{page}

\begin{page}{second}
Search the 2nd Tier of the library for the ``New Philosophy Room’’. If possible, bring \cHistory{} along as their study of History may help provide important context. Once you find the ``New Philosophy Room’’ open \nbref{third}.
\end{page}

\begin{page}{third}
In pursuing these (fairly) modern treatises something stands out to you. \emph{(OOC: Read this part to anyone who helped you, e.g. \cHistory{}).} Many of the texts observe the ways in which the Deities are not so different from humans - they too are subject to strong emotions like jealousy and regret. \emph{(OOC: Stop reading here.}

Once \textbf{\cScholarship{}} has also opened page 3, discuss your findings with them for at least 2 minutes. Then open \nbref{fourth}.
\end{page}

\begin{page}{fourth}
Putting together the information you’ve found and the information that \cScholarship{} has found leads you to the next key question: What do we really know about where magic comes from, and what is it costing the Gods, physically and emotionally, to grant it to us? What could it mean that most of the energy feeding into the Ley Lines is coming from the Minor Gods? Bring a \iCrystalLens{} to the Ley Line Nexus in the Old Wing and gaze at the Ley Lines through it to see if you can gain any insights (it is not consumed). Once you have accomplished this, open \nbref{fifth}.
\end{page}

\begin{page}{fifth}
Gazing through a Crystal Lens at such a powerful concentration of magic is blinding, so it is hard to make out details, but you can see the Ley Lines that feed magic into the Nexus coming up out of the floor. As you gaze at those Ley Lines, you are overwhelmed with pain and anguish, sensations which seem to be filtered out by the Nexus itself. Wherever this magic is coming from, it is tainted with suffering. Spend five minutes meditating on your findings, then open \nbref{sixth}.
\end{page}

\begin{page}{sixth}
After some applied geometry, you calculate that based on the angle of the Ley Lines feeding power into the Nexus, they must be coming from somewhere deep within the floating island, beneath even the 3rd Tier of the Library. Bring a \iCrystalLens{} to “The Crackling Gates” (page 52) in the deepest part of the Library, study what you find there through the lens, and follow the instructions on that page and the ones that follow it (this will consume the \iCrystalLens{}). \emph{(OOC: This is a difficult location to reach alone, so you should bring your collaborators and anyone else willing to help.)} Once you have accomplished this, open \nbref{seventh}.
\end{page}

\begin{page}{seventh}
The shocking truth begins to emerge: The Minor Gods are imprisoned behind gates of crackling lightning deep within the floating island, their magical energy being siphoned off to fuel the Ley Line Nexus that in turn feeds magic to all of Cengea. What’s more, their pain and suffering seems to be fueling the chaotic and destructive energies of the Storm itself. But how did this come to be? Why was it kept hidden for so long? Once both \cScholarship{} and \cEbbPriest{} have opened page 7 of their notebooks too you can open \nbref{eighth}.
\end{page}

\begin{page}{eighth}
Tell \cHistory{} to open \cHistory{\their} “\mWTwo{}” - something about this investigation has jogged \cHistory{\their} memory with an important detail. Then, invite \cHistory{} to come discuss your findings with you and your fellow researchers ( \cScholarship{} and \cEbbPriest{}) and anyone else they wish to include.  Once everyone is assembled, open \nbref{ninth}.
\end{page}

\begin{page}{ninth}
Speculate with the assembled group about what all of your findings mean. Once you agree on a possible alternative creation story that incorporates the things you have discovered, go to the great hall, and lift the sign with the ``\sCreationMythOfficial{}'' on it. Read the sign below it, and reposition the ``\sCreationMythOfficial{}'' next to it, so both can be read freely by anyone.
\end{page}

\endnotebook

\end{document}

