\documentclass[notebook]{GL2020} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nCreationThree{}}

\begin{page}{first}
You are very interested in researching the creation of \pEarth{}. You have two allies in this investigation, \cEbbPriest{} and \cHeadScientist{}. Each of you has a different but related line of investigation that when combined all together should yield an exciting and interesting discovery. When the game starts, open \nbref{second}.
\end{page}

\begin{page}{second}
Conduct some experiment regarding the leylines and ambient magic. If possible, include \cDisney{} in the activity. They may notice something you don’t.

Access the ``\sLeyLinesNexus{}’’ in the Old Wing of the \pSc{}. Meditate here for 3 minutes. If possible, have \cDisney{} join in your meditation, or at least observe. \cDisney{\They} \cDisney{\have} a very different perspective from you and may notice something you don’t. Once you are finished meditating, open \nbref{third}.
\end{page}

\begin{page}{third}
In your meditation, you reach down into the very fabric of the world, sorting through the threads of divine essence. \emph{(OOC: Read this part to anyone who helped you, e.g. \cDisney{}).} We reach out for and find the essences of the 4 Patron Deities, and many, many minor deities, all of which are familiar in modern religious studies. However, At the very base of existence we find two threads we don't not recognize. These residual essences are from the very creation of \pEarth{}, but they are not from any part of the current pantheon. These lost Deities must be related to the creation of the world. But why were they lost? \emph{(OOC: Stop reading here.}

Once \textbf{\cHeadScientist {}} has also opened page 3, discuss your findings with them for at least 2 minutes. Then open \nbref{fourth}.
\end{page}

\begin{page}{fourth}
Putting together the information you’ve found, and the information that \cHeadScientist{} has found leads you to the next key realization: There must have been another Deity, who’s name is lost to time, who originally thought up the idea of creating Cengea. Can you learn anything more about them, or what happened to them? Open \nbref{fifth}.
\end{page}

\begin{page}{fifth}
More investigation is required. Visit \textbf{3 different locations} around the College. In each location, cleanse the space (you can do this as an initiate), or have someone else cleanse it while you watch. Cleansing should help remove any modern influences and give you a better sense of the various residuals. Concentrate on these mysterious residuals that don’t belong to any known deities. Once you have visited and cleansed the spaces, open \nbref{sixth}.
\end{page}

\begin{page}{sixth}
Spend the next 30 min contemplating what you have learned. You may do other things in the meantime, but you can’t open the next page until at least 30 minutes have elapsed. Once at least 30 minutes have passed, open \nbref{seventh}.
\end{page}

\begin{page}{seventh}
Through careful thought, you have coalesced the following ideas about the missing deities: One of the residuals that you have been investigating is the spark of creation, but it also resonates with forgiveness. The other residual is much colder, and harsher. It has a sharp edge to it that feels like it could cut your soul if you look at it wrong. It is hungry, and demanding, and you are not at all sure you like it.  Once both \cHeadScientist{} and \cEbbPriest{} have opened page 7 of their notebooks, you can open \nbref{eighth}.
\end{page}

\begin{page}{eighth}
Tell \cDisney{} to open their “\mWThree{\MyName}” - something about this investigation has jogged \cDisney{\their} memory with an important detail. Then, invite \cDisney{} to come discuss your findings with you and your fellow researchers ( \cHeadScientist{} and \cEbbPriest{}) and anyone else they wish to include.  Once everyone is assembled, open\nbref{ninth}.
\end{page}

\begin{page}{ninth}
Speculate with the assembled group about what all of your findings mean. Once you agree on a possible alternative creation story that incorporates the things you have discovered, go to the great hall, and lift the sign with the ``\sCreationMythOfficial{}'' on it. Read the sign below it, and reposition the ``\sCreationMythOfficial{}'' next to it, so both can be read freely by anyone.
\end{page}

\endnotebook

\end{document}
