\documentclass[notebook]{GL2020} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nTest{}}

\begin{page}{first}
This Fifth God, whoever they are, is trying to upend the power structure of the Divine realm. Surely there must be some way that someone as clever as you could benefit from the power vacuum that is about to be created. You just have to find your way into the inner circle of this Deity, which necessitates finding the circle. When the game starts, open \nbref{second}
\end{page}

\begin{page}{second}
You’ve actually already set the first step in motion by sending \cDisney{} to steal whatever \cDisney{\they} can from \cBunker{}. \cBunker{} is suspiciously well informed of many things, and hails from the \pShip{}. They could be a member of this group, or they might at least know something. Once you have an item with Item Number ``\iFolderOfNotes{\MYnumber}’’, open \nbref{third}
\end{page}

\begin{page}{third}
Damnit. Naturally it's in code. It is much, much faster to decode things like this with help from other scholarly, analytical minds. Get at least one of \cAssistantScientist{} and \cHeadScientist{} to help you decode this. If 1 of them helps you, roleplay deciphering the code for 10 minutes. If both of them help, this will only take 5 minutes instead. Be aware that whoever helps you will learn the same things you do. Once the time has elapsed, open \nbref{fourth}
\end{page}

\begin{page}{fourth}
\emph{(OOC: Read this part aloud; to anyone who helped you decipher the code.)} The notes speak of a group called the ``Followers of Genesis'' - a heretical cult that worships \cGenesis{}, the \cGenesis{\God} of luck, instead of one of the Patron Deities. They further speak of a spy network being compromised by these Followers. \emph{OOC: stop reading aloud here.}

Well, it’s not the complete answer you might hope for, but then that would make this too easy. At least you know that \cBunker{} isn’t one of the Followers. They are definitely a spy. And maybe an ally? Now that you have the name  ``Genesis’’ at least, you can ask the Clerics about it. Once you have asked at least 1 Cleric from each of the 3 nations about this Fifth God, open \nbref{fifth}
\end{page}

\begin{page}{fifth}
You maybe have a little bit more information now. But time is running out. It’s time to get your own hands dirty. You've got to find a way to get yourself inducted into the cult. It’s the only way you’ll get more information. If you haven’t found any leads yet, maybe you could buy some information on the black market? Once you have been inducted into the cult, open \nbref{sixth}
\end{page}

\begin{page}{sixth}
Okay, you’re in, but not surprisingly, the Followers operate in a cell based structure. Not everyone knows everything. Find the highest ranking Follower you can, and either use a \iHonesty{} on them (which naturally you’ll need to acquire first) or the \iLariat{} to compel a true answer to the question ``What are you really up to this weekend?’’ (remember that the \iLariat{} can only be used to compel truth if it is currently attuned to somewhere.) Once you have an answer to this, open \nbref{seventh}
\end{page}

\begin{page}{seventh}
Well that’s certainly\ldots{} a bold move. All that’s left for you to decide is whether you can somehow use this to your benefit, or if it’s time to admit that there are some schemes with too high a risk, or too uncertain a reward, even for you. If you determine that is the case, you should probably try to stop them, or at least tell someone.
\end{page}

\endnotebook

\end{document}
