\documentclass[notebook]{GL2020} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nRestoreMemories{}}

\begin{page}{first}
\cDisney{} has mentioned on several occasions that \cDisney{\they} cannot remember important things around the time \cDisney{\they} \cDisney{\were} put to sleep. \cTechStar{} has been researching a method to help restore \cDisney{}’s memories with science (and magic)! This research notebook is for those assisting with those efforts. At game start, \cDisney{} has 2 copies, and \cTechStar{} has 1 copy. If the two characters choose to, they can give the extra copy to \cWildCard{} to bring them in on this work. At any point, characters who have this notebook can compare notes and open pages to match if one person has opened more pages than the other. Collaborating to accomplish steps is likely to be to your benefit. When the game starts, open \nbref{second}
\end{page}

\begin{page}{second}
The most well known cause of memory loss is punishment from the Deities for murder. But the scope of things \cDisney{} has forgotten is so small and specific, it can’t possibly be the same thing. Ask at least 5 people if they know of any other reason why someone might lose memories. When you’re done asking, open \nbref{third}
\end{page}

\begin{page}{third}
Not a lot of leads, but maybe the Library holds the answer? Go to ``The Catalog of Esoterica'' in the 3rd Tier of the Library, consume 1 Stone Flower there as an offering to Verit, minor god of remembrance and written knowledge (this will also give you “Subject Matter Expert” status), and \textbf{complete} a research inquiry into amnesia and ways to treat it. Once you’ve accomplished this, open \nbref{fourth}
\end{page}

\begin{page}{fourth}
You found a lead! ``The River of Forgetting’’ is on a partial list of the wonders accessible somewhere in the deepest part of the Library. You think a sample of the water will actually be key to \textbf{restoring} \cDisney{}’s memories. In order to get some, you’ll need a ``\iGlassVial{}’’. Take the vial to the ``River of Forgetting’’ in the in the deepest part of the Library. Label the vial as having water from the ``River of Forgetting.’’ . Once you’ve accomplished this, open \nbref{fifth}
\end{page}

\begin{page}{fifth}
Next you need to change the nature of the water from Forgetting to Remembering. Bring the vial filled with water from the River of Forgetting to Prometheus’ Flame in the Old Wing of the \pSc{}. Heat the vial over the flame for at least 30 seconds. Then, open \nbref{sixth}
\end{page}

\begin{page}{sixth}
Take the vial to the garden. Bury it in the dirt by placing it in ``Sign-M’’ in the garden. (There is another item in the envelope; ignore it for now.) The effect developing in the vial needs at least 30 minutes to mature. Once the time has elapsed, open \nbref{seventh}
\end{page}

\begin{page}{seventh}
You may now retrieve the vial and the ``\iMemoryCure{}’’ item from ``\sSignM{}’’ in the garden. Return the vial item card to the nearest stock; it has been transformed into what you hope will restore \cDisney{}’s lost memories. Apply a symbol or design to one corner of the item envelope. This is your maker’s mark. Don’t use anything you’ve seen on other curses, or anything that makes it obvious it is your mark (e.g.: don’t use your character or player signature.) Roleplay emptying the contents of the ``\iMemoryCure{}’’ over \cDisney{}, then tell them OOC to open their ``A Packet.’’ Fingers crossed this works! (Return the ``\iMemoryCure{}’’ item to the nearest stock after this; it has been used up.)

\end{page}

\endnotebook

\end{document}

