\documentclass[notebook]{GL2020} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nReverseMindWipe{}}

\begin{page}{first}
A cold sensation washes over your body. What was that? A curse? Like grains of sand through an hour-glass, you can feel your memories starting to slip away. No big, important memories will be lost until post-game, but you should still act forgetful and distractible (as though your short term memory is compromised).

Surely you can try to reverse this? This isn’t how the Deities’ amnesia works, and you definitely didn’t kill anybody just now. Get a cleric to examine you for 30 seconds, then open \nbref{second}
\end{page}

\begin{page}{second}
\emph{(OOC: Read this part out loud to the cleric who examined you)} This is definitely a memory curse of some kind. You aren’t familiar with it, so it is probably someone’s personal creation. Regardless, it seems to cause a degradation of memory that will accelerate over the next few days if not stopped. After 72 hours it will be irreversible. But you don’t know how to stop it. \emph{(Stop reading out loud here.)}

You will need to research a cure. Go to the ``Curse Carrel’’ in the Mid-Tier area of the library and search through the books there for 3 minutes. This should allow you to learn a little about the theory behind curse and cure creation, and the types of ingredients that might accomplish what you want. \textbf{You must bring at least one cursemaker along with you} to help explain what you find. Once you have completed the research, open \textbf{page 3}. \nbref{third}
\end{page}

\begin{page}{third}
\emph{(OOC: Read this part aloud; to anyone who helped you research.)} The work of cursemaking hinges both on the inherent properties of the ingredients used, and the intentions imbued by the maker. While a true panacea that would reverse \textbf{any} curse cannot be constructed, it is possible to make something very close. \emph{The rest of the page is badly smudged; making it impossible to read. OOC: stop reading aloud here.}

It seems that \cTechGod{} has noticed your plight. In the sudden inspiration of a well-stocked Maker’s Space, the knowledge of \cTechGod{} enters your mind. To create a Cure that will help you reverse this mind-wipe:
\begin{enumerate}
	\item Collect the following ingredients: \iFish{}, \iCharcoal{}, and \iSight{}
	\item  Obtain a sample of your own blood (you will need to find a mechanic to do this) to lock the intention of the cure, so no one can use it for something else.
\end{enumerate}

Once you have the four things you need, open \nbref{fourth}
\end{page}

\begin{page}{fourth}
Get a cursemaker to make you a ``\iPanacea{}'' by using the three items plus the sample of your blood. They must be skilled enough to create curses that use 4 components, so \cPrince{} or \cCurse{} are your best bets. (creating the cure will destroy the individual components). The cure will take \textbf{2 hours} to brew (They have a mechanic that says that someone else can bring them a recipe to make a cure they don’t otherwise know how to make for just such a situation as this). Once you have the Cure in hand, open \nbref{fifth}
\end{page}

\begin{page}{fifth}
Activate the cure on yourself (the normal effects of this cure don't apply for this mechanic). Then reach the ``River of Forgetting’’ in the ``4th/Extreme Tier’’ of the Library. Wash your hands in the water. As long as you don’t drink any of it, it should only carry away the remnants of this Curse, not actually take any memories from you. -- Once that is done, you can rest assured that the curse is neutralized. But why would someone try to do that to you?

\end{page}

\endnotebook

\end{document}
