%%%%%
%%
%% This file sets up the Mem, MemFold, and MemEnvelope datatypes, and
%% creates possible macros for each.
%%
%% The Mem datatype isn't really used directly; it's there so the
%% other datatypes can inherit and share its code.
%%
%%%%%

\DECLARESUBTYPE{Mem}{Element}
\PRESETS{Mem}{
  %% \MYname is the trigger
	\FD\MYtrigger{}
  \F\MYtext	%%  text
  }


%%%%%
%% MemFold and MemEnvelope are both subtypes of Mem.  MemFold is for
%% fold-n-staple style mempackets, MemEnvelope is for stuff-n-seal
%% style mempackets.  If you want a mempacket to contain interesting
%% contents, like sheets, abilities, and other mempackets, use a
%% MemEnvelope.
\DECLARESUBTYPE{MemFold}{Mem}
\DECLARESUBTYPE{MemEnvelope}{Mem}


%%%%%
%% MemCover and MemPage are for the cover and pages of mempacket
%% booklets, which resemble research notebooks.  These are good
%% substitutes for large piles of MemFolds, and can be useful for
%% things like amnesiac characters.
%%
%% Like MemFolds, MemPages shouldn't directly own any other elements
%% as contents.  Use MemEnvelope instead.
%%
%% MemPages are usually assigned to a MemCover (via \MYmems), with the
%% MemCover representing the entire booklet and assigned to a
%% character.
%%
%% A MemCover is not a mempacket in and of itself; its name is not its
%% trigger and its text is not a memory.
\DECLARESUBTYPE{MemCover}{Mem}
\PRESETS{MemCover}{
  \sd\MYtext	{Each page is a memory/event packet with a separate
		trigger.}
  }

\DECLARESUBTYPE{MemPage}{Mem}


%%%%%
%% \memfold{<trigger>}{<text>}
%% \memenvelope{<trigger>}{<text>}
%% \memcover{<name>}{<pages>}
%% \mempage{<trigger>}{<text>}
%% \startmembook{<name>} <pages> \endmembook
%%
%% These are wrappers around \INSTANCE, useful as 1-shots.
%% \startmembook...\endmembook is a simple wrapper around \memcover
%% that may have better syntax for use within character sheets (inside
%% a \starttag{mems}...\endtag block).
\newinstance{MemFold}{\memfold[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemEnvelope}{\memenvelope[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemCover}{\memcover[2]}{
  \s\MYname{#1}\s\MYmems{#2}}
\newinstance{MemPage}{\mempage[2]}{
  \s\MYname{#1}\s\MYtext{#2}}

\long\def\startmembook#1#2\endmembook{\memcover{#1}{#2}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{MemFold}{\mTest}{
  \s\MYname	{Test Trigger}
	\s\MYtrigger {Open if you see a red handkerchief.}
  \s\MYtext	{This is a Test of a fold-n-staple memory packet}
  }
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{MemEnvelope}{\mPacketA}{
  \s\MYname	{Packet A}
	\s\MYtrigger {Do not open unless directed to do so.}
  \s\MYtext	{You are suddenly flooded with memories and sensations. \textbf{Fall unconscious for 5 minutes.} You can use that time to read the rest of the stuff inside this packet.

\emph{In your unconscious state, the following memories and knowledge flood into you.}

It's dim, and warm. You're underground. No, you're in a huge stone room. Every door is blocked by heavy stones. There are many people here. You can't see them distinctly. But you hear the rustle of cloth. And a sense of anticipation. Your own heart beats fast with excitement. The candle-light flickers. There must be hundreds of ritual candles everywhere. They contribute to the heat and the stuffiness. Excited whispers flow across the room and then fall silent as the head Cleric of the Aethers steps into the center of the room, into the center of the ritual circle. They hold an oak staff in one hand, and a crystal vial filled with a clear liquid in the other.

This is it. You're going to the Realm of the Gods. You are going to talk to \cFarmGod{} face to face. See the great tree where the hummingbird avatars rest between missions. Walk where no human has walked since time immemorial when the Deities were forced to sever the connection between the material plane and the Divine Realm. The Aethers have been preparing for this moment for years. A massive, exhausting (and very illegal according to the mainstream church) ritual to journey to the Divine realm. 

The ritual begins. The magical energy builds as the group chants and sways. Sweeping your spirit up in a vortex of jubilation. You lose track of time. How long has it been? Minutes? Hours? Days? You watch as the leader of the Aethers upends the contents of the vial into a clay bowl. It's really happening.

And then there is a massive crashing sound! Utterly discordant with the power of the Aethers. A crack appears in one of the stones used to seal the doorways. Another massive crash. More cracks, this time in more of the seals. You're surrounded. Trapped.  The crowd of Aethers is thrown into chaos. The magical energy spins out of control. Any hope of reaching the Divine Realm shredding before your eyes. The stones give way. People you don't recognize enter the chamber from every direction. They point their wands and staves at the wall, the ceiling, and the floor. Thunderous blasts shatter the structure. Chunks of stone start to rain from the ceiling. There is nowhere to run. Nowhere to escape to. Your friends, your family, are being hurt, being killed\ldots{}

As you stare in horror,  \cDisneyMentor{} grabs your shoulder and pulls you away, through a secret passage. \cDisneyMentor{\They} close\cDisneyMentor{\plural} the doorway behind you, sending a quick muttered prayer to \cFarmGod{} that no one saw in the chaos. Down toward the crypt the two of you hurry. \cDisneyMentor{\They} pull\cDisneyMentor{\verbs} you toward a glass coffin. ``Here'' \cDisneyMentor{\they} say, ``You must come here. I'm going to put you into a magical sleep. Hopefully they will think you don't know anything and leave you be.'' ``But what about you?'' you whisper, tears filling your eyes. ``Don't worry about me,'' \cDisneyMentor{} replies soothingly. As you lay down in the coffin, \cDisneyMentor{} kisses your forehead. A feeling of warmth and peace flows over you, washing away the memories of this dreadful night, and the knowledge of the Ritual to reach the Divine Realm. ``Sleep well, child'' \cDisneyMentor{} whispers. ``May you wake in a more tolerant time.''

\emph{When you wake from being unconscious you will remember all of this, and have access to the ``\gRitualDivineRealm{}'' greensheet included in this packet.}
}
	\s\MYgreens {\gRitualDivineRealm{}}
  }

\NEW{MemFold}{\mCPacket}{
  \s\MYname	{C-Packet}
	\s\MYtrigger {Do not open unless directed to do so.}
  \s\MYtext	{You have been cursed, by some sort of degenerative curse. You don't feel well. Act wobbly and disoriented for \textbf{5 minutes}. \emph{You no longer regenerate magical energy at meal times - if you put a unit of magical energy into an item of Tass, or use it for some other mechanic, it is gone forever.} Over the course of months your body will waste away and you will die unless you can find a cure. \textbf{The only cure to a curse this intense must lie with the one who cast it.} Find them if you want to reverse it.}
}

\NEW{MemEnvelope}{\mPacketThree}{
  \s\MYname	{Packet 3}
	\s\MYtrigger {Open when you meet the requirements listed in ``\gPunishKidnappers{}.''}
  \s\MYtext	{These curses you have managed are actually really complex. There is no ``graduating'' from a basic cursemaker to an advanced one, but there is no denying your skill now. You are now able to create curses that require $>$2 ingredients, as reflected in your new greensheet (included here-in).}
  \s\MYgreens	{\gCursemakingAdvanced{}}
}

\NEW{MemFold}{\mParent}{
  \s\MYname	{Parent?}
	\s\MYtrigger {Open if/when you find and talk to your parent for at least 2 minutes.}
  \s\MYtext	{Your vision blacks out and you faint - go unconscious for 5 minutes and read the rest of this packet in the meantime. 

\emph{You are overcome with a vision from a Deity. The self-same one from your dream. This time they reveal themselves -- it's Luminary, the Deity of the Children of the Sun. And on either side of them, Ebb and Flow. “Justice!” they scream, so loud you can barely hear it. “Balance,” they whisper, so quiet it nearly deafens you. What has your parent done that is in such desperate need of penance? When you regain consciousness, you remember this dream perfectly.} }
}

\NEW{MemFold}{\mWOne}{
  \s\MYname	{W Packet}
	\s\MYtrigger {Do not open unless directed to do so.}
  \s\MYtext	{Some scholars have observed an almost angry or rueful tone in \cTechGod{}'s teachings around respecting intellectual property, an almost sorrowful tone in \cFarmGod{}'s teachings around refraining from violence, and an almost defiant tone in \cEbb{}'s and \cFlow{}'s teachings around Balance and repaying others in kind. When it comes to the universal prohibition against murder, a few scholars have noted a hint of regret in the teachings of the Patron Gods. While many theories abound, none really resonate with the \textbf{full truth} yet.}
}

\NEW{MemFold}{\mWTwo}{
  \s\MYname	{W Packet}
	\s\MYtrigger {Do not open unless directed to do so.}
  \s\MYtext	{In some of the oldest, most obscure histories, there are references to ``The Wars of the Gods'' from before the dawn of time — a series of cataclysmic conflicts that shaped the Cengea we know today, including forming the mountain range known as the Bones of the World. The references are fragmentary and vague, but every war has its winners and losers. What if those now known as the Patron Gods were the victors of those conflicts, and those now known as the minor gods were the losers?}
}

\NEW{MemFold}{\mWThree}{
  \s\MYname	{W Packet}
	\s\MYtrigger {Do not open unless directed to do so.}
  \s\MYtext	{In some of the earliest known religious writings, there are references to \pEarth{} as the ``Corpse of the Creator.'' They were always assumed to be metaphorical or mistranslations, but what if they are literally true?}
}

\NEW{MemFold}{\mLuca}{
  \s\MYname	{Why do they look familiar?}
	\s\MYtrigger {Open if you see badge number \cAssistantScientist{\MYnumber}}	
  \s\MYtext	{That person looks awfully familiar. They remind you of someone. But no, it couldn't be. Could it? They look very much like \cKidScientist{\full}. \cKidScientist{\They} did have family in the \pTech{}, but not by the name \cAssistantScientist{\formal}\ldots{}}
}

\NEW{MemFold}{\mGreenHeadband}{
  \s\MYname	{It Can't Be!}
  \s\MYtrigger {Open if you see a BLUE headband.}
  \s\MYtext	{Oh my Deities, it's \cKidScientist{}!! Six years older, sure, but it is, without a doubt, \cKidScientist{\them}. How in the world did \cKidScientist{\they} survive?}
}

\NEW{MemFold}{\mSisterMemory}{
  \s\MYname	{Who is that?}
  \s\MYtrigger	{Open if you complete the ritual to look into the past and learn what happened to your sister (read ``\sSignJTwo{}’’ first).}
  \s\MYtext	{You recognize the young woman in \cWildCard{\formal} colors as your sister, Lorraine. The young \cHedonist{\person} in \cHedonist{\formal} colors is clearly a young \cHedonist{}.}
}
	
	
%%%%%%%%%%%%% Mem Books %%%%%%%%%%%%%%%

\NEW{MemCover}{\mLibMemories}{
  \s\MYname	{Who AM I?}
  \s\MYmems	{\mLibOne{}\mLibTwo{}\mLibThree{}\mLibFour{}\mLibFive{}\mLibSix{}\mLibSeven{}\mLibEight{}\mLibNine{}}
  }

\NEW{MemPage}{\mLibOne}{
  \s\MYname	{Open at the Beginning of Game.}
  \s\MYtext	{The amnesia weighs on you. How can you remember nothing from before the last school break? Nothing at all? You can only hope that earnest appeals to \cTechGod{} will change \cTechGod{\their} mind and restore some of your memories. \cTechGod{} deeply values hard work, so a lot of your plans involve the Library. \emph{(OOC: You may take actions based on the triggers in this book. This is a deviation from normal for mem-books.)}}
}

\NEW{MemPage}{\mLibTwo}{
  \s\MYname	{Spend 5 minutes in private meditation with Kero in the Temple to plead your case.}
  \s\MYtext	{A brush of power fills you with hope. \cTechGod{} is listening to you. Surely this means there's a chance?!?}
}

\NEW{MemPage}{\mLibThree}{
  \s\MYname	{Visit five different locations in the 1st Tier of the library. Also find the location ``A Lonesome Volume'' in the 2nd Tier of the library, and earn a ``Tome's Gratitude.''}
  \s\MYtext	{Increase your L-Score by 1. Your memory of the 1st Tier of the library returns in near complete detail. You may now freely review the 1st Tier locations without actually traversing them. You may look at any/all of them.}
}

\NEW{MemPage}{\mLibFour}{
  \s\MYname	{Spend at least five minutes having a deep, personal conversation with Milfoil Du'Pond.}
  \s\MYtext	{This feels nice. This feels familiar. The two of you must have been very close before you lost your memories. You get a flash of sitting just like this, only you are holding hands and gazing into each other's eyes. The memory sets your heart aflutter, and you find yourself wanting to get more reacquainted with \cInterpol{}.}
}

\NEW{MemPage}{\mLibFive}{
  \s\MYname	{Find the location ``The Catalog of Esoterica'' in the 3rd Tier of the library and consume 1 Stone Flower there as an offering to Verit, minor god of remembrance and written knowledge.}
  \s\MYtext	{Increase your L-Score by 1. Your memory of the 2nd Tier of the library returns in near complete detail. You may now freely review 2nd Tier locations without actually traversing them. You may look at any/all of them.}
}

\NEW{MemPage}{\mLibSix}{
  \s\MYname	{Find the location ``The Heart of the Library'' in the 4th Tier of the library, reach out to the Heart, and commune with the library.}
  \s\MYtext	{Increase your L-Score by 1. Your memory of the 3rd Tier of the library returns in near complete detail. You may now freely review 3rd Tier locations without actually traversing them. You may look at any/all of them.}
}

\NEW{MemPage}{\mLibSeven}{
  \s\MYname	{Engage in conversation with Milfoil Du'Pond and at least 2 other people (doesn't have to be the same conversation) about the \textbf{other} people's current romantic situation or prospects.}
  \s\MYtext	{Talking about romance makes you smile, and you realize that you are a bit of a hopeless romantic. Ideas like ``soulmates'' speak to you. The kind of tooth-rotting fluff that would make others gag simply sets your heart aflutter. Your heart seems to be aflutter a lot around \cInterpol{}. Surely you are not falling in love with \cInterpol{\them} already? Could this feeling be a memory? Or is that just wishful thinking? }
}

\NEW{MemPage}{\mLibEight}{
  \s\MYname	{Attack someone you legitimately believe to be a pirate (you do not need to succeed in upstaging or knocking them out, but you can't just make up a reason you believe someone to be a pirate. You must find something that constitutes reasonable suspicion.)}
  \s\MYtext	{You see a house on the shore. Judging by the sun, it must be on the northern coast of the continent of \pEarth{}. The house looks familiar; feels familiar; two people smile at you from the doorway - your parents? Sails on the horizon draw your attention. Pirates! The ship drives a sea serpent toward the shore. Toward  your home. You blink. Rowboats have beached near you. A dozen pirates disembark, and start to drive the sea-serpent inland. One notices your parents, and starts to shout for the others. You blink again. Your mother is washing blood off your hands, trying to soothe you, reassuring you that you had no choice, that you saved her and your father's lives. It's no easy task since your hands shake uncontrollably. Out the kitchen window, you see your father buries something in the backyard}
}

\NEW{MemPage}{\mLibNine}{
  \s\MYname	{Go on a date with Milfoil Du'Pond. It could be as simple as sharing a private meal or going for a moonlit stroll together in the garden.)}
  \s\MYtext	{Memories come flooding back. Your long, passionate conversations about music, the preservation of knowledge, and what makes a just society. \cInterpol{}'s startling confession that \cInterpol{\theyare} an undercover operative from the \pFarm{}here to hunt down a heretical cult that threatens the very fabric of society, and \cInterpol{\their} growing doubts about \cInterpol{\their} mission. You were surprised, but felt honored by the trust \cInterpol{\they} had placed in you, and promised to keep \cInterpol{\their} secret. A deepening friendship built on caring, mutual trust, and love of learning. A lingering look here, a touch there, the seamless transition from deep friendship to romantic love. Your first kiss in the Meadow of Black Crocuses in the library. There are still pieces missing, but you know now that the two of you were in a relationship. And still are? It's confusing, but in a nice way. You'd better talk it over with \cInterpol{} and figure out how you want to move forward.}
}	
  
%%%%%%%
  
\NEW{MemCover}{\mIdleThoughts}{
  \s\MYname	{Idle Thoughts}
  \s\MYmems	{\mIdleOne{}\mIdleTwo{}\mIdleThree{}\mIdleFour{}\mIdleFive{}\mIdleSix{} \mIdleSeven{}\mIdleEight{}}
}

\NEW{MemPage}{\mIdleOne}{
  \s\MYname	{Page 1; do not open until directed to do so.}
  \s\MYtext	{You aren't one to drift off into daydreams, but you just had quite the vivid daydream of the ``River of Forgetting.'' How odd.}
}

\NEW{MemPage}{\mIdleTwo}{
  \s\MYname	{Page 2; do not open until directed to do so.}
  \s\MYtext	{This feels familiar, this feels comfortable. \cChupAvenger{} is really easy to talk to.}
}

\NEW{MemPage}{\mIdleThree}{
  \s\MYname	{Page 3; do not open until directed to do so.}
  \s\MYtext	{It's nice to have help sometimes. And the way \cChupAvenger{\they} lit up when you said ``thank you.'' Like the sun breaking through clouds. It warms your own heart in return. You feel like you're on the same wavelength with \cChupAvenger{} even though you just met\ldots{}}
}

\NEW{MemPage}{\mIdleFour}{
  \s\MYname	{Page 4; do not open until directed to do so.}
  \s\MYtext	{Talking about romance makes you smile. You've always been a bit of a hopeless romantic. Ideas like ``soulmates'' and ``love at first sight,'' always spoke to you. The kind of tooth-rotting fluff that would make others gag simply sets your heart aflutter. Your heart seems to be aflutter a lot around \cChupAvenger{}. Surely you are not falling in love with \cChupAvenger{\them}?}
}

\NEW{MemPage}{\mIdleFive}{
  \s\MYname	{Page 5; do not open until directed to do so.}
  \s\MYtext	{Sharing food with \cChupAvenger{} feels like falling into an old habit. How? You just met! This\ldots{} this\ldots{} misplaced familiarity irks you. Why? What is going on? Uncertainty fits ill on you.}
}

\NEW{MemPage}{\mIdleSix}{
  \s\MYname	{Page 6; do not open until directed to do so.}
  \s\MYtext	{Oh these flowers are lovely. How did \cChupAvenger{} know all of your favorites? Even the one you've never told anyone, intending to save that for a special secret between you and your true love\ldots{} An image flits through your mind. \cChupAvenger{} and you in your apartment in \pTech{} talking over a bouquet of \iBlackCrocus{}es. But how? Part of your mind thinks you should be freaking out right now. But mostly this feels\ldots{} nice, familiar, comforting, right.}
}

\NEW{MemPage}{\mIdleSeven}{
  \s\MYname	{Page 7; do not open until directed to do so.}
  \s\MYtext	{You remember watching the sunset holding someone's hand. Just like this. You sigh, and lean your head on their shoulder. A shoulder exactly the same height as \cChupAvenger{}'s shoulder. You turn to look at them. It's \cChupAvenger{}'s face, smiling at you. This is clearly your memory. How could you have forgotten it?}
}

\NEW{MemPage}{\mIdleEight}{
  \s\MYname	{Page 8; do not open until directed to do so.}
  \s\MYtext	{Like a tsunami breaking over your mind, a flood of memories smashes into you, \textbf{knocking you out}. You will wake up in 5 minutes; take the rest of this time to read the following. -- Dripping saltwater, memory after memory floods your mind. You met \cChupAvenger{} years ago.Your courtship was long, and slow, and sweet. The physical distance between your home and \cChupAvenger{\theirs} never seemed a barrier, just that your time together became all the more precious. You were going to propose to them\ldots{} But then\ldots{} Another wave smashes into you, scattering your thoughts like an upended basket of shells. What happened? Where did it all go? How could you have forgotten the love of your life? \cChupAvenger{} will have some explaining to do when you wake up. Even with the memories that have come back to you, there are still gaps. This isn't the full story of your courtship, and there's no clue as to why these memories were lost.\emph{(OOC: Restoration of further memories is outside the scope of the game, but possible in epilogue. Other characters, e.g. \cChupAvenger{} may have information that fills in some of the gaps.)}}
}

