\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\usepackage{multicol}
\usepackage{ltablex}
\usepackage{tabularx}

\begin{document}
\name{\gAssassinateWarlord{}}

The following mechanic describes how to create a fast acting poison and use it to assassinate \cLoud{\full}, leader of the \pShip{} warmongers plaguing your shores. \cEvil{\full} and \cDiplomat{\full} are conspiring on this. If you wish to use the poison for another purpose, contact a GM. You \textbf{must} make the ritual to convert the ``\iSlowActingPoison{}'' into the ``\iFastActingPoison{}'', and send it off to your assassin before you go to bed on Saturday night to have any chance of pulling this off.

To make the poison, you will need to collect the following:
\begin{enumerate}
  \item 1 ``\iSlowActingPoison{}''
  \item A vial of blood from the Warlord’s child, \cWarlordDaughter{\full}. You start game with an ``\iGlassVial{}''. The item card has more information on how to draw blood. You cannot do so without the described mechanic.
  \item 3 Ritual Candles
  \item A ``\iStoneFlower{}’’
  \item 3 participants.
\end{enumerate}

The above Curse can be obtained from trained Cursemakers, hailing from the \pFarm{}, such as \cPrince{\full} and \cCurse{\full}. Be cautious who you ask and how, though, as asking for a ``\iSlowActingPoison{}'' could easily raise suspicions. Watch your timing as well, as these curses can take a while to prepare, even once they have been commissioned.

Once you have the three components, you can combine them to make Fast Acting Poison using the following ritual:
\begin{enumerate}
  \item The ritual must be performed in a place which has known violence and/or death, such as the Graveyard, the Combat Circle in the Training Ground, the Student Lounge where the students perished six years ago, or a location which has experienced violence during game.
  \item The ritual requires three participants. One participant holds the Curse, a second holds the \iStoneFlower{}, and the third holds the vial of blood.
  \item Arrange the Ritual Candles in the middle of the space
  \item The participants hold out their items, and circle each other and the candles, chanting three times in unison, “Pour forth our malice into this vessel.”
  \item Each participant picks up 1 of the Ritual Candles in their free hand, and turns their back to the others.
   \begin{enumerate}
      \item The participant with the ``\iStoneFlower{}'' holds it over the candle and intones: ``I invoke the power of death from within this flower.’’
      \item The participant with the sample of \cWarlordDaughter{}’s blood holds it over the candle and intones: ``I tie the power of death to this bloodline.’’
      \item The participant with the ``\iSlowActingPoison{}'' holds it over the candle and intones: ``I infuse the power of death to this vessel.’’
   \end{enumerate}
  \item The ritual is now complete. Discard the six item cards to the nearest stock. If the ritual gets interrupted, the items are not destroyed, but you must start over.
  \item After completing the ritual, retrieve the ``\iFastActingPoison{}'' item from ``\sSignP{}'' in GM headquarters.
  \item Open up the item and write on the paper inside which bloodline it is tied to (based on the blood sample used in the ritual). Put the paper back inside.
\end{enumerate}

The next step is to send the poison in a letter to one of your \pShip{} agents; you can do this through the normal letter writing mechanic (the letters home ability does not normally allow you to send items; this mechanic overrides that). This step must be accomplished by \textbf{Saturday night}, as your agent needs time to get into position. 

Lastly, you must get \cLoud{} to go to the Goddesses’ Lighthouse, a particular island in 1st Fleet territory, where your assassin will lie in wait. You must obtain a letter addressed to the Warlord, asking \cLoud{\them} to go to the Lighthouse. You \textbf{cannot} do this step until at least two meals, or overnight has passed since you sent the poison to your agent; otherwise, the timing will not work and the attempt will fail. 

You can try to accomplish this in one of several ways, but the more likely they will succeed at getting the Warlord to go where you need, the more difficult to accomplish, and the more likely to arouse suspicion among those who would rather you did not succeed in removing \cLoud{}. \emph{(OOC Note: It is also possible for other actions taken in game to change the probabilities of success.)}

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}X |>{\centering\arraybackslash}c |}
\hline
	\textbf{Source of the Letter} & \textbf{Probability of Success} \\
\hline
\hline
	\cWarlordDaughter{\full}	&	100\%	\\
\hline
	Two of the \pShippie{} advisors	&	100\%	\\
\hline
	One of the \pShippie{} advisors	&	75\%	\\
\hline
	A forged letter obtained on the black market	&	50\%	\\
\hline
\end{tabularx}

The \pShippie{} advisors are: \cEbbPriest{\full}, \cJuniorStatesman{\full}, \cChupLeader{\full}, and \cBunker{\full}.

If you complete the above steps within the aforementioned timeline, the assassination is expected to succeed. News of \cLoud{}’s death will be shared with other players if you do succeed.

You could theoretically repeat this ritual, multiple times, with different samples of blood. Each time, it would create a ``\iFastActingPoison{}'' tied to that bloodline. Delivering such a curse counts as killing someone, so unless you are prepared to lose your memory, you would need to find someone willing to take the fall for you. See a GM if you wish to do this.

\end{document}

