\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gBMUse{}}

If you have this greensheet, it means you know that the Black Market exists. This does not guarantee that you know how to reliably contact the market. You may have to ask around \textbf{discreetly.} The rumors suggest you are looking for one or more \textbf{people}, rather than a secret drop off point of some kind.

\textbf{Once you are able to contact the market, you should ask for what you want.} There are many kinds of things one can obtain on the black market. Here are some examples:
\begin{itemize}
  \item The permanent imbuing of Technology with magic - this is highly illegal, and directly against the edicts of \cTechGod{}.
  \item Curses of all kinds from the \pFarm{}
  \item Forged documents for assuming a new identity, possibly in a new country.
  \item False evidence incriminating someone of something. (The evidence will convince most authorities, but is fabricated and therefore not foolproof; other PCs especially may be able to spot this.)
  \item Quality of Life Technology and Goods from any of the nations. (e.g.: clothes, food, art)
  \item Black Market Credits (at the discretion of the Market Managers)
  \item Information/secrets, in general, or specifics.
  \item If you want something else, ask!
\end{itemize}

\textbf{Nothing is free however, and you should have some idea of what you are willing to pay for what you want.} These are some of the things that one generally offers in payment:
\begin{itemize}
  \item Placing magical energy into an item of Tass.
  \item Curses.
  \item Promises / IOUs to render aid/assistance.
  \item Black Market Credits (at the discretion of the Market Managers)
  \item Information/secrets.
  \item If you want to pay something else, propose it and see what happens!
\end{itemize}

You can ask for something and let them set a price, or offer a price from the get go. The market manager(s), whoever they are, will ultimately approve or reject an offer.

You may freely teach other people about the market, however, this comes with risks. None of the 3 nations like the black market, and the \pTech{} is taking particular pains to stamp it out. \textbf{If you get caught messing around with the black market by someone who disapproves, you will be in big trouble both here, and back home.}
\end{document}

