\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gCrownPrince{}}

You are the youngest \cPrince{\child} of \cQueen{\full}. You and your \cQueen{\parent} are very much alike - more so than any of your siblings.You have thrived in the viper's nest \cQueen{} has cultivated in the royal court of the \pFarm{}. \cQueen{\They} would very much like to name you ``Heir Apparent'' but cannot do so without inciting significant conflict that could lead to a civil war, \textbf{unless} you can stand out so far above your other siblings in your accomplishments that no one will be able to deny that you are the best successor for your \cQueen{\parent}.

There is one thing you \textbf{absolutely must} do for this to work. You must retrieve the royal signet ring that your \cQueen{\parent} lent you, which was stolen by pirates. So far no one knows that you’ve lost it, but your \cQueen{\parent} expects you to return it to \cQueen{\them} in a grand public ceremony on Monday (where \cQueen{\they} also hope\cQueen{plural} to name you ``heir apparent''). So you have to find it and bring it home if you are to have any chance at securing the throne of the \pFarm{} for yourself.

Finding the ring alone will not earn you the title of ``heir apparent'' though. You must do something (or many somethings) that will distinguish you this weekend. Among the options you’ve already thought about are:
\begin{itemize}
  \item Being the \textbf{mediator} on a signed treaty to end the war. As a teacher, you are supposed to be neutral toward all three nations, so you cannot actually sign a treaty proposal as an advisor, even though you are royalty.
  \item Acquire one or more powerful magical artifacts.
  \item Learn the identities of any spies that report to the spymasters of \pTech{} and \pShip{}.
  \item Help \cMusic{\full} become the new principal - They will probably be more sympathetic to the \pFarm{} than \cBeetle{\full}.
  \item Root out any traitors to the crown among your own citizens. Anyone who is against \cQueen{\full}, you, the royal family, or the nobility in general is a threat. Expose them, and have them stripped of as much power/influence as possible.
  \item Reduce the pirate threat against the \pFarm{} coastland as much as possible.
  \item The Fairweather family is already a staunch supporter of the \cQueen{\Majesty}, but getting \cInitiate{\full} to return to them and take on the role of Heir would truly cement that alliance.
  \item Likewise, the \cAdopted{\formal} family has had some trouble getting their adopted \cAdopted{\child} \cAdopted{\full} to truly embrace their role and do the family proud. If you could be secure \cAdopted{\their} cooperation, the family would be another valuable asset.
\end{itemize}

This is not an exhaustive list. Anything you can do to make yourself look good or your opponents look bad, aid your allies/supporters and hinder your enemies, or elevate the \pFarm{} will be valuable in your mission. \emph{(OOC Note: At the end of the game, please confer with the GMs on everything you’ve accomplished so we can include whether you succeed in our wrap up).}

\end{document}
