\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gEbbAvatar{}}

The avatars of \cEbb{} and \cFlow{} are housed in the physical forms of sea serpents. There are advantages to this, such as increasing the amount of influence that Goddess can apply to the situation in which their avatar is present. On the other hand, there are disadvantages, like the fact that the mortal vessel can be destroyed, throwing the avatar spirit back into the Divine Realm. 

This appears to be what has happened to \cEbb{}’s avatar, some time in the past few months. With \cEbb{\their} avatar removed from the mortal plane, \cEbb{}’s influence is lesser, and \cEbb{\their} followers weakened. The church has kept this information \textbf{very quiet,} because it puts the \pShip{}, a nation at war, in a precarious position. Killing a normal sea serpent is no easy task. Killing an Avatar of the Goddesses is even harder.

Creating a new Avatar is obviously important, but also incredibly difficult; it is probably one of the most complicated and difficult things you are undertaking this weekend. \textbf{You should expect both strong character and environmental opposition. Secrecy, speed, and cooperation among those you trust will be crucial.} It would also be \textbf{a lot easier and less painful} to perform this ritual in the Divine Realm. If only it were not blasphemous to even talk of trying to reach the Divine Realm when the Deities themselves severed the connection\ldots{}

To create a new Avatar of \cEbb{}:
\begin{enumerate}
  \item In order to reverse it, you must first learn more about how this terrible deed was accomplished: 
\begin{enumerate}
	\item Collect at least 3 people, including at least 1 Cleric of any deity.
	\item Acquire the  necessary supplies to bless a person.
	\item Reach ``A Slow Boat on a Dark River’’ (Library: Tier 3). Everyone must reach this location, although you may do so in multiple groups as long as a Cleric is present for the next step.
	\item Have the Cleric bless the group with a single blessing (this is an unusual use of their ability to bless a single person or location.)
	\item Have the group return to the Temple and meditate for 5 minutes to ask the Goddesses what they can tell you. -- everyone who meditates \textbf{must} have been blessed in ``A Slow Boat on a Dark River’’ (Library: Tier 3). You can meditate in silence, or someone can lead a group visualization, song or another form of meditation.
	\item At the end of the 5 minute meditation, go to ``Sign E’’ and lift it to read what is underneath. Everyone who meditated with you will learn the same information.
\end{enumerate}
  \item Acquire whatever was used to kill the \cEbb{} avatar. If it was a relic, attune it to \pShip{}. Even if it is a relic traditionally associated with another nation, you can still attune it to \pShip{}.
  \item Find a sea serpent, ideally a baby one. You have faith that the Goddesses will smooth your path somehow. Someone here this weekend either has one, or will be able to acquire one. (You will know you have the item you seek because the item number will be: \iBabySeaSerpent{\MYnumber})
  \item Enact the ritual to summon \cEbb{}’s avatar spirit, and bind it to the sea serpent:
  \begin{enumerate}
    \item Collect at least \textbf{2 clerics or initiates of \cEbb{} and \cFlow{}}, at least 3 other followers of \cEbb{} and \cFlow{}, and 1 GM for the ritual. If you have a secret follower of another patron deity participating, the ritual will still succeed, but the GM will let you know after the fact that something felt off about the resonance of the group; in such a case, suspicion would be warranted. 
    \item Designate 1 character to lead the ritual. That character must activate a ``\iSkill{}’’ on themselves (normal effects do not apply), \textbf{unless} this ritual is performed in the Divine Realm, in which case, no ``\iSkill{}’’ is necessary. (if the ritual is interrupted or fails, the item is not consumed, but neither are the normal effects taken.)
    \item Place the sea serpent in the middle of a circle formed of the ritual participants. You will need to find some way to restrain it. - Those participating in the ritual cannot also dedicate attention to restraining the sea serpent.
    \item In keeping with \cEbb{}’s teachings, each participant must truthfully share with the group one part of themselves that they feel no longer serves them and they want to work on overcoming/relinquishing.
    \item Have everyone in the group close their eyes, or otherwise turn their attention inward. Do a quick breathing exercise (e.g.: ``Breath in for 4… 2, 3, 4. Hold for 4… 2, 3, 4. Breath out for 4… 2, 3, 4. Hold for 4… 2, 3, 4.’’) to calm and focus everyone.
    \item Spend at least 30 seconds bringing the participants into harmony by using vocalizations, rhythm, and/or body movements.
    \item Slowly and reverently pass the item that was used to kill the previous avatar around the circle \textbf{3 times in a clockwise direction}, and then \textbf{3 times in a counter-clockwise direction}. You may have the group continue using vocalizations, rhythm, and/or body movements. You may also choose to intersperse moments of silence.
    \item Use a call and repeat to say: ``\cEbbFull{\full}, send your avatar to us.’’ Have the other participants repeat it back to you. Do this 3 times.
    \item Help the group focus their attention and will on the sea serpent in the middle, perhaps by having everyone point at it, or constricting the circle around it.
    \item After at least 15 seconds of intense focus,the ritual is complete.
  \end{enumerate}
  \item Consequences of the Ritual - These ONLY occur if the ritual completes successfully: (would be circumvented if this could be done in the Divine Realm.)
  \begin{enumerate}
    \item Everyone who participates in this ritual will lose 3 CR tokens (to a minimum of zero) until they can be regenerated, \textbf{unless} this ritual is performed in the Divine Realm, in which case, there is no CR cost.
 
  \end{enumerate}
\end{enumerate}

After a successful ritual, the sea serpent will become the \cEbb{} avatar (get the new Item card from the GM). It will still be in a somewhat weakened state for 72 hours. You will need to protect it until the end of the game and make sure it is taken off the island by people you trust.

\end{document}

