\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gEscapingFoG{}}

Switching Patron Deities is hard under normal circumstances — you have to convince a Cleric of both your current and future Deities to support you switching. Leaving \cGenesis{} is quite a bit harder, since no Cleric of \cGenesis{} would agree to that, and you are all pretending to follow one of the Patron Deities anyway. Leaving \cGenesis{} as an Avenger is nearly impossible. The additional consecration rituals and years of work killing in \cGenesis{}’ name leave a nearly indelible mark on your soul. You can’t just talk your way out of this one.

You also cannot rely upon being welcomed back just because you are leaving the cult. Many would still look upon you with suspicion, or regard you as a criminal. You should also bear in mind that \textbf{you still support the goals of the \pGoaties{},} you just no longer feel able to serve yourself. You \textbf{do not} want to reveal the cult or their plans to anyone. Not that you are particularly clear on this weekend's plan. It seems that the leadership forgot who you were before you could be briefed.

After your first, naive attempt went so poorly, you spent the last few weeks \textbf{frantically} searching for an alternate escape. Despite it being a daunting task, escaping from the \pGoaties{} is important to you, and you are willing to put in the work. You believe that your escape must happen in 3 parts. All of the tasks for the first 2 parts can happen in any order, but they must all be complete before you can undertake the 3rd part

You are very glad that you have \cLibrarian{\full}’s help and support in all of this.

\begin{enumerate}
  \item Disconnect yourself from \cGenesis{}:
  \begin{enumerate}
    \item Change your luck — you must fail at 3 luck based challenges and succeed at 3 luck based challenges (aka mechanics that require rolling a D20.) You can’t just auto fail challenges; you have to legitimately roll a fail. Likewise, mechanics that would cause you to auto succeed a check don’t count either. You may count group checks that are passed or failed.
    \item Cleanse your soul:
 	\begin{enumerate}
    \item Collect a sample of your own blood (you will need to find a mechanic to draw blood, and a container), and bring it to \sPFlameTwo{} in the Old Wing of the \pSc{}. Heat the sample over the flame for 30 seconds to change its nature.
    \item Gain access to the ``River of Forgetting’’ in the deepest part of the Library, and wash the container clean of your blood in the water of the River to wash away your affiliation with \cGenesis{}. This mechanic overrides any normal effects of interacting with the River.
  \end{enumerate}
  \end{enumerate}
  
  \item Re-ingratiate yourself with \cEbb{} and \cFlow{}:
  \begin{enumerate}
    \item Repay a debt to someone who did something positive to you (e.g. gave you a gift, helped you with something) by doing something positive for them, preferably without any chance of them discovering that you were involved.
    \item Get even with someone who did something bad to you (e.g. stole something from you.) If nothing in game presents itself as an option, you can always find a way to get even with \cChupLeader{\full} and/or \cChupSecond{\full}. Outing them to the authorities would certainly do it, but that would likely bring the whole movement crashing down. Surely there’s something more subtle you could do to repay them for costing you your legacy and relationships.
    \item Acquire a Ritual candle and meditate at a source of water for 5 minutes with at least 1 other person. (Find an in-game sign that describes water.)
      \end{enumerate}
  
  \item Participate in a conversion ritual:
  \begin{enumerate}
    \item You could theoretically use the normal conversion ritual, but there are a lot of complications to it:
    \begin{enumerate}
      \item You would need one of the \pGoaties{} to agree to helping you leave, something they will certainly be loath to do.
      \item The Cleric and other participants would learn of the Deific allegiance of both you and the other Follower, and that would put the \pGoaties{} and their mission in jeopardy; something you are not interested in doing
    \end{enumerate}

    \item You could use a \textbf{modified} conversion ritual, \textbf{if} you can convince a Cleric to do it. 
     \item The NORMAL conversion ritual has the following constraints: 
  \begin{enumerate}
    \item Should take no less than 2 minutes, and no more than 5 minutes.
    \item This ritual must happen in the temple.
    \item Requires: 1 cleric, the person changing to a new patron deity, 1 person who remains a follower of their previous patron, 2 people who already follow the new patron deity.
	\item Send the person to a GM when you are done.
  \end{enumerate}
     \item The modified conversion ritual you’ve managed to dig up has the following constraints that \textbf{differ} from the normal conversion ritual and may raise suspicion:
    \begin{enumerate}
\item Should take no less than \textbf{5 minutes,} and no more than \textbf{10 minutes.} 
\item Requires 1 cleric of \cEbb{} or \cFlow{}, yourself as the person converting, and \textbf{3 people} who already follow \cEbb{} and \cFlow{}, but no one who follows \cGenesis{}.
      \item All participants will feel exhausted after the ritual and should roleplay accordingly for at least 20 minutes.
    \end{enumerate}
  \end{enumerate}
\end{enumerate}

\textbf{Set your V-Score to Zero (0) once the conversion ritual is complete. You will also lose access to your \aLuck{} ability. Give it to a GM or discard it to the nearest stock.}

You hope this escape is also connected to restoring \cHeadScientist{}’s memories of your time together. See your ``\gRestoringLove{}’’ greensheet for more information.


\end{document}

