\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gFaledonHeir{}}

\cHeir{\full} does not wish to be the heir to the \cFaledonParent{\formal} estate, dynasty, and all of the responsibilities therein. Their older sibling \cHeirSibling{\full} was the heir until \cHeirSibling{\they} \cHeirSibling{\were} killed 6 years ago. So for now the burden rests on \cHeir{}. But through an immense amount of research and digging through ancient family history, \cHeir{} has discovered both why \cHeir{\theyare} magically the only viable candidate to take on the head of family, and \textbf{a way to escape.} The founder of the \cFaledonParent{\formal} family commissioned a blood curse from the \pFarm{} so many generations ago. So it will take blood magic to alter \cHeir{}’s fate. 

It is important to orchestrate \cHeir{}’s escape this weekend because \cDiplomat{\full} has turned up to the Time of Deciding with 2 pieces of truly abominable news. One, \cFaledonParent{\full} has decided that since this weekend is such a rite of passage, that \cHeir{} should take on the role of head of house \textbf{now.} If \cDiplomat{}, the \cFaledonParent{\formal} agent, succeeds in the ``Ritual of Sealing,’’ there will be no chance of escape later. Two, \cHeir{} and \cChupStudent{\full}’s parents have also decided that it is high time they were married - that marriage is scheduled for Monday! If \cHeir{} does not wish to wed, ducking their leadership role will be crucial to getting the arranged marriage called off.

The curse is so old, and so well crafted that undoing it entirely is impossible. The best \cHeir{} and \cAmbition{\full} can manage is to attempt to spoof things such that the two of them are identical as far as the curse is concerned, making both equally eligible. Past that, it will be up to their social skills to convince \cDiplomat{} that \cAmbition{} is the better choice.

To make \cAmbition{} metaphysically identical to \cHeir{} for the purposes of the \cFaledonParent{\formal} family blood curse:
\begin{enumerate}
  \item Obtain the following supplies:
  \begin{enumerate}
    \item 2 ``\iBlindness{}''
    %\item 2 ``\iFlameOrihid{}''
    \item A sample of blood from each of \cHeir{} and \cAmbition{} (you will need to find a mechanic to do this.)
  \end{enumerate}
  \item At some point \textbf{after} the sun sets on Friday or Saturday, collect at 4 people you trust (more may watch, but will not have an active role in the ritual), in addition to \cHeir{} and \cAmbition{}.
  \item Pick a place to perform the actual ritual somewhere you hopefully won’t be interrupted.
  \item \cHeir{} and \cAmbition{} must explain to their helpers what this ritual will accomplish. If you are not truthful with your helpers, they cannot pour their intention into the ritual, and it would go awry.
  \item Give each helper either one of the ``\iBlindness{}'' or one of the samples of blood. %\cHeir{} and \cAmbition{} must each hold a ``\iFlameOrchid{}.''
  \item Arrange \cHeir{} and \cAmbition{} in the center, with the helpers arrayed around them in a circle.
  \item Everyone participating in the ritual must concentrate on each other’s breathing until everyone is breathing in and out together.  One everyone is in sync, you may continue.
  \item Whoever is holding the sample of blood from \cHeir{} should pour it out over one of the curses of blindness, thus imbuing it with \cHeir{}’s essence.
  \item The same should be done with the sample of blood from \cAmbition{} for the other curse.
  \item Give the curse with \cHeir{}’s essence to \cAmbition{}. \cAmbition{} must say aloud ``With this, I make you my sibling,'' then activate the curse on themselves, taking the effect.
  \item Give the curse with \cAmbition{}’s essence to \cHeir{}. \cHeir{} must say aloud ``With this, I make you my twin,'' then activate the curse on themselves, taking the effect.
  \item Discard all of the items involved in the ritual to the nearest stock; they have been consumed.
  \item \textbf{\cAmbition{} should change their F-Score from 0 to 1.}
\end{enumerate}

The ritual is complete, but \cHeir{} and \cAmbition{} will be temporarily blinded until the effect of the curse wears off.

\end{document}
