\documentclass[green]{GL2020}
\parindent=0pt
\begin{document}
\name{\gFPFStudentMorality{}}
\emph{\textbf{(OOC: If your character changes Patron Deities, see a GM because you will need a new version of this Morality Mechanic. Changing Patron Deities will reset your morality score to Zero.)}}

This document outlines how you, the students, will keep track of your ongoing Morality score. The score is a judge of how well you are following the tenets of your nation’s religion, and will affect your final voting authority for directing the Storm. The Deities are watching closely this weekend. As members of the \pTech{}, doing things that \cTechGod{} approves of earns you points. Doing things \cTechGod{\they} disapprove\cTechGod{\plural} of loses you points - \cTechGod{\they} care as much or more about the intention than the impact, for \cTechGod{\they} can see into your heart.

The following action \textbf{earns} you a Morality point:
\begin{enumerate}
  \item Building something new
  \item Fixing something broken
  \item Otherwise advancing science or the arts
\end{enumerate}

The following action \textbf{lose} you a Morality point:
\begin{enumerate}
  \item Lying
  \item Not giving credit where it is due
  %\item Unauthorized activation of technology
  \item Murder
\end{enumerate}

These activities affect only your Morality score (see your stat card or character sheet for what you start at; most people will start at zero).  Note that your morality score \textbf{can} go negative! You will likely find yourself doing things that will lose you points to accomplish other goals - that’s okay; everyone will be trying to walk that line. You are only being compared within students from your own country, and therefore under the same restrictions. The exact difference between the Morality scores does not matter, only your relative ranking compared to other students of your nation, so don’t feel the need to forego opportunities in order to absolutely max your Morality score. Moreover, the teachers and advisors also get a say in your voting authority, so even if your Morality score is the worst among the students, you could still end up with the most voting authority. 

You must keep track of your Morality score yourself \emph{(OOC: use your judgment for whether an action counts; if in doubt, ask a GM or another student from the same country)}. You must submit your final Morality score by \textbf{9:00 pm Saturday.} Write your character name, what country you are from, and your final Morality score on a piece of paper, and drop it in the envelope attached to “\sSignV{}” in GM headquarters. 


\end{document}
