\documentclass[green]{GL2020}

\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{ltablex}
\usepackage{tabularx}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
\setlength{\columnsep}{1cm}

\usepackage{makecell}

\begin{document}
\name{\gFPFAdvisorRanking{}}

This document describes how you will influence which students get the most votes to direct the Storm. Voting for advisors is by ranked choice - you will rank the four students (from your nation) on your ballot from most (1) to least (4) preferred. Additionally, you have the option to list 1 student who is not on your list under “special recommendation.” 

Advisors are encouraged to take their time deciding how to vote to properly represent their nation’s interests - most advisors will submit their ballot late on Saturday. Talk to the students from your nation to get a sense of where they stand. Talk amongst yourselves and try and sway your fellow Advisors to vote for your favorite students. The stakes, after all, could not be higher.

This greensheet serves as your ballot. You will either turn this document in entirely, or you can tear off just the table portion and submit that. \textbf{Please remember that greensheets are out of game documents.} This means that you may not show your ballot to anyone else, but also, it cannot be stolen from you. 

\textbf{Ballots must be submitted to Sign V in GM Headquarters by 9:00 PM on Saturday night.}\\
\vspace{1cm}

{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|p{7cm}|X|}
\hline
\multicolumn{2}{|c|}{\textbf{\large \pTech{} Advisor Ballot}} \\
\hline 
\multicolumn{2}{|X|}{\textbf{Your Name:}} \\
\hline
  \textbf{Students (\pTech{})} & \makecell{\textbf{Your Ranking from 1 (most)} \\ \textbf{to 4 (least) preferred}}  \\
\hline
  \cTechStar{\full} &  \\
\hline
  \cAmbition{\full} &  \\
\hline
  \cHeir{\full} &  \\
\hline
  \cScholarship{\full} &  \\
\hline
\multicolumn{2}{|p{2cm}|}{\makecell{\textbf{Optional Special Recommendation}\\ \textbf{for a student \textbf{not} on your list:}}}\\
\hline
\end{tabularx}}

\end{document}
