\documentclass[green]{GL2020}

\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{ltablex}
\usepackage{tabularx}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
\setlength{\columnsep}{1cm}

\usepackage{makecell}

\begin{document}
\name{\gFPFTeacherRanking{}}

This document describes how you will influence which students get the most votes to direct the Storm. Voting for teachers is by ranked choice - you will rank the four students on your ballot from most (1) to least (4) preferred. Additionally, you have the option to list 1 student who is not on your list under “special recommendation.” 

Teachers do not rank the students from their own nation; instead, they rank students from another nation. Specifically:
\begin{itemize}
	\item Free People’s Federation Teachers will rank Children of the Sun students. 
	\item Children of the Sun Teachers will rank Waver Rider students. 
	\item Wave Rider Teachers will rank Free People’s Federation students.
\end{itemize}

This system was designed to reduce favoritism and foster dialogue between different nations. Teachers are encouraged to take their time deciding how to vote - most teachers will submit their ballot late on Saturday. Talk to the students you are ranking. Talk amongst yourselves and try and sway your fellow Teachers to vote for your chosen students. The stakes, after all, could not be higher.

This greensheet serves as your ballot. You will either turn this document in entirely, or you can tear off just the table portion and submit that. \textbf{Please remember that greensheets are out of game documents.} This means that you may not show your ballot to anyone else, but also, it cannot be stolen from you. 

\textbf{Ballots must be submitted to Sign V in GM Headquarters by 9:00 PM on Saturday night.}\\
\vspace{1cm}

{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|p{7cm}|X|}
\hline
\multicolumn{2}{|c|}{\textbf{\large \pTech{} Teacher Ballot}} \\
\hline 
\multicolumn{2}{|X|}{\textbf{Your Name:}} \\
\hline
  \textbf{Students (\pFarm{})} & \makecell{\textbf{Your Ranking from 1 (most)} \\ \textbf{to 4 (least) preferred}}  \\
\hline
  \cLibAssist{\full} &  \\
\hline
  \cChupStudent{\full} &  \\
\hline
  \cAdopted{\full} &  \\
\hline
  \cDisney{\full} &  \\
\hline
\multicolumn{2}{|p{2cm}|}{\makecell{\textbf{Optional Special Recommendation}\\ \textbf{for a student \textbf{not} on your list:}}}\\
\hline
\end{tabularx}}

\end{document}
