\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gGenesisAvatar{}}

Summoning the Avatar of \cGenesis{} is an important part of bringing \cGenesis{} on par with the other Patron Deities. Indeed, any deity whose avatar(s) are not currently on the mortal plane will be at a disadvantage in comparison. This summoning ritual requires a \textbf{ritual leader.} Whoever performs the role of ritual leader will have \textbf{tremendous sway over the group going forward, and gain a special power (see below).} 

Once summoned, the Avatar will \textbf{not be easy to hide}, so careful timing and planning are key if you wish to avoid being discovered by the uninitiated. Summoning the Avatar too early could easily blow your cover and make it impossible for you to accomplish your mission.  \cChupInventor{\full} has a secret black market stash in the Alchemy Lab in the Old Wing of the college that could serve as a suitable hiding place. While usually something as large as the Avatar could not be hidden there, Genesis’ luck will permit this exception. 

\textbf{To summon the Avatar of \cGenesis{}:}
\begin{enumerate}
  \item This ritual can only be accomplished in a place strongly attuned to \cGenesis{} - The Cavern of Fortune’s Shadow (page 48) in the depths of the Library. You will need to find this location if you wish to summon the Avatar.
  \item This ritual requires at least 4 participants, one of whom must be designated the \textbf{ritual leader,} who will guide the rest of the ritual. All participants must agree on the leader. Also get a GM.
  \item This ritual requires the following items:
    \begin{enumerate}
      \item 1 ``\iGlassVial{}'' filled with water from somewhere.
      \item 1 ``\iStoneFlower{}''
      \item 1 ``\iRabbitStatue{}''  (\cGenesis{} indicated that \textbf{one and only one} could be found at the \pSchool{} somewhere.)
    \end{enumerate}
  \item Arrange the participants in a circle.
  \item Have everyone in the group hold a vial of water and focus on it. Do a quick breathing exercise (e.g.: ``Breath in for 4… 2, 3, 4. Breath out for 8… 2, 3, 4, 5, 6, 7, 8.’’ Repeat 2x) to calm and harmonize the participants.
  \item Starting with the \textbf{Ritual Leader}, pass the \iRabbitStatue{} around the group to the \textbf{left} (clockwise looking down at the circle). Have each person hold the statue for a moment and pour their intention to summon the Avatar of \cGenesis{} into it. Have the last person place the statue in the middle of the circle.
  \item Use a call and repeat to say: ``\cGenesis{}, send your avatar to us.’’ Have the other participants repeat it back to you. Do this 3 times.
  \item The Ritual Leader must turn to the person to their \textbf{right} and pour the vial of water out over that person’s head. That person should then do the same, and so forth, \textbf{counterclockwise} around the circle.
    \begin{enumerate}
      \item The vials are tiny, but somehow they hold enough water to get each person soaking wet with ice cold water.
    \end{enumerate}
  \item Help the group focus their attention and will on the statue in the middle, perhaps by having everyone point at it, or constricting the circle around it. \textbf{Each} participant must sacrifice one CR token (to a minimum of zero) until they can be regenerated, as they pour some of their magical energy into the rabbit.
  \item After at least 15 seconds of intense focus, the ritual leader should feed the stone flower to the now live rabbit.
  \item The GM will step in to embody the Avatar if you wish to speak with them at this time.
    \begin{enumerate}
      \item The GM will also have a new item card for the rabbit avatar.
      \item The person who \textbf{led the ritual} also gains an enhanced version of their “Luck of Genesis” ability. For the ritual leader \textbf{only}, the number of uses for that ability increases from 1x/day to 3x/day (update the ability card accordingly).
    \end{enumerate}
\end{enumerate}

All of the ritual components are consumed by the ritual. Discard them to the nearest stock.

\textbf{Make sure to tell the participants in the ritual this before split up:} Participants in this ritual will end up soaking wet for 20 minutes. Tell people you encounter this OOC. On the other hand, \textbf{the next time you attempt an action that requires a die roll, you automatically succeed on the action.}

\end{document}

