\documentclass[green]{GL2020}
\parindent=0pt
\begin{document}
\name{\gLeyLines{}}

The ley lines that pass through the island upon which the \pSchool{} is built supply the magic to all of \pEarth{}. Their maintenance is incredibly important for the continued existence of the \pSc{}, and for magic in general. Renewing the Ley Lines is also important if something should happen to the Relics. The Relics for the Ritual to Control the Storm can be de-attuned through a variety of means, and unattuned relics contribute next to nothing to the Ritual. The ley-lines \textbf{must be renewed} before relics can be re-attuned. Ideally, no one would do anything that de-attuned the relics, but politics can rarely keep its hands off of the ritual, and it is not unusual for the alternate uses of the relics to be required, therefore obligating re-attunment at least once during the Time of Deciding.

This crucial task normally falls to the principal of the school, but since \cPrincipal{\full} is retiring this year, \cPrincipal{\they} \cPrincipal{\have} passed this task to \cBeetle{} as a way to assess \cBeetle{\their} readiness for such an important role. \cPrincipal{} will be assessing \cBeetle{}’s ability to execute this as smoothly as possible.

Instructions for Renewing the Ley Lines:
\begin{enumerate}
  \item Prepare the representations of the 3 nations (these can be done in any order)
  \begin{enumerate}
    \item Find a ``\iClay{}''. Get it blessed by a Cleric of \cFarmGod{}.
    \item Find a ``\iObsidian{}''. Get it blessed by a Cleric of \cTechGod{}.
    \item Find a ``\iLimestone{}''. Get it blessed by a Cleric of \cEbb{} or \cFlow{}.
  \end{enumerate}  
%  \item Retrieve the ``Flawless Diamond’’ from the Jewelry Box in the Library (3rd Tier). This is an incredibly powerful item of Tass that can hold up to 10 units of magical energy.
  \item Bring a group of people to the Ley Line Nexus in the Old Wing of the College. You should ideally have at least 1 student from each nation, 1 teacher from each nation, and 1 advisor from each nation (in addition to \cBeetle{} and \cPrincipal{}) but you can manage with any combination as long as you have at least 6 people in total. Please also bring a GM \textbf{The ritual will be more costly if you have fewer people.}
%  \item Place the ``Flawless Diamond’’ item near the Ley Lines where everyone can see it.
  \item Bring all of the participants together in harmony with each other by using a vocalization (e.g.: “humm…” “humm…”). You may continue this for as long as necessary, varying the volume, tone, and duration of the vocalization until it feels like everyone is engaged.
  \item Focus the attention of the group toward the leylines by adding some repetitive hand motion (e.g.: clapping, touching one’s chest and then extending that hand out toward the middle and back again.)
  \item Have the group pass around the \iClay{}, the \iObsidian{}, and the \iLimestone{}, until everyone has held each stone once. Place the 3 stones on the ground near the Ley Lines.
  \item Build the energy of the group by using a combination of vocalization, repetitive hand motions, and body movements (e.g. step left, lean forward and back, etc. - have alternatives ready to accommodate varying range of motion). Start slowly and quietly, and lead the group to increase the speed and volume slowly.
  \item When the group is doing the actions as quickly and loudly as you feel is comfortable, call for silence. Let the silence exist for at least 5 seconds.
%  \item Indicate participants one by one (don’t forget yourself!). When indicated, the person will step forward, and place one of their CR stones into the envelope attached to the ``Flawless Diamond’’ item of Tass. As they do so, they must say aloud “I give a piece of myself to renew the Ley Lines”. 
%    \begin{enumerate}
%    \item If you have fewer than 10 participants total, you will need to call on some participants more than once to repeat this process until the Diamond holds 10 units of magical energy. If you have more than 10 participants, you need not call on everyone.
%    \item As with all items of Tass, this action temporarily reduces the characters’ CR scores. Players may draw more CR stones up to their maximum at the next meal.
%  \end{enumerate}  
  \item Indicate participants one by one (don’t forget yourself!). When indicated, the person will step forward, and place one of their CR stones in a pile. As they do so, they must say aloud “I give a piece of myself to renew the Ley Lines”. 
    \begin{enumerate}
    \item If you have fewer than 10 participants total, you will need to call on some participants more than once to repeat this process until 10 units of magical energy have been expended. If you have more than 10 participants, you need not call on everyone.
    \item The Ley Lines are absobing this energy. As with Tass, this action temporarily reduces the characters’ CR scores. Players may draw more CR stones up to their maximum at the next meal.
  \end{enumerate}  
  \item Tear down the sign titled ``\sLeyLinesSad{}’’ (leave the other signs up). Tear it in half. Hand each half to a different participant. Have them tear that piece in half, and pass the pieces on to other people, until every participant has had a chance to tear up a piece of the sign.
  \item Declare the ritual complete, thank your participants, and let them be about their business.
%  \item Return the magical energy in the ``Flawless Diamond’’ to the nearest stock. The energy has been poured into the ley lines. Return the ``Flawless Diamond’’ item to the nearest GM. it has served it’s only purpose during the Time of Deciding.
  \item Leave the \iClay{}, the \iObsidian{}, and the \iLimestone{} by the Ley Lines. While their task in this ritual is done, they are not consumed by it. It is generally held that whoever might need them for something else will be drawn to the nexus to find them here.
\end{enumerate}

\emph{\textbf{(OOC NOTE: Don’t forget to tell your participants that they may draw CR stones up to their maximum at the next meal.)}}

\end{document}
