\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gLifeAfterDeath{}}

\textbf{If you haven't played your body for 10 minutes; go back and do that first!} When the time has elapsed, leave all of your items in a pile, along with your character badge. Then go to GM HQ and grab a yellow headband; you may need it. We will also print you a new character badge.

Unfortunately your character was killed at The Time of Deciding. That your murderer is now an amnesiac may not be much consolation to you. Your spirit will eventually move on to the afterlife (whatever that entails), but for the remainder of the weekend, your spirit is in a transitional period on the Divine Plane, still able to interact with and influence the mortal plane in some ways.

\textbf{{\large You may not freely interact with people or things on the Mortal Plane anymore.}}

While all of your items stayed with your physical body, you retain all knowledge and abilities you had in life. If you can find a way to gain access to any required items, you can continue to use all of your abilities and greensheets as long as your target is on the Divine Plane.

\subsubsection*{Close Contacts:} 
\textbf{Pick 4 characters your character was very close to at their time of death. These can be any mix of very strong positive connections and very strong negative ones.} These characters become your ``Close Contacts.’’ You will be able to interact to a greater extent with these characters than others now that you are a ghost. You can’t just pick the 4 people it would be most \textbf{convenient} for your character to be able to interact with; they have to be people your character has a strong connection to as that connection is what is being drawn on for the effect. Feel free to consult with a GM if you are having trouble deciding.

As a ghost, you are limited to the following:
\begin{enumerate}
  \item You may freely explore the Divine Plane, interact with any mechanics you find, and may converse and interact freely with anyone else who is also dead, or any living being who manages to reach the Realm of the Gods.
  \item You may generally read any objects or signs on the \textbf{mortal plane} as if you met the interaction criteria. (You’re a ghost; you can walk through walls and stuff.) You may not bring other people with you though; they are not immaterial like you. \textbf{Exception:} Signs that only contain OOC information remain off limits. (e.g.: ``you may not interact with this sign unless you know otherwise.’’) 
  \item You may go among the living invisibly and listen in to conversations that are not magically protected (ghosts can be invisible - use the OOC symbol; people in a magically protected conversation will tell you they are protected.).
  \item You may whisper in the ear of any of your ``Close Contacts’’ (see above) at any time, as much as you want.
  \item \textbf{Three times per day} you may temporarily manifest on the material plane. You may manifest for up to \textbf{10 minutes} at a time. Put a \textbf{yellow} headband on. During that time, it is as if you were alive again. You may talk to people, interact with things and mechanics (including combat and rituals), etc. You may \textbf{not} opt out of mechanics, except by cutting your manifestation short (e.g. you may become immaterial to avoid taking a knock out attack). Unused time is not refunded.
\end{enumerate}

\end{document}

