\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gLightningRod{}}

\emph{OOC: Make sure this greensheet goes with the ``\iLightningRod{}'' item.}

This ``\iLightningRod{}'' is the control interface for the array of complex magitech installations built on the highest peaks of the \pSpine{} in the \pTech{}. This item has two functions: 

\begin{enumerate}
	\item If incorporated in the preparations for the Ritual to Control the Storm, to allow ``Coordinate Zero'' or ``Coordinate One'' to be a valid target for the Storm.
	\item To identify which Locations in the Divine Realm correspond to ``Coordinate Zero'' and ``Coordinate One.''
\end{enumerate}

\textbf{To incorporate the \iLightningRod{} to the Ritual to Control the Storm:} The Ritual Circle that is created in Runic Chalk must designate a place for the \iLightningRod{} to sit, just like it designates places for the 3 relics. Only the \textbf{teachers} can make or change the Ritual Circle. If you can't convince the teachers to include a spot for the \iLightningRod{} before they make the Circle, not all is lost. \textbf{This mechanic overrides} the limitation that once the Ritual Circle is laid out it cannot be changed. The Ritual Circle \textbf{can} be modified to add a place for the \iLightningRod{}, \textbf{but} once the spot is added, it cannot be removed.

The \iLightningRod{} will not influence where the storm is sent. It is not a relic, and cannot be attuned like one; its incorporation into the ritual serves the purpose of allowing locations in the Divine Realm to be targeted. If the \iLightningRod{} is \textbf{not} included in the ritual, and some element that \textbf{does} influence where the storm goes directs it to a location in the Divine Realm, that influence will be lost.

\textbf{To identify which Locations in the Divine Realm correspond to ``Coordinate Zero'' and ``Coordinate One,'' Do the following:}
\begin{enumerate}
	\item Bring the \iLightningRod{} to the Divine Realm. (Easier said than done when the Gods themselves severed the connection in time immemorial.)
	\item At any location in the Divine Realm, you may compare the ``Coordinate'' number combination listed on the sign to the combinations below.
	\begin{enumerate}
		\item Coordinate Zero: 34x07x50x96 
	\item Coordinate One: 68x90x56x41
	\end{enumerate}
	\item If you do not have the \iLightningRod{} in hand, the numbers are out of game information and mean nothing to you. You cannot memorize the numbers to check later. Please respect the intent of this mechanic, that locations can only be determined if you have the lightning rod in your possession.
\end{enumerate}


\end{document}

