\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gMagicBeans{}}

\emph{\cCurse{} starts with the ``\iBeansNB{},'' having been working on them at home before arriving.} \cFlowPriest{\full} and \cCurse{\full} have been collaborating on this project for several years now, mailing the work in progress back and forth. \cAssistantScientist{\full} has been consulting by letter for several years. \cAmbition{\full} is a fairly new addition and collaborates directly with \cFlowPriest{}. Now that you are all here in the same place, at a time of such intense magical energy, you hope to finish the ``\iBeansNB{}’’ and open a portal to the Realm of the Gods.

The gateway grown will be a permanent fixture, so wherever you plant the beans is it. There will be no way to move the portal after the fact. If you decide to forego the chance to reach the Divine Realms this weekend, and take the beans home (or send them with someone) to plant somewhere else, you should \textbf{not} plant them (last step). But are you really going to delay such an amazing accomplishment? No mortal has traveled the Divine Plane since the Deities themselves severed the connection, not long after \pEarth{} was created, and humans set to walk upon it. And the longer you wait, the greater the chance that \textbf{politicians} get involved. The beans could be taken away from you entirely after all of your hard work to do something thought impossible! 

You do not all need to be present for all steps of this process \emph{(OOC: but it’s probably more fun to do it together)}. Sometimes, it may make sense to divide and conquer, but the trip to the library will likely benefit from going together as a group.

To finish the enchantment on the Beans, complete the following steps:
\begin{enumerate}
  \item Prepare a Cure of \cCurse{}’s own design. \cCurse{} can either brew it \cCurse{\them}self, or convince another curse maker with advanced skill to do it. This is a modification of a traditional Cure made to try to cleanse seed stock of fungus when there is no fertility magic (aka noble magic) available to do it. This will empower the seeds to grow at an impossible rate.
  \begin{enumerate}
    \item Ingredients: 1 ``\iHollyhock{}'', 1 ``\iBlackCrocus{}'', 1 ``\iClay{}’’.
    \item Brew it just like a normal curse/cure. Ask the GMs for an ``\iEyeOfVulture{}.’’ (While one could theoretically brew multiple of these, using it on these beans is the only mechanic in game that uses it.)
  \end{enumerate}
  \item Since the Deities severed the connection to the Realm of the Gods, you’ll need a little of their power to restore it. Pour the contents of either the \iPitcher{} or the \iChalice{} over the beans. \textbf{The relic must be attuned to do this.} Open the attached envelope to check if there is a piece of paper inside the envelope (don’t read the paper!). If there is a paper inside; the relic is attuned. This will de-attune the relic as its stored magic is poured into the beans. Deatune the relic by pulling the piece of paper out of the envelope (don’t read it!) and discarding it to the nearest stock. You can complete this step before you have the ``\iEyeOfVulture{}’’ in hand.
  \item Bring the curse to The Crystal Cavern (Library: Tier 3). Meditate there for five minutes as you pray to Aura, minor god of portals, to bless your endeavor. Then, travel through one of the portals located there to another location in game; this represents infusing the curse with the energies of portal travel. 
  \item Expend the ``\iEyeOfVulture{}’’on the \iBeansNB{}.  \item Bring the \iBeansNB{} to ``\sPFlameOne{}'' in the Old Wing of the \pSc{}. Heat the beans over the flame for at least 30 seconds.
  \item Wait 4 hours for the beans to mature, \textbf{OR} if you are in a hurry, you can choose to have someone stay outside of the bunkers during one of the storm surges with the \iBeansNB{}. The beans will mature much faster with exposure to a storm surge, and will be ready as soon as the surge is over. You may not leave the beans somewhere unattended to achieve this effect.
  \item Open the \iBeansNB{} item envelope. Retrieve the \iBeansMB{} item card from inside, and discard \iBeansNB{} to the nearest stock.
  \item Plant the beans in the Garden (Discard \iBeansMB{} to the nearest stock and \textbf{tell a GM ASAP!}). They will grow into a gateway that will allow passage into the Realm of the Gods. You aren’t entirely sure how long it will take, but you anticipate no more than a few hours (this is a kludge so the GMs can prepare). When the GMs are ready, they will remove ``\sSignB{},’’ Revealing the ``\sMagicPortal{}’’ sign underneath for all to see and interact with.
\end{enumerate}

\end{document}

