\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gMagicalLayer{}}

To repair the keystone of each of the bunkers, you must reconstruct the spell that was used to seal the magical and physical protections together. Thank the Deities that the spell was constructed of parts of other written things, so it can be pieced back together.

\textbf{Find the following to reconstruct the spell:}

Line 1: The 3rd Line of the ``\sTeachersOath{}’’ in the Great Hall.\\
\vspace{1.5cm}

Line 2: The 9th Line of the ``\sAppeal{}’’ In the Temple.\\
\vspace{1.5cm}

Line 3: The 3rd Line of the ``Library Dedication’’, on a plaque on the 1st tier of the Library.\\
\vspace{1.5cm}

Line 4: The 6th Line from the ``\sBlackCrocusWishOne{}’’ artistic banner, anonymously gifted to the school over 1000 years ago, and hung in the Old Wing of the College.\\
\vspace{1.5cm}

Line 5: The College’s First Principle, coined by the first Principal, and inscribed upon her gravestone in the Graveyard. (Find the ``\sTombOfFirstPrincipal{}'')\\
\vspace{1.5cm}

\textbf{Once you have reconstructed the spell, you must cast it:}
This keystone spell must be recited inside any bunker that needs the Keystone Repaired. A group of at least \textbf{5 people} must recite the prayer together in each bunker that needs the keystone repaired. This step may be accomplished at any time (you don’t need to wait for any other repairs to complete). 

A total of 5 CR tokens must be paid (in any combination) among the participants \textbf{each time} this spell is cast. This spell is \textbf{deeply draining} to those who perform it; you may need different groups to cast the spell if it needs to be done more than once. Players are encouraged to roleplay feeling exhausted for up to 30 minutes afterwards.

Once you have cast the spell inside a bunker, add \textbf{+4} to the number of people the damaged bunker can protect. If this is the \textbf{last repair,} (the bunker can now protect 13 people) you may remove the ``Damaged Bunker’’ sign to reveal the one below it.

\end{document}

