\documentclass[green]{GL2020}
\parindent=0pt
\begin{document}
\name{\gMindWipe{}}

The Vid-Com Devices have been an incredible boon to the \pTech{} in the war. So much so that the tide may even be turning in their favor. Since it was the \pTech{} that orchestrated the treaty with the \pFarm{} that betrayed the \pShip{}, and left 11 of your classmates dead, you are deeply invested in sabotaging their war efforts.

Ideally you would convince \cTechStar{\full}, their inventor, to defect from the \pTech{}, move to the \pShip{}, and provide the Vid-Com technology to the \pShippies{} instead. If \cTechStar{\they} refuse, however, you have begun preparations for a more extreme contingency: A mind-wipe. If \cTechStar{} can’t remember how to make the Vid-Com devices, you can at least buy time for someone to reverse-engineer them (if you get your hands on a few copies).

This mind-wipe is of your own invention, and pretty straightforward to make (since it’s a last resort for you). All students at the \pSchool{} get some basic training in cursemaking, but after 6 years, you’re pretty rusty. You’re pretty sure this will work, but probably not immediately, and in the interim, \textbf{the target may be able to reverse the effects,} so it’s not a fool-proof backup plan either. But you never know, maybe it could ultimately be a valuable item to bargain for something else.

\textbf{To prepare the mindwipe:}
\begin{enumerate}
  \item Gain access to the River of Forgetting on the “4th/Extreme Tier” of the library. Fill a ``\iGlassVial{}’’ with water from the river and change the item text per the instructions at that location.
  \item Get a ``\iWeakness{}’’ curse from a cursemaker.
  \item Go to the Temple of \pTechGod{}. In that space, expend the curse over the vial of water. (Discard the curse to the nearest stock.)
  \item Cross out the text on the vial of water and write,  “This is full of cloudy liquid. Tell a GM if you drink it.”
  \item The mind wipe needs 4 hours to mature. At the end of this time, go to the GM HQ and take the ``\iMindWipeCurse{}’’ Item from ``\sSignN’’. Discard the glass vial to the nearest stock; it has been replaced.
  \begin{enumerate}
    \item If you are in a hurry, you can stay outside the bunkers during a Storm Surge. If you do so, the mind wipe will be ready as soon as the surge ends.
  \end{enumerate}
  \item Apply a symbol or design to one corner of the item envelope. This is your maker’s mark. Don’t use anything you’ve seen on other curses, or anything that makes it obvious it is your mark (e.g.: don’t use your character or player signature.)
  \item This curse can now be administered like any other curse, with the following \textbf{addition} (also described on the item): After applying the curse, open the item envelope and give the research-notebook inside to whoever you activated the curse on.
\end{enumerate}

\end{document}
