\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gMusicBox{}}

The clerics of \cFarmGod{} hold the magical music of healing tight in their grasp. So tightly that it is out of reach for far too many of the \pFarmers{}. You don’t care if it’s blasphemous, you have plans to create a device that will perpetually hold that magic, so anyone can access it, any time they need it.

You hope that \cScholarship{\full} will help you with this. You haven’t yet decided if you are going to risk asking \cInterpol{\full} and/or \cMusic{\full} for help too.

\textbf{To create your magic music box:}
\begin{enumerate}
  \item Discuss music theory for \textbf{5 min} with someone who is \textbf{not} a cleric. You may shorten the time to only 2 minutes if you speak with \cMusic{\full} since this is \cMusic{\their} area of expertise.
  \item Discuss the healing power of music for 5 min with \textbf{any} cleric. You may shorten the time to only 2 minutes if you speak with a cleric of \cFarmGod{} (\cDisney{\full} or \cHedonist{\full}) but the trade off is that they may become suspicious of you.

  \item Build a prototype music box in the Maker’s Space.
  \begin{enumerate}
    \item Find the following items:
    \begin{enumerate}
      \item 1 ``\iMagitechParts{}'' (probably best sourced from the Black Market)
      \item 1 ``\iWoodenBlock{}'' (there’s got to be one around here somewhere)
    \end{enumerate}
    \item Spend 5 minutes roleplaying building your prototype. You may shorten the time to only 2 minutes if \cChupInventor{\full}, \cPirate{\full}, \cBunker{\full} or \cTechStar{\full} helps you.
  \end{enumerate}
  \item Retrieve your ``\iProtypeMusicBox{}'' from sign D.

  \item Charge up your prototype music box:
  \begin{enumerate}
	\item Take the prototype to ``The Chamber of the Sun (Library: Tier 3)’’ along with at least two other people. Meditate together at this location for 2 minutes to invite \cFarmGod{}’s power into the box. You can mediate silently, us a visualization, music/song, or anything else you want.
	\item Take the prototype to ``\sLeyLinesNexus{}’’ in the old wing along with at least 2 other people. Repeat your 2 minute meditation here, to borrow some power from the ley lines.
	\item Between you and however many volunteers you find, expend 3 CR stones, imbuing the object with your own magic too.
     \end{enumerate}

  \item Test your prototype music box:
  \begin{enumerate}
\item Arrange to have a volunteer be knocked out. Try healing them with the music box. \emph(OOC: It won’t work this time, but your character does not know that.)
 	\item Once your volunteer wakes up naturally, or is healed by normal healing magic, spend at least 2 minutes interviewing your volunteer about what felt different this time to gain magitechnobabble on what needs to be changed in your prototype.
\item Update your prototype by consuming 1 \iCrystalLens{} (a way to examine magic, and findable in Tier 2 of the Library). Spend 5 more minutes roleplaying making changes to your prototype. You don’t need to do this in the Maker's Space, but you may still shorten the time to only 2 minutes if \cChupInventor{\full}, \cPirate{\full}, \cBunker{\full} or \cTechStar{\full} helps you.
\item Discard the \iCrystalLens{} to the nearest stock. Retrieve the ``\iMagicMusicBox{}'' item from inside the ``\iProtypeMusicBox{}’’ envelope. Discard the ``\iProtypeMusicBox{}'' item to the nearest stock.
\item Arrange to have your same volunteer from before knocked out a second time. Try healing them with the music box. You may freely use the ability associated with the ``\iMagicMusicBox{}'' this time, without having to expend a CR token. Subsequent uses will follow the mechanic described on the item card.
  \end{enumerate}
  \item Find a way to get the ``\iMagicMusicBox{}'' \textbf{imbued with magic.} This is some technomagic that will allow your music box to retain its magical effect forever. Someone from the \pTech{} surely knows how to do this. If they refuse, the Black Market can probably help with this too.
  \item Anyone can now cast basic healing magic as long as they are in possession of this music box. There is an ability inside the ``\iMagicMusicBox{}’’ item that can be freely read that explains how.
\end{enumerate}

See if you can get the \cHeir{\formal} family heir (\cHeir{\full}) to agree to have the family mass produce these so that you can get them into the hands of as many people as possible!

\end{document}

