\documentclass[green]{GL2020}

\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gNPCGuide{}}

A good reference doc/guide for things we can anticipate players might want, and notes to remind us of stuff.


Notes on being an NPC:
For your ``\gHireTeacher{}’’ greensheet, it is written for a PC perspective, since you will be physically passing off that piece of paper to a PC near the end of game. As an \textbf{NPC}, we ask that you don’t actually fire any teachers. Just get on their case and nag them if you feel they are being too blatantly involved in the treaty or the war, or influencing the student vote. Examples:
Participating in treaty negotiations representing one or more countries, rather than just a neutral mediator.
Passing secrets to spies that could impact the course of the war.



Before Game:
Please grab the phys reps for the sacred chalk! (6 colors of masking tape)

During Game:
Please prepare a short speech (seriously, it can be really short) to open the event IC by welcoming the advisors, and probably reminding each cohort of their important role this weekend.
Players (or a GM who is running off to do something else) may ask you to check if a relic matches the ``restriction’’ on a pedestal. To do this, set a 15 minute timer. Between 10 min later and when the timer goes off, go and check the attunement of the relic by opening the attached envelope and reading the piece of paper inside it. Put the paper back and don’t tell anyone what it says. If the pedestal has a ``restriction’’ the location will be written on the item card for the pedestal. If the relic attunement \textbf{does not} match, put the relic either on the floor next to the pedestal, or on a nearby table/etc. If the location \textbf{does} match the ``restriction.’’ Just put the relic back on the pedestal.
The time delay is \textbf{important} here. It prevents this mechanic from being abused to side step other mechanics in the game. Don’t cut it short.
\textbf{Relics attuned to the school} always match whatever restriction is listed

Mechanics we would like your help keeping tabs on:
Players are directed to tell either a GM or the Principal when certain steps of the Preparations for the Ritual to Control the Storm are completed. As an NPC, you are authorized to verify that the thing has been accomplished. Please come to GM HQ and mark off the tasks, with any necessary notes on whether they were only partially successful, on the copy of the \gPreparingTheRitual{} greensheet that will be stationed there permanently.
You have a copy of this sheet to keep on your person, however we REALLY need you to mark it off in GM HQ so everyone can see at a glance how progress is going.
You are primary on point for keeping track of this progress, but if players can’t find you, they may tell one of the GMs something instead. We’ll mark it on the greensheet in GM HQ.

Pacing Notes:
Expected pacing on Research into the History of \pEarth{}.
Tell the GMs when the players inform you to open your ``W Packet’’


Timeline to reach Divine Realm. Check in with someone on the following teams Saturday asap after dinner
\cFlowPriest{}, \cCurse{}, \cAmbition{}, \cAssistantScientist{}; need to sus out whether they are prepared to plant the \iBeansMB{} tonight - may require great finesse if the group has not gone public with their work.
\cDisney{}, \cTechStar{}, \cWildCard{} about progress on restoring \cDisney{}’s memories.

\end{document}

