\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gPhysicalLayer{}}

Repairing the magical protections on the bunker will involve a \textbf{lot} of running around and collecting the shards of the previous protections that have scattered across the \pSc{}. You are encouraged to remember that many hands make light the work.

You must retrieve \textbf{8 pieces} to construct \textbf{1 puzzle} for each bunker that is damaged (you start with the center piece). If only 1 bunker is damaged, you need only retrieve 8 total pieces. If more than one is damaged, you will need more pieces.

The shards of the magical protections left faint traces when they were scattered. You can follow these to the probable locations for where to find the shards. Once you find the location however, you will still need to figure out the specific requirements to recover that particular shard.

In each case, you are looking for bricks that glow a particular color. When you find one, the sign will say “You may not interact with this sign unless you know otherwise. Once you find a mechanic that prompts you to search for ``glowing bricks,’’ you may read the rest of this sign.” This mechanic is you knowing otherwise. You may read the sign, which will specify the requirements for retrieving the shard of magical protection lodged there.

Once you complete the requirement, you may retrieve the puzzle piece from the envelope, and then \textbf{discard the entire sign to the nearest stock} so it is easy to keep track of which pieces have been retrieved. Any retrieved puzzle pieces (with their associated item cards) are \textbf{in game items} that can be lost/stolen/etc.

Your clues for where to look:
\begin{enumerate}
  \item \textbf{Corner Pieces}
  \begin{enumerate}
    \item Can be found in \textbf{inside} locations
    \item Look for \textbf{red} glowing bricks or stones.
    \item Retrieving them will require a keen mind for word puzzles and the like.
  \end{enumerate}  
  \item \textbf{Edge Pieces}
  \begin{enumerate}
    \item Can be found in all kinds of locations, but mostly \textbf{outside} locations, \textbf{the library}, and \textbf{The Old Wing of the \pSc{}}.
    \item Look for \textbf{blue} glowing bricks or stones.
    \item Retrieving them will require the cooperation of many different groups of people.
  \end{enumerate}  
\end{enumerate}

\textbf{Once the puzzle is complete}, update the capacity of the appropriate bunker by \textbf{+4} (the appropriate bunker is the one the center piece came from). If this is the last repair, (the bunker can now protect 13 people) you may remove the ``Damaged Bunker’’ sign to reveal the one below it.
\end{document}

