\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gHealingRelic{}}

You may use this Relic to cast healing magic normally reserved exclusively for the clerics of \cFarmGod{}. 

\textbf{Number of Uses: U; Relic must be attuned somewhere.}

To use this relic to heal:
\begin{enumerate}
  \item The ``\iPitcher{}'' \textbf{MUST} be attuned to someplace in order to use this ability.
  \begin{enumerate}
    \item Check the item-envelope to see if there is a piece of paper inside it (do not read the paper; do not even pull it out of the envelope if you can avoid it).
    \item If there is \textbf{no} paper, this ability \textbf{cannot} be used until the Relic is re-attuned to someplace.
    \item Using this ability will cause the Relic to become de-attuned.
  \end{enumerate}
  \item You must be within 1 ZoC of the person to be healed.
  \item You must declare your desired effect out loud. Your options are:
  \begin{enumerate}
    \item Completely restore an individual to their max CR.
    \item Immediately revive an unconscious target.
    \item Resuscitate an apparently dead target if they have been dead for less than \textbf{5 minutes.} - The 5 min applies to when you begin the ritual.
  \end{enumerate}
  \item Call out the following: ``\cFarmGod{}, heed my call. See <Name of target> here before me. Lend us your healing warmth.’’ Then, state the effect you wish to have happen out loud (e.g.: Restore their magical energy.) You cannot conceal from anyone listening what your intentions are.
  \item Mime pouring liquid over the person to be healed. They become \textbf{wet} for 20 minutes after this effect, and should tell this to people they meet.
  \item If the desired effect applies to the situation, it now takes effect.
  \item Open the item-envelope for the ``\iPitcher{},'' take out the piece of paper inside without reading it, and discard it to the nearest stock or give it to the nearest GM.
  \begin{enumerate}
    \item \textbf{DO NOT} read what the piece of paper said.
  \end{enumerate}
\end{enumerate}


\end{document}
