\documentclass[green]{GL2020}
\parindent=0pt
\begin{document}
\name{\gInvisible{}}

\emph{Uses: Unlimited; relic must be attuned} 

You may use this locket to become invisible. temporarily.To do so requires:

\begin{enumerate}
	\item The \iLocket{} \textbf{MUST} be attuned to someplace in order to use this ability:
	\begin{enumerate}
		\item You may open the envelope at any time to check if there is a piece of paper inside. \textbf{DO NOT READ the paper if present.}
		\item  If there is no paper, this ability \textbf{CANNOT} be used until the Relic is re-attuned to someplace.
		\item \textbf{Using this ability will cause the Relic to become de-attuned.}
	\end{enumerate}
	\item Switch your badge to ``Not Here.'' Put your fist on your head (OOC symbol) and start a 5 min timer. Your character is now invisible and silent and can move freely/listen in to any conversation that is not magically protected from eavesdropping (people in such a conversation will tell you so).
	\begin{enumerate}
		\item You may dispel the effect early if you choose to.
		\item You may take no actions other than listening while invisible. (no waylaying people from invisible)
	\end{enumerate}
	\item At the end of the 5 minutes or if you choose to dispel the effect early, the locket becomes deattuned:
	\begin{enumerate}
		\item Open the item-envelope for the \iLocket{}, take out the piece of paper inside and discard it to the nearest stock or give it to the nearest GM.
		\item DO NOT read what the piece of paper said.
	\end{enumerate}
\end{enumerate}

\end{document}
