\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gRestoringLove{}}

Losing your romantic relationship with \cHeadScientist{\full} was the last straw. No matter how much you believe in the \pGoaties{}’ mission, you just can’t be part of it any more. But just leaving the \pGoaties{} will not restore \cHeadScientist{}’s memories of your time together. You aren’t sure it’s possible to do that. But you’ve got to try. The relationship the two of you had meant so much to both of you.

Your best guess right now is to try to recreate touchstones of your relationship with \cHeadScientist{}; hopefully without weirding \cHeadScientist{\them} out so much that \cHeadScientist{\they} won’t talk to you (starting with claiming a forgotten relationship and confessing to being part of a secret, blasphemous cult is a great way to weird \cHeadScientist{\them} out so \cHeadScientist{\they} won’t talk to you. Don’t do that.) You hope that the touchstones will spark individual memories to return. And you don’t necessarily have to do this alone. \cInitiate{\full} has already volunteered \cInitiate{\themself} to help, and of course your friend \cLibrarian{}.

To restore \cHeadScientist{}’s memories of you, complete the following tasks. Please try to complete the tasks in order, but if you stall out on one for too long, you may skip over it. Once you complete \textbf{task 8} however, you may not go back and complete others for the purposes of this mechanic. After each task, wait approximately 5 minutes, then ask a nearby player or GM to tell \cHeadScientist{} to open the relevant page in \cHeadScientist{\their} mem-book entitled ``\mIdleThoughts{}.’’

\begin{enumerate}
  \item Talk to \cLibrarian{\full} about memory loss, to see if they know anything, or can point you toward any resources. Do the same with one of the three librarian assistants: \cAmbition{\full}, \cLibAssist{\full}, and \cPresident{\full}.
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 1} of \cHeadScientist{\their} mem-book. 
  \end{itemize}
  \item Talk to \cHeadScientist{} 1:1 for at least 3 minutes; engage in pleasantries as if to get to know each other. \cHeadScientist{} doesn’t remember you \textbf{at all} and it’s important you ease into this and don’t scare \cHeadScientist{\them} off.
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 2} of \cHeadScientist{\their} mem-book.
  \end{itemize}
  \item The two of you used to help each other out all the time. Get a genuine “thank you” from helping \cHeadScientist{} somehow.
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 3} of \cHeadScientist{\their} mem-book.
  \end{itemize}
  \item Perhaps proximity to talk of romance might spark some memories for \cHeadScientist{}? Engage in conversation with \cHeadScientist{} and at least 2 other people (doesn’t have to be the same conversation) about the \textbf{other} people’s current romantic situation or prospects.
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 4} of \cHeadScientist{\their} mem-book.
  \end{itemize}
  \item On those occasions that you could get away from your duties to the \pGoaties{} and responsibilities as a teacher, the two of you would share meals and talk for hours. Share a meal or snack with \cHeadScientist{}, either by actually sitting together at a meal and engaging in soft RP, or by roleplaying doing so, together in the Great Hall at a time other than meals.
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 5} of \cHeadScientist{\their} mem-book.
  \end{itemize}
  \item You used to send \cHeadScientist{} flowers whenever you couldn’t be together. Maybe a bouquet including a \iBlackCrocus{} will spark a memory? Black Crocuses are \cHeadScientist{}’s secret favorite flower. When \cHeadScientist{\they} told you this, \cHeadScientist{\they} explained that it was a secret \cHeadScientist{\they} were sharing with you because \cHeadScientist{} believed you to be \cHeadScientist{\their} true love. Present \cHeadScientist{} with a bouquet of flowers (collect 3 or more item-cards of flowers, at least one of which must be a ``\iBlackCrocus{}''.)
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 6} of \cHeadScientist{\their} mem-book.
  \end{itemize}
  \item Consensually hold hands with \cHeadScientist{} (default is to mime this; ask before actually physically touching another player.)
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 7} of \cHeadScientist{\their} mem-book.
  \end{itemize}
  \item Complete your escape from the FoG (see the greensheet).
  \begin{itemize}
    \item Have \cHeadScientist{} open \textbf{Page 8} of \cHeadScientist{\their} mem-book.
  \end{itemize}
\end{enumerate}

\end{document}

