\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gRitualControlStorm{}}
\textbf{This greensheet is publicly viewable by everyone.} A copy is available in the GreatHall. \cPrincipal{\full} and \cChupSecond{\full} also have copies. \cChupSecond{} has been tasked with overseeing the students' design, any walkthroughs deemed necessary, and the final execution of this ritual. 

At each Time of Deciding, the students design their own Ritual to Control the Storm. Below follows a list of common components of such rituals, and various considerations you may wish to take into account. \emph{OOC Note: If you have a cool idea for something to do for this ritual that isn’t listed, feel free to do that instead/as well!)}

While anyone can offer advice on designing the ritual, the students have the final say. The ritual \textbf{must} have at least one designated ritual leader who will guide the actual execution of the ritual starting at 1:30 pm on Sunday Afternoon. Having more than 3 ritual leaders is not recommended. \textbf{The ritual leader(s) must write down the plan and give it to the GMs by 1:00 pm on Sunday so that the GMs can make their own preparations for when and how to interrupt with descriptions of what is happening in the environment as the ritual proceeds.}

\textbf{Requirements for your design:}
\begin{enumerate}
  \item The relics, their pedestals, and The Storm Seed must be included somehow.
  \item The ritual should take between 5 and 15 minutes to complete.
  \item The ritual should involve as many of the 37 characters in game as possible in some active way. Characters can be grouped for this (e.g.: all teachers clap a rhythm.) — participants should get to feel cool doing whatever they are being asked to do.
  \item Be aware of mobility issues and ensure your plans allow for participants to be seated/stationary for part or all of the ritual if they need it, and still be able to participate.
\end{enumerate}

\textbf{Components often Employed in this Ritual:}
\begin{enumerate}
  \item Positioning the relics and the \sStormSeed{} within the ritual circle.
  \item Having a Grand Procession into the Ritual Space.
  \item Arranging people around/within the ritual circle in specific groups.
  \item One or more clerics blessing the space, the relics, or the participants.
  \item One or more characters making speeches.
  \item The use of ritual candles.
  \item Passing objects around the circle.
  \item Call-and-repeat sequences.
  \item Repetitive vocal (e.g. singing, humming, etc.) and/or physical activities (e.g. clapping, stomping, hand gestures).
  \item Moments of silence / stillness.
\end{enumerate}

Depending on exactly how long this ritual takes, characters will have approximately 30 minutes after the conclusion of this ritual before the game ends.

\emph{OOC: Below is a default ritual that can be performed if the Students are not interested in designing a ritual themselves. It also serves a an example if they need inspiration.}

\textbf{Default Ritual:}
\cPrincipal{}, \cChupSecond{} and the 3 designated student leaders may speak or step out of the ritual positioning at any point to help with directions for other characters. Other participants should generally remain quiet unless directed otherwise.

\textbf{Items used in this ritual cannot be stolen/removed during the ritual.} The incredibly powerful magic of the ritual prevents it.

\begin{enumerate}
	\item Ensure that the Storm Seed is placed in easy access of the ritual circle (can be inside it). Place a small container of some kind in the middle of the ritual circle; this container is OOC. The relics for the ritual will have already been locked in place on their pedestals.
\item The entry procession:
	\begin{enumerate}
\item Collect 37 Ritual Candles in a container, or place on a table in the ritual space, near whichever entrance you designate.
\item Clear the ritual space of everyone except the current Principal of the School. This may be \cPrincipal{}, or whoever \cPrincipal{\theyhave} chosen as \cPrincipal{\their} successor.
\item Have the \textbf{advisors} enter the space one at a time.The Principal greets each one in a manner of their choosing (nod, bow, high five, hug, etc.). The Principal then hands them \textbf{3} ritual candles.
\item Advisors array themselves behind the Principal, in a line facing the entrance.
\item Have the \textbf{teachers} enter the space one at a time. The Principal greets each one in a manner of their choosing.
\item Advisors with 3 candles may offer up 2 of them.  Each teacher approaches an advisor, accepts the 2 candles, and stands in front of the advisor, facing the entrance. Nods or bows may be exchanged. Each new teacher to enter will have fewer choices of advisors to accept a candle from. There is no mechanical consequence to who each teacher picks.
\item If an advisor refuses to participate, the Principal can fill in as many times as needed, but those teachers will end up standing in front of an empty spot.
\item Have the \textbf{students} enter the space one at a time. The Principal greets each one in a manner of their choosing.
\item Teachers with 2 candles offer up 1 of them. Each student approaches a teacher, accepts the candle, and stands in front of the teacher, facing the entrance. Nods or bows may be exchanged. Each new student to enter will have fewer choices of teachers to accept a candle from. There is no mechanical consequence to who each student picks.
\item If a teacher refuses to participate, the Principal can fill in as many times as needed, but those students will end up standing in front of an empty spot.
\item NOTE: Firings, Hirings, Promotions, etc. do NOT change the role a character plays in this part of the ritual (e.g. a student hired as a teacher would still participate as a student.)
\item From one end of the line, the students will proceed to the ritual circle, and surround it, facing inward.
\item Teachers will follow after, and finally advisors, forming 2 concentric circles behind the students. The Principal may choose to stand with the teachers, or stand apart, behind the advisors.
\end{enumerate}
\item Focusing the Ritual Energy:
\begin{enumerate}
\item Students all turn to their right, teachers to the left, and advisors to the right. All 3 circles walk slowly around the ritual circle while one of the student leaders counts out 10 steps. 
\item Everyone reversed directions (students now facing left) repeat counting out 10 steps. Everyone turns back to face the middle.
\item One of the student leaders begins to clap a slow rhythm, participants join.
\item A second student leader begins a vocalization (like humming or another short noise to repeat), participants join.
\item The third student leader picks up the Storm Seed and holds it aloft for all to see.
\item The first student leader adds a gesture between claps, perhaps a hand to one’s heart, or pointing toward the Storm Seed. Participants join.
\item The second student leader increases the volume and/or speed of the vocalization. Participants join.
\item The 3rd student leader lowers the Storm Seed and pours the contents of it out into the container in middle of the ritual circle, and places the Storm Seed down. When they are finished, they call for \textbf{silence.} (Pour from a fairly low position to avoid CR tokens from jumping out of the container and scattering across the space.)
\end{enumerate}
\item Claiming your Authority:
\begin{enumerate}
\item This section is a series of calls and responses/repeats. The student leaders can alternate leading these. For this section, if characters have changed nations or cohorts they may decide to speak with their new one, or their original one.
\item “We are the Students of the \pSchool{}” $<$All students repeat statement$>$.
\item “We are the Teachers of the \pSchool{}” $<$All Teachers repeat statement$>$.
	\item “We are the Advisors of the \pSchool{}” $<$All Advisors repeat statement$>$.
\item “We are the \pFarm{}” $<$All \pFarm{} repeat statement$>$.
\item “We are the \pTech{}” $<$All \pTechies{} repeat statement$>$.
\item “We are the \pShip{}” $<$All \pShippies{} repeat statement$>$.
\item “We are the Children of the Gods” $<$All characters repeat statement$>$.
\item “The storm goes where we will it.” $<$All characters repeat statement$>$.
\end{enumerate}
\item Invoking the Relics:
\begin{enumerate}
\item Each student leader designates a Cleric to step into the middle of the ritual circle and bless one of the relics. If other components have been included in the ritual, it is optional to bless those as well. Clerics return to their spots when the blessing is complete.
\item A student leader sets the teachers to a repetitive motion and sound. The advisors can be set to the same motion and sound, or different ones.
\item Each relic (and any extra component) should be picked up one at a time and passed around the circle of students, then returned to its place
\end{enumerate} 
\item The 3 student leaders step into the middle of the ritual circle. A GM will whisper to the student leaders where the storm is sent.
\item All students chant “The storm goes where we will it” over and over until the Student Leaders call for silence. (recommend no more than 5x repetition)
\item The three students leaders speak in unison: “The storm is sent to $<$Location$>$.”
\end{enumerate}

The ritual is now complete. All students may roleplay feeling exhausted.


\end{document}

