\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gRitualDivineRealm{}}

This ritual was created through the painstaking work of dozens of \cDisneySect{} over decades of work in the strictest of secrecy. The mainstream church of \cFarmGod{} outright banned any attempts to reach the Divine Realm, stating that if the Deities wanted humanity there, that they never would have severed the connection. The \cDisneySect{} felt differently. 

If you choose to undertake this dangerous and blasphemous ritual, you will be transported to the Realm of the Gods, but at a cost. Deep under the Bones of the World, where the \cDisneySect{}' hidden temple was (before it was destroyed), flowed a tributary of the River of Forgetting, which is required for this ritual. The \cDisneySect{} were also convinced that the River reaches the \pSchool{}. This ritual \textbf{MUST} happen at ``The River of Forgetting'' in the deepest part of the Library.

As with other rituals, you should expect to need to teach/explain this ritual to your other participants. Never assume someone else knows all the steps as well as you do \emph{(OOC: Not everyone has the greensheet in front of them; you have to explain to them how to participate.)}

\begin{enumerate}
    \item Assemble everybody who wishes to participate in the ritual at ``The River of Forgetting.'' You will need one \iGlassVial{} and one \iRitualCandle{} textbf{per person}.
    \item \textbf{You MUST honestly tell anyone participating in this ritual that:}
    \begin{itemize}
        \item This ritual will transport us to the Divine Realm. We will all arrive together, but do not need to stay together once we are there.
        \item Your mortal body will be protected for the duration of your time in the Divine Realm. No harm can come to it.
        \item You can return any time by returning to the location at which we arrive.
        \item The cost for the ritual is extracted from each person participating when they leave the Divine Realm. That cost is that you must either \textbf{permanently} give up a significant memory, OR, you must share a major secret of your own with someone else. (It doesn't count if the other person already knows the secret!)
        \item Once you return from the Divine Realm, you will be able to perform this ritual yourself. Stop by GM HQ to grab a copy of this greensheet from ``\sSignG{}''.
        \item All three branches of the mainstream church think that going to the Divine Realm is blasphemous.
    \end{itemize}
    \begin{itemize}
        \item Form a circle. Direct each participant one at a time to mime scooping water from the river with their hands and drinking it, then return to their place in the circle. The Ritual Leader should drink last. This will \textbf{not} cause immediate memory loss like normal, though you will pay the aforementioned price when you return from the Divine Realm.
        \item Starting with the Ritual Leader, each person must briefly share why they wish to travel to the Divine Realm, to infuse the ritual with intentionality. (The reason shared need not be the whole true, but it must be at least partially true.)
        \item One at a time, each participant must mime placing their \iRitualCandle{} inside their \iGlassVial{} and placing the \iGlassVial{} gently into the river, then return to the circle. (Hold on to these items!)
        \item While watching the candles float away down the river, the Ritual Leader starts a call and response: ``I'm floating. I'm drifting.'' <other participants repeat.> The group should repeat the full call and response 5 times.
        \item Direct the group to turn their badges to display ``Not Here'', and place their fist on their head (or equivalent), signaling that they are out of game. Your souls have left your bodies and are transported to the Divine Realm by the floating candles; \textbf{the ritual conceals and protects your bodies while they remain in the Mortal Plane}.
        \item Relocate to ``The River Lethe'' in the Divine Realm, then turn your badges back around and go into character. If no one in your group knows where this is, find a GM and we will take you there.
        \item When you wish to return to your body in the Mortal Plane, return to ``The River Lethe'' in the Divine Realm. You must then either \textbf{permanently} give up a significant memory, OR you must share a major secret of your own with someone else. (It doesn't count if the other person already knows the secret!) Once you have done this, turn your badges to display ``Not Here'', and place your fist on your head (or equivalent), signaling that you are out of game. 
       \item Relocate to ``The River of Forgetting'' in the Library (page 56), then turn your badges back around and go into character. You still have the \iRitualCandle{} and \iGlassVial{} you used in the ritual, as they return to the Mortal Plane with you.
    \end{itemize}
\end{enumerate}

\end{document}


