\documentclass[green]{GL2020}
\parindent=0pt
\begin{document}
\name{\gSealingFaledonHeir{}}

You have been charged by \cFaledonParent{\full}, the current head of the \cFaledonParent{\formal} with the unenviable task of Sealing the \cFaledonParent{\formal} heir this weekend. \cHeir{} being at the Time of Deciding is a big milestone in \cHeir{\their} life and \cFaledonParent{} believes it is time to pass on the mantle of Head of the Family. \cFaledonParent{} seems oblivious to the fact that \cHeir{} wants nothing to do with the role.

Your neck is on the line because if you *don’t* come home with a Sealed Heir (a.k.a. A new head of the \cFaledonParent{\formal} household), you will lose your privileged relationship with the family, and your role in the \pTech{} government will be withdrawn. In other words, it will end your career and you are probably too old to claw your way back to favor.

When to perform this ritual is a balancing act. On the one hand, getting it out of the way as soon as possible would allow you to focus on other important matters about the Time of Deciding. On the other hand, the longer you wait, the more of \cHeir{}'s accomplishments you'll have to celebrate (e.g. A role in the Ceremony of Excellence, having won the most voting authority, helped with preparations for the ritual, etc.)

To Seal the Faledon Heir, you must enact the following:
\begin{enumerate}
  \item Collect the following in a location that you feel reflects the true nature of the Heir-apparent.
    \begin{enumerate}
      \item The ``\iFaledonRing{}'' (this starts in your possession; don’t lose it).
      \item At least one Cleric from \cTech{}.
      \item 3 Ritual Candles.
      \item The person you are Sealing as the Head of the \cFaledonParent{\formal} household (referred to in this document as the ``Heir-apparent’’). This person \textbf{must have an F-Score = 1} (you may freely ask players for their F-Score). You are presuming this must be \cHeir{}, as they are the oldest living child of the \cFaledonParent{\formal} family. The heir-apparent must either be willing or restrained (they may not be unconscious).
      \item At least 2 additional witnesses. (more is always better for a grand event such as this)
    \end{enumerate}
  \item Distribute the Ritual candles to yourself, the Cleric, and the Heir-apparent.
  \item Take out the ``\iFaledonRing{}'', hold it up/out and explain to all assembled its significance as the symbol of the head of the \cFaledonParent{\formal} family.
  \item Have the cleric form the beginning of a single file line in front of the Heir-apparent. Have the witnesses line up behind the cleric. Hand the signet ring to the cleric. Have them approach the heir-apparent, hold the ring up/out and say ``May you bring greatness to the Faledon Family.''They should then turn around and hand the ring to the next audience member. The last audience member should hand the ring to you.
  \item Direct the audience to collect on one side and the heir-apparent on the other, with yourself and the Cleric in between.
  \item Have the Cleric say a blessing over the Heir-apparent in the name of \cTechGod{}. Then hold their candle out in front of them, and circle the Heir-apparent 3 times. They should stop at the heir-apparent’s left shoulder, facing the audience.
    \begin{enumerate}
      \item Normally a cleric cannot bless someone without their consent. This mechanic overrides that.
    \end{enumerate}
  \item You should now make a short speech (1-2 min) to those assembled about the accomplishments of the heir-apparent this weekend, and throughout their life up until now. Then, hold your ritual candle out, and circle the Heir-apparent 3 times. Stop at the heir-apparent’s right shoulder, facing the audience.
  \item Ideally the Heir-Apparent will now make a short speech (1-2 min) about how they plan to elevate the \cFaledonParent{\formal} family as its Head of the House, but if you are coercing them, they may refuse to do so.
  \item Lead the audience in some sort of cheer. (E.g.: ``3 cheers for the new head of the \cFaledonParent{\formal} family. Hip, hip, hurray!...’’).
  \item Give the ``\iFaledonRing{}'' to the Heir-Apparent. (if they are restrained, they cannot refuse the item.)
  \item Return the 3 ritual candles to the nearest stock; they have been consumed  by the ritual.
\end{enumerate}

The ritual is now concluded, the role of Head of the \cFaledonParent{\formal} family is now bestowed upon the former heir-apparent, and your job in this is done.

\end{document}
