\documentclass[green]{GL2020}

\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{ltablex}
\usepackage{tabularx}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
\setlength{\columnsep}{1cm}

\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gStormSurgeOutside{}}

If you are unable to take shelter inside a bunker during one of the 3 storm surges, consult the nearest one of these signs to see what consequences (if any) you suffer. Different areas have slightly different risks of consequences.

Because this is an IC outdoor space, you will end up soaking wet and cold. You must also roll a D20 to see if you suffer any additional consequences. If your V-score = 1 or 2, roll twice and take the higher.

{\large For the \textbf{Friday night} surge, there are \textbf{no modifiers} to the roll.}\\
{\large On \textbf{Saturday afternoon}, you will \textbf{subtract 6} from whatever you roll.}\\
{\large on \textbf{Sunday Morning}, you will \textbf{subtract 9} from whatever you roll.}\\

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}c | >{\centering\arraybackslash}X |}
\hline
  {\large Your Total} & {\large Consequence}  \\
\hline
 \textbf{-8 to -6} &  You have been afflicted with the \iSlowActingPoison{}. Go to the ``\sStormSurgeConsequences{}'' sign in GM HQ to pick up a copy of the effects for your reference. \\
\hline
 \textbf{-5 to -3} & You have been afflicted with ``\gBadLuckCurse{}''. Go to the ``\sStormSurgeConsequences{}'' sign in GM HQ to pick up a copy of the effects for your reference. \\
\hline
 \textbf{-2 to 0} & Your current and max CR are reduced by 1. This cannot be healed by normal healing magic. It would take the power of a Relic or something greater to repair.  \\
\hline
 \textbf{1 to 3} & Knocked out for 5 min starting at the end of the storm surge.  \\
\hline
  \textbf{4 to 6} & Struck deaf or blind (player’s choice) for 5 minutes starting at the end of the storm surge.  \\
\hline
  \textbf{7 to 9} & Minus 1 CR until the next meal. Drop one of your CR stones in the nearest stock to remind you of this.  \\
\hline
  \textbf{10 to 12} & Lose a random item (give it to a GM).  \\
\hline
 \textbf{19 to 20} & Gain +1 CR until the next meal. Pick up an extra CR stone from the nearest stock to remind you of this.  \\
\hline
\end{tabularx}

\end{document}

