\documentclass[green]{GL2020}

\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{ltablex}
\usepackage{tabularx}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
\renewcommand{\arraystretch}{1.5}
\setlength{\columnsep}{1cm}

\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gTallyingVotes{}}

Count total votes by desired location. Each student gets between 1 and 5 votes, with some vote switching, and a few anonymous options. Use tally marks to count the votes
\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}X |>{\centering\arraybackslash}m {8cm} |}
\hline
	\textbf{Location} & Num of Votes \\
\hline
	\pFarm{}	&	\\
\hline	
	\pTech{}	&	\\
\hline	
	\pShip{}	&	\\
\hline	
	\pSchool{}	&	\\
\hline	
	Coor. Zero	&	\\
\hline	
	Coor. One	&	\\
\hline	
\end{tabularx}

Count relic attunement: For the \textbf{School}, 1 relic must be attuned to it for it to be a valid target. If none are attuned, then student and treaty votes toward the school fizzle.  For either Divine location (Coordinate Zero or One), the Lightning rod must have been incorporated into the preparations. Each relic is worth 6 votes \textbf{except} a relic attuned to the school is worth 8 votes instead.

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}X |>{\centering\arraybackslash} m{6cm} |}
\hline
	\textbf{Relic} & \textbf{Attuned To (worth 6 or 8 votes)} \\
\hline
\hline
	Relic 1	&	\\
\hline
	Relic 2	&	\\
\hline
	Relic 3	&	\\
\hline
\end{tabularx}


Any treaty in place that declares a target for the Storm also affects where the storm will go. Record below where any treaty says the Storm should go. At game start the ``End of Suffering’’ treaty is in place, and declares the target to be the \pShip{}. If the ``End of Suffering’’ treaty is nullified, and no new target declared, the Treaty portion of the storm control fizzles.

\vspace{2cm}

Treaty Target: \rule{8cm}{0.4pt}

\vfill

\subsection*{Final Summary}
Use the table below to collect the results from the three components that influence the Storm direction. If there is a tie (all 3 components direct the storm differently), the Votes from the Students trumps the other two. 
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}X |>{\centering\arraybackslash}X |>{\centering\arraybackslash}X | >{\centering\arraybackslash}X  | >{\centering\arraybackslash} m{2.5cm} |}

\hline
	Location & 	Student Votes  & Relic Votes (+6,+8) & Treaty Vote (+18) & Total \\
\hline
\hline
	\pFarm{} &	&	& & \\
\hline
	\pTech{} &	&	& & \\
\hline
	\pShip{} &	&	& & \\
\hline
	\pSchool{} &	&	& & \\
\hline
	Coor. Zero &	&	& & \\
\hline
	Coor One &	&	& & \\
\hline
\hline
\multicolumn{2}{|C{6cm}|}{\textbf{Target with Highest Total: (This is where the storm is going)}} & \multicolumn{3}{|c|}{} \\
\hline
\end{tabularx}


\end{document}

