\documentclass[green]{GL2020}
\parindent=0pt
\begin{document}
\name{\gVotingInstructions{}}

This document outlines how voting to guide the Storm works. For students struggling to decide how to cast their votes, Ethics Professor \cEthics{\full} has offered their services in thinking through how to balance all the conflicting pressures. The Principal and his designees will distribute the voting stones to the students Sunday morning shortly after game-on. Stones will be attached to item-envelopes. 

\textbf{Unless a mechanic explicitly states otherwise, stones may not be stolen, traded, or stashed; you must carry them on your person until you are ready to submit your votes.} However, some teachers may have the ability to transfer votes from one willing student to another. Students with multiple voting stones may choose to split their votes however they like. Once you have received your stones, you may cast your votes anytime \textbf{up until the 11:30am deadline.} To cast your votes, follow these steps:

\begin{enumerate}
  \item Write your name on the outside of the envelope attached to the voting stone just before submitting. Make sure to write legibly. You cannot put anyone else’s name on it.
  \item Open the envelope, remove the enclosed piece of paper, write your vote for the destination of the Storm on the paper, and replace it inside the envelope.
  \item Place the envelope (with the stone attached) in the voting box.
\end{enumerate}

You must complete steps 1-3 with 1 vote before starting another (it is theoretically possible for someone to do something to one of your other voting stones while you are submitting the first one). You may \textbf{not} fill in the voting slip inside the voting stone and then carry the voting stone around. To the best of your ability, it \textbf{must} go straight into the ballot box after you have filled it out. Only an explicit mechanic can interrupt this.

GMs will tally the vote over lunch, and reveal the result at the appropriate point in the ritual to guide the Storm. Final counts will not be provided in game - only the revelation of where the Storm is headed.

\end{document}
