\documentclass[green]{GL2020}

\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{ltablex}
\usepackage{tabularx}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
\setlength{\columnsep}{1cm}


\parindent=0pt
\begin{document}
\name{\gWeekendSchedule{}}

Below is the full event schedule, including both in game and out of game events as of 16Jan2022. \textbf{While there are a number of activities scheduled throughout the weekend, there is also lots of time that is unstructured, for characters to run around and do whatever they judge fit.} Not all of the structured activities are required either, but they can be good places to find people and learn things.

Since post game activities affect when carpools can leave, players should plan to be on site until 5 pm on Sunday, even if they personally wish to opt out of post game workshops.

This schedule is subject to change between now and game start as in and out of game needs mandate. We will have a final copy of the schedule at game, which will supersede this one if any changes are made.

%%%%%%%% Meal times: 8 am, 12 pm, 5:30 pm

For workshops on Friday afternoon, you should plan the following:
\begin{itemize}
	\item Pack a jacket and sunscreen in an easily accessible place, we will be outside the whole time, and you may want to grab one or both.
	\item Bring camp chairs or similar if you have them, workshops and orientation are almost 4 hours, and that is a very long time to be on your feet. Even if you don’t need them, or need them the whole time, someone else may benefit greatly from borrowing them.
\end{itemize}

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash} m{1.5cm} | >{\centering\arraybackslash} m{1.8cm} | >{\centering\arraybackslash} m{1.8cm} | >{\centering\arraybackslash}X |}
 \hline
\multicolumn{4}{|c|}{\textbf{Friday (Pre-Game Activities) 12:00 pm}} \\
\hline 
 \emph{Time} & \emph{Location} & \emph{Event} & \emph{Description}\\
\hline
 12:00 pm - 1:00 pm   & Dining hall & Registration and mingling over lunch &  Players will need to check in with the logistics team. Hard copies of game material will be provided at this time. Lunch is only served for 1 hour, starting at \textbf{noon}, so either please do not be late, or plan to bring your own food to tide you over until dinner. \\
    \hline
  1:00 pm - 1:15 pm  & Band Shell  & Orientation for Workshops & We will walk to the Band Shell from Dining hall together. GMs will address all players to explain how workshops will work. The workshops are designed to help players get into character, create shared cultural touchpoints, and foster trust among players.The workshops are also designed to help players enter and exit game play safely and for GMs to reiterate rules and expectations, and for everyone to ask questions. \\
    \hline
  1:15 pm - 2:15 pm & Band Shell & Workshop by Country & For workshop 1, players will be split up by home nation. In this workshop we will introduce players and characters, and then spend some time creating cultural touchstones. We will also take some time to reflect on the impact that the war has had on the nation, and on the characters.  \\
    \hline
  2:20 pm - 3:20 pm & Band Shell  & Workshop by Cohort & For workshop 2, players will be split up by cohort (student, teacher, advisor). In this workshop we will introduce players and characters again, and then spend some time creating cultural touchstones. We will also take some time to reflect on the Time of Deciding, and the role each cohort plays in it. \\
 \hline
  3:25 pm - 4:25 pm & Band Shell  & Safety, Combat, and Calibration & For workshop 3, players will be split up by the GMs in a mix across nation and cohort. In this workshop we will introduce players and characters one last time. We will talk about safety in a broad sense, and then review and practice the safety mechanics for this game in specific. We will practice the combat mechanic. Lastly, we will take some time to reflect on how magic is integral in these character’s lives and the world. \\
 \hline
  4:30 pm - 5:00 pm & Band Shell  & Logistics Briefing & Logistics team will review camp and game policies with all players. \\
 \hline
 5:00 pm - 5:30 pm & Sleeping Spaces  & Load-in to sleeping spaces & Time for players to unpack from cars into sleeping spaces. Cars should ultimately end up parked in the lot behind the Band Shell. \\
 \hline
  5:30 pm - 6:30 pm & Dining Hall & Dinner. & Please eat food! This is also time to hang out and do any calibration you need to with other players you haven't had a chance to interact with before this point. \\
 \hline
  6:30 pm - 7:30 pm & Sleeping Spaces  & Costuming Time & Time to get into costume, continue unpacking, continue calibration, ask GMs last minute questions, etc. \\
 \hline
\multicolumn{4}{|c|}{\textbf{GAME ON 7:30 pm}} \\
\hline 
7:30 pm & Gyro Lodge & Game Starts & \cPrincipal{\full} should have a few words to say to start the weekend. \\
 \hline
  8:30 pm - 9:00 pm & Jay Cabins  & First Storm Surge & Characters should probably take shelter in the bunkers. Traditionally characters shelter by country during this surge, but it is not mandatory. \\
\hline
  10 pm & Everywhere / Aviary  & Quiet Hours Start; GM HQ Closes & Starting at this time, please keep noise from ongoing game activities quiet. No shouting or we’ll get in trouble with the venue. Please respect players who wish to go to sleep, and move game play outside, or to other areas when necessary. The GM HQ will also close at this time so GMs can go to bed or circulate for late night shenanigans. If you need something game related, it will have to wait till morning.\\
\hline
  12 am (midnight) & Everywhere  & Game Off & Please get some sleep. \\
    \hline
 \end{tabularx}
  

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash} m{1.5cm} | >{\centering\arraybackslash} m{1.8cm} | >{\centering\arraybackslash} m{1.8cm} | >{\centering\arraybackslash}X |}
 \hline
\multicolumn{4}{|c|}{\textbf{Saturday (Pre-Game Activities) 8:00 am}} \\
\hline
\emph{Time} & \emph{Location} & \emph{Event} & \emph{Description}\\
\hline
8:00 am - 9:00 am & Dining Hall & Breakfast & Please eat food! This meal is \textbf{out of game}.  \\
\hline 
9:00 am - 9:30 am & Sleeping Areas & Costuming Time & Time between breakfast and game-on to put costumes and makeup on.\\
\hline 
\multicolumn{4}{|c|}{\textbf{GAME ON 9:30 am}} \\
\hline
  9:30 am & Gyro Lodge & Game On & Game starts for the day. GMs may have game related announcements (IC or OOC) at this time, so please plan to attend.  \\
 \hline
  10:30 am - 11:00 am  & Gyro Lodge & Graduation Ceremony & \cMusic{} is in charge of organizing the Graduation Ceremony for those students who are graduating. Characters are encouraged, but not mandated to attend.  \\
 \hline
  12:00 pm - 1:00 pm & Dining Hall & Lunch & Please eat food! This meal is \textbf{in game}, but the food is not (no poison mechanics will involve real life food).   \\
 \hline
  2:00 pm - 2:30 pm & Jay Cabins & Second Storm Surge & Characters should probably take shelter in the bunkers. Traditionally characters shelter by job category during this surge, but it is not mandatory. \\
\hline
 3:30 pm - 4:00 pm & Gyro Lodge & Scientific Presentation. & \cHeadScientist{} and \cAssistantScientist{} are scheduled to present the details of the ongoing research into ending the Storms for good.\\
\hline
\multicolumn{4}{|c|}{\textbf{GAME OFF 4:30 pm}} \\
\hline
4:30 pm - 5:30 pm & Band Shell & Game Re-balancing. & While this activity is optional, it is highly encouraged. If you choose to skip this event, please respect that this is off game time and take a break on your own. This \textbf{OOC} activity on Saturday afternoon will be an opportunity for players to evaluate their play experience, and refocus if they wish. We will take some time to introspect on the play experience so far, and identify if there are things you wish to change about how you approach play, either internally, or interpersonally. We will close the activity by connecting players who feel overly busy, and those who feel bored or left out of play. These connections will have the opportunity to discuss player to player about how to bring characters into plots and share story. These conversations can continue into Dinner, which is \textbf{mandatorily} OOC. \\
\hline
 5:30 pm - 6:30 pm & Dining Hall & Dinner. & Please eat food! This meal is \textbf{out of game}.\\
\hline
\multicolumn{4}{|c|}{\textbf{GAME ON 6:30 pm}} \\
\hline
 9 pm & Aviary  & Voting Authority related mechanics due & Many players will need to submit information related to the mechanics for determining voting authority no later than 9 pm so GMs can tally it all up before morning.\\
\hline
  10 pm & Everywhere / Aviary  & Quiet Hours Start; GM HQ Closes & Starting at this time, please keep noise from ongoing game activities quiet. No shouting or we’ll get in trouble with the venue. Please respect players who wish to go to sleep, and move game play to other areas when necessary. The GM HQ will also close at this time so GMs can go to bed or circulate for late night shenanigans. If you need something game related, it will have to wait till morning.\\
\hline
  12 am (midnight) & Everywhere  & Game Off & Please get some sleep. \\
\hline
\end{tabularx}

\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash} m{1.5cm} | >{\centering\arraybackslash} m{1.8cm} | >{\centering\arraybackslash} m{1.8cm} | >{\centering\arraybackslash}X |}
\hline
\multicolumn{4}{|c|}{\textbf{Sunday (Pre-Game Activities) 8:00 am}} \\
\hline
\emph{Time} & \emph{Location} & \emph{Event} & \emph{Description}\\
\hline
8:00 am - 9:00 am & Dining Hall & Breakfast & Please eat food! This meal is \textbf{out of game}.  \\
\hline 
9:00 am - 10:00 am & Sleeping Areas & Costuming Time and Load-Out & Time between breakfast and game-on to put costumes on, and pack things out of the sleeping areas. We MUST be out of the sleeping areas by 11 am at the latest to avoid accruing charges for an additional night.\\
\hline
\multicolumn{4}{|c|}{\textbf{GAME ON 10:00 am}} \\
\hline
 10:00 am & Gyro Lodge & Game On & Game starts for the day. GMs \textbf{will} have game related announcements at this time, so please plan to attend.  \\
 \hline
  10:30 am - 11:00 am  & Jay Cabins & Third Storm Surge & Characters should probably take shelter in the bunkers. There is no traditional grouping and characters should shelter as they see fit. \\
\hline
  11:30 am & Gyro Lodge & Votes to Direct the Storm Due & Students must submit their votes for where to send the storm by this time. Uncast votes will be forfeit beyond this time. This allows GMs time to tally the votes before lunch.\\
\hline
  12:00 pm - 1:00 pm & Dining Hall & Lunch & Please eat food! This meal is \textbf{in game}, but the food is not (no poison mechanics will involve real life food).   \\
 \hline
  1:30 pm - 2:00 pm & Gyro Lodge & Ritual To Control the Storm & The actual ritual to control where the storm is sent will happen at this time. The storm will go where the students voted to send it.  \\
\hline
3:00 pm & Everywhere & Game Off & Game ends at 3 pm. This gives players 1 hour to react to the aftermath of where the storm is sent, and wrap up any last things.  \\
\hline
\multicolumn{4}{|c|}{\textbf{GAME ENDS 3:00 pm}} \\
\hline
3:00 pm - 3:30 pm & Band Shell & Derolling Exercise & This \textbf{optional} activity is a structured time to separate the player from the character and begin processing the experience of game. If you wish to opt out of the formal version, please take time to reflect individually, or help us clean up. Save the war-stories and “what happened?” questions for Debrief. \\
 \hline
  3:30 - 5:00 pm & Band Shell & Debrief and Goodbyes. & This \textbf{optional} activity is structured time for players to share what their character was actually attempting to accomplish, and how well or poorly that went. After the structured debrief time, players will be able to mingle, share more stories, and say goodbye.   Everyone will get a chance to share a little about who their character was and what they were trying to accomplish this weekend. This is a great opportunity to learn about the other stories being told over the weekend.\\
 \hline
  5:00 pm & Everywhere & Event End & Drive safely on your way home!.  \\
	\hline
\end{tabularx}


\end{document}
