\documentclass[green]{GL2020}
\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gWhatHappenedSixYearsAgo{}}

\cPresident{}and \cHeir{}, with help from \cWildCard{}, have devised a ritual to attempt to look 6 years into the past, using \iMirror{\MYname} (\iMirror{\MYnumber}), to see what happened leading up to the last Time of Deciding, when the students were killed. The ritual involves many steps that must happen at precise times, so coordination and collaboration among the participants will be crucial. The ritual requires gathering items and charging them at specific times of day, then casting your intent into the mirror. The mirror will influence the dreams of everyone present for the ritual to provide answers.

\textbf{Required (Needed for the final ritual, which must take place Saturday night before bed)}
\begin{itemize}
  \item \iMirror{} - The \pTech{} advisor, \cDiplomat{\full} should be bringing this relic to the school.
  \item \iMorningGlory{}
  \item \iLily{}
  \item \iMoonflower{}
  \item \iStoneFlower{} (\emph{Optional; Used to replace any of the other flowers if they cannot be gathered at the correct time, but may introduce unforeseen consequences.})
  \item 6 (or more) people for the ritual
\end{itemize}

Steps:
\begin{enumerate}
  \item One or more people involved in the ritual must acquire a \iMorningGlory{} flower and charge it with the energy of sunrise by standing with it at the ``\pGarden{}'' during the morning (any time before lunch), and speaking words of hope and potential to the flower. 
  \item One or more people involved in the ritual must acquire a \iLily{} flower and charge it with the energy of midday by standing with it in the ``\pTrainingField{}'' during the afternoon (any time between lunch and dinner) and shouting words of triumph and success to the flower.
  \item One or more people involved in the ritual must acquire a \iMoonflower{} and charge it with the energy of sunset by standing with it in the evening (any time after dinner)  in the ``\pGraveyard{}'' and whispering words of darkness and quiet to the flower.
  \item \textbf{Warning: ``\iMirror{}’’ must be attuned somewhere in order for this ritual to work. Performing this ritual will de-attune it!} Check if ``\iMirror{}’’ is attuned by opening up the attached envelope and checking if there is a piece of paper inside. If there is, the relic is attuned and can be used, else the relic must be re-attuned by a Cleric before it can be used.
  \item Cast the ritual by assembling \textbf{6 or more people} either in the ``\pStudentLoungeBunker{}'', or at the ``\sMemorialToFallenStudents{}'' out in ``\pGraveyard{}''. The closer to bedtime the better. One person should be nominated to lead the ritual (\emph{OOC note: Anyone may lead this ritual, but if they don't have this greensheet, someone who does have it will have to instruct them}). 
  \begin{itemize}
  \item  If the ritual is interrupted the participants must remove any outside person or influence from the ritual space, join together briefly in singing or humming to re-attune the space, and then continue. If the outside influence cannot be removed the ritual will be prevented from happening.
  \item If an item necessary for the ritual is removed, it must be retrieved. Once retrieved, the space should be re-attuned as described above, and then the ritual may continue.

  \end{itemize}
  \item Place \iMirror{} in the center of the area, with the three flowers (\iMorningGlory{}, \iLily{}, and \iMoonflower{}) spaced around it in a triangle. Everyone should form a circle around this.
  \begin{itemize}
  \item If one or more of the flowers could not be found and charged properly, a \iStoneFlower{} may be substituted for each missing component. The \iStoneFlower{}s do not need to be charged.
  \end{itemize}
  \item Going clockwise around the circle, each person should relate a memory they have that’s tied to a specific time of day: dawn, noon, or evening.
  \item Once everyone has gone, the leader should pick up \iMirror{} and walk slowly around the circle, holding it up for every participant to look into in turn.
  \item The leader then replaces \iMirror{} in the center and everyone closes their eyes. Soft singing or humming may help at this point. Once the leader feels that the mirror has been fully charged (this should take no more than a minute or two) they announce in a quiet voice that the ritual is completed.
  \item After successful completion of the ritual, each participant  will see the mirror in their dream, just as they looked into it during the ritual, but instead of their own face looking back they’ll see one or more scenes of the past.
  \item Discard the item cards for the flowers to the nearest stock. Give \iMirror{} to a GM to adjust the attunement of the relic (this ritual is expected to de-attune the relic). The GM will then return \iMirror{} to the character who gave it to them.
\end{enumerate}

If the ritual is successfully completed on \textbf{Saturday night}, then on \textbf{Sunday morning}, all of the participants of the ritual may go (individually or collectively) to GM HQ, and lift ``\sSignCOne{}'' to read ``\sSignCTwo{}'' underneath.

\end{document}

