\documentclass[green]{GL2020}

\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gPreGameAdvisor{}}

\section*{(25-30 min)}

Hello and welcome. Once again my name is X and my pronouns are Y. If you are here, it is because your character is an advisor. If you are not an advisor, you're in the wrong place!

Over the next hour we are going to:
\begin{enumerate}
	\item Introduce just our characters.
	\item Review game locations
	\item Create some social and cultural norms for our cohort, which can help us feel like a more coherent group.
	\item Reflect on the role of this cohort in the Time of Deciding, and the consequences of the decision before us.
	\item And Reflect on how magic influences these character’s lives.
\end{enumerate}

\subsection*{Character Introductions (5 min)}
We’re going to go around the circle and introduce our \textbf{character}. Please share your character’s name, pronouns, what nation they are from, and whether they are a student, teacher or an advisor. Use the 1st person. $<$GM models$>$

\subsection*{Introduce Game Space, and time for discussing mobility considerations. (2 min)}
Reminders of game spaces!
\textbf{``IC Outdoor Spaces"} Garden, Training Field, Graveyard. 
\textbf{``IC Indoor Spaces"} Temple, Maker's Space, Great Hall/Ritual Space, Student Lounge/Bunker 1, Teacher Lounge/Bunker 2, Advisor Lounge/Bunker 3, Old Wing of the College, and the Library.
\textbf{``OOC Spaces''} Player OOC space, GM HQ.

Remember that we have players stationed in X location(s). They are full characters in this story. Help us make sure that they as players have that experience this weekend. Seek them out, support their play, include them in yours, and if need be, come get a GM and we will bring parts of the world to them.

\subsection*{Social and Cultural norms (10 min)}
Now we’re going to work together to create some shared experiences as a cohort.

\textbf{Reflect Alone:} 
\begin{enumerate}
	\item How involved in national politics are you?
	\item What are your personal feelings about the war? How does this compare to the public stance of your nation?
\end{enumerate}

\textbf{Discuss Together:}
\begin{enumerate}
	\item How do advisors normally conduct meetings here at the Time of Deciding? How are things likely to be different with the defacto leader, Madrone, not in attendance?
	\item Are the students and teachers allowed, welcome, or expected/``required'' at the advisor meetings? Only some students or teachers?
\end{enumerate}

\subsection*{Role in the Time of Deciding (5 min)}
Now we’re going to think about our cohort in the Time of Deciding. Reflect to yourself about this. We won't discuss it now, but you may want to talk about it in character later.

\textbf{Is now the time for a new peace treaty? What must a treaty have in order for your character to support it?}

\subsection*{Impact of Magic (5 min)}
And one last thing to reflect on: The impact of Magic in these character’s lives. Collect in groups by nation (within the cohort). I’ll ask each group a question. You’ll have a few minutes to discuss among yourselves, and then share with the larger group.
\begin{enumerate}
	\item \pFarm{}
	\begin{enumerate}
		\item How does magic enable us to feed the population?
		\item How does healing magic allow us to improve quality of life? (e.g. medicine without magic is non-existent)
	\end{enumerate}
	\item \pTech{}
	\begin{enumerate}
		\item How is magic necessary for technology? (e.g. magic powers all technology; no concept of engines or batteries)
		\item How does magic support innovation?
	\end{enumerate}
	\item \pShip{}
	\begin{enumerate}
		\item How does magic empower us to face the sea serpents? (e.g. non-magical weapons won’t pierce the hide)
		\item How does magic improve our crafting/building/art?
	\end{enumerate}
\end{enumerate}

\subsection*{Send Off (5 min tops)}
Now that the workshops are complete, think back to any goals you may have set for your player experience of this game, and any expectations you had going in this afternoon. 
\begin{itemize}
	\item Did any of those change organically during the workshops? 
	\item Do you want to specifically and intentionally change any of them now? 
	\item What concrete steps can you take to help you get what you want out of this weekend?
\end{itemize}

Think about these things in the back of your mind over the next few hours. You have between now and 5:30 to unload the cars, get unpacked and start costuming if you want. Dinner is at 5:30. Once you finish eating, you’ll have the remaining time before game starts to get into costume. Game starts at 7:00 pm at X location. Please don’t be late; we won’t wait.


\end{document}
