\documentclass[green]{GL2020}

\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gPreGameTeacher{}}

\section*{(40 min)}

Hello and welcome. Once again my name is X and my pronouns are Y. If you are here, it is because your character is a teacher. If you are not a teacher, you're in the wrong place!

Over the next 40 minutes we are going to:
\begin{enumerate}
	\item Introduce ourselves and our characters.
	\item Create some social and cultural norms for our cohort, which can help us feel like a more coherent group.
	\item Reflect on the role of this cohort in the Time of Deciding, and the consequences of the decision before us.
	\item And Reflect on how magic influences these character’s lives.
\end{enumerate}

\subsection*{Character Introductions (5 min)}
We’re going to go around the circle and introduce \textbf{players}. Please share your name, pronouns, and what state you live in normally. Use the 1st person for this. $<$GM models$>$

Now we are going to go around the circle and introduce our \textbf{character}. Please share your character’s name, pronouns, what nation they are from, what they teach and how long they have been teaching at the school.Use the 1st person. $<$GM models$>$

\subsection*{Social and Cultural norms (10 min)}
Now we’re going to work together to create some shared experiences as a cohort

Please remember to allow others to speak and share the spotlight.  Please raise your hand if you want to share.

\textbf{Reflect Alone:}
\begin{enumerate}
	\item Which student is your favorite? Why?
	\item How strongly do you hold to the purported neutrality of the teachers toward the students and international politics?
\end{enumerate}

\textbf{Discuss Together:}
\begin{enumerate}
	\item How are students assessed for learning? Do you give homework? Are there a lot of tests, or essays, or practical exams? Etc.
	\item What do you do to relax and socialize in your off time?
\end{enumerate}

\subsection*{Role in the Time of Deciding (5 min)}
Now we’re going to think about our cohort in the Time of Deciding. Reflect to yourself about this. We won't discuss it now, but you may want to talk about it in character later.

\textbf{How are you going to guide and support the students? How are you going to guide and support the advisors?}

\subsection*{Impact of Magic (10 min)}
And one last thing to reflect on: The impact of Magic in these character’s lives. Collect in groups by nation (within the cohort). I’ll ask each group a question. You’ll have a few minutes to discuss among yourselves, and then share with the larger group.
\begin{enumerate}
	\item \pFarm{}
	\begin{enumerate}
		\item How does magic enable us to feed the population?
		\item How does healing magic allow us to improve quality of life? (e.g. medicine without magic is non-existent)
	\end{enumerate}
	\item \pTech{}
	\begin{enumerate}
		\item How is magic necessary for technology? (e.g. magic powers all technology; no concept of engines or batteries)
		\item How does magic support innovation?
	\end{enumerate}
	\item \pShip{}
	\begin{enumerate}
		\item How does magic empower us to face the sea serpents? (e.g. non-magical weapons won’t pierce the hide)
		\item How does magic improve our crafting/building/art?
	\end{enumerate}
\end{enumerate}


Alright, last up is a workshop by nation. Check your manila envelope for which GM you are going to be with next.

\end{document}