\documentclass[green]{GL2020}

\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gMidGame{}}

{\Large \textbf{This meal is Off game.}} Please use this time to take a break! If you want some ideas for what to do during this time, see the list below. (Optional reflection activity at the bottom!)

\subsection*{OOC Socializing}
This is a time for OOC socializing. You are all wonderful people and this is a chance to hang out and get to know your fellow players a little better, or catch up with old friends. Just be careful about spoilers about this game. Please do not take any in game actions, or make plans for in game actions during this time. Pretend the game world has had the ``pause'' button pressed.

\subsection*{GM Office Hours}
GMs will specifically be available at this time for players to come ask questions, get clarifications/guidance, etc. Be advised that the GMs will also be eating during this time.

\subsection*{Player to Player Calibration}
As with Friday dinner, this time can be used for player calibration or recalibration if necessary. The same guidance applies regarding checking in with a player about whether they want to calibrate. Don’t forget to ask: ``are you open to calibrating with me?'' to open the conversation.

%\clearpage
\subsection*{Reflection and Expectation Management (estimated time: <15 min)}
This is a personal reflection activity that is a great opportunity to reflect on your experience in the game so far, see whether it is lining up with what you hoped to get out of the experience of this game, and construct a plan for how to make changes if necessary to how you are approaching the game to better improve your experience.

\begin{enumerate}
	\item Get comfortable, close your eyes if you want, and turn your attention to your breathing for a few moments, or use another small meditative exercise of your choice to bring you firmly into the present moment. See if you can imagine taking your character off like a jacket and hanging it in a closet. Some people find taking off a piece of a costume or your badge can help with this visualization. Right now we want to be as much in our player minds as possible. 
	\item Think about your \textbf{player} experience in this game so far. E.g.: ``Am I having fun? Do I feel engaged and involved? Am I getting enough play time with people I want to play with?”''
	\item Think back to any player goals/expectations you may have set at the beginning of game. Compare them to the experience you are \textbf{actually} having. What is going well? Are there gaps? Is your experience different than expected but still enjoyable? 
	\item If there are gaps between your current experience and what you wanted, can you think of ways to help close those gaps? If you can’t think of anything, come chat with the GMs and we’ll try to help. Are there things you want to do \textbf{more} of? Something that brings you and the players around you joy? Are there aspects of your character or the setting that you haven’t had a chance to give much attention to yet?
	\item Do you want to update any of your personal expectations for this game?
	\item As you end this activity, close your eyes again and turn your attention to your breathing. Reach out for your character hanging in the closet. Touch it. Know that it is there, ready for you to put back on after dinner or whenever you are ready.
\end{enumerate}

\end{document}