\documentclass[green]{GL2020}

\usepackage{enumitem}
\setlist{nosep}
\parindent=0pt
\begin{document}
\name{\gPreGameStudent{}}

\section*{(25-30 min)}

Hello and welcome. Once again my name is X and my pronouns are Y. If you are here, it is because your character is a student. If you are not a student, you're in the wrong place!

Over the next hour we are going to:
\begin{enumerate}
	\item Introduce just our characters.
	\item Create some social and cultural norms for our cohort, which can help us feel like a more coherent group.
	\item Reflect on the role of this cohort in the Time of Deciding, and the consequences of the decision before us.
	\item And Reflect on how magic influences these character’s lives.
\end{enumerate}

\subsection*{Character Introductions (5 min)}
We’re going to go around the circle and introduce our \textbf{character}. Please share your character’s name, pronouns, what nation they are from, and whether they are a student, teacher or an advisor. Use the 1st person. $<$GM models$>$

\subsection*{Social and Cultural norms (10 min)}
Now we’re going to work together to create some shared experiences as a cohort.

\textbf{Reflect Alone:} What is your home life like, how has your relationship with your family changed in your time at the College?

\textbf{Discuss Together:}
\begin{enumerate}
	\item How competitive vs. cooperative is the student body at large? What about this smaller group that was selected for the Time of Deciding?
	\item How much time do students spend with students from other nations? Is there a lot of mixing? Or are there strong national divides?
	\item What extracurriculars are the most popular?
\end{enumerate}

\subsection*{Role in the Time of Deciding (5 min)}
Now we’re going to think about our cohort in the Time of Deciding. Reflect to yourself about this. We won't discuss it now, but you may want to talk about it in character later.

\textbf{Where do you think the Storm should be sent this year? What could change your mind?}

\subsection*{Impact of Magic (5 min)}
And one last thing to reflect on: The impact of Magic in these character’s lives. Collect in groups by nation (within the cohort). I’ll ask each group a question. You’ll have a few minutes to discuss among yourselves, and then share with the larger group.
\begin{enumerate}
	\item \pFarm{}
	\begin{enumerate}
		\item How does magic enable us to feed the population?
		\item How does healing magic allow us to improve quality of life? (e.g. medicine without magic is non-existent)
	\end{enumerate}
	\item \pTech{}
	\begin{enumerate}
		\item How is magic necessary for technology? (e.g. magic powers all technology; no concept of engines or batteries)
		\item How does magic support innovation?
	\end{enumerate}
	\item \pShip{}
	\begin{enumerate}
		\item How does magic empower us to face the sea serpents? (e.g. non-magical weapons won’t pierce the hide)
		\item How does magic improve our crafting/building/art?
	\end{enumerate}
\end{enumerate}

\subsection*{Send Off (5 min tops)}
Now that the workshops are complete, think back to any goals you may have set for your player experience of this game, and any expectations you had going in this afternoon. 
\begin{itemize}
	\item Did any of those change organically during the workshops? 
	\item Do you want to specifically and intentionally change any of them now? 
	\item What concrete steps can you take to help you get what you want out of this weekend?
\end{itemize}

Think about these things in the back of your mind over the next few hours. You have between now and 5:30 to unload the cars, get unpacked and start costuming if you want. Dinner is at 5:30. Once you finish eating, you’ll have the remaining time before game starts to get into costume. Game starts at 7:00 pm at X location. Please don’t be late; we won’t wait.

\end{document}
